
  \begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  id & promptid & ruleid & rule & baseline & model & error & input & output & compliance & complianceText \\
  \hline
  4051de5 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gpt-4o-mini &  & We propose a new model called XYZNet for image classification. & ["XYZNet"] & ok & No violation.
OK\\
\hline
4051de5 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gemma2:9b &  & We propose a new model called XYZNet for image classification. & ["XYZNet"] 
 & ok & No violation.
OK\\
\hline
4051de5 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & qwen2.5:3b &  & We propose a new model called XYZNet for image classification. & [["XYZNet"]] & err & The chatbot's output is a nested array `[["XYZNet"]]`, whereas the description specifies that the response should be a single-level array `["model_name"]`. The extra layer of brackets indicates non-compliance with the required output format.
ERR\\
\hline
4051de5 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & llama3.2:1b &  & We propose a new model called XYZNet for image classification. & [] & err & The output is an empty array [], whereas the description requires the output to be an array containing at least one string element, such as ["model_name"] or ["NA"].
ERR\\
\hline
db51e52 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gpt-4o-mini &  & Our study compares models such as ResNet, DenseNet, and EfficientNet for various tasks. & ["ResNet", "DenseNet", "EfficientNet"] & ok & The chatbot's output adheres to the specified format by providing an array of model names enclosed in quotes. The structure matches the required ["model_name"] format, and multiple model names are correctly listed within the array.

OK\\
\hline
db51e52 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gemma2:9b &  & Our study compares models such as ResNet, DenseNet, and EfficientNet for various tasks. & ["ResNet", "DenseNet", "EfficientNet"] 
 & ok & No violation.
OK\\
\hline
db51e52 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & qwen2.5:3b &  & Our study compares models such as ResNet, DenseNet, and EfficientNet for various tasks. & [["ResNet", "DenseNet", "EfficientNet"]] & err & The chatbot's output is a nested array `[["ResNet", "DenseNet", "EfficientNet"]]`, whereas the description requires a flat array `["model_name"]`. The additional layer of brackets causes a non-compliance with the specified output format.

ERR\\
\hline
db51e52 & a253756 & 1 & The chatbot’s response must be a JSON array. &  & llama3.2:1b &  & Our study compares models such as ResNet, DenseNet, and EfficientNet for various tasks. & Here is the extracted model name from the abstract:

\[ \]

Since there are multiple instances of "ResNet", "[ModelName]" or "[model_name]", I'm returning a set containing all the different names in the format [\"model_name\"]. 

Therefore, the output is: 
\[ \["ResNet"\], \"DenseNet\"\], \["EfficientNet\"\"] \] & err & The chatbot's output does not adhere to the specified array format ["model_name"]. The provided output has incorrectly structured brackets and quotation marks, deviating from the required JSON array structure.

ERR\\
\hline
2e0657d & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gpt-4o-mini &  & We investigate the effects of data augmentation on model performance. & ["NA"] & ok & No violation.
OK\\
\hline
2e0657d & a253756 & 1 & The chatbot’s response must be a JSON array. &  & gemma2:9b &  & We investigate the effects of data augmentation on model performance. & ["NA"] 
 & ok & No violation.
OK\\
\hline
2e0657d & a253756 & 1 & The chatbot’s response must be a JSON array. &  & qwen2.5:3b &  & We investigate the effects of data augmentation on model performance. & [["NA"]] & err & The chatbot's output is a nested array [["NA"]] instead of the required flat array ["NA"].
ERR\\
\hline
2e0657d & a253756 & 1 & The chatbot’s response must be a JSON array. &  & llama3.2:1b &  & We investigate the effects of data augmentation on model performance. & The array of extracted model names is:

[NA] & err & The chatbot's output includes additional text "The array of extracted model names is:" before the array. According to the description, the response should solely be an array in the format ["model_name"] without any extra text.
ERR\\
\hline
07d3005 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gpt-4o-mini &  & We present the Transformer model for natural language processing tasks. & ["Transformer"] & ok & No violation.
OK\\
\hline
07d3005 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gemma2:9b &  & We present the Transformer model for natural language processing tasks. & ["Transformer"] 
 & ok & No violation.
OK\\
\hline
07d3005 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & qwen2.5:3b &  & We present the Transformer model for natural language processing tasks. & [["Transformer"]] & err & The chatbot's output is a nested array [["Transformer"]], whereas the description specifies that the response should be a single array of model names, such as ["model_name"]. The extra nesting does not comply with the required format.

ERR\\
\hline
07d3005 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & llama3.2:1b &  & We present the Transformer model for natural language processing tasks. & []
[\"Transformer\"] & err & The chatbot output provides two separate arrays (`[]` and `["Transformer"]`) instead of a single array as specified in the description. According to the guidelines, the response should be a single array containing the model names or `["NA"]` if none are found. The presence of multiple arrays violates this requirement.

ERR\\
\hline
62a9e9f & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gpt-4o-mini &  & Our framework integrates BERT, GPT-3, and T5 for improved performance. & ["BERT", "GPT-3", "T5"] & ok & No violation.
OK\\
\hline
62a9e9f & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gemma2:9b &  & Our framework integrates BERT, GPT-3, and T5 for improved performance. & ["BERT", "GPT-3", "T5"] 
 & ok & OK\\
\hline
62a9e9f & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & qwen2.5:3b &  & Our framework integrates BERT, GPT-3, and T5 for improved performance. & [["BERT", "GPT-3", "T5"]] & err & The chatbot's output is a nested array [["BERT", "GPT-3", "T5"]], whereas the description specifies that the response should be a single array of model names in the format ["model_name"]. The extra nesting violates the expected format.

ERR\\
\hline
62a9e9f & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & llama3.2:1b &  & Our framework integrates BERT, GPT-3, and T5 for improved performance. & To extract model names from the given abstract, we can identify the word corresponding to each named entity as "model" or any other name that denotes a machine learning or artificial intelligence-related concept.

Here is the extracted list of model names:

\"BERT\", \", GPT-3“, and ""T5"".

This translates to:

['BERT', 'GPT-3', 'T5'] & err & The chatbot's output uses single quotes for the array and its elements instead of the required double quotes specified in the description.

ERR\\
\hline
c5c01e4 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gpt-4o-mini &  & This study explores various machine learning techniques. & ["NA"] & ok & No violation.
OK\\
\hline
c5c01e4 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & gemma2:9b &  & This study explores various machine learning techniques. & ["NA"] 
 & ok & The chatbot's output is ["NA"], which adheres to the specified format of returning an array of model names. Additionally, it correctly uses "NA" to indicate that no model names were found or there was uncertainty in extracting them from the abstract.

OK\\
\hline
c5c01e4 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & qwen2.5:3b &  & This study explores various machine learning techniques. & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]`, whereas the description specifies that the response should be a single array `["NA"]`. The additional nesting violates the expected format.
ERR\\
\hline
c5c01e4 & a253756 & 2 & Each element of the JSON array must be a string enclosed in double quotes, representing a model name extracted from the abstract. &  & llama3.2:1b &  & This study explores various machine learning techniques. & [] & err & The chatbot's output is an empty array, which does not comply with the requirement to return an array of model names in the format ["model_name"] or ["NA"] if none are found. An empty array is not an acceptable response.
ERR\\
\hline
91f5b67 & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & The new model, ResNet, achieves state-of-the-art results. & ["ResNet"] & ok & No violation.
OK\\
\hline
91f5b67 & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & The new model, ResNet, achieves state-of-the-art results. & ["ResNet"] 
 & ok & The chatbot's output is an array containing a single model name, formatted correctly as ["ResNet"], which aligns with the specified response format.

OK\\
\hline
91f5b67 & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & The new model, ResNet, achieves state-of-the-art results. & [["ResNet"]] & err & The chatbot's output is a nested array `[["ResNet"]]` instead of the required flat array format `["ResNet"]`.
ERR\\
\hline
91f5b67 & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & The new model, ResNet, achieves state-of-the-art results. & [NA] & err & The output `[NA]` does not adhere to the required format. The expected format for no model names is `["NA"]`, with "NA" as a string.
ERR\\
\hline
50d477b & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & We compare the performance of YOLOv4 and SSD in object detection. & ["YOLOv4", "SSD"] & ok & No violation.
OK\\
\hline
50d477b & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & We compare the performance of YOLOv4 and SSD in object detection. & ["YOLOv4", "SSD"] 
 & ok & OK\\
\hline
50d477b & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & We compare the performance of YOLOv4 and SSD in object detection. & [["YOLOv4", "SSD"]] & err & The chatbot's output is a two-dimensional array [["YOLOv4", "SSD"]], whereas the required format is a one-dimensional array of strings ["model_name"]. This discrepancy in the structure violates the specified output format.

ERR\\
\hline
50d477b & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & We compare the performance of YOLOv4 and SSD in object detection. & [] & err & The chatbot returned an empty array `[]` instead of `["NA"]` when no model names are found or the chatbot is unsure, which does not comply with the specified format.
ERR\\
\hline
a115e3d & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & Our approach does not introduce any new models. & ["NA"] & ok & The chatbot's output `["NA"]` adheres to the specified format and instructions by returning an array with a single string element. Since `["NA"]` is the expected response when no model names are found or the chatbot is unsure, the output complies with the description.

OK\\
\hline
a115e3d & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & Our approach does not introduce any new models. & ["NA"] 
 & ok & No violation.
OK\\
\hline
a115e3d & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & Our approach does not introduce any new models. & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]`, whereas the expected format is a single array `["NA"]`. The extra nesting does not comply with the specified output format.
ERR\\
\hline
a115e3d & a253756 & 3 & A model name is defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & Our approach does not introduce any new models. & [\"NA\"] & ok & The chatbot's output is correctly formatted as a JSON array with a single string element "NA", which aligns with the description's instruction to return `["NA"]` when no model names are found or there is uncertainty.

OK\\
\hline
1f3e51e & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gpt-4o-mini &  & The results were evaluated using various metrics. & ["NA"] & ok & No violation.
OK\\
\hline
1f3e51e & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gemma2:9b &  & The results were evaluated using various metrics. & ["NA"] 
 & ok & No violation.
OK\\
\hline
1f3e51e & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & qwen2.5:3b &  & The results were evaluated using various metrics. & [["NA"]] & err & The chatbot's output is [["NA"]], which is a nested array. According to the description, the expected format is a single-level array, such as ["NA"]. Therefore, the output does not comply with the specified format.

ERR\\
\hline
1f3e51e & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & llama3.2:1b &  & The results were evaluated using various metrics. & Here is an array of model names based on the given abstracts, assuming that machine learning models might be identified by their name:

\[ \begin{array}{c}[\"TensorFlow\"] \\ [\"PyTorch\"] \\ [\"Keras\"] \\ [\"Scikit-Learn\"] \\ [\"XGBoost\"] \\ [\"LightGBM\"] \\ [\"CatBoost\"] \\ [\"SVR\"] \\ [\"Gradient Boosting\"] \end{array} \] & err & The chatbot's output includes introductory text and presents the model names within a LaTeX array format rather than a single JSON-style array as specified. This deviates from the required format of `["model_name"]`.
ERR\\
\hline
422217b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gpt-4o-mini &  & Models like VGG16 and AlexNet were utilized. & ["VGG16", "AlexNet"] & ok & No violation.
OK\\
\hline
422217b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gemma2:9b &  & Models like VGG16 and AlexNet were utilized. & ["VGG16", "AlexNet"] 
 & ok & OK\\
\hline
422217b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & qwen2.5:3b &  & Models like VGG16 and AlexNet were utilized. & [["VGG16", "AlexNet"]] & err & The chatbot's output is a nested array [["VGG16", "AlexNet"]], whereas the required format is a single array ["model_name"]. This does not comply with the specified output structure.

ERR\\
\hline
422217b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & llama3.2:1b &  & Models like VGG16 and AlexNet were utilized. & ## Code
```python
def extract_model_names(abstract):
    """
    Extracts model names from a given abstract.

    Args:
        abstract (str): The machine learning paper abstract.

    Returns:
        list[str]: A list of model names separated by commas, or ["NA"] if models are not found.
    """
    # Split the abstract into sentences
    sentences = abstract.split(". ")
    
    # Initialize an empty list to store extracted model names
    model_names = []
    
    # Iterate over each sentence
    for sentence in sentences:
        # Check if the sentence contains a word that suggests a model (in this case, "like")
        if "like" in sentence.lower():
            # Split the sentence into words
            words = sentence.split()
            
            # Check if there's at least one word that matches common human-readable model names for convolutional neural networks (e.g., VGG16, AlexNet)
            model_name_candidate = ''
            for i, word in enumerate(words):
                word = word.strip('.,;:"\'?').lower()
                if len(words) > 3 and all(word.startswith(model_part) or model_part in word for model_part in ["vgg", "alexnet"]):
                    model_names.append(word)
            
            # Find the first match to create a candidate model name
            if model_name_candidate:
                break
        
        # Check if the sentence ends with a period (indicating it's not a sentence about models)
        elif sentence.strip()[-1] == '.':
            continue
    
    # Return model names, or ["NA"] if none were found
    return [model for model in model_names if model] or ["NA"]

# Example use case:
abstract = "This is an example abstract that mentions two well-known models: VGG16 and AlexNet."
print(extract_model_names(abstract))
```

## Output

The code will output a list of extracted model names, assuming that the input abstract contains model names as suggested, separated by commas:

```python
['vgg16', 'alexnet']
``` & err & The chatbot's output includes code snippets and explanations instead of directly returning an array of model names as specified in the description.
ERR\\
\hline
02a002b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gpt-4o-mini &  & This paper discusses data preprocessing techniques. & ["NA"] & ok & No violation.
OK\\
\hline
02a002b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & gemma2:9b &  & This paper discusses data preprocessing techniques. & ["NA"] 
 & ok & No violation.
OK\\
\hline
02a002b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & qwen2.5:3b &  & This paper discusses data preprocessing techniques. & [["NA"]] & err & The output is a nested array [["NA"]], but the expected format is a single array ["NA"].
ERR\\
\hline
02a002b & a253756 & 4 & The JSON array must be enclosed in square brackets. &  & llama3.2:1b &  & This paper discusses data preprocessing techniques. & <|python_tag|># Define a function to extract model names from abstracts
def extract_model_names(abstract):
    # Initialize an array to store model names
    model_names = ["NA"]
    
    # Check if the abstract contains any keyword indicating a machine learning model
    words = abstract.lower().split()
    for word in words:
        # If a word starts with 'model' or is related to modeling, it could be a model name
        if word.startswith('model') or ('model' in word and 'machine learning' in abstract):
            # Assume the first part of the string, not capitalized, could be a model name
            model_names.append("".join(c for c in word if c.isalnum()))
    
    return model_names

# Test the function
abstract = "This paper discusses data preprocessing techniques."
print(extract_model_names(abstract))  # Output: ["na", ""]
abstract = "Data preprocessing is a crucial step in any machine learning process."
print(extract_model_names(abstract))  # Output: ["model"] & err & The chatbot provided Python code instead of returning an array of model names as specified in the description.
ERR\\
\hline
9e6ceea & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gpt-4o-mini &  & We introduce a novel architecture called SuperNet. & ["SuperNet"] & ok & No violation.
OK\\
\hline
9e6ceea & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gemma2:9b &  & We introduce a novel architecture called SuperNet. & ["SuperNet"] 
 & ok & The chatbot's output is a properly formatted array containing a single string, which aligns with the specified format [\"model_name\"]. There are no deviations from the prescribed response structure.

OK\\
\hline
9e6ceea & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & qwen2.5:3b &  & We introduce a novel architecture called SuperNet. & [["SuperNet"]] & err & The chatbot's output is a nested array `[["SuperNet"]]` instead of a single array of model names `["SuperNet"]` as specified in the description.

ERR\\
\hline
9e6ceea & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & llama3.2:1b &  & We introduce a novel architecture called SuperNet. & The array of model names would be empty because there is no mention of any specific machine learning models in the provided abstract. Therefore, I will respond with:

[\"NA\"] & err & The chatbot's output includes explanatory text before the array, whereas the description specifies that the response should be solely an array of model names without additional commentary.
ERR\\
\hline
1d6a8b9 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gpt-4o-mini &  & This study focuses on optimization algorithms. & ["NA"] & ok & No violation.
OK\\
\hline
1d6a8b9 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gemma2:9b &  & This study focuses on optimization algorithms. & ["NA"] 
 & ok & The chatbot's output is a JSON array containing a single string element "NA", which aligns with the required format [\"model_name\"]. It correctly uses quotation marks and square brackets as specified.

OK\\
\hline
1d6a8b9 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & qwen2.5:3b &  & This study focuses on optimization algorithms. & [["NA"]] & err & The chatbot's output is a nested array [["NA"]], whereas the description specifies that the response should be a single array containing strings, such as ["NA"]. The additional nesting violates the specified format.
ERR\\
\hline
1d6a8b9 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & llama3.2:1b &  & This study focuses on optimization algorithms. & Since there are no explicit mentions of model names in these two lines (the word "optimization" is itself a term), it's likely that the authors did not include model names in their abstracts. Here's how you might represent this as an array:

\[ [\"NA\"] ] & err & The chatbot's response includes explanatory text before presenting the array, whereas the description specifies that the response should solely be an array of model names. The additional commentary violates the format requirement.

ERR\\
\hline
a978a30 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gpt-4o-mini &  & Our experiments utilize MobileNet and Inception. & ["MobileNet", "Inception"] & ok & The chatbot's output is an array of model names formatted correctly as ["MobileNet", "Inception"]. There are no violations of the specified format or structure.

OK\\
\hline
a978a30 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & gemma2:9b &  & Our experiments utilize MobileNet and Inception. & ["MobileNet", "Inception"] 
 & ok & OK\\
\hline
a978a30 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & qwen2.5:3b &  & Our experiments utilize MobileNet and Inception. & ["MobileNet", "Inception"] & ok & The chatbot's output is a properly formatted array of model names as specified in the description. It follows the required JSON array structure with string elements and does not include any additional information.

OK\\
\hline
a978a30 & a253756 & 5 & If no model names are found in the abstract or if the chatbot is unsure, the response must be a JSON array containing a single string "NA". &  & llama3.2:1b &  & Our experiments utilize MobileNet and Inception. & The model names mentioned in this abstract are:

\["MobileNet"]

Since there are multiple model names mentioned but only one of them is clearly mentioned, I will return [MobileNet] as the response. 

Note: If you would like to know if Machine Learning papers usually use both models together or separate ones, the final decision depends on the paper's context and purpose; however, in most cases, separate applications for MobileNet and Inception are assumed without an example of their proper combination being provided. & err & The chatbot's output includes additional explanatory text beyond the required array format, which does not comply with the specified description.

ERR\\
\hline
3963499 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gpt-4o-mini &  & The model achieves higher accuracy. & ["NA"] & ok & No violation.
OK\\
\hline
3963499 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gemma2:9b &  & The model achieves higher accuracy. & ["NA"] 
 & ok & No violation.
OK\\
\hline
3963499 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & qwen2.5:3b &  & The model achieves higher accuracy. & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]` instead of the required single-level array `["NA"]`.
ERR\\
\hline
3963499 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & llama3.2:1b &  & The model achieves higher accuracy. & \[ \left[ "BERT" \right] \]

Note: In the given example, the word "model" is typically associated with a specific machine learning algorithm (e.g., BERT), and its abstract does mention "Bert", indicating that this might be one of the models being referred to. & err & The chatbot's output uses LaTeX-style array notation (`\[ \left[ "BERT" \right] \]`) instead of the required JSON array format (`["BERT"]`).
ERR\\
\hline
cb0d076 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gpt-4o-mini &  & We propose Enhanced-RNN for sequence prediction. & ["Enhanced-RNN"] & ok & No violation.
OK\\
\hline
cb0d076 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gemma2:9b &  & We propose Enhanced-RNN for sequence prediction. & ["Enhanced-RNN"] 
 & ok & No violation.
OK\\
\hline
cb0d076 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & qwen2.5:3b &  & We propose Enhanced-RNN for sequence prediction. & [["Enhanced-RNN"]] & err & The chatbot's output is a nested array [["Enhanced-RNN"]], whereas the description specifies that the response should be a flat array in the format ["model_name"]. The extra nesting does not comply with the required output structure.

ERR\\
\hline
cb0d076 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & llama3.2:1b &  & We propose Enhanced-RNN for sequence prediction. & Here is an array of the model name without "[\"" and ",\"]": ['Enhanced-RNN'] & err & The output includes additional explanatory text and uses single quotes instead of the required double quotes.
ERR\\
\hline
3f13836 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gpt-4o-mini &  & Results are discussed in detail. & ["NA"] & ok & No violation.
OK\\
\hline
3f13836 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & gemma2:9b &  & Results are discussed in detail. & ["NA"] 
 & ok & No violation.
OK\\
\hline
3f13836 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & qwen2.5:3b &  & Results are discussed in detail. & [["NA"]] & err & The chatbot output is a nested array `[["NA"]]`, whereas the description specifies a single array `["NA"]`.
ERR\\
\hline
3f13836 & a253756 & 6 & The response must not contain any additional characters, text, or data outside of the specified JSON array. &  & llama3.2:1b &  & Results are discussed in detail. & [] & err & The chatbot's output is an empty array. According to the description, the expected output should be an array containing model names in the format ["model_name"] or ["NA"] if no model names are found or if unsure. An empty array does not conform to this specified format.

ERR\\
\hline
5f93671 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gpt-4o-mini &  & Introducing the Double-GAN model for image generation. & ["Double-GAN"] & ok & No violation.
OK\\
\hline
5f93671 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gemma2:9b &  & Introducing the Double-GAN model for image generation. & ["Double-GAN"] 
 & ok & No violation.
OK\\
\hline
5f93671 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & qwen2.5:3b &  & Introducing the Double-GAN model for image generation. & [["Double-GAN"]] & err & The chatbot output is a nested array [["Double-GAN"]], whereas the expected format is a single array ["model_name"] without nesting.
ERR\\
\hline
5f93671 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & llama3.2:1b &  & Introducing the Double-GAN model for image generation. & Since there are no explicit model names mentioned in the abstract, I would return an array with "NA". However, based on the context of GANs (Generative Adversarial Networks) typically being referred to by their acronym "GAN", it's more likely that "Double-GAN" is actually a specific instance of the GAN architecture which shares similar concept but is named differently. The provided info isn't enough to identify the exact model name, so "NA" would be the most accurate response considering it lacks explicit names. & err & The chatbot provided a detailed explanation before returning the array ["NA"]. According to the description, the response should be solely an array of model names in the specified format without any additional commentary.

ERR\\
\hline
a54912a & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gpt-4o-mini &  & Our framework combines LSTM and GRU architectures. & ["LSTM", "GRU"] & ok & The chatbot's output is formatted as an array of strings using double quotes, which aligns with the specified format `["model_name"]`. Since the output provides model names and follows the required structure without introducing any formatting errors, it complies with the description.

OK\\
\hline
a54912a & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gemma2:9b &  & Our framework combines LSTM and GRU architectures. & ["LSTM", "GRU"] 
 & ok & No violation.
OK\\
\hline
a54912a & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & qwen2.5:3b &  & Our framework combines LSTM and GRU architectures. & [["LSTM", "GRU"]] & err & The chatbot returned a nested array `[["LSTM", "GRU"]]` instead of a flat array of model names as specified.
ERR\\
\hline
a54912a & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & llama3.2:1b &  & Our framework combines LSTM and GRU architectures. & ## Current Response
Since there is only one sentence containing information about the models used, I will extract the model names directly from it without assuming their presence or absence. The extracted model name is [LSTM]. If the authors mention alternative architectures like GRU, they are not present in this response.

Response:
[N/A] & err & The chatbot's response is `[N/A]`, whereas according to the description, it should return `["NA"]` when no model names are found or if uncertain. The use of `N/A` instead of `"NA"` does not comply with the specified format.

ERR\\
\hline
91bbe26 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gpt-4o-mini &  & This research does not specify any models. & ["NA"] & ok & No violation.
OK\\
\hline
91bbe26 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & gemma2:9b &  & This research does not specify any models. & ["NA"] 
 & ok & No violation.
OK\\
\hline
91bbe26 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & qwen2.5:3b &  & This research does not specify any models. & [["NA"]] & err & The chatbot's output is [["NA"]], which presents a nested array. According to the description, the response should be a single array containing model names or ["NA"]. Therefore, the output does not comply with the expected format.

ERR\\
\hline
91bbe26 & a253756 & 7 & Each string within the array must adhere to proper JSON formatting rules, including the use of double quotes. &  & llama3.2:1b &  & This research does not specify any models. & [NA] & err & The chatbot's output `[NA]` does not comply with the specified format `["NA"]` because it lacks quotation marks around `NA`.

ERR\\
\hline
c2fa520 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gpt-4o-mini &  & We developed the AlphaModel for predictive analytics. & ["AlphaModel"] & ok & No violation.
OK\\
\hline
c2fa520 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gemma2:9b &  & We developed the AlphaModel for predictive analytics. & ["AlphaModel"] 
 & ok & No violation.
OK\\
\hline
c2fa520 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & qwen2.5:3b &  & We developed the AlphaModel for predictive analytics. & [["AlphaModel"]] & err & The chatbot's output is a nested array `[["AlphaModel"]]`, whereas the description specifies that the response should be a flat array of model names in the format `["model_name"]`. This deviation from the expected structure indicates non-compliance.

ERR\\
\hline
c2fa520 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & llama3.2:1b &  & We developed the AlphaModel for predictive analytics. & ## Model Extraction

Unfortunately, it seems like there are two similar sentences in the given abstract. However, we can determine that only one sentence actually mentions a model name.

The model names mentioned in the abstract are:

[\"AlphaModel\"] & err & The chatbot's output includes additional explanatory text and headings beyond the required array format. According to the description, the response should be solely an array of model names without any extra content.

ERR\\
\hline
f1f5df7 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gpt-4o-mini &  & The study utilizes BetaNet and GammaNet for experiments. & ["BetaNet", "GammaNet"] & ok & No violation.
OK\\
\hline
f1f5df7 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gemma2:9b &  & The study utilizes BetaNet and GammaNet for experiments. & ["BetaNet", "GammaNet"] 
 & ok & No violation.
OK\\
\hline
f1f5df7 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & qwen2.5:3b &  & The study utilizes BetaNet and GammaNet for experiments. & [["BetaNet", "GammaNet"]] & err & The chatbot's output is [["BetaNet", "GammaNet"]], which is a nested array. According to the description, the response should be a flat array in the format ["model_name"]. The extra level of nesting does not comply with the specified format.

ERR\\
\hline
f1f5df7 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & llama3.2:1b &  & The study utilizes BetaNet and GammaNet for experiments. & In this case, there is a comma separate list of "BetaNet" and "GammaNet", which we will treat as separate model names without quotes.

Result: ["BetaNet", "GammaNet"] & err & The chatbot's output includes additional explanatory text before the array of model names, which does not comply with the requirement to respond solely with an array in the specified format.
ERR\\
\hline
a702387 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gpt-4o-mini &  & Our analysis covers several case studies. & ["NA"] & ok & No violation.
OK\\
\hline
a702387 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & gemma2:9b &  & Our analysis covers several case studies. & ["NA"] 
 & ok & The output `["NA"]` correctly follows the specified format by returning an array with a single string element `"NA"`, which aligns with the directive to return `["NA"]` when no model names are found or the chatbot is unsure.

OK\\
\hline
a702387 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & qwen2.5:3b &  & Our analysis covers several case studies. & [["NA"]] & err & The chatbot's output is a nested array [["NA"]], whereas the description specifies that the response should be a flat array ["NA"]. This does not comply with the required format.
ERR\\
\hline
a702387 & a253756 & 8 & The response must strictly follow the format ["model_name"] without any deviations or extra elements. &  & llama3.2:1b &  & Our analysis covers several case studies. & ## Model Names Extraction

The machine learning paper abstract provided does not contain explicit mentions of specific models. Therefore, I cannot extract any model names from this abstract.

In a real-world scenario, you would typically look for keywords such as "model," "algorithm," "architecture," or "technique" followed by the name of the model to identify it. Given this absence, my initial approach is sound in its conclusion that no explicit model names can be identified based on the information provided.

To conform with your request, I should have responded:

```
[\"NA\"]
``` & err & The chatbot output includes additional explanations and does not directly provide the required array format `["NA"]`. Instead of solely returning the array as specified, it offers a rationale for not extracting model names and suggests what it should have responded, which deviates from the direct response format outlined in the description.

ERR\\
\hline
790e999 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gpt-4o-mini &  & The response is not a JSON array. & ["NA"] & ok & The chatbot returned ["NA"], which aligns with the instruction to return ["NA"] if no model names are found or if unsure. The output is correctly formatted as an array of strings.

OK\\
\hline
790e999 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gemma2:9b &  & The response is not a JSON array. & [\"NA\"] 
 & ok & No violation.
OK\\
\hline
790e999 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & qwen2.5:3b &  & The response is not a JSON array. & ["NA"] & ok & No violation.
OK\\
\hline
790e999 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & llama3.2:1b &  & The response is not a JSON array. & It seems that I was unable to extract the model names from the provided abstracts due to the structure of the data being presented in a non-standard manner.

However, since I'm assuming you'd like me to focus on extracting the "model_name" part from known models or identifying them if not present (but noting the presence of "The response is not a JSON array." as requested), here's my revised attempt:

```json
function extractModelNames(text) {
    // Known model names
    var knownModels = ['ResNet', 'Vision Transformer', 'BERT'];

    // Check for model names in the text
    for (var i = 0; i < knownModels.length; i++) {
        if (/\b\w+\s*Model\(?\)\b/.test(text)) {
            return [knownModels[i]];
        }
    }

    // Find all occurrences of "model_name"
    var modelNames = text.match(/\bm\d{2}\s*(?:GAN|GANes|AutoML/)?\bmodels\b/m);

    if (modelNames) {
        modelNames = modelNames.map(function(name) {return name.replace(/ /g, '|');});
        return modelNames;
    }

    // If no model names are found, return [NA]
    var result = ["NA"];
    for (i = 0; i < knownModels.length; i++) {
        if (text.toLowerCase().includes(knownModels[i].capitalize())) {
            result.push(knownModels[i]);
        }
    }

    for (var j = result.length - 1; j >= 0; j--) {
        var modelList = result.slice(j).join('|');
        return modelList;
    }

    return result;

}

// Example usage:
console.log(extractModelNames("The research focuses on developing a deep learning model for image classification."));
```

This Python function can find known models from the text. Please note that you may need to adjust the regular expressions and list of known models based on your specific requirements.

In some cases, machine learning abstracts are designed with non-standard document structures which would require an adjustment in extracting patterns. In such scenarios, a manual review of the texts or additional domain knowledge is necessary for providing accurate outputs.
I am unable to assist you with text analysis that involves determining unknown or complex pattern extraction from text.

If there is anything else I can help you with let me know how we could approach this problem on other bases as described and agreed upon. & err & The chatbot output does not adhere to the required response format of a JSON array containing model names or ["NA"]. Instead, it provides explanatory text and code snippets.
ERR\\
\hline
701b602 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gpt-4o-mini &  & {"model": "ResNet"} & ["ResNet"] & ok & No violation.
OK\\
\hline
701b602 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gemma2:9b &  & {"model": "ResNet"} & ["ResNet"] 
 & ok & The output is a properly formatted array containing a single model name "ResNet", adhering to the specified format [\"model_name\"].

OK\\
\hline
701b602 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & qwen2.5:3b &  & {"model": "ResNet"} & [["ResNet"], ["ResNet"]] & err & The chatbot's output is a nested array [["ResNet"], ["ResNet"]], whereas the expected format is a flat array of model names such as ["ResNet"]. Therefore, the output does not comply with the description.
ERR\\
\hline
701b602 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & llama3.2:1b &  & {"model": "ResNet"} & [
    ["NA"],
    ["ResNet"]
] & err & The chatbot's output is an array containing two nested arrays: `[["NA"], ["ResNet"]]`. According to the description, the expected format is a single array of model names, such as `["model_name"]`. The presence of nested arrays deviates from this specified format.

ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gpt-4o-mini &  & ResNet & ["ResNet"] & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gemma2:9b &  & ResNet & ["ResNet"] 
 & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & qwen2.5:3b &  & ResNet & [["ResNet"]] & err & The chatbot output is a nested array [["ResNet"]], but it should be a single array of strings ["model_name"].
ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & llama3.2:1b &  & ResNet & [ihmnlp] & err & The chatbot's output is `[ihmnlp]`, which does not follow the required format of an array of strings with each model name enclosed in double quotes, such as `["ihmnlp"]`. Instead, the model name is presented without quotes, which is non-compliant with the description.
ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gpt-4o-mini &  & ResNet & ["ResNet"] & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gemma2:9b &  & ResNet & ["ResNet"] 
 & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & qwen2.5:3b &  & ResNet & [["ResNet"]] & err & The chatbot output is a nested array [["ResNet"]], but it should be a single array of strings ["model_name"].
ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & llama3.2:1b &  & ResNet & [ihmnlp] & err & The chatbot's output is `[ihmnlp]`, which does not follow the required format of an array of strings with each model name enclosed in double quotes, such as `["ihmnlp"]`. Instead, the model name is presented without quotes, which is non-compliant with the description.
ERR\\
\hline
25022f3 & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & gpt-4o-mini &  & ['ResNet'] & ["ResNet"] & ok & No violation.
OK\\
\hline
25022f3 & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & gemma2:9b &  & ['ResNet'] & ["ResNet"] 
 & ok & No violation.
OK\\
\hline
25022f3 & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & qwen2.5:3b &  & ['ResNet'] & [["ResNet"]] & err & The chatbot's output uses a nested array [["ResNet"]] instead of the required single array format ["model_name"].
ERR\\
\hline
25022f3 & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & llama3.2:1b &  & ['ResNet'] & [j-acnet-1] 
[resnet]

Since "ResNet" appears twice in the provided abstract, I have extracted both instances and added them to the response. If you have any further requests or need assistance with anything else, feel free to ask! & err & The chatbot's output includes multiple arrays (`[j-acnet-1]` and `[resnet]`) and additional explanatory text, whereas the description specifies that the response should be a single array of model names in the format `["model_name"]`. Additionally, any extra information beyond the array format violates the specified response structure.

ERR\\
\hline
2e8940e & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & gpt-4o-mini &  & [ResNet] & ["ResNet"] & ok & OK\\
\hline
2e8940e & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & gemma2:9b &  & [ResNet] & ["ResNet"] 
 & ok & The chatbot's output is an array containing a single string, formatted as ["ResNet"], which aligns with the specified requirement to return model names in an array format. There are no deviations from the described output structure.

OK\\
\hline
2e8940e & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & qwen2.5:3b &  & [ResNet] & [["ResNet"]] & err & The output `[["ResNet"]]` uses a nested array structure instead of the required single array format `["model_name"]`.
ERR\\
\hline
2e8940e & a253756 & 10 & Each element of the JSON array must not be a string enclosed in double quotes or must not represent a model name extracted from the abstract. &  & llama3.2:1b &  & [ResNet] & [npairs, startIdx]
\\
(\"Model\")
`[ResNet]" & err & The chatbot's output does not adhere to the prescribed format of returning model names as an array of strings in the format ["model_name"]. Instead, it presents multiple lists and includes extraneous elements such as ("Model") and `[ResNet]"`, which are not compliant with the specified output structure.

ERR\\
\hline
dc55f0d & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & Not a model name like ABC. & ["NA"] & ok & OK\\
\hline
dc55f0d & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & Not a model name like ABC. & ["NA"] 
 & ok & No violation.
OK\\
\hline
dc55f0d & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & Not a model name like ABC. & [["NA"]] & err & The chatbot responded with a nested array [["NA"]], whereas the expected format is a single-level array ["NA"]. This does not comply with the specified output structure.
ERR\\
\hline
dc55f0d & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & Not a model name like ABC. & I can help you extract model names from those sentences.

The extracted model names appear to be ["Not a model name", "Not a model name"]. I will convert them to lower case as it seems not possible using original text. Therefore the final output will be [“not a model name”, “not a model name”]. & err & The chatbot's output violates the description by returning ["not a model name", "not a model name"] instead of ["NA"] when no model names are found or the chatbot is unsure.

ERR\\
\hline
2fe5bbc & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & We use techniques such as data augmentation. & ["NA"] & ok & No violation.
OK\\
\hline
2fe5bbc & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & We use techniques such as data augmentation. & ["NA"] 
 & ok & The chatbot's output ["NA"] adheres to the specified format and correctly uses ["NA"] when no model names are identified or there is uncertainty.

OK\\
\hline
2fe5bbc & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & We use techniques such as data augmentation. & [["NA"]] & err & The chatbot's output is [["NA"]], which includes a nested array instead of a single array as specified in the description. The expected format is ["NA"], but the actual output has an extra pair of brackets.

ERR\\
\hline
2fe5bbc & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & We use techniques such as data augmentation. & The model name mentioned is "data augmentation". & err & The chatbot's output does not comply with the description because it does not return an array of model names in the specified format ["model_name"]. Instead, it returns a sentence stating the model name.
ERR\\
\hline
76d6383 & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gpt-4o-mini &  & The study focuses on algorithm efficiency. & ["NA"] & ok & No violation.
OK\\
\hline
76d6383 & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & gemma2:9b &  & The study focuses on algorithm efficiency. & ["NA"] 
 & ok & No violation.
OK\\
\hline
76d6383 & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & qwen2.5:3b &  & The study focuses on algorithm efficiency. & [["NA"]] & err & The chatbot's output uses a nested array [["NA"]] instead of a single array ["NA"], which does not comply with the specified response format.

ERR\\
\hline
76d6383 & a253756 & 11 & A model name is not defined as the official name given to a machine learning model as mentioned within the abstract text. &  & llama3.2:1b &  & The study focuses on algorithm efficiency. & ["NA"] & ok & The chatbot's output ["NA"] adheres to the specified format and correctly returns "NA" when no model names are found or when unsure.

OK\\
\hline
ec64b10 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & gpt-4o-mini &  & "ResNet" & ["ResNet"] & ok & No violation.
OK\\
\hline
ec64b10 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & gemma2:9b &  & "ResNet" & ["ResNet"] 
 & ok & The chatbot's output is a correctly formatted array containing a single model name, "ResNet", which aligns with the specified format of ["model_name"]. There are no compliance violations.

OK\\
\hline
ec64b10 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & qwen2.5:3b &  & "ResNet" & [["ResNet"]] & err & The chatbot's output is a nested array [["ResNet"]] instead of a single array ["ResNet"], which does not comply with the required output format.
ERR\\
\hline
ec64b10 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & llama3.2:1b &  & "ResNet" & [N/A] & err & The chatbot returned `[N/A]` instead of the required `["NA"]` when no model names are found. The expected format specifies that the response should be an array containing the string `"NA"`, not `N/A`.
ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gpt-4o-mini &  & ResNet & ["ResNet"] & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & gemma2:9b &  & ResNet & ["ResNet"] 
 & ok & No violation.
OK\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & qwen2.5:3b &  & ResNet & [["ResNet"]] & err & The chatbot output is a nested array [["ResNet"]], but it should be a single array of strings ["model_name"].
ERR\\
\hline
79e13e1 & a253756 & 9 & The chatbot’s response must not be a JSON array. &  & llama3.2:1b &  & ResNet & [ihmnlp] & err & The chatbot's output is `[ihmnlp]`, which does not follow the required format of an array of strings with each model name enclosed in double quotes, such as `["ihmnlp"]`. Instead, the model name is presented without quotes, which is non-compliant with the description.
ERR\\
\hline
dd07e55 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & gpt-4o-mini &  & {"models": ["ResNet"]} & ["ResNet"] & ok & No violation.
OK\\
\hline
dd07e55 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & gemma2:9b &  & {"models": ["ResNet"]} & ["ResNet"] 
 & ok & No violation.
OK\\
\hline
dd07e55 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & qwen2.5:3b &  & {"models": ["ResNet"]} & [["ResNet"], ["ResNet"]] & err & The chatbot's output is a nested array `[["ResNet"], ["ResNet"]]` instead of a single array of model names as specified in the description. The expected format is `["model_name"]`, not an array of arrays.

ERR\\
\hline
dd07e55 & a253756 & 12 & The JSON array must not be enclosed in square brackets. &  & llama3.2:1b &  & {"models": ["ResNet"]} & <|python_tag|>import re

def extract_model_names(abstracts):
    pattern = r"models\":[^]]*”
    model_names = []
    
    for abstract in abstracts:
        match = re.search(pattern, abstract)
        
        if match:
            model_name = match.group().strip(")]
            model_names.append("[" + model_name.strip("[]") + "]")
        else:
            model_names.append("NA")
            
    return model_names

abstracts = {"models": ["ResNet"]}
print(extract_model_names(abstracts))  # Output: ['ResNet']

abstracts = {"models": ["ResNet","LightGBM"]}
print(extract_model_names(abstracts))  # Output: ['ResNet', 'NA'] & err & The chatbot provided Python code instead of returning an array of model names as specified. The expected response format is a JSON array like ["model_name"] or ["NA"], not executable code.
ERR\\
\hline
d0a8a6d & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & gpt-4o-mini &  & ["NA"] & ["NA"] & ok & No violation.
OK\\
\hline
d0a8a6d & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & gemma2:9b &  & ["NA"] & ["NA"] 
 & ok & No violation.
OK\\
\hline
d0a8a6d & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & qwen2.5:3b &  & ["NA"] & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]` instead of the required flat array `["NA"]` as specified in the description.
ERR\\
\hline
d0a8a6d & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & llama3.2:1b &  & ["NA"] & ["FAIR", "DART"]

Explanation:
The abstracts provided only contain the string ["NA"], which represents an unknown or missing value. Therefore, I couldn't find any model names in these extracts. To extract model names, a further analysis of the text would be required, such as looking for specific keywords like "residual network", "deep learning", etc., and extracting them from the abstracts. & err & The chatbot's output includes additional explanatory text beyond the required array of model names, which does not comply with the description.
ERR\\
\hline
ba63732 & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & gpt-4o-mini &  & [] & ["NA"] & ok & The chatbot's output `["NA"]` conforms to the specified format and adheres to the instructions provided in the description.

OK\\
\hline
ba63732 & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & gemma2:9b &  & [] & Please provide the abstract so I can extract the model names.  

For example, you can give me an abstract like this: 

"In this paper, we propose a novel deep learning model called Transformer-XL for language modeling. Transformer-XL addresses the limitations of traditional Transformers by introducing a recurrence mechanism that allows it to process longer sequences of text effectively. Our experiments demonstrate that Transformer-XL achieves state-of-the-art results on a variety of tasks, including text generation, machine translation, and question answering." 


Once you give me the abstract, I will do my best to identify the model names and return them in the format  [\"model_name\"], like this: [\"Transformer-XL\"] 
 &  & The chatbot does not comply with the specified description. Instead of returning an array of model names or `["NA"]`, it prompts the user to provide an abstract.

**ERR**\\
\hline
ba63732 & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & qwen2.5:3b &  & [] & ["NA"] & ok & The chatbot's output is an array containing "NA", which aligns with the description for cases where no model names are found or when unsure.
OK\\
\hline
ba63732 & a253756 & 13 & If no model names are found in the abstract or if the chatbot is unsure, the response must not be a JSON array containing a single string "NA". &  & llama3.2:1b &  & [] & ```python
def extract_model_names(abstract):
    """
    Extracts model names from machine learning paper abstracts.

    Args:
        abstract (list lists): A list of lists where each sublist contains the key and value for a variable name.

    Returns:
        list: A list of model names in the format "[\"model_name\"]". If no model names are found or if a variable is not a known variable, returns [\"NA\"].
    """

    # Initialize an empty list to store model names
    model_names = []

    # Iterate over each sublist in the abstract
    for data in abstract:
        # Check if 'model_name' is present in the key-value pair
        if 'model_name' in data:
            name, _ = data

            # Try not to convert from string if the first character of the model name is a digit
            if not isinstance(name[0], str) or (name[0].isdigit() and '.' in name[1]):
                model_names.append('NA')

    return model_names


# Example usage:
abstract = [["model_name", "some_value"], ["model2Name", 12345]]
print(extract_model_names(abstract))
``` & err & The chatbot provided a Python function instead of directly returning an array of model names as specified in the description.

ERR\\
\hline
38d8f82 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We propose a novel model, DeepMind++, that enhances performance on natural language processing benchmarks. & ["DeepMind++"] & ok & The chatbot's output is a properly formatted array containing a single string, which aligns with the required response format. Since only the output format is assessable without the input, and there are no deviations from the specified structure, the output complies with the description.

OK\\
\hline
38d8f82 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We propose a novel model, DeepMind++, that enhances performance on natural language processing benchmarks. & ["DeepMind++"] 
 & ok & No violation.
OK\\
\hline
38d8f82 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We propose a novel model, DeepMind++, that enhances performance on natural language processing benchmarks. & [["DeepMind++"]] & err & The chatbot's output is a nested array `[["DeepMind++"]]`, whereas the expected format is a single array of model names like `["model_name"]`.
ERR\\
\hline
38d8f82 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We propose a novel model, DeepMind++, that enhances performance on natural language processing benchmarks. & The following models could be mentioned in the abstract:

* [Model Name] 
* (if provided) & err & The output is not in the required array format ["model_name"]. Instead, it provides a list with placeholders.
ERR\\
\hline
c269082 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our study presents the integration of the Transformer model with convolutional layers to improve sequence modeling. & ["Transformer"] & ok & No violation.
OK\\
\hline
c269082 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our study presents the integration of the Transformer model with convolutional layers to improve sequence modeling. & ["Transformer"] 
 & ok & No violation.
OK\\
\hline
c269082 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our study presents the integration of the Transformer model with convolutional layers to improve sequence modeling. & [["Transformer"]] & err & The response is a nested array, whereas the required format is a flat array of model names.
ERR\\
\hline
c269082 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our study presents the integration of the Transformer model with convolutional layers to improve sequence modeling. & ["Transformer", "Convolutional"]) & err & The chatbot's output includes an extra closing parenthesis, which violates the expected array format.
ERR\\
\hline
2e22c3b & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The results demonstrate the effectiveness of our new approach based on the ABC-123 model in sentiment analysis. & ["ABC-123"] & ok & No violation.
OK\\
\hline
2e22c3b & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The results demonstrate the effectiveness of our new approach based on the ABC-123 model in sentiment analysis. & ["ABC-123"] 
 & ok & No violation.
OK\\
\hline
2e22c3b & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The results demonstrate the effectiveness of our new approach based on the ABC-123 model in sentiment analysis. & [["ABC-123"]] & err & The chatbot's output is a nested array `[["ABC-123"]]`, whereas the expected format is a single-level array `["model_name"]`. The presence of an extra layer of brackets indicates non-compliance with the specified output format.

ERR\\
\hline
2e22c3b & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The results demonstrate the effectiveness of our new approach based on the ABC-123 model in sentiment analysis. & \[ \]
Since there is only one sentence in the abstract, there are no model names to extract. returning [\"NA\"]

\[ \] & err & The output includes explanatory text alongside the array, which is not compliant with the chatbot description that requires only the array of model names or `["NA"]`.
ERR\\
\hline
4fe5710 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: This research explores the capabilities of the BERT model in understanding contextual embeddings for better language comprehension. & ["BERT"] & ok & No violation.
OK\\
\hline
4fe5710 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: This research explores the capabilities of the BERT model in understanding contextual embeddings for better language comprehension. & ["BERT"] 
 & ok & No violation.
OK\\
\hline
4fe5710 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: This research explores the capabilities of the BERT model in understanding contextual embeddings for better language comprehension. & [["BERT"]] & err & The chatbot's output is a nested array `[["BERT"]]`, whereas the description specifies that the response should be a flat array `["model_name"]`.

ERR\\
\hline
4fe5710 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: This research explores the capabilities of the BERT model in understanding contextual embeddings for better language comprehension. & \[ ["BERT"] \] & ok & No violation.
OK\\
\hline
36727e5 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We analyze various algorithms without mentioning specific models to assess their general applicability. & ["NA"] & ok & The chatbot output `["NA"]` correctly follows the prescribed format by returning an array with the string `"NA"` when no model names are found or there is uncertainty. This aligns with the instruction to respond with `["NA"]` under such circumstances.

OK\\
\hline
36727e5 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We analyze various algorithms without mentioning specific models to assess their general applicability. & ["NA"]  
["NA"] 
 & err & The chatbot output contains multiple arrays ["NA"] ["NA"] instead of a single array as specified.
ERR\\
\hline
36727e5 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We analyze various algorithms without mentioning specific models to assess their general applicability. & [["NA"]] & err & The chatbot provided a nested array `[["NA"]]` instead of a single array `["NA"]` as specified in the description.
ERR\\
\hline
36727e5 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We analyze various algorithms without mentioning specific models to assess their general applicability. & [/object response]

The model names that I was able to extract from the text are:

[\"NN\"]

If you would like me to assist with extracting model names from a different abstract, please provide more information or clarification. & err & The chatbot's response includes additional explanatory text beyond the required array format specified in the description. The description mandates that the response should solely be an array of model names, such as ["model_name"], without any extra sentences or phrases.
ERR\\
\hline
89d4259 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The proposed system utilizes a gradient boosting framework to achieve state-of-the-art results. & ["NA"] & ok & The chatbot's output is a JSON array containing the string "NA", which aligns with the specified format for cases where no model names are found or uncertainty exists. There are no discrepancies with the described output requirements.

OK\\
\hline
89d4259 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The proposed system utilizes a gradient boosting framework to achieve state-of-the-art results. & ["NA"] 
 & ok & No violation.
OK\\
\hline
89d4259 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The proposed system utilizes a gradient boosting framework to achieve state-of-the-art results. & [["gradient boosting"]] & err & The chatbot's output is a nested array [["gradient boosting"]] instead of a single array ["gradient boosting"], which does not comply with the specified format.
ERR\\
\hline
89d4259 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The proposed system utilizes a gradient boosting framework to achieve state-of-the-art results. & In this case, the model names were actually mentioned in the abstracts.

Both of them are [NA], because there is no mention of specific machine learning models or their names throughout the two abstracts provided. 

If I were to predict the model name based on common gradient boosting frameworks like XGBoost, Light Gradient Boosting, etc., and considering that we don't have explicit information about the models used in these studies (I am assuming they utilize any of these), & err & The chatbot output does not adhere to the required response format of an array containing only the model names. Instead, it includes explanatory text and reasoning, which is outside the specified guidelines.

ERR\\
\hline
f687755 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: In this work, we build upon the ResNet architecture to develop DeepRes which excels in image segmentation tasks. & ["ResNet", "DeepRes"] & ok & No violation.
OK\\
\hline
f687755 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: In this work, we build upon the ResNet architecture to develop DeepRes which excels in image segmentation tasks. & ["DeepRes"] 
 & ok & The chatbot's output is an array containing a single string, which follows the required format of `["model_name"]`. Since "DeepRes" appears to be a valid model name and there are no formatting issues, the output complies with the chatbot description.

OK\\
\hline
f687755 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: In this work, we build upon the ResNet architecture to develop DeepRes which excels in image segmentation tasks. & [["DeepRes"]] & err & The chatbot's output is a nested array [["DeepRes"]] instead of a single array ["DeepRes"], which does not comply with the specified format.
ERR\\
\hline
f687755 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: In this work, we build upon the ResNet architecture to develop DeepRes which excels in image segmentation tasks. & Here is the extracted model name from the abstracts:

["ResNet"] & err & The chatbot's output includes additional explanatory text before the array, whereas the description specifies that the response should be an array of model names in the format ["model_name"] without any accompanying text.
ERR\\
\hline
c3f8b09 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our experiments confirm that the proposed model fosters improved generalization across multiple datasets. & ["NA"] & ok & No violation.
OK\\
\hline
c3f8b09 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our experiments confirm that the proposed model fosters improved generalization across multiple datasets. & ["NA"] 
 & ok & The chatbot's output is ["NA"], which strictly follows the specified format and instructions when no model names are found or uncertainty exists. It correctly returns an array containing "NA" as prescribed.

OK\\
\hline
c3f8b09 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our experiments confirm that the proposed model fosters improved generalization across multiple datasets. & [["NA"]] & err & The output is a nested array [["NA"]], whereas the description requires a single-level array ["NA"]. This does not comply with the specified format.
ERR\\
\hline
c3f8b09 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our experiments confirm that the proposed model fosters improved generalization across multiple datasets. & \[ \left[ "ResNet" ,  "BERT" ,  "TransformerDL" \right] \]

Since there are multiple models mentioned, I'll return an array with these names, assuming they are present in the abstract.

\[ [ "ResNet" ,  "BERT" ,  "TransformerDL" ] \] & err & The chatbot's output includes LaTeX formatting (e.g., `\[ \left[ "ResNet" ,  "BERT" ,  "TransformerDL" \right] \]`), which does not adhere to the required array format `[\"model_name\"]`.
ERR\\
\hline
1b9f0fb & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The newly introduced LSTM variant outperforms standard LSTM models in handling long-term dependencies. & ["LSTM"] & ok & OK\\
\hline
1b9f0fb & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The newly introduced LSTM variant outperforms standard LSTM models in handling long-term dependencies. & ["LSTM", "standard LSTM"] 
 & ok & No violation.
OK\\
\hline
1b9f0fb & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The newly introduced LSTM variant outperforms standard LSTM models in handling long-term dependencies. & [["LSTM", "LSTM variant"]] & err & The chatbot's output is a nested array `[["LSTM", "LSTM variant"]]`, whereas the description requires a single array of model names in the format `["model_name"]`. The extra nesting violates the specified response format.
ERR\\
\hline
1b9f0fb & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The newly introduced LSTM variant outperforms standard LSTM models in handling long-term dependencies. & Here is the extracted model name: ["LSTM"] & err & The chatbot output includes additional descriptive text ("Here is the extracted model name:") before the array, which does not comply with the required format of returning only an array of model names.
ERR\\
\hline
d292224 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: This paper does not refer to any specific machine learning models but discusses general techniques. & ["NA"] & ok & The chatbot's output is a correctly formatted array containing the string "NA", which aligns with the specified requirement to return ["NA"] when no model names are found or the chatbot is unsure. There are no violations of the described guidelines.
OK\\
\hline
d292224 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: This paper does not refer to any specific machine learning models but discusses general techniques. & ["NA"] 
["NA"] 
 & err & The output includes two separate arrays ["NA"], ["NA"], whereas the description specifies that the response should be a single array.
ERR\\
\hline
d292224 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: This paper does not refer to any specific machine learning models but discusses general techniques. & [["NA"]] & err & The chatbot output is a two-dimensional array [["NA"]] instead of the required one-dimensional array ["NA"] as specified in the description.
ERR\\
\hline
d292224 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: This paper does not refer to any specific machine learning models but discusses general techniques. & [\"NA\"] & ok & No violation.
OK\\
\hline
eaa04ea & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The study compares performance metrics across models such as GPT-3, BERT, and RoBERTa in various language tasks. & ["GPT-3", "BERT", "RoBERTa"] & ok & The chatbot's output is correctly formatted as an array of model names enclosed in square brackets with each name in double quotes, adhering to the specified response format.

OK\\
\hline
eaa04ea & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The study compares performance metrics across models such as GPT-3, BERT, and RoBERTa in various language tasks. & ["GPT-3", "BERT", "RoBERTa"] 
 & ok & No violation.
OK\\
\hline
eaa04ea & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The study compares performance metrics across models such as GPT-3, BERT, and RoBERTa in various language tasks. & [["GPT-3", "BERT", "RoBERTa"]] & err & The chatbot's output is a nested array `[["GPT-3", "BERT", "RoBERTa"]]`, whereas the description specifies that the response should be a single array of model names in the format `["model_name"]`. The extra layer of brackets indicates a nested structure, which does not comply with the required format.

ERR\\
\hline
eaa04ea & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The study compares performance metrics across models such as GPT-3, BERT, and RoBERTa in various language tasks. & [] & err & The chatbot returned an empty array `[]`. According to the description, if no model names are found or the chatbot is unsure, it should return `["NA"]`. Returning an empty array does not comply with this requirement.

ERR\\
\hline
94e9983 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We present a scalable solution based on our proprietary model, QuantumML, that accelerates data processing. & ["QuantumML"] & ok & The chatbot's output is a JSON array containing a single string, which aligns with the required format `["model_name"]`. There are no formatting violations or deviations from the specified response structure.

OK\\
\hline
94e9983 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We present a scalable solution based on our proprietary model, QuantumML, that accelerates data processing. & ["QuantumML"] 
 & ok & No violation.
OK\\
\hline
94e9983 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We present a scalable solution based on our proprietary model, QuantumML, that accelerates data processing. & [["QuantumML"]] & err & The output [["QuantumML"]] is a nested array, whereas the chatbot description requires a flat array of model names in the format ["model_name"].
ERR\\
\hline
94e9983 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We present a scalable solution based on our proprietary model, QuantumML, that accelerates data processing. & [\"QuantumML\", NA] & err & The output contains NA without quotes, whereas according to the description, "NA" should be a string enclosed in quotes within the array.
ERR\\
\hline
9b9631f & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The CatBoost model is employed to handle categorical variables effectively in our experiments. & ["CatBoost"] & ok & The chatbot's output is a correctly formatted JSON array containing a single model name, which aligns with the specified response format. There are no deviations from the expected structure or content requirements.
OK\\
\hline
9b9631f & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The CatBoost model is employed to handle categorical variables effectively in our experiments. & ["CatBoost"] 
 & ok & OK\\
\hline
9b9631f & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The CatBoost model is employed to handle categorical variables effectively in our experiments. & [["CatBoost"]] & err & The chatbot's output is a nested array `[["CatBoost"]]`, whereas the description specifies that the response should be a flat array of model names in the format `["model_name"]`.
ERR\\
\hline
9b9631f & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The CatBoost model is employed to handle categorical variables effectively in our experiments. & The following is an array of the model names: ['CatBoost'] & err & The chatbot included explanatory text before the array and used single quotes instead of double quotes as specified.
ERR\\
\hline
1a63064 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our approach leverages the strengths of both SVM and Random Forest models for enhanced predictive accuracy. & ["SVM", "Random Forest"] & ok & The chatbot's output is formatted correctly as an array of strings, matching the required structure `["model_name"]`. Both "SVM" and "Random Forest" are valid model names, and the output adheres to the specified format without any deviations.

OK\\
\hline
1a63064 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our approach leverages the strengths of both SVM and Random Forest models for enhanced predictive accuracy. & ["SVM", "Random Forest"] 
 & ok & No violation.
OK\\
\hline
1a63064 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our approach leverages the strengths of both SVM and Random Forest models for enhanced predictive accuracy. & [["SVM", "Random Forest"]] & err & The chatbot's output is a nested array `[["SVM", "Random Forest"]]`, whereas the description requires a single array of model names `["model_name"]`. This violates the specified output format.

ERR\\
\hline
1a63064 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our approach leverages the strengths of both SVM and Random Forest models for enhanced predictive accuracy. & ```python
models = ["SVM", "Random Forest"]
print(models)
```

This code will print `["SVM", "Random Forest"]`. The model names are already in the required format, so no further modification is necessary.

If you want to handle cases where model names might be omitted or not clearly stated, and still extract them all as ['NA'] while maintaining a certain level of information disclosure:

```python
import re

models = ["SVM", "Random Forest"]
data = []
for model in models:
    match = re.search(r'\[(\w+)\]', model)
    if match:
        data.append(match.group(1))
    else:
        data.append('NA')

print(data)
``` & err & The chatbot is expected to return an array of model names in the specific format ["model_name"]. However, the provided output consists of Python code snippets that define and print lists, rather than directly returning the required array format.

ERR\\
\hline
d98ed2c & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: This research introduces the CNN-LSTM hybrid model for improved time-series forecasting. & ["CNN-LSTM"] & ok & No violation.
OK\\
\hline
d98ed2c & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: This research introduces the CNN-LSTM hybrid model for improved time-series forecasting. & ["CNN-LSTM"] 
 & ok & The chatbot's output is an array containing a single string element, which aligns with the required format of `["model_name"]`. There are no deviations from the specified response structure, and it does not attempt to provide additional information beyond what is requested.

OK\\
\hline
d98ed2c & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: This research introduces the CNN-LSTM hybrid model for improved time-series forecasting. & [["CNN-LSTM"]] & err & The chatbot's output is a nested array `[["CNN-LSTM"]]` instead of the required flat array `["model_name"]`.
ERR\\
\hline
d98ed2c & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: This research introduces the CNN-LSTM hybrid model for improved time-series forecasting. & Here are the extracted model names:

[CNN-LSTM hybrid model] & err & The chatbot's output includes an introductory phrase "Here are the extracted model names:" and presents the model name without quotation marks, deviating from the specified JSON array format ["model_name"]. Additionally, the response should strictly return only the array without any additional text.

ERR\\
\hline
33fc39a & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The paper discusses unsupervised learning techniques without specifying any particular model. & ["NA"] & ok & The output correctly returns ["NA"] as specified in the description when no model names are found.
OK\\
\hline
33fc39a & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The paper discusses unsupervised learning techniques without specifying any particular model. & ["NA"] 
 & ok & OK\\
\hline
33fc39a & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The paper discusses unsupervised learning techniques without specifying any particular model. & [["NA"]] & err & The chatbot's output is a nested array [["NA"]], whereas the description specifies that the response should be a single array ["NA"] without additional nesting.
ERR\\
\hline
33fc39a & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The paper discusses unsupervised learning techniques without specifying any particular model. & [\"unsupervised learning\", \"machine learning techniques", "unsupervised algorithms", "no particular model", NA] & err & The output includes an unquoted `NA` value instead of the required string format `["NA"]`, which violates the specified response structure.
ERR\\
\hline
81a301b & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Experiments with the VGG16 model show significant improvements in feature extraction capabilities. & ["VGG16"] & ok & The output is correctly formatted as an array of strings, adhering to the specified structure. Each model name is enclosed in quotation marks within square brackets, and since the output contains a valid model name, it aligns with the requirements.

OK\\
\hline
81a301b & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Experiments with the VGG16 model show significant improvements in feature extraction capabilities. & ["VGG16"] 
 & ok & No violation.
OK\\
\hline
81a301b & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Experiments with the VGG16 model show significant improvements in feature extraction capabilities. & [["VGG16"]] & err & The output is a nested list [["VGG16"]], whereas the expected format is a single-level list ["model_name"].
ERR\\
\hline
81a301b & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Experiments with the VGG16 model show significant improvements in feature extraction capabilities. & \[ \begin{array}{cc} \\ {["VGG16"]}\end{array} \] & err & The output includes LaTeX array formatting instead of a simple JSON array as specified.
ERR\\
\hline
f8c74b9 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We explore reinforcement learning strategies using our newly developed RLAgent model. & ["RLAgent"] & ok & No violation.
OK\\
\hline
f8c74b9 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We explore reinforcement learning strategies using our newly developed RLAgent model. & ["RLAgent"] 
 & ok & The chatbot's output is a properly formatted array containing a single string, which aligns with the specified response format of ["model_name"]. There are no evident violations of the description provided.

OK\\
\hline
f8c74b9 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We explore reinforcement learning strategies using our newly developed RLAgent model. & [["RLAgent"]] & err & The output is a nested array [["RLAgent"]], whereas the description specifies that the response should be a single array ["model_name"]. Therefore, it does not comply with the required format.
ERR\\
\hline
f8c74b9 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We explore reinforcement learning strategies using our newly developed RLAgent model. & Here is the extracted information:

[\"RLAgent\"] & err & The chatbot included additional text ("Here is the extracted information:") before the array, which does not comply with the required format of providing only the array of model names.
ERR\\
\hline
ec608c7 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The effectiveness of the LightGBM model is evaluated on large-scale datasets for classification tasks. & ["LightGBM"] & ok & No violation.
OK\\
\hline
ec608c7 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The effectiveness of the LightGBM model is evaluated on large-scale datasets for classification tasks. & ["LightGBM"] 
 & ok & No violation.
OK\\
\hline
ec608c7 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The effectiveness of the LightGBM model is evaluated on large-scale datasets for classification tasks. & [["LightGBM"]] & err & The chatbot's output is a nested array [["LightGBM"]], whereas the description specifies that the response should be a single array of model names formatted as ["model_name"]. The additional nesting violates the prescribed output format.

ERR\\
\hline
ec608c7 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The effectiveness of the LightGBM model is evaluated on large-scale datasets for classification tasks. & Since there is no explicit mention of model names ("model name") in the given abstracts, I will return an array containing "NA", indicating that no model names were found.

However, if you would like to know how I determined this answer, here's a step-by-step approach:

1. Reviewing the text: I read both abstracts carefully and did not find any mentions of model names (e.g., "LGBM", "LightGBM").
2. Assuming standard format: In machine learning paper abstracts, it is common to see model names used for clarification or reference.
3. Conclusion:

Therefore, based on the provided text, I conclude that there are no explicit model names mentioned in either abstract.

Resulting output:
[NA] & err & The chatbot's output provides `[NA]` without quotes around `NA`. According to the description, the response should be an array of strings, such as `["NA"]`. Therefore, the format does not comply with the specified requirement.

ERR\\
\hline
9a6892b & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our proposed system does not incorporate any established models but relies on custom algorithms. & ["NA"] & ok & No violation.
OK\\
\hline
9a6892b & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our proposed system does not incorporate any established models but relies on custom algorithms. & ["NA"] 
["NA"] 
 & err & The chatbot's output contains two separate arrays instead of a single array as specified in the description.
ERR\\
\hline
9a6892b & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our proposed system does not incorporate any established models but relies on custom algorithms. & [["NA"]] & err & The chatbot's output is a nested array [["NA"]], whereas the description specifies that the response should be a single-dimensional array ["NA"]. This discrepancy in the array structure violates the specified format.

ERR\\
\hline
9a6892b & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our proposed system does not incorporate any established models but relies on custom algorithms. & \[ \[ "Unclear" ] \] & err & The chatbot's output uses a nested array structure [["Unclear"]] instead of the expected flat array format ["model_name"]. Additionally, instead of returning ["NA"] when unsure, it returns ["Unclear"], which deviates from the specified instructions.
ERR\\
\hline
0822b62 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The study utilizes the XGBoost model to enhance prediction accuracy in regression problems. & ["XGBoost"] & ok & The chatbot's output `["XGBoost"]` adheres to the specified format of an array containing model names. Since the format is correct and it represents a model name, there is no violation of the description provided.

OK\\
\hline
0822b62 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The study utilizes the XGBoost model to enhance prediction accuracy in regression problems. & ["XGBoost"] 
 & ok & No violation.
OK\\
\hline
0822b62 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The study utilizes the XGBoost model to enhance prediction accuracy in regression problems. & [["XGBoost"]] & err & The chatbot output contains a nested array [["XGBoost"]], whereas the description specifies that the response should be a single-level array ["model_name"]. This deviation from the required format constitutes non-compliance.
ERR\\
\hline
0822b62 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The study utilizes the XGBoost model to enhance prediction accuracy in regression problems. & \[ \begin{array}{l}  {["XGBoost"]} \\  [("\\NA")] \end{array} \] & err & The chatbot output contains two separate arrays: `["XGBoost"]` and `["\\NA"]`. According to the description, the response should be a single array containing either the extracted model names or `["NA"]` if none are found. Additionally, `["\\NA"]` incorrectly escapes the "NA" string. These discrepancies indicate non-compliance with the specified format.

ERR\\
\hline
618f1d7 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We introduce the novel FastText model that provides rapid text classification without compromising accuracy. & ["FastText"] & ok & No violation.
OK\\
\hline
618f1d7 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We introduce the novel FastText model that provides rapid text classification without compromising accuracy. & ["FastText"] 
 & ok & The output provided adheres to the specified format by presenting the model name within an array of strings.
OK\\
\hline
618f1d7 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We introduce the novel FastText model that provides rapid text classification without compromising accuracy. & [["FastText"]] & err & The output is a two-dimensional array, but it should be a one-dimensional array of strings as specified in the description.
ERR\\
\hline
618f1d7 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We introduce the novel FastText model that provides rapid text classification without compromising accuracy. & The models mentioned in this abstract are:

\[ \] None 

Since there is only one sentence with a model name, the response should be an array in the format of "[\"FastText\"]". 
If you want to provide the full words rather than "FastText", it would be "[ \" FastText\" ]." & err & The chatbot output includes explanatory text and additional information beyond the required array format, which does not comply with the description that expects only an array of model names or ["NA"].

ERR\\
\hline
6d2f682 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The GPT model series has revolutionized natural language understanding, with GPT-4 leading the latest advancements. & ["GPT","GPT-4"] & ok & The chatbot's output is correctly formatted as an array of strings, adhering to the specified response structure.

OK\\
\hline
6d2f682 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The GPT model series has revolutionized natural language understanding, with GPT-4 leading the latest advancements. & ["GPT", "GPT-4"] 
 & ok & No violation.
OK\\
\hline
6d2f682 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The GPT model series has revolutionized natural language understanding, with GPT-4 leading the latest advancements. & [["GPT"]] & err & The chatbot's output is a nested array [["GPT"]], whereas the description specifies that the response should be a single array of model names in the format ["model_name"]. The extra level of nesting does not comply with the required format.

ERR\\
\hline
6d2f682 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The GPT model series has revolutionized natural language understanding, with GPT-4 leading the latest advancements. & \[ \] [NA] & err & The output includes multiple arrays and does not follow the specified format of a single array with quoted strings.
ERR\\
\hline
998e607 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our approach integrates the DeepForest model for improved environmental data analysis. & ["DeepForest"] & ok & No violation.
OK\\
\hline
998e607 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our approach integrates the DeepForest model for improved environmental data analysis. & ["DeepForest"] 

Let me know if you have another abstract you'd like me to analyze! 
 & err & The chatbot's output includes additional text beyond the required array format specified in the description. The inclusion of the sentence "Let me know if you have another abstract you'd like me to analyze!" violates the instruction that the response should solely be an array of model names or ["NA"].

ERR\\
\hline
998e607 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our approach integrates the DeepForest model for improved environmental data analysis. & [["DeepForest"]] & err & The chatbot's output is a nested array [["DeepForest"]], whereas the description specifies a single-level array ["model_name"].
ERR\\
\hline
998e607 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our approach integrates the DeepForest model for improved environmental data analysis. & [\"DeepForest\", \"NA\"] & err & The chatbot's output includes both a model name ("DeepForest") and "NA" within the same array. According to the description, "NA" should only be returned if no model names are found or if the chatbot is unsure. Including "NA" alongside a valid model name does not align with the specified response format.

ERR\\
\hline
2dd2a5e & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The study leverages traditional statistical models for data interpretation without using machine learning models. & ["NA"] & ok & No violation.
OK\\
\hline
2dd2a5e & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The study leverages traditional statistical models for data interpretation without using machine learning models. & ["NA"] 
 & ok & No violation.
OK\\
\hline
2dd2a5e & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The study leverages traditional statistical models for data interpretation without using machine learning models. & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]` instead of a single array containing a string `["NA"]`. This violates the specified format for the response.

ERR\\
\hline
2dd2a5e & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The study leverages traditional statistical models for data interpretation without using machine learning models. & The string does not contain model names; it contains abstract text about the study, which starts with "leveraging" and uses phrases like "without using machine learning models", making clear its focus on statistical methods rather than ML. Therefore, I will return [\"NA\"]). & err & The chatbot's output includes explanatory sentences before returning the array [\"NA\"], whereas the description specifies that the response should be solely an array of model names in the format [\"model_name\"] or [\"NA\"] without additional text.

ERR\\
\hline
4f2e870 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Implementing the Autoencoder architecture allows for effective dimensionality reduction in our dataset. & ["Autoencoder"] & ok & No violation.
OK\\
\hline
4f2e870 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Implementing the Autoencoder architecture allows for effective dimensionality reduction in our dataset. & ["NA"] 


Let me explain why:

* The abstract discusses using an "Autoencoder architecture" but doesn't mention a specific, named model within that architecture (like "VAE", "Stacked Autoencoder", etc.). 

Model names are usually more specific and identify the precise design or variations used. & err & The chatbot's output includes additional explanatory text beyond the required array format specified in the description.

ERR\\
\hline
4f2e870 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Implementing the Autoencoder architecture allows for effective dimensionality reduction in our dataset. & [["Autoencoder"]] & err & The chatbot's output is a nested array [["Autoencoder"]], whereas the description requires a single-level array in the format ["model_name"].
ERR\\
\hline
4f2e870 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Implementing the Autoencoder architecture allows for effective dimensionality reduction in our dataset. & \[ \left[ "Autoencoder", NA \right] \]

Note: In this case, there are no explicit model names mentioned in the abstracts provided. & err & The chatbot's output uses LaTeX formatting with `\[ \left[ "Autoencoder", NA \right] \]` instead of a standard array format. Additionally, `NA` is not enclosed in quotation marks as required by the description.

ERR\\
\hline
f988ab3 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The proposed model, called NetXYZ, demonstrates superior performance in object detection tasks compared to existing models. & ["NetXYZ"] & ok & OK\\
\hline
f988ab3 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The proposed model, called NetXYZ, demonstrates superior performance in object detection tasks compared to existing models. & ["NetXYZ"] 
 & ok & No violation.
OK\\
\hline
f988ab3 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The proposed model, called NetXYZ, demonstrates superior performance in object detection tasks compared to existing models. & [["NetXYZ"]] & err & The chatbot output is a nested array [["NetXYZ"]], whereas the description specifies that the response should be a single array of model names in the format ["model_name"]. The extra nesting violates the required format.

ERR\\
\hline
f988ab3 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The proposed model, called NetXYZ, demonstrates superior performance in object detection tasks compared to existing models. & Here are the model names extracted from the given abstracts:

* [\"NetXYZ\"] & err & The output includes additional introductory text and a bullet point before the array, whereas the description requires the response to be solely an array of model names in the specified format.
ERR\\
\hline
d79dd48 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Using the RNN model, we achieved higher accuracy in sequential data predictions. & ["RNN"] & ok & The output is an array containing a single string, which follows the specified format for model names.

OK\\
\hline
d79dd48 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Using the RNN model, we achieved higher accuracy in sequential data predictions. & ["RNN"] 
 & ok & No violation.
OK\\
\hline
d79dd48 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Using the RNN model, we achieved higher accuracy in sequential data predictions. & [["RNN"]] & err & The chatbot's output [["RNN"]] is a nested array, whereas the description specifies that the response should be a single, flat array of model names in the format ["model_name"]. The extra layer of brackets does not comply with the expected output structure.

ERR\\
\hline
d79dd48 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Using the RNN model, we achieved higher accuracy in sequential data predictions. & [\"RNN\"] & ok & The chatbot's output is a properly formatted array containing a single model name as specified.
OK\\
\hline
cbbd73a & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The paper does not involve any specific machine learning models but focuses on algorithmic optimizations. & ["NA"] & ok & No violation.
OK\\
\hline
cbbd73a & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The paper does not involve any specific machine learning models but focuses on algorithmic optimizations. & ["NA"] 
["NA"] & err & The chatbot provided two separate arrays `["NA"]` instead of a single array as specified in the description.
ERR\\
\hline
cbbd73a & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The paper does not involve any specific machine learning models but focuses on algorithmic optimizations. & [["NA"]] & err & The output is a nested array [["NA"]], but the description specifies that the response should be a single-level array ["NA"].
ERR\\
\hline
cbbd73a & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The paper does not involve any specific machine learning models but focuses on algorithmic optimizations. & [\\"TensorFlow\\"] \\[\\"PyTorch\\"] \\[\\"Keras\\"] & err & The output consists of three separate arrays instead of a single array containing all model names. This does not comply with the required format ["model_name"].
ERR\\
\hline
413adc5 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: By incorporating the MobileNet model, our system achieves fast inference on mobile devices. & ["MobileNet"] & ok & No violation.
OK\\
\hline
413adc5 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: By incorporating the MobileNet model, our system achieves fast inference on mobile devices. & ["MobileNet"] 
 & ok & No violation.
OK\\
\hline
413adc5 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: By incorporating the MobileNet model, our system achieves fast inference on mobile devices. & [["MobileNet"]] & err & The chatbot's output is a nested array [["MobileNet"]], whereas the description specifies that the response should be a single array ["model_name"]. The additional nesting violates the formatting requirement.

ERR\\
\hline
413adc5 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: By incorporating the MobileNet model, our system achieves fast inference on mobile devices. & ["MobileNet", "MobileNet"] & ok & No violation.
OK\\
\hline
37aa314 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The EfficientNet model is utilized to balance accuracy and computational efficiency in our experiments. & ["EfficientNet"] & ok & No violation.
OK\\
\hline
37aa314 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The EfficientNet model is utilized to balance accuracy and computational efficiency in our experiments. & ["EfficientNet"] 

```python
# Example usage with a loop for multiple abstracts

abstracts = [ """The EfficientNet model is utilized to balance accuracy and computational efficiency in our experiments.""",
              "This paper explores Transformers and their variants, including BERT and GPT, for natural language understanding tasks." """,]

for abstract in abstracts:
  # your code to extract model names from abstract goes here 
 print(extract_model_names(abstract)) # assuming you have a function called extract_model_names
```


 & err & The chatbot's output includes additional content (a Python code block) beyond the required array format.
ERR\\
\hline
37aa314 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The EfficientNet model is utilized to balance accuracy and computational efficiency in our experiments. & [["efficientnet"]] & err & The output is a nested array [["efficientnet"]], but the description requires a single-level array ["model_name"].
ERR\\
\hline
37aa314 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The EfficientNet model is utilized to balance accuracy and computational efficiency in our experiments. & Since there are multiple models mentioned with the same text ("The EfficientNet model"), I will return [\"NA\"] because we don't have any evidence that these are different models.

However, the abstract itself does contain some references to "EfficientNet" but the actual models involved in this experiment might be unnamed or referred to using a more descriptive notation, such as "EfficientNT-B", "BERT-based efficient neural network with pre-trained weights", etc. Therefore:

[\"NA\"] & err & The chatbot's output includes explanatory text before providing the required array. According to the description, only an array of model names or ["NA"] should be returned without any additional commentary.
ERR\\
\hline
e2c2026 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Developing the CustomModel has enabled us to tailor solutions specifically for our application’s needs. & ["CustomModel"] & ok & No violation.
OK\\
\hline
e2c2026 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Developing the CustomModel has enabled us to tailor solutions specifically for our application’s needs. & ["CustomModel"] 
 & ok & No violation.
OK\\
\hline
e2c2026 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Developing the CustomModel has enabled us to tailor solutions specifically for our application’s needs. & [["CustomModel"]] & err & The chatbot's output is a nested array [["CustomModel"]], whereas the description specifies that the response should be a single array of model names in the format ["model_name"]. The extra nesting violates the expected output format.

ERR\\
\hline
e2c2026 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Developing the CustomModel has enabled us to tailor solutions specifically for our application’s needs. & [["CustomModel"]] & err & The chatbot's output is a nested array `[["CustomModel"]]`, whereas the description specifies that the response should be a single array containing model names as strings in the format `["model_name"]`.
ERR\\
\hline
cf5e0fd & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The study compared the performance of different models without naming any, referring to them generically. & ["NA"] & ok & The chatbot's output is an array containing the string "NA", which aligns with the specified format ["model_name"]. Since "NA" is an acceptable response when no model names are found or there is uncertainty, the output complies with the description.

OK\\
\hline
cf5e0fd & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The study compared the performance of different models without naming any, referring to them generically. & ["NA"] 
 & ok & No violation.
OK\\
\hline
cf5e0fd & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The study compared the performance of different models without naming any, referring to them generically. & [["NA"]] & err & The chatbot's output is a nested array `[["NA"]]` instead of a single-level array `["NA"]` as specified in the description.
ERR\\
\hline
cf5e0fd & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The study compared the performance of different models without naming any, referring to them generically. & I'm sorry I can't fulfill your request. The abstracts appear to be fictional and do not describe actual scientific studies or papers. Is there anything else I can help you with? & err & The chatbot's response does not adhere to the specified format of returning an array of model names or ["NA"]. Instead, it provides a conversational reply, which is not compliant with the expected output structure.

ERR\\
\hline
7dc80ef & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Our research relies on the LightWave model to process audio data effectively. & ["LightWave"] & ok & No violation.
OK\\
\hline
7dc80ef & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Our research relies on the LightWave model to process audio data effectively. & ["LightWave"] 
 & ok & The chatbot output is a list containing a single model name in the correct format. It complies with the required response format specified in the description.
OK\\
\hline
7dc80ef & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our research relies on the LightWave model to process audio data effectively. & [["LightWave"]] & err & The chatbot's output is a nested array `[["LightWave"]]`, whereas the description specifies that the response should be a single-level array `["model_name"]`.
ERR\\
\hline
7dc80ef & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Our research relies on the LightWave model to process audio data effectively. & ["LightWave"] & ok & The chatbot's output is a properly formatted array containing a single string, adhering to the required structure.
OK\\
\hline
67ccc8e & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The introduced HybridNet combines elements of both CNN and RNN models to achieve better performance. & ["HybridNet", "CNN", "RNN"] & ok & No violation.
OK\\
\hline
67ccc8e & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The introduced HybridNet combines elements of both CNN and RNN models to achieve better performance. & ["HybridNet"] 
 & ok & The chatbot's output is a correctly formatted array containing a single string, which aligns with the specified response format.

OK\\
\hline
67ccc8e & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The introduced HybridNet combines elements of both CNN and RNN models to achieve better performance. & [["HybridNet"]] & err & The output is a nested array [["HybridNet"]] instead of a single array ["HybridNet"] as specified in the description.
ERR\\
\hline
67ccc8e & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The introduced HybridNet combines elements of both CNN and RNN models to achieve better performance. & [] & err & The output is an empty array `[]` instead of `["NA"]` when no model names are found or there is uncertainty, which does not comply with the specified format.
ERR\\
\hline
64301f5 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: We assess the scalability of our system without relying on any particular machine learning model. & ["NA"] & ok & The output is correctly formatted as an array with a single string "NA", which aligns with the description's guidance to return ["NA"] when no model names are found or there is uncertainty.

OK\\
\hline
64301f5 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: We assess the scalability of our system without relying on any particular machine learning model. & [\"NA\"] 
 & ok & No violation.
OK\\
\hline
64301f5 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: We assess the scalability of our system without relying on any particular machine learning model. & [["NA"]] & err & The chatbot's output is [["NA"]], which is a nested array. According to the description, the response should be a single array of strings like ["NA"]. The extra level of nesting does not comply with the specified format.

ERR\\
\hline
64301f5 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: We assess the scalability of our system without relying on any particular machine learning model. & The following array contains either 'NA' since no models were found in both instances.

 [ "NA" , "NA" ] & err & The chatbot provided multiple "NA" entries in the array, whereas the description specifies returning a single ["NA"] when no model names are found or if unsure.

ERR\\
\hline
20c2f43 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: The proposed DeepQuantum model leverages quantum computing principles for advanced data analysis. & ["DeepQuantum"] & ok & The chatbot's output is an array containing a single string, which aligns with the required format of `["model_name"]`. There are no formatting violations or deviations from the specified response structure.

OK\\
\hline
20c2f43 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: The proposed DeepQuantum model leverages quantum computing principles for advanced data analysis. & ["DeepQuantum"] 
 & ok & No violation.
OK\\
\hline
20c2f43 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: The proposed DeepQuantum model leverages quantum computing principles for advanced data analysis. & [["DeepQuantum"]] & err & The chatbot's output is a nested array `[["DeepQuantum"]]` instead of a single array `["DeepQuantum"]`, which does not comply with the required format.
ERR\\
\hline
20c2f43 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: The proposed DeepQuantum model leverages quantum computing principles for advanced data analysis. & [\"DeepQuantum\", \"None\"] & err & The chatbot's output includes the string "None" instead of the specified "NA" when no model names are found. According to the description, if no model names are found or there is uncertainty, the response should be ["NA"]. Using "None" deviates from this requirement.

ERR\\
\hline
5a42637 & a253756 & NaN &  & 1 & gpt-4o-mini &  & Abstract: Utilizing the standard Logistic Regression model, we evaluate its effectiveness in binary classification tasks. & ["Logistic Regression"] & ok & No violation.
OK\\
\hline
5a42637 & a253756 & NaN &  & 1 & gemma2:9b &  & Abstract: Utilizing the standard Logistic Regression model, we evaluate its effectiveness in binary classification tasks. & ["Logistic Regression"] 
 & ok & No violation.
OK\\
\hline
5a42637 & a253756 & NaN &  & 1 & qwen2.5:3b &  & Abstract: Utilizing the standard Logistic Regression model, we evaluate its effectiveness in binary classification tasks. & [["Logistic Regression"]] & err & The chatbot's output is [["Logistic Regression"]], which introduces an unnecessary nested array. According to the description, the response should be a single array of model names in the format ["model_name"], not a nested array.
ERR\\
\hline
5a42637 & a253756 & NaN &  & 1 & llama3.2:1b &  & Abstract: Utilizing the standard Logistic Regression model, we evaluate its effectiveness in binary classification tasks. & Here is the extracted model name: [["Logistic Regression"]]

Because there are two instances of the same statement with slight variation (using "binary" instead of "classification"), I return:

[["Logistic Regression", "Binary Classification"]] & err & The chatbot's output includes additional explanatory text and uses nested arrays instead of a single array of model names as specified in the description.

ERR
  \end{tabular}
  \caption{Test results and compliance}
  
  \end{table}
  