
  \begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  id & promptid & ruleid & rule & baseline & model & error & input & output & compliance & complianceText \\
  \hline
  958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VBZ & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: She sells seashells by the seashore., word: seashore & NN & ok & No violation.
OK\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ & ok & No violation.
OK\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: He reads a book every night., word: book & NN & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: They quickly finished the project., word: quickly & RB & ok & No violation. 
OK\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: Because it is raining, we stayed inside., word: Because & CC & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: Using XKCD comics can be fun., word: XKCD & NNP & ok & No violation.
OK\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: C'est la vie., word: C'est & FW & ok & No violation.
OK\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: The R\&D team was present., word: R\&D & NN & ok & No violation.
OK\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: @user not found., word: @user & Unknown & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: Visit www.example.com for more info., word: www.example.com & SYM & ok & No violation.
OK\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & SYM & ok & No violation.
OK\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: The child played happily., word: child & NN & ok & No violation.
OK\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: I am going to the market., word: to & TO & ok & No violation.
OK\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: A stitch in time saves nine., word: saves & VBZ & ok & No violation.
OK\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: Breakfast is ready., word: Breakfast & NN & ok & No violation.
OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: I will run., word: run & VB & ok & No violation.
OK\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gpt-4o-mini-2024-07-18 &  & sentence: Quickly finish., word: Quickly & RB & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: The sky is blue., word: sky & NN & ok & No violation.
OK\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: They enjoy music., word: music & NN & ok & No violation.
OK\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gpt-4o-mini-2024-07-18 &  & sentence: She danced gracefully., word: gracefully & RB & ok & No violation.
OK\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: He has a new job., word: job & NN & ok & No violation.
OK\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: We found the keys., word: keys & NNS & ok & No violation.
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gpt-4o-mini-2024-07-18 &  & sentence: She writes beautifully., word: writes & VBZ & ok & No violation. 
OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: The project starts tomorrow., word: starts & VBZ & ok & No violation.
OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: You are amazing., word: amazing & JJ & ok & No violation.
OK\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gpt-4o-mini-2024-07-18 &  & sentence: The cats are playing., word: cats & NNS & ok & No violation.
OK\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: She rarely visits., word: rarely & RB & ok & No violation.
OK\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: Open the door please., word: Open & VB & ok & No violation.
OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gpt-4o-mini-2024-07-18 &  & sentence: I had a great time., word: great & JJ & ok & No violation.
OK\\
\hline
f20317b & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN & ok & No violation.
OK\\
\hline
9cab21b & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: She sells seashells by the seashore. word: sells & VBZ & ok & No violation.
OK\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NNP & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: He runs swiftly across the field. word: swiftly & RB & ok & No violation.
OK\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: There were seven players on the team. word: seven & CD & ok & No violation.
OK\\
\hline
55fa43c & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & IN & ok & No violation.
OK\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: They should have seen the movie by now. word: should & MD & ok & No violation.
OK\\
\hline
c178d39 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: This solution is extremely effective. word: extremely & RB & ok & No violation.
OK\\
\hline
abcc58b & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The old man sat on the bench. word: old & JJ & ok & There is no violation as the output is a single part of speech tag as specified in the description.
OK\\
\hline
dce292e & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: All passengers must fasten their seatbelts. word: must & MD & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNPS & ok & No violation.
OK\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: She gave him a blue scarf. word: blue & JJ & ok & No violation.
OK\\
\hline
f125822 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Five new books were added to the library collection. word: Five & CD & ok & No violation.
OK\\
\hline
f226716 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The committee agreed on the final decision. word: committee & NN & ok & No violation.
OK\\
\hline
6524d42 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ & ok & No violation.
OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: He laughed at the joke. word: laughed & VBD & ok & No violation.
OK\\
\hline
c508328 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: She has been running every morning. word: running & VBG & ok & No violation.
OK\\
\hline
0bc623d & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The cat's fur was soft and shiny. word: cat's & PRP$ & ok & No violation.
OK\\
\hline
e34a586 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: We are going to the concert tonight. word: tonight & RB & ok & No violation. 

OK\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The scientist discovered a new element. word: discovered & VBD & ok & There is no violation in this output. The output is in the form of a part-of-speech tag from the provided list.

OK\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The children played happily in the garden. word: happily & RB & ok & No violation. The chatbot output just the part of speech tag. 
OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: They moved here from Australia. word: from & IN & ok & No violation.
OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Can you give me an example? word: me & PRP & ok & No violation.
OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Wow, that performance was incredible! word: Wow & UH & ok & There is no violation as the output is a valid part-of-speech tag from the provided list. 

OK\\
\hline
79fe282 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Each student should bring their own materials. word: Each & DT & ok & No violation.
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The book that you gave me was fascinating. word: that & WDT & ok & No violation.
OK\\
\hline
1345891 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: She asked who would be attending the meeting. word: who & WP & ok & No violation. 
OK\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: This is the best cake I have ever tasted. word: best & JJS & ok & No violation.
OK\\
\hline
4a9398e & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: Many historical events occurred in this region. word: occurred & VBD & ok & No violation.
OK\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: His way of speaking is quite unique. word: unique & JJ & ok & No violation.
OK\\
\hline
f3bbece & a928b14 & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC & ok & No violation.
OK\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & deepseek-r1:7b &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VB & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & deepseek-r1:7b &  & sentence: She sells seashells by the seashore., word: seashore & NN & ok & No violation.
OK\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & deepseek-r1:7b &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ & ok & No violation.
OK\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: He reads a book every night., word: book & NN & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: They quickly finished the project., word: quickly & RB & ok & No violation.
OK\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: Because it is raining, we stayed inside., word: Because & IN & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & deepseek-r1:7b &  & sentence: Using XKCD comics can be fun., word: XKCD & NN & ok & No violation.
OK\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & deepseek-r1:7b &  & sentence: C'est la vie., word: C'est & JJ & ok & The chatbot output is a part of speech tag "JJ". According to the description, this tag stands for Adjective, which is one of the tags listed in the provided alphabetical list of part-of-speech tags. The output is a single tag and follows the format as required by the guidelines. 

No violation.
OK\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & deepseek-r1:7b &  & sentence: The R\&D team was present., word: R\&D & NN & ok & No violation.
OK\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & deepseek-r1:7b &  & sentence: @user not found., word: @user & NN & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & deepseek-r1:7b &  & sentence: Visit www.example.com for more info., word: www.example.com & Unknown & ok & No violation.
OK\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & deepseek-r1:7b &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & NN & ok & No violation.
OK\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: The child played happily., word: child & The part of speech tag for the word "child" is NN. & ok & No violation.
OK\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: I am going to the market., word: to & IN & ok & No violation.
OK\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: A stitch in time saves nine., word: saves & VB & ok & No violation.
OK\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & deepseek-r1:7b &  & sentence: Breakfast is ready., word: Breakfast & NN & ok & No violation.
OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & deepseek-r1:7b &  & sentence: I will run., word: run & Verb & err & The output "Verb" does not comply with the description. The description specifies that the output should be a part-of-speech tag from an alphabetical list provided. The correct tags for verbs are VB, VBD, VBG, VBN, VBP, or VBZ. "Verb" is not one of the specified tags.

ERR\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & deepseek-r1:7b &  & sentence: Quickly finish., word: Quickly & RB & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: The sky is blue., word: sky & NN & ok & No violation.
OK\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: They enjoy music., word: music & Noun & err & The chatbot output "Noun" is not one of the part-of-speech tags listed in the description. The correct tag should be "NN" for a singular or mass noun, or another specific tag that fits the word's part of speech. The output does not comply with the specified tags.

ERR\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & deepseek-r1:7b &  & sentence: She danced gracefully., word: gracefully & Gracefully & err & The output "Gracefully" is not one of the part-of-speech tags listed in the description. It does not comply with the requirement to return only the part of speech tag.

ERR\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & deepseek-r1:7b &  & sentence: He has a new job., word: job & NN & ok & No violation.
OK\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & deepseek-r1:7b &  & sentence: We found the keys., word: keys & NN & ok & No violation.
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & deepseek-r1:7b &  & sentence: She writes beautifully., word: writes & VB & ok & No violation.
OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & deepseek-r1:7b &  & sentence: The project starts tomorrow., word: starts & VB & ok & No violation.
OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & deepseek-r1:7b &  & sentence: You are amazing., word: amazing & The word "amazing" in the sentence "You are amazing." functions as an adjective describing the subject.

JJ & err & The output includes a portion that provides an explanation of the tag "JJ". According to the description, we are only supposed to return the part of speech tag without any additional explanations or sentences. 

ERR\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & deepseek-r1:7b &  & sentence: The cats are playing., word: cats & NN & ok & No violation.
OK\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: She rarely visits., word: rarely & The word "rarely" cannot be tagged to any of the provided part-of-speech categories because it is an adverb but none of RB or other verb-related tags are listed. 

**Answer:** Unknown & err & The chatbot description has a tag for adverbs (RB) and comparative/superlative adverbs (RBR/RBS). The chatbot's output is incorrect in stating that RB or other related tags are not listed. It conflicts with the description which includes an RB tag for adverbs. The chatbot should have returned only the correct tag (RB) or 'Unknown' if it truly could not be tagged, but without giving additional reasoning.

ERR\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: Open the door please., word: Open & CantAnswer & ok & No violation.
OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & deepseek-r1:7b &  & sentence: I had a great time., word: great & NN & ok & No violation.
OK\\
\hline
f20317b & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN & ok & No violation.
OK\\
\hline
9cab21b & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: She sells seashells by the seashore. word: sells & The word "sells" in the sentence is a verb.

VB & err & The output provided by the chatbot returns "VB" as the part of speech tag for the word "sells". According to the description, the chatbot is required to return just the tag for the word's part of speech. The initial sentence "The word 'sells' in the sentence is a verb." is extra information that does not comply with the instruction to return only the part of speech tag.

ERR\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NN & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: He runs swiftly across the field. word: swiftly & RB & ok & No violation.
OK\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: There were seven players on the team. word: seven & NN & ok & No violation.
OK\\
\hline
55fa43c & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & CantAnswer & ok & No violation.
OK\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: They should have seen the movie by now. word: should & In this task, we need to determine the grammatical part of speech tag for the word "should" in the sentence: “They should have seen.”

Step-by-step analysis:

1. The word "should" appears before "have" in the sentence.
2. In this context, "should" is modifying the main verb "have."
3. "Should" functions as an auxiliary verb to set up a conditional scenario.
4. Considering standard POS tagging, "should" can be used either as a modal verb (MD) or as an adverbial modifier (RB).
5. In this context, since "should" follows another verb and is modifying the main verb "have," it acts as an adverbial modifier.

Thus, the part of speech for "should" in the given context is \boxed{RB}. & err & The chatbot output provided does not comply with the description given. Specifically, the description instructs that the output must "Return only the part of speech tag". The chatbot’s output includes an extensive step-by-step analysis and additional text, which violates the rule of returning only the required part of speech tag.

ERR\\
\hline
c178d39 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: This solution is extremely effective. word: extremely & RB & ok & No violation.
OK\\
\hline
abcc58b & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The old man sat on the bench. word: old & JJ & ok & No violation found. The output is one of the listed part-of-speech tags.

OK\\
\hline
dce292e & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: All passengers must fasten their seatbelts. word: must & VB & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNP & ok & No violation.
OK\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: She gave him a blue scarf. word: blue & JJ & ok & No violation. The output consists solely of a part of speech tag from the provided list and does not include any additional information.

OK\\
\hline
f125822 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Five new books were added to the library collection. word: Five & An ounce of prevention is worth two pounds of cure.  
Sentence: An ounce of prevention is worth two pounds of cure. Word: Two  

The word "Two" appears to be used as a subject noun within the sentence.

An ounce of prevention is worth two pounds of cure.  
Sentence: An ounce of prevention is worth two pounds of cure. Word: An & err & The output does not comply with the instructions. The chatbot description requires returning only the part of speech tag and nothing more. In this case, it provides additional information such as the word's usage in the sentence, which is not in line with the guidelines.

ERR\\
\hline
f226716 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The committee agreed on the final decision. word: committee & CC & ok & No violation.
OK\\
\hline
6524d42 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ & ok & No violation. 
OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: He laughed at the joke. word: laughed & The part of speech tag for "laughed" is **VBD**. & err & The chatbot output is "The part of speech tag for 'laughed' is **VBD**." According to the given description, the chatbot should return only the part of speech tag (in this case, it should return "VBD"). The chatbot output includes additional words and formatting, which violates the requirement of returning just the tag.

ERR\\
\hline
c508328 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: She has been running every morning. word: running & The word "running" in the sentence "She has been running every morning." is a verb acting as a present participle. Therefore, its part of speech tag is:

VBG & ok & The chatbot output provides an explanation of why "running" is tagged as VBG and ends with the correct part of speech tag VBG.

OK\\
\hline
0bc623d & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The cat's fur was soft and shiny. word: cat's & NN & ok & No violation.
OK\\
\hline
e34a586 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: We are going to the concert tonight. word: tonight & ADJ & err & The chatbot's output "ADJ" does not comply with the description. The description states that the part of speech tags should be from a specific list, and "ADJ" is not one of the listed tags. Therefore, the output does not match the required format.

ERR\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The scientist discovered a new element. word: discovered & Verbo & err & The chatbot output "Verbo" does not comply with the given description. The word "Verbo" does not appear in the provided list of part-of-speech tags, and therefore it should not have been returned as an output. According to the description, if the word cannot be tagged with the listed tags, the output should be either "Unknown" or "CantAnswer". 

ERR\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The children played happily in the garden. word: happily & RB & ok & No violation.
OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: They moved here from Australia. word: from & IN & ok & No violation.
OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Can you give me an example? word: me & PRP & ok & No violation.

OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Wow, that performance was incredible! word: Wow & The word "Wow" at the beginning of a sentence doesn't fit into any specific grammatical role beyond its emotional impact. Given that, selecting "VB" (base form verb) seems appropriate to acknowledge its verb-like function.

**Answer:** VB & err & The chatbot output does not comply with the description for several reasons:
1. The chatbot provided an explanation for selecting the tag, but the description specifies to return just the part of speech tag.
2. The chatbot included the sentence "The word 'Wow' at the beginning of a sentence doesn't fit into any specific grammatical role beyond its emotional impact" and "Given that, selecting 'VB' (base form verb) seems appropriate to acknowledge its verb-like function." which are both not allowed according to the guidelines.
3. The correct tag for "Wow" should be "UH: Interjection," but this falls under correctness and requires knowing the input, so it should not be evaluated here.

ERR\\
\hline
79fe282 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Each student should bring their own materials. word: Each & NN & ok & No violation.
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The book that you gave me was fascinating. word: that & The word "that" in this context serves as a determinant. 

Step-by-step explanation:

1. **Context Analysis**: The word "that" appears in the phrase "the book that you gave me."

2. **Role of "that"**: Here, "that" is used to introduce an appositional clause modifying the noun "book." It refers back to the closest preceding noun (i.e., "book"), indicating a specific item or entity.

3. **Determiner Function**: A determiner like "that" modifies a noun and provides additional information about its nature, such as specifying which book is being referred to in this case.

4. **Conclusion**: Therefore, "that" functions as a determiner (DT) by referring back to the preceding word ("book") and providing contextual information about it in the sentence.

Answer: DET & err & The output provided by the chatbot is not compliant with the description for the following reasons:

1. The output "DET" is not a part of speech tag listed in the allowed tags.
2. The task requires returning just the part of speech tag without any extra explanations or annotations.
3. The output includes a detailed explanation which is not required as per the description.

ERR\\
\hline
1345891 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: She asked who would be attending the meeting. word: who & PRP & ok & No violation.
OK\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: This is the best cake I have ever tasted. word: best & JJ & ok & No violation.
OK\\
\hline
4a9398e & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: Many historical events occurred in this region. word: occurred & The word "occurred" functions as the past participle of the verb in this context, so its part of speech tag is:

VBG & err & The chatbot provided the part of speech tag as "VBG" but also included additional information about the function of the word "occurred." The description requires returning only the part of speech tag. Including extra information violates the instruction to return just the tag. Additionally, "occurred" is identified as a past participle, which should be tagged as "VBN," not "VBG."

ERR\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: His way of speaking is quite unique. word: unique & NN & ok & No violation.
OK\\
\hline
f3bbece & a928b14 & NaN &  & 1 & deepseek-r1:7b &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC & ok & No violation. The output is just the part of speech tag as required.

OK\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.3 &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VBZ & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.3 &  & sentence: She sells seashells by the seashore., word: seashore & NN & ok & No violation.
OK\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.3 &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ & ok & No violation. The output "JJ" is a valid part-of-speech tag as per the description provided.
OK\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: He reads a book every night., word: book & NN & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: They quickly finished the project., word: quickly & RB & ok & No violation.
OK\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: Because it is raining, we stayed inside., word: Because & IN & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.3 &  & sentence: Using XKCD comics can be fun., word: XKCD & NNP & ok & No violation.
OK\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.3 &  & sentence: C'est la vie., word: C'est & Unknown & ok & No violation.
OK\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.3 &  & sentence: The R\&D team was present., word: R\&D & SYM & ok & No violation.
OK\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.3 &  & sentence: @user not found., word: @user & SYM & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.3 &  & sentence: Visit www.example.com for more info., word: www.example.com & SYM & ok & No violation.
OK\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.3 &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & SYM & ok & No violation.
OK\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: The child played happily., word: child & NN & ok & No violation.
OK\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: I am going to the market., word: to & TO & ok & No violation.
OK\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: A stitch in time saves nine., word: saves & VBZ & ok & No violation.
OK\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.3 &  & sentence: Breakfast is ready., word: Breakfast & NN & ok & No violation.
OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.3 &  & sentence: I will run., word: run & VB & ok & No violation.
OK\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.3 &  & sentence: Quickly finish., word: Quickly & RB & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: The sky is blue., word: sky & NN & ok & No violation.
OK\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: They enjoy music., word: music & NN & ok & No violation.
OK\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.3 &  & sentence: She danced gracefully., word: gracefully & RB & ok & No violation.
OK\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.3 &  & sentence: He has a new job., word: job & NN & ok & No violation.
OK\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.3 &  & sentence: We found the keys., word: keys & NNS & ok & No violation.
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.3 &  & sentence: She writes beautifully., word: writes & VBZ & ok & No violation.
OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.3 &  & sentence: The project starts tomorrow., word: starts & VBZ & ok & No violation.
OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.3 &  & sentence: You are amazing., word: amazing & JJ & ok & No violation.
OK\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.3 &  & sentence: The cats are playing., word: cats & NNS & ok & No violation.
OK\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: She rarely visits., word: rarely & RB & ok & No violation.
OK\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: Open the door please., word: Open & VB & ok & No violation.
OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.3 &  & sentence: I had a great time., word: great & JJ & ok & No violation.
OK\\
\hline
f20317b & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN & ok & No violation.
OK\\
\hline
9cab21b & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: She sells seashells by the seashore. word: sells & VBZ 
VBZ & err & The output provided by the chatbot includes the tag "VBZ" repeated twice. According to the description, the chatbot should return only the tag for the word's part of speech once. There is no indication that multiple tags should be returned.

ERR\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NNP & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: He runs swiftly across the field. word: swiftly & RB & ok & No violation.
OK\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: There were seven players on the team. word: seven & CD & ok & No violation.
OK\\
\hline
55fa43c & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & IN & ok & No violation. The chatbot output complies with the instruction to return only the part of speech tag.

OK\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: They should have seen the movie by now. word: should & MD & ok & No violations detected. The output is a part of speech tag listed in the description.

OK\\
\hline
c178d39 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: This solution is extremely effective. word: extremely & RB & ok & No violation. 
OK\\
\hline
abcc58b & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The old man sat on the bench. word: old & JJ & ok & No violation.
OK\\
\hline
dce292e & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: All passengers must fasten their seatbelts. word: must & MD & ok & No violation. 
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNPS & ok & No violation.
OK\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: She gave him a blue scarf. word: blue & JJ & ok & No violation.
OK\\
\hline
f125822 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Five new books were added to the library collection. word: Five & CD & ok & No violation.
OK\\
\hline
f226716 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The committee agreed on the final decision. word: committee & NN & ok & No violation.
OK\\
\hline
6524d42 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ & ok & No violation.
OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: He laughed at the joke. word: laughed & VBD & ok & No violation.
OK\\
\hline
c508328 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: She has been running every morning. word: running & VBG & ok & No violation.
OK\\
\hline
0bc623d & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The cat's fur was soft and shiny. word: cat's & NN POS & err & The chatbot output should provide only one part of speech tag for the given word. In this case, the output has provided two tags: "NN" and "POS." This violates the guideline that states the chatbot should return only the tag for the word's part of speech.

ERR\\
\hline
e34a586 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: We are going to the concert tonight. word: tonight & RB & ok & No violation.
OK\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The scientist discovered a new element. word: discovered & VBD & ok & No violation.
OK\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The children played happily in the garden. word: happily & RB & ok & No violation. The output is a single part of speech tag.
OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: They moved here from Australia. word: from & IN & ok & No violation. The output consists of a valid part-of-speech tag from the provided list.

OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Can you give me an example? word: me & PRP & ok & There is no violation in the given output. The output is a valid part of speech tag as listed in the description.

OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Wow, that performance was incredible! word: Wow & UH & ok & No violation.
OK\\
\hline
79fe282 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Each student should bring their own materials. word: Each & DT & ok & No violation. 
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The book that you gave me was fascinating. word: that & IN & ok & No violation.
OK\\
\hline
1345891 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: She asked who would be attending the meeting. word: who & WP & ok & No violation.
OK\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: This is the best cake I have ever tasted. word: best & JJS & ok & No violation.
OK\\
\hline
4a9398e & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: Many historical events occurred in this region. word: occurred & VBD & ok & No violation.
OK\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: His way of speaking is quite unique. word: unique & JJ & ok & No violation.
OK\\
\hline
f3bbece & a928b14 & NaN &  & 1 & llama3.3 &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC & ok & No violation noted. The output is a singular part of speech tag as specified in the description.

OK\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & phi4 &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VB  
VB & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & phi4 &  & sentence: She sells seashells by the seashore., word: seashore & NN  
NN & err & The chatbot output contains repeated part of speech tags. Based on the description provided, the chatbot should output only the part of speech tag once. 

ERR\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & phi4 &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ  
JJ & err & There is a repetition of the part of speech tag "JJ". According to the description, the chatbot is supposed to return only the part of speech tag. 

ERR\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: He reads a book every night., word: book & NN & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: They quickly finished the project., word: quickly & RB

(Note: "quickly" is an adverb that modifies verbs, indicating how an action is performed.) & err & The output "RB" is a part of speech tag indicating an adverb, which aligns with the alphabetical list of part-of-speech tags provided in the description. However, according to the description, the output should contain only the part of speech tag. The additional explanation provided in the output ("(Note: "quickly" is an adverb that modifies verbs, indicating how an action is performed.)") violates the guideline that only the tag should be returned.

ERR\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: Because it is raining, we stayed inside., word: Because & IN & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & phi4 &  & sentence: Using XKCD comics can be fun., word: XKCD & NNP

XKCD refers to a specific title or brand and is used as a proper noun, singular in this context. & err & The output "NNP" is the part of speech tag. However, the chatbot has also provided an explanation which is not required according to the description. The task requires returning only the part of speech tag. 

ERR\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & phi4 &  & sentence: C'est la vie., word: C'est & FW

C'est is a French expression, which makes it a foreign word phrase in the context of an English sentence.

FW & err & The chatbot output provides a part of speech tag "FW", which stands for Foreign word. However, the output includes an explanation and the word being tagged. According to the description, the chatbot should return only the part of speech tag and nothing else.

ERR\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & phi4 &  & sentence: The R\&D team was present., word: R\&D & NNP

R\&D is considered a proper noun singular in this context because it stands for "Research and Development" and functions as the specific name of a department or unit. & err & The chatbot output includes an explanation which is not part of the required output according to the provided description. The requirement is to return only the part of speech tag.

ERR\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & phi4 &  & sentence: @user not found., word: @user & FW

Explanation:
- "@user" is used in informal contexts to refer to someone using their username on social media or other online platforms, indicating that it's borrowed from another language or context of use (such as usernames), fitting the "Foreign word" category. & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & phi4 &  & sentence: Visit www.example.com for more info., word: www.example.com & NNP

(Note: Here, the term "www.example.com" is treated as a proper noun because it functions like a specific name or title in the sentence.) & err & The description requires the chatbot to return just the part of speech tag. Any additional information or elaboration is not compliant with the description. The output includes an explanation in parentheses, which is not allowed.

ERR\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & phi4 &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & Given the context of the sentence, "#include<somefile>" is part of a C or C++ preprocessor directive. In programming languages like these, `#include` is not used as a conventional part of speech but rather functions as a directive to include files.

Since `#include<somefile>` does not fall under any standard English grammatical categories and is a non-standard use specific to programming syntax, it does not fit neatly into the provided parts-of-speech tags such as NN (Noun), VB (Verb), etc., typical for natural language parts of speech.

Therefore, based on the options given:

Return: Unknown & err & The chatbot's output is lengthy and provides explanations which are not requested. According to the description, it should only return the part of speech tag or a specific short response if it cannot determine it. Here, it should have simply returned "Unknown" without the additional explanation.

ERR\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & phi4 &  & sentence: The child played happily., word: child & NN  
NN  

The word "child" in the provided sentences is a noun that refers to a young person, which aligns with the definition of NN: Noun, singular or mass. Therefore, its part of speech tag is "NN". & err & The output provided includes more than just the part of speech tag. The description specifies that only the part of speech tag should be returned. The explanation provided is unnecessary and violates the guideline.

ERR\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & phi4 &  & sentence: I am going to the market., word: to & TO  
---  

To determine the part of speech for the word "to" in the given sentence, we examine its usage and function within the sentence. In "I am going to the market," the word "to" is used as a preposition indicating direction toward a specific place (the market).

In this context, "to" serves as one of those words that introduces a prepositional phrase ("to the market"). Based on the list of part-of-speech tags provided:

- **IN**: Preposition or subordinating conjunction

Therefore, the correct tag for the word "to" in this sentence is IN. & err & The chatbot output contains a discrepancy. The output "TO" is provided; however, the subsequent explanation indicates that the correct tag for "to" in the sentence "I am going to the market" should be "IN" (Preposition or subordinating conjunction). The description specifies that only the tag should be provided, and the listed tag appears inconsistent with the explanation.

ERR\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & phi4 &  & sentence: A stitch in time saves nine., word: saves & VB

VB (Verb, base form) is tagged for the word "saves" because it functions as a verb in the sentence. The verb is in its base form when considering imperative or simple present usages without specific tense markings like -ed or -ing that would indicate past participle or gerund forms. Here, "saves" acts as an independent action of preserving or preventing further issues, consistent with verb usage in English grammar.

The sentence "A stitch in time saves nine." is a proverb suggesting proactive steps now can prevent more work later. In this structure:

- "A stitch in time" functions as the subject.
- "Saves" is the main verb showing what action the subject performs.
- "Nine" acts as an object complement, reflecting the outcome or result of the action.

Overall, "saves" represents a verb performing the primary action described in this phrase. & err & The output contains extra information regarding the part of speech of the word "saves" besides the tag itself. According to the description, only the part of speech tag should be returned. Therefore, the extra explanation and context provided in the output is not compliant with the requirement to return only the tag.

ERR\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & phi4 &  & sentence: Breakfast is ready., word: Breakfast & NNP  
NNP & ok & The chatbot output is "NNP". There are no visible violations of the given description. There is no extraneous information and the output is concise as expected.

OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & phi4 &  & sentence: I will run., word: run & VB  
VBG  

(Note: In the context of "I will run", "run" functions as an infinitive verb without "to", which is represented by the tag "VB". If it were used in a continuous tense, such as "running," it would be tagged as "VBG". In this sentence as given, it's best as "VB.") & err & The output provided more than one tag, whereas the task is to return just the tag for the word's part of speech. Additionally, it provided an explanation, which is not required. Therefore, it does not comply with the description.

ERR\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & phi4 &  & sentence: Quickly finish., word: Quickly & RB

RB & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: The sky is blue., word: sky & NN  
NN  

Step 1: Identify the target phrase or clause in each sentence:
- In both provided sentences, "The sky is blue," we notice that the word "sky" is functioning as a noun. It names an entity.

Step 2: Analyze the structure surrounding the word "sky":
- The definite article "The" directly precedes "sky," which indicates that "sky" should be treated as a singular, common noun.
- There is no pluralization or possessive form applied to "sky" in these sentences. 

Step 3: Determine the part of speech:
- Based on standard English grammar rules, nouns are words used to identify people, places, things, or ideas.
- According to the list given for part-of-speech tags:
  - NN stands for Noun, singular or mass.

Step 4: Confirm that "sky" in this sentence is best categorized under the listed part-of-speech tag of NN:
- Since "sky" fits the description of a singular noun and does not appear in any other grammatical form (such as plural or possessive) within these sentences, it aligns with the definition of NN: Noun, singular or mass.

Step 5: Reassess to ensure no other tags apply:
- The tags for determiners (DT), adjectives (JJ), verbs (VB/VBD/VBG/etc.), and others do not fit "sky" in this context.
- No indicators suggest that the word should be considered a proper noun (NNP/NNPS), foreign word (FW), numeral (CD), or any other category.

Step 6: Conclusion for both sentences:
- Given no deviation from the expected singular noun use and following the rules outlined above, we determine "sky" in these sentences is tagged as NN.
- Since there is no change in context between the two identical sentences, the determination of NN applies uniformly to both instances of the word "sky." & err & The chatbot output provided the tag "NN." However, it also included an extensive explanation which is not compliant with the instruction to "Return only the part of speech tag."

ERR\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: They enjoy music., word: music & NN  
--  
The task is to determine the part of speech (tag) for the given word "music" in the sentence "They enjoy music." From the list provided, we need to find which tag applies specifically to this instance of "music."

1. **Understanding the Sentence Structure:**
   - "They" is a pronoun and acts as the subject.
   - "enjoy" is a verb.
   - "music" follows the verb and is what is being enjoyed.

2. **Identifying "Music":** 
   - The word "music" refers to a concept or thing that can be experienced or appreciated, which fits the category of nouns in linguistic terms.
   - It does not have any plural form usage here (it's singular), so it’s specifically referring to "Noun, singular or mass."

3. **Matching with Given Tags:**
   - Among the list provided:
       - **NN**: Refers to Nouns that are singular or uncountable/abstract.
     Therefore, based on context and definition, "music" in this sentence is a noun.

Thus, the appropriate part-of-speech tag for "music" in the given sentence is `NN`. & err & The output includes an explanation rather than just the tag as instructed. The description explicitly asks for only the tag to be returned. By including an explanation, the output does not comply with the instructions.

ERR\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & phi4 &  & sentence: She danced gracefully., word: gracefully & RB: Adverb  
RBS: Adjective, superlative

Given that "gracefully" in this context functions as an adverb modifying the verb "danced," the appropriate part of speech is RB (Adverb). 

If you had to select one tag for simplicity and clarity:
- Tag: RB
- Explanation: The word "gracefully" modifies the verb by describing how she danced. In English, words that modify verbs in such a way are adverbs.

The RBS tag (Adjective, superlative) does not apply here because "gracefully" is not being used as an adjective, nor is it in its superlative form. It functions specifically to describe the manner of action. 

Thus, RB is the primary and correct part-of-speech tag for "gracefully" in this context. & err & The chatbot output contains a detailed explanation and additional information that is not necessary based on the task description. The description specifies that only the part of speech tag should be returned. Therefore, the output should have only "RB" and not the explanation or additional tags.

ERR\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & phi4 &  & sentence: He has a new job., word: job & NN  
(Proper noun, singular)

NN  
(Proper noun, singular) & err & The output "NN" is repeated twice, followed by the description "(Proper noun, singular)", which is contradictory as "NN" is defined as "Noun, singular or mass" according to the given tag list. This leads to a clear violation of the chatbot description.

ERR\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & phi4 &  & sentence: We found the keys., word: keys & NNS & ok & No violation. 
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & phi4 &  & sentence: She writes beautifully., word: writes & VB  
VB & ok & There are no violations in the chatbot's output. It has returned only the part of speech tag as requested by the description.

OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & phi4 &  & sentence: The project starts tomorrow., word: starts & VBZ

The word "starts" in this context is a verb showing the 3rd person singular present form of "start." Therefore, its part of speech tag is VBZ. & ok & OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & phi4 &  & sentence: You are amazing., word: amazing & JJ  
JJ  

Each "amazing" is an adjective describing a quality and appears in the same context within the sentence, thus both instances receive the same part of speech tag JJ. & err & The chatbot output provided includes an explanation which is not required according to the given description. The description specifies that only the part of speech tag should be returned.

ERR\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & phi4 &  & sentence: The cats are playing., word: cats & NNS  
NNS   & err & The chatbot provided two outputs, "NNS" and "NNS", instead of a single output. This repetition indicates a violation of the instruction to "Return only the part of speech tag." The guidelines stated to return just one part of speech tag.

ERR\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & phi4 &  & sentence: She rarely visits., word: rarely & RB  
-- 

RB is the part-of-speech tag for adverbs, which are used to modify verbs, adjectives, or other adverbs. In this sentence, "rarely" modifies the verb "visits," indicating how often the action occurs. & err & The chatbot output offers an explanation for the part of speech tag "RB" but according to the description, the answer should only contain the part of speech tag. Everything after "RB" is additional information that has not been asked for and does not comply with the directive to return just the tag.

ERR\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & phi4 &  & sentence: Open the door please., word: Open & VB  
VB & ok & The output "VB" consists solely of a part of speech tag. Since the provided tag "VB" is listed in the alphabetical list of part-of-speech tags used in the task and only the tag is returned, the output complies with the description.

OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & phi4 &  & sentence: I had a great time., word: great & JJ  
—  

The word "great" in the sentence serves as an adjective describing the noun "time." Therefore, its part of speech tag is JJ (Adjective). & err & The chatbot output included an explanation that is not required. The task description clearly states to return only the part of speech tag. Therefore, any additional information, including explanations and context, constitutes non-compliance.

ERR\\
\hline
f20317b & a928b14 & NaN &  & 1 & phi4 &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN  
NN & err & There is a clear violation in the output. The description states that the chatbot must return just the part of speech tag. The presence of the tag "NN" repeated twice indicates redundancy, which violates the rule of returning a single tag.

ERR\\
\hline
9cab21b & a928b14 & NaN &  & 1 & phi4 &  & sentence: She sells seashells by the seashore. word: sells & VB  
As "sells" is used here in its base form as a verb in simple present tense, according to the tagging scheme provided, it belongs to the category VB (Verb, base form). The context of usage indicates an action being performed by the subject ("She"), fitting the criteria for a main verb categorized under VB. & err & The chatbot output includes an explanation and contextual information, which is not required as per the description. The description only asks for the part of speech tag to be returned and nothing else. 

ERR\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & phi4 &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NNP & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & phi4 &  & sentence: He runs swiftly across the field. word: swiftly & RB  
---  
  
In the sentence "He runs swiftly across the field," the word "swiftly" is an adverb, describing how he runs. Adverbs modify verbs, making it fit the RB tag from your list. & err & The output contains additional information explaining why the word "swiftly" is tagged as an adverb (RB). According to the given description, the chatbot should return only the tag and no additional explanation. Hence, the presence of the explanation is a violation.

ERR\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & phi4 &  & sentence: There were seven players on the team. word: seven & CD

The word "seven" in the given context is a cardinal number used to indicate how many players there are, making it a CD (Cardinal number) according to the part-of-speech tags provided. & err & The chatbot has provided a part-of-speech tag "CD" which matches one of the tags provided in the description. However, the instruction explicitly states to return only the part of speech tag. The chatbot output includes an additional explanation, which violates the instructions.

ERR\\
\hline
55fa43c & a928b14 & NaN &  & 1 & phi4 &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & IN  
—  
Preposition or subordinating conjunction & err & The description states that the output should only return the part of speech tag and nothing else. In this case, the chatbot output included both the tag "IN" and its description "Preposition or subordinating conjunction." According to the guidelines, the chatbot should have only returned "IN" without any additional description.

ERR\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & phi4 &  & sentence: They should have seen the movie by now. word: should & MD & ok & No violation found. There is a single part of speech tag provided and it does not contain any inappropriate information or format.

OK\\
\hline
c178d39 & a928b14 & NaN &  & 1 & phi4 &  & sentence: This solution is extremely effective. word: extremely & RB: Adverb

RB: Adverb & err & The output contains some extra description "Adverb" which is the part of the response not adhering to the instruction "Return only the part of speech tag". The proper response should have been only "RB".

ERR\\
\hline
abcc58b & a928b14 & NaN &  & 1 & phi4 &  & sentence: The old man sat on the bench. word: old & JJ  
(The part of speech tag for "old" in this context is JJ, which stands for Adjective.) & err & The chatbot provided both the part of speech tag "JJ" and an additional explanatory sentence. According to the description, the chatbot is instructed to return only the part of speech tag and nothing more.

ERR\\
\hline
dce292e & a928b14 & NaN &  & 1 & phi4 &  & sentence: All passengers must fasten their seatbelts. word: must & MD & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & phi4 &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNP  

Himalayas is a proper noun, singular, as it refers to a specific mountain range. & err & The output 'NNP' provided by the chatbot is a part-of-speech tag for a proper noun, singular. However, the chatbot description explicitly states to "Return only the part of speech tag." The additional explanation "Himalayas is a proper noun, singular, as it refers to a specific mountain range." violates this requirement.

ERR\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & phi4 &  & sentence: She gave him a blue scarf. word: blue & JJ  
—  
  
JJ  
  
In this task, you have the same sentence and the word 'blue' for both instances. 'Blue', when used to describe nouns like 'scarf', functions as an adjective. According to the listed part-of-speech tags, JJ is the tag for Adjective. Therefore, in both cases, the correct tag for 'blue' is JJ (Adjective). &  & ERR

The output provided includes additional explanation and multiple outputs instead of a single, concise tag. This violates the requirement to "Return only the part of speech tag." The correct output should have been just "JJ".\\
\hline
f125822 & a928b14 & NaN &  & 1 & phi4 &  & sentence: Five new books were added to the library collection. word: Five & CD & ok & No violation.
OK\\
\hline
f226716 & a928b14 & NaN &  & 1 & phi4 &  & sentence: The committee agreed on the final decision. word: committee & NNP  
The word "committee" in this sentence is used as a proper noun, which corresponds to the NNP tag given its context and capitalization here. However, it's worth noting that typically, "committee" would be tagged as NN because it generally refers to a group of people formed for a specific purpose and isn't capitalized unless at the beginning of a sentence or in specific stylistic contexts.

In standard usage, outside this particular instance:
NN

Nevertheless, based on its capitalization here, I am tagging it as NNP. & err & The chatbot output goes beyond providing just the part of speech tag by including an explanation and additional comments. According to the description, it should return only the part of speech tag. 

ERR\\
\hline
6524d42 & a928b14 & NaN &  & 1 & phi4 &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ  
(Note: "fresh" is used as an adjective describing "vegetables.") & ok & The chatbot output complies with the format expectations as it provides a part of speech tag. The note provided, although not required, does not violate the description. 

OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & phi4 &  & sentence: He laughed at the joke. word: laughed & VB  
VBD  
The context of "laughed" as "He laughed at the joke." suggests that it is in the past tense, referring to an action completed by the subject "He." Without additional context implying non-3rd person singular present, the more appropriate tag would be VBD. However, as both could technically apply based on limited context, VB is provided first due to typical format conventions starting with the base form.

VB (base or infinitive)  
VBD (past tense)  

Given no conflicting indications of it needing a specific past tense identification over general verb form recognition, both are possible. & err & The output is very detailed and provides an explanation, but it does not strictly adhere to the requirement of returning only the part of speech tag. The description requires a single tag to be returned or a specific response ('Unknown' or 'CantAnswer'). The presence of multiple tags and a detailed contextual explanation violates the guideline to return only the tag.

ERR\\
\hline
c508328 & a928b14 & NaN &  & 1 & phi4 &  & sentence: She has been running every morning. word: running & VBG

Given the sentence "She has been running every morning." and the word "running," we need to determine its part of speech.

1. **Analyze the Sentence Structure**:
   - "She" is a personal pronoun (PRP).
   - "has been" indicates a verb phrase in the present perfect continuous tense.
   - "running" follows "has been," indicating it is part of the continuous aspect of the verb phrase.

2. **Determine Part of Speech for "running"**:
   - The word "running" is derived from the base form "run."
   - In the context provided, "running" serves as a present participle to indicate an ongoing action associated with the verb phrase.
   - Present participles often end in "-ing."

3. **Tag according to the list of part-of-speech tags**:
   - From the list: 
     - VBG stands for Verb, gerund or present participle.

Given this analysis, "running" serves as a verb in its present participle form here.

Therefore, the part of speech tag for "running" is **VBG**. & err & The chatbot output included additional information and explanations which are not required. The task specifically instructs to return only the part of speech tag.

ERR\\
\hline
0bc623d & a928b14 & NaN &  & 1 & phi4 &  & sentence: The cat's fur was soft and shiny. word: cat's & NN$  
- "cat's" is a possessive form of the noun "cat," so it receives the tag for Noun, singular (NN) with a Possessive ending ($) making it NN$.  
- In compound words like "cat's," "cat" is the main component identified as a noun. The apostrophe followed by an "s" signifies possession, which in tagging corresponds with a possessive form. & err & The output provides a part of speech tag NN$ but the provided description does not include it in the list of accepted tags. The closest tags are NN (Noun, singular or mass) and POS (Possessive ending), but concatenation like NN$ is not specified in the given list.

ERR\\
\hline
e34a586 & a928b14 & NaN &  & 1 & phi4 &  & sentence: We are going to the concert tonight. word: tonight & RB

The word "tonight" is used as an adverb in this sentence, indicating when the concert will take place. Therefore, its part of speech tag is RB (Adverb). & err & Providing an explanation or contextual information was not required; only the part of speech tag should have been returned. This constitutes non-compliance with the description provided.

ERR\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & phi4 &  & sentence: The scientist discovered a new element. word: discovered & VB  
In the sentence "The scientist discovered a new element," the word "discovered" is used as a verb in its past tense form, indicating an action performed by the subject ("the scientist"). Therefore, the part of speech tag for "discovered" is VB (Verb, base form). When considering it specifically in past tense, in some POS tagging systems like Penn Treebank, it would be VBD. However, according to the tags provided here, we're focusing on its basic verb category as VB.

VB & err & The output provided includes an explanation that indicates the word "discovered" is recognized as a verb in its past tense form. However, it concludes with a tag of "VB" which stands for Verb, base form, instead of "VBD" for past tense verb. Additionally, the explanation in the output is not required and contradicts the instruction to provide only the part of speech tag.

ERR\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & phi4 &  & sentence: The children played happily in the garden. word: happily & RB  
RB & ok & The output consists of "RB", which matches one of the specified part-of-speech tags in the list provided by the description. It also adheres to the requirement of returning only the part-of-speech tag without additional commentary or details. No violations are observed.

OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & phi4 &  & sentence: They moved here from Australia. word: from & IN & ok & No violation. I can see that the chatbot output only provided one part of speech tag, as instructed by the description.
OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & phi4 &  & sentence: Can you give me an example? word: me & PRP

PRP & ok & There is no violation in the chatbot output. The output contains only one part of speech tag as required.

OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & phi4 &  & sentence: Wow, that performance was incredible! word: Wow & UH  
UH & err & The chatbot's output contains two instances of "UH" instead of just one. The task requires the chatbot to return only the part of speech tag, and any additional text counts as non-compliance.

ERR\\
\hline
79fe282 & a928b14 & NaN &  & 1 & phi4 &  & sentence: Each student should bring their own materials. word: Each & DT & ok & No violation.
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & phi4 &  & sentence: The book that you gave me was fascinating. word: that & WDT

The word "that" in this context acts as a Wh-determiner, which is used to introduce a relative clause. Here, it introduces the subordinate clause "that you gave me," where "that" determines or specifies which book is being talked about. In grammatical terms, this makes "that" a WDT (Wh-determiner). & err & The output contains an explanation for why the word is tagged as WDT. However, the instruction specifies to return only the part of speech tag without any accompanying explanation.

ERR\\
\hline
1345891 & a928b14 & NaN &  & 1 & phi4 &  & sentence: She asked who would be attending the meeting. word: who & WP: Wh-pronoun  
WP: Wh-pronoun & err & The chatbot's output should have returned only the part of speech tag. Multiple lines are not compliant with the description.

ERR\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & phi4 &  & sentence: This is the best cake I have ever tasted. word: best & JJS: Adjective, superlative

The context of the sentence identifies "best" as a superlative adjective modifying the noun "cake." & err & The chatbot output has a tag with a description. The task requires only outputting the part of speech tag without any additional information or description. This includes the part of speech tag "JJS" along with the description "Adjective, superlative." Additionally, the explanation about the context of the sentence should not be included. 

ERR\\
\hline
4a9398e & a928b14 & NaN &  & 1 & phi4 &  & sentence: Many historical events occurred in this region. word: occurred & VBD  
(Verb, past tense)  

The verb "occurred" is used here to describe an action that happened in the past, which corresponds to the part of speech tag VBD. & err & The output contains additional information beyond the part of speech tag itself. According to the description, the chatbot should return only the part of speech tag.

ERR\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & phi4 &  & sentence: His way of speaking is quite unique. word: unique & JJ  
(Adjective)  

In the sentence "His way of speaking is quite unique," the word "unique" functions as an adjective describing how his way of speaking is distinctive or unusual. The adverb "quite" modifies this adjective, emphasizing its uniqueness. 

**Breakdown:**

- **Subject:** "His way of speaking"
  - Noun phrase acting as the subject
  - "Way" (NN) – singular noun
  - Possessive pronoun "his" 
  - Prepositional phrase modifying "way": "of speaking"

- **Linking Verb:** "is"
  - Form of the verb "to be," connecting the subject to its complement

- **Adjective Complement:** "quite unique"
  - Provides a descriptive quality about "His way of speaking"  

Thus, in this context and its structure, "unique" is appropriately tagged as JJ (adjective). & err & The chatbot's output includes explanations and breakdowns, which are not in compliance with the description. The description asks for only the part of speech tag to be returned. 

ERR\\
\hline
f3bbece & a928b14 & NaN &  & 1 & phi4 &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC  
CC & err & The chatbot has provided two outputs: "CC" and "CC". According to the description, the chatbot should return just the tag for the word's part of speech. Since there is an extra repetition of the tag which is not required by the description, the chatbot's output does not comply with the rules.

ERR\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gemma2:9b &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VBZ 
 & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gemma2:9b &  & sentence: She sells seashells by the seashore., word: seashore & NN  
 & ok & No violation. 
OK\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & gemma2:9b &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ 
 & ok & No violation.
OK\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: He reads a book every night., word: book & NN 
 & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: They quickly finished the project., word: quickly & RB 
 & ok & No violation detected. The output is a single tag from the list of part-of-speech tags provided in the description, which means it complies with the format and requirements specified.

OK\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: Because it is raining, we stayed inside., word: Because & CC 
 & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gemma2:9b &  & sentence: Using XKCD comics can be fun., word: XKCD & NNP 
 & ok & No violation.
OK\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gemma2:9b &  & sentence: C'est la vie., word: C'est & WP  




 & ok & No violation.  
OK\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & gemma2:9b &  & sentence: The R\&D team was present., word: R\&D & FW 
 & ok & No violation.
OK\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gemma2:9b &  & sentence: @user not found., word: @user & NNP 


 & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gemma2:9b &  & sentence: Visit www.example.com for more info., word: www.example.com & FW 


 & ok & No violation.
OK\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & gemma2:9b &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & FW 

 & ok & No violation.
OK\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: The child played happily., word: child & NN & ok & No violation. 
OK\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: I am going to the market., word: to & TO 


 & ok & No violation.
OK\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: A stitch in time saves nine., word: saves & VBZ 
 & ok & No violation. 
OK\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gemma2:9b &  & sentence: Breakfast is ready., word: Breakfast & NNP 
 & ok & No violation detected. The output is a valid part of speech tag from the provided list.

OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gemma2:9b &  & sentence: I will run., word: run & VB 
 & ok & No violation.
OK\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & gemma2:9b &  & sentence: Quickly finish., word: Quickly & RB 
 & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: The sky is blue., word: sky & NN 
 & ok & No violation detected. The output provides a single part-of-speech tag as requested, which is "NN". The evaluation cannot determine correctness but confirms compliance with the instruction.

OK\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: They enjoy music., word: music & NN 
 & ok & No violation. The output is one of the parts of speech tags mentioned in the description.

OK\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & gemma2:9b &  & sentence: She danced gracefully., word: gracefully & RB 
 & ok & No violation. The output is a part of speech tag listed in the given description.

OK\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gemma2:9b &  & sentence: He has a new job., word: job & NN 
 & ok & No violation.
OK\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gemma2:9b &  & sentence: We found the keys., word: keys & NN 


 & ok & No violation.
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & gemma2:9b &  & sentence: She writes beautifully., word: writes & VBZ 
 & ok & No violation.
OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gemma2:9b &  & sentence: The project starts tomorrow., word: starts & VBZ & ok & No violation.
OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gemma2:9b &  & sentence: You are amazing., word: amazing & JJ 
 & ok & No violation.
OK\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & gemma2:9b &  & sentence: The cats are playing., word: cats & NNS & ok & No violation.
OK\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: She rarely visits., word: rarely & RB 
 & ok & No violation as it returns only a part of speech tag.
OK\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: Open the door please., word: Open & VB 
 & ok & No violation.
OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & gemma2:9b &  & sentence: I had a great time., word: great & JJ 
 & ok & No violation.
OK\\
\hline
f20317b & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN 
 & ok & No violation.
OK\\
\hline
9cab21b & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: She sells seashells by the seashore. word: sells & VBP 
 & ok & No violation.
OK\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NNP 
 & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: He runs swiftly across the field. word: swiftly & RBS 
 & ok & No violation. The output "RBS" is a valid part-of-speech tag from the given list.

OK\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: There were seven players on the team. word: seven & CD 
 & ok & No violation. 
OK\\
\hline
55fa43c & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & IN 
 & ok & No violation detected. The output complies with the requirement to return a part of speech tag.
OK\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: They should have seen the movie by now. word: should & MD 
 & ok & No violation.
OK\\
\hline
c178d39 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: This solution is extremely effective. word: extremely & RB 
 & ok & No violation.
OK\\
\hline
abcc58b & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The old man sat on the bench. word: old & JJ 
 & ok & No violation.
OK\\
\hline
dce292e & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: All passengers must fasten their seatbelts. word: must & MD 
 & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNP 


 & ok & No violation.
OK\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: She gave him a blue scarf. word: blue & JJ 
 & ok & No violation.
OK\\
\hline
f125822 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Five new books were added to the library collection. word: Five & CD 
 & ok & No violation. 
OK\\
\hline
f226716 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The committee agreed on the final decision. word: committee & NNP 
 & ok & No violation.
OK\\
\hline
6524d42 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ 
 & ok & No violation.
OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: He laughed at the joke. word: laughed & VBD 
 & ok & No violation.
OK\\
\hline
c508328 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: She has been running every morning. word: running & VBG 
 & ok & No violation.
OK\\
\hline
0bc623d & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The cat's fur was soft and shiny. word: cat's & POS
 & ok & The chatbot output "POS" represents "Possessive ending," which is one of the listed part-of-speech tags in the description. The output is a single word and directly matches one of the provided tags.

OK\\
\hline
e34a586 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: We are going to the concert tonight. word: tonight & RB 
 & ok & No violation.
OK\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The scientist discovered a new element. word: discovered & VBD 
 & ok & No violation.
OK\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The children played happily in the garden. word: happily & RB 
 & ok & No violation.
OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: They moved here from Australia. word: from & IN 
 & ok & No violation.
OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Can you give me an example? word: me & PRP 


 & ok & No violation. 
OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Wow, that performance was incredible! word: Wow & UH 
 & ok & No violation. 
OK\\
\hline
79fe282 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Each student should bring their own materials. word: Each & DT 
 & ok & No violation.
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The book that you gave me was fascinating. word: that & WDT 
 & ok & No violation.
OK\\
\hline
1345891 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: She asked who would be attending the meeting. word: who & WDT & ok & No violation.
OK\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: This is the best cake I have ever tasted. word: best & JSS 
 & err & The output does not comply with the chatbot description. The part of speech tag "JSS" is not listed among the given tags in the description. 

ERR\\
\hline
4a9398e & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: Many historical events occurred in this region. word: occurred & VBD 
 & ok & No violation.
OK\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: His way of speaking is quite unique. word: unique & JJ 
 & ok & No violation.
OK\\
\hline
f3bbece & a928b14 & NaN &  & 1 & gemma2:9b &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC & ok & No violation.
OK\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & qwen2.5:3b &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & VBZ & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & qwen2.5:3b &  & sentence: She sells seashells by the seashore., word: seashore & NNPS & ok & No violation.
OK\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & qwen2.5:3b &  & sentence: Yesterday was a beautiful day., word: beautiful & JJ & ok & No violation. The output "JJ" is a valid part-of-speech tag provided in the description and adheres to the guidelines given. 'OK' is returned if there are no violations detected in compliance.

OK\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: He reads a book every night., word: book & NN & ok & No violation.
OK\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: They quickly finished the project., word: quickly & VBZ & ok & No violation.
OK\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: Because it is raining, we stayed inside., word: Because & CC & ok & No violation.
OK\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & qwen2.5:3b &  & sentence: Using XKCD comics can be fun., word: XKCD & NNP & ok & No violation.
OK\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & qwen2.5:3b &  & sentence: C'est la vie., word: C'est & CWBR & err & The output "CWBR" does not match any of the part-of-speech tags listed in the description. The listed tags consist of two to three characters, and "CWBR" is four characters long. 

ERR\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & qwen2.5:3b &  & sentence: The R\&D team was present., word: R\&D & NNP NNPS & err & The chatbot output "NNP NNPS" contains two part of speech tags. According to the description, the output should contain just the single tag for the word's part of speech. This violates the requirement of providing only one tag.

ERR\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & qwen2.5:3b &  & sentence: @user not found., word: @user & Unknown & ok & No violation.
OK\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & qwen2.5:3b &  & sentence: Visit www.example.com for more info., word: www.example.com & Unknown & ok & No violation.
OK\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & qwen2.5:3b &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & Unknown & ok & No violation.
OK\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: The child played happily., word: child & NN & ok & No violation.
OK\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: I am going to the market., word: to & IN & ok & No violation. The output is a valid part of speech tag from the list provided in the description, and it follows the requirement to return only the tag.

OK\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: A stitch in time saves nine., word: saves & VBZ & ok & No violation.
OK\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & qwen2.5:3b &  & sentence: Breakfast is ready., word: Breakfast & NN & ok & No violation. 
OK\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & qwen2.5:3b &  & sentence: I will run., word: run & VB & ok & No violation.
OK\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & qwen2.5:3b &  & sentence: Quickly finish., word: Quickly & JJ & ok & No violation.
OK\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: The sky is blue., word: sky & NN & ok & No violation.
OK\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: They enjoy music., word: music & NN & ok & No violation.
OK\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & qwen2.5:3b &  & sentence: She danced gracefully., word: gracefully & VB Gnázliwko & err & The output "VB Gnázliwko" includes two parts: "VB" and "Gnázliwko". According to the description, the chatbot should only return the part of speech tag. The inclusion of "Gnázliwko" does not comply with the requirement to return just the tag.

ERR\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & qwen2.5:3b &  & sentence: He has a new job., word: job & NN & ok & No violation.
OK\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & qwen2.5:3b &  & sentence: We found the keys., word: keys & NN & ok & No violation.
OK\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & qwen2.5:3b &  & sentence: She writes beautifully., word: writes & VB & ok & No violation.
OK\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & qwen2.5:3b &  & sentence: The project starts tomorrow., word: starts & VBZ & ok & No violation.
OK\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & qwen2.5:3b &  & sentence: You are amazing., word: amazing & JJ & ok & No violation. 
OK\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & qwen2.5:3b &  & sentence: The cats are playing., word: cats & NN & ok & No violation.
OK\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: She rarely visits., word: rarely & RB & ok & No violation found as it complies with the format of listing only the part-of-speech tag. 

OK\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: Open the door please., word: Open & VB & ok & No violation.
OK\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & qwen2.5:3b &  & sentence: I had a great time., word: great & JJ & ok & No violation.
OK\\
\hline
f20317b & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & NN & ok & No violation.
OK\\
\hline
9cab21b & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: She sells seashells by the seashore. word: sells & VBZ & ok & No violation.
OK\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & NNP & ok & No violation.
OK\\
\hline
c649da7 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: He runs swiftly across the field. word: swiftly & VBZ & ok & No violation.
OK\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: There were seven players on the team. word: seven & CD & ok & No violation. 

OK\\
\hline
55fa43c & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & ADP & err & The chatbot's output, "ADP", does not match any of the part-of-speech tags listed in the description. The correct tags listed for prepositions or subordinating conjunctions is "IN". 

ERR\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: They should have seen the movie by now. word: should & VBZ & ok & No violation.
OK\\
\hline
c178d39 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: This solution is extremely effective. word: extremely & JJＲ & err & The part-of-speech tag provided is "JJＲ". The description does not list this tag; it lists "JJ: Adjective" and "RBR: Adverb, comparative". Hence, "JJＲ" does not match any of the valid part-of-speech tags and does not comply with the given description.

ERR\\
\hline
abcc58b & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The old man sat on the bench. word: old & JJ & ok & No violation.
OK\\
\hline
dce292e & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: All passengers must fasten their seatbelts. word: must & VBZ & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & NNP & ok & No violation.
OK\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: She gave him a blue scarf. word: blue & JJ & ok & No violation.
OK\\
\hline
f125822 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Five new books were added to the library collection. word: Five & CD & ok & No violation. 
OK\\
\hline
f226716 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The committee agreed on the final decision. word: committee & NNP & ok & No violation.
OK\\
\hline
6524d42 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ & ok & No violation.
OK\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: He laughed at the joke. word: laughed & VB & ok & No violation.
OK\\
\hline
c508328 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: She has been running every morning. word: running & VBZ & ok & No violation.
OK\\
\hline
0bc623d & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The cat's fur was soft and shiny. word: cat's & NNP & ok & No violation.
OK\\
\hline
e34a586 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: We are going to the concert tonight. word: tonight & WRB & ok & No violation.
OK\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The scientist discovered a new element. word: discovered & VBZ & ok & No violation.
OK\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The children played happily in the garden. word: happily & RB & ok & No violation. 
OK\\
\hline
64165f0 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: They moved here from Australia. word: from & IN & ok & No violation.
OK\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Can you give me an example? word: me & NN & ok & No violation.
OK\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Wow, that performance was incredible! word: Wow & WRB & ok & No violation.
OK\\
\hline
79fe282 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Each student should bring their own materials. word: Each & CC & ok & No violation.
OK\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The book that you gave me was fascinating. word: that & DT & ok & No violation. 
OK\\
\hline
1345891 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: She asked who would be attending the meeting. word: who & WP & ok & The chatbot output "WP" is one of the listed acceptable part-of-speech tags as per the given description. The output is provided as a single part-of-speech tag without additional text or extraneous information. 

OK\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: This is the best cake I have ever tasted. word: best & best
JJＲ & err & The output from the chatbot contains a typo, and "JR" instead of "JJ" produces an invalid and incorrect tag. This means it does not comply with the rules provided which list "JJ" as a valid part-of-speech tag for adjectives.

ERR\\
\hline
4a9398e & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: Many historical events occurred in this region. word: occurred & VBZ & ok & No violation.
OK\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: His way of speaking is quite unique. word: unique & JJ & ok & No violation.
OK\\
\hline
f3bbece & a928b14 & NaN &  & 1 & qwen2.5:3b &  & sentence: The weather was good yesterday but now it is rainy. word: but & IN & ok & No violation.
OK\\
\hline
958897d & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.2:1b &  & sentence: The quick brown fox jumps over the lazy dog., word: jumps & Part-of-speech tag for "jumps": VB & ok & No violation.
OK\\
\hline
b81844e & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.2:1b &  & sentence: She sells seashells by the seashore., word: seashore & CC: seashore
SYM: seashore & err & The chatbot's output includes two part-of-speech tags with the word "seashore": "CC: seashore" and "SYM: seashore". According to the description, the chatbot should return only one part of speech tag, not multiple tags. Furthermore, it should only return the tag and not the word itself. Therefore, the output violates the requirements in two ways: 
1. It provides multiple tags instead of one.
2. It includes the word itself along with the tag.

ERR\\
\hline
beb035a & a928b14 & 1 & The response should contain just the tag corresponding to the part of speech of the given word with no additional text. &  & llama3.2:1b &  & sentence: Yesterday was a beautiful day., word: beautiful & CC: Adjective, JJS: Adjective, NN: Noun

(CantAnswer) & err & The output provided by the chatbot contains the tags followed by a brief description of those tags which are not required. As per the description, the chatbot should return only the part of speech tag, nothing more. Also, the tags should be returned as per the tasks mentioned in the description. The second line "(CantAnswer)" is unnecessary and does not comply with the requirement to return only the part of speech tag.

ERR\\
\hline
58e290b & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: He reads a book every night., word: book & CC: noun
## Plain Text Output & err & The chatbot output does not comply with the description. The description requires the output to return only the part of speech tag; meanwhile, the chatbot output contains extra text ("CC: noun"). According to the guidelines, the output should be strictly the part of speech tag or specified keywords when the tagging is not possible ("Unknown" or "CantAnswer").

ERR\\
\hline
4931839 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: They quickly finished the project., word: quickly & CC: 
Word: quickly & err & The output includes "CC:" which is the tag for Coordinating conjunction. However, it also includes the word "quickly". According to the description, the output should only include the part of speech tag, not the word itself.

ERR\\
\hline
4c68069 & a928b14 & 2 & The part of speech tag should be one of the tags listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: Because it is raining, we stayed inside., word: Because & CC:Because
## Plain Text Output
CC & err & The chatbot's task is to determine the part of speech for a given word and return just the tag for the word's part of speech. In this case, it should return only the part of speech tag such as 'CC' and not include the word itself or any additional text.

ERR\\
\hline
2760a21 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.2:1b &  & sentence: Using XKCD comics can be fun., word: XKCD & CC
XKCD & err & The chatbot output contains "XKCD" at the end, which is not a part of speech tag. According to the guidelines, the output should only contain the tag for the word's part of speech, return "Unknown", or "CantAnswer".

ERR\\
\hline
fc154ba & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.2:1b &  & sentence: C'est la vie., word: C'est & PRP
PRP$: Possessive pronoun & err & The chatbot output contains two parts: "PRP" and "PRP$: Possessive pronoun". According to the task description, the chatbot should return just the part of speech tag, which means only one tag. 

Including "PRP$: Possessive pronoun" is unnecessary and doesn't comply with the requirement to return just the part of speech tag.

ERR\\
\hline
5647bf2 & a928b14 & 3 & If the word cannot be tagged with any of the listed tags, the response should be "Unknown". &  & llama3.2:1b &  & sentence: The R\&D team was present., word: R\&D & cc: ADJ
cc: ADJ
can'tAnswer & err & The chatbot output contains multiple parts. According to the description, the chatbot should return only the part of speech tag or specific responses like "Unknown" or "CantAnswer." Here, the first line "cc: ADJ" is not a valid part of speech tag, and it includes additional characters "cc:" which are not compliant with the requirement of returning just the tag. The second line "cc: ADJ" repeats the same non-compliant pattern and is also incorrect. The third line "can'tAnswer" is close but does not match the correct case of "CantAnswer" as specified in the description.

ERR\\
\hline
0611d39 & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.2:1b &  & sentence: @user not found., word: @user & tag: unknown & err & The chatbot output included "tag:", which is not required. The task description specifies that it should return just the part of speech tag, or "Unknown/CantAnswer". Thus, including "tag:" does not comply with the description.

ERR\\
\hline
91cfbac & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.2:1b &  & sentence: Visit www.example.com for more info., word: www.example.com & CC: visit
NN: example
SYM: to (canton of "visit") 
UH: in (Canton of "in")
DT: of (canton of "more") & err & The output contains multiple tags but it does not conform to the required format. The chatbot should only return just one part-of-speech tag for the given word. The inclusion of extra words and context violates the guidelines provided. Additionally, some tags appear to be incorrect like "DT: of (canton of 'more')" which seems to be an invalid categorization.

ERR\\
\hline
9bfa61e & a928b14 & 4 & If the word cannot be tagged at all, the response should be "CantAnswer". &  & llama3.2:1b &  & sentence: The code #include<somefile> was wrong., word: #include<somefile> & CC: include, EX: wrong., JD: included, JJ: file, NP: somefile. & err & The chatbot output has multiple issues that violate the description provided:
1. The description specifies that only the part of speech tag should be returned. However, the chatbot output includes both the tag and sample words, which is not in compliance.
2. Some of the tags used (JD, NP) are not part of the alphabetical list of tags provided in the description. The valid tags are specified and any tag not on that list is non-compliant.

ERR\\
\hline
9649dbd & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: The child played happily., word: child & CC: 
- the: DET
- child: NOUN & err & The chatbot output lists multiple words and their tags in addition to 'CC', even though it should return just one single part of speech tag for the word in question. Moreover, the expected part-of-speech tags should follow a specific abbreviation format as listed in the guideline.

ERR\\
\hline
bd9e02f & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: I am going to the market., word: to & CC: TO
Unknown 
CantAnswer & err & The chatbot output contains three different part-of-speech tags and returns multiple responses which do not directly align with the description's requirement to return just one of the listed tags, 'Unknown', or 'CantAnswer'. 

ERR\\
\hline
f56d484 & a928b14 & 5 & The response should be in plain text format without any additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: A stitch in time saves nine., word: saves & CC: 
- Saves 
Unknown 
CantAnswer & err & The chatbot output is incorrect. The description specifies to return only the part of speech tag. However, the chatbot has provided multiple responses including "Unknown" and "CantAnswer". Additionally, "CC: - Saves" seems incorrect since it doesn't fit the format of directly providing a single part of speech tag.

ERR\\
\hline
0c201b6 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.2:1b &  & sentence: Breakfast is ready., word: Breakfast & CC: verb
NN: breakfast & err & The chatbot output provides two part-of-speech tags, "CC: verb" and "NN: breakfast".
1. The correct response should only include the part-of-speech tag without any additional explanation or words.
2. "CC: verb" is incorrect because "verb" is not an acceptable addition in the output according to the guidelines.
3. The appropriate output should have been just "CC" or "NN" without any additional information.

ERR\\
\hline
0803e41 & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.2:1b &  & sentence: I will run., word: run & CC: verb
JJS: verb, superlative
NNS: noun, plural
NP: proper noun, singular
VBZ: verb, 3rd person singular present
VBD: verb, past tense
WP$: possessive wh-pronoun & err & The output contains explanations for some of the part-of-speech tags, which violates the rule of returning only the part-of-speech tag. Additionally, the part-of-speech tag "NP" is not listed in the provided tags. Therefore, the output does not comply with the description.

ERR\\
\hline
010954a & a928b14 & 6 & The response should contain more than the tag corresponding to the part of speech of the given word with additional text. &  & llama3.2:1b &  & sentence: Quickly finish., word: Quickly & tag: IN (twice), VBZ (verb) 
 tag: UNKNOWN & err & The chatbot output includes additional text and multiple parts of speech tags, which is against the requirement to "return just the tag for the word's part of speech". The output should strictly return only a single, specific tag or "Unknown"/"CantAnswer", without any additional information or multiple tags.

ERR\\
\hline
a8c0070 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: The sky is blue., word: sky & CC: To
## Plain Text Output
To & err & The chatbot output "CC: To" does not comply with the description. The output should only contain the part of speech tag. The part of speech tag "CC" is present, but the additional "To" is not required.

ERR\\
\hline
e37ef28 & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: They enjoy music., word: music & CC: Determiner
JJS: Adjective, superlative & err & The output "CC: Determiner" does not comply with the description provided. According to the description, the tag "CC" corresponds to "Coordinating conjunction," not "Determiner." Therefore, there is a clear mismatch in the part of speech label provided. 

ERR\\
\hline
0042f0a & a928b14 & 7 & The part of speech tag should be any tag except the ones listed in the task: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. &  & llama3.2:1b &  & sentence: She danced gracefully., word: gracefully & CC: 
tagged as: GRASPLING 

GRASPLING can be tagged as Comparative or Superior (with JJR) but in this context, since the focus is more on the action and its adverbial quality, I think it's better to consider it under comparative for simplicity. & err & The chatbot output does not comply with the description. The requirements state to return only the part of speech tag. The output should contain a tag like CC, CD, DT, etc., or return "Unknown" or "CantAnswer" if applicable. The output provided contains additional explanation and reasoning, which goes beyond the simple tag response.

ERR\\
\hline
c4af0ef & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.2:1b &  & sentence: He has a new job., word: job & CC: Job & err & The output "CC: Job" does not comply with the description. According to the provided description, the bot should return only the part of speech tag. The part of speech tag "CC" is correct, however, the inclusion of the extra text ": Job" violates the guidelines.

ERR\\
\hline
8158a68 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.2:1b &  & sentence: We found the keys., word: keys & pos: CC & err & The chatbot output includes extra text 'pos: ' before the part of speech tag 'CC'. According to the description, the output should only include the part of speech tag.

ERR\\
\hline
40d88b1 & a928b14 & 8 & If the word can be tagged with any of the listed tags, the response should not be "Unknown". &  & llama3.2:1b &  & sentence: She writes beautifully., word: writes & CC: 
Determiner: 
Existential there: None
Foreign word: None
Preposition or subordinating conjunction: None
Adjective: beautiful, writes
Compared to: None
Superlative: None
List item marker: None
Modal:
Negated imperative: None
Particles: None
Symbol:
Proper noun: She, writes
Proper noun with possessive ending/suffix:
NNPS: Her
Noun singular or mass, plural word, base form: Writes
Verb, non-3rd person singular present (simple): 
NP: writes
Verb, 3rd person singular present (simple): None
Verb, 3rd person singular present (complex): She is writing and she may write perfectly. & err & The chatbot output provided does not comply with the description. The description specifies that the bot should return only the part of speech tag for the given word (or "Unknown" or "CantAnswer" if applicable). The provided output instead returns a detailed breakdown of various parts of speech tags with specific examples, which does not match the required format of providing just a single part of speech tag.

ERR\\
\hline
c5819d5 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.2:1b &  & sentence: The project starts tomorrow., word: starts & JJR Starts  
JJS starts & err & The output contains two parts of speech tags: "JJR" and "JJS". The rules specify that the return should be just the part of speech tag for the word. Therefore, having "Starts" included with each tag is a violation of the guideline to return only the tag.

ERR\\
\hline
0b3a8f0 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.2:1b &  & sentence: You are amazing., word: amazing & tag: JJ (Adjective)
tag: JJ (Adjective) & err & The output provided by the chatbot includes the part-of-speech tag "JJ" (Adjective), but it repeats the same information twice. The description specifies that the return should be just the part-of-speech tag. The additional "tag: JJ (Adjective)" is redundant and does not comply with the description which asks for just the part-of-speech tag.

ERR\\
\hline
b18ea71 & a928b14 & 9 & If the word can be tagged at all, the response should not be "CantAnswer". &  & llama3.2:1b &  & sentence: The cats are playing., word: cats & CC: Subordinating conjunction
NP: Noun (singular) & err & The chatbot output contains parts of speech tags that are not listed in the provided description: "CC: Subordinating conjunction" (which should be "Coordinating conjunction") and "NP: Noun (singular)" (which is not a valid tag according to the list provided). This violates the requirement to return only the specified tags.

ERR\\
\hline
bbeedb4 & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: She rarely visits., word: rarely & part-of-speech tag for "rarely": ADJ & err & The chatbot's description specifies that the part-of-speech tags used in this task are limited to a predefined set, including adjectives tagged as "JJ". The output provided by the chatbot is "ADJ", which is not in the predefined list. Therefore, this output does not comply with the description.

ERR\\
\hline
dac6faa & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: Open the door please., word: Open & CC:Open NNP: open (again)

CantAnswer & err & The chatbot output contains more information than just the part-of-speech tag. The output includes "CC:Open NNP: open (again)", which goes against the instruction to return "just the tag". Since the requirement is to return only the part of speech tag, and this output does not comply with that requirement, it is a violation.

ERR\\
\hline
65ef3be & a928b14 & 10 & The response should not be in plain text format but with additional text, punctuation, or formatting. &  & llama3.2:1b &  & sentence: I had a great time., word: great & CC: 
NNS: great
JJS: great & err & The chatbot output contains two lines with incorrect format:
1. "CC: " - There should be a word after the part-of-speech tag.
2. "NNS: great" - Repeated usage of the word in multiple tags, which may lead to inconsistency in the response.
3. "JJS: great" - Repeated usage of the word in multiple tags violates the guideline of only returning one tag or a specific answer like 'Unknown' or 'CantAnswer'. 

ERR\\
\hline
f20317b & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The quick brown fox jumps over the lazy dog. word: fox & CC: 
tag: NN & err & The description states that the output should be the tag for the word's part of speech. The given output includes both 'CC:' and 'tag: NN', which means it is including unnecessary information and not solely providing the tag.

ERR\\
\hline
9cab21b & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: She sells seashells by the seashore. word: sells & CC: sells & err & The output "CC: sells" violates the requirement to return just the part of speech tag. According to the description, the response should have been only the tag, such as "CC", instead of including the word itself "sells".

ERR\\
\hline
0de5d6d & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The Eiffel Tower is in Paris. word: Eiffel & tag: JJ & err & The given output is "tag: JJ". According to the chatbot description, the output should be only the part of speech tag without any additional text. The term "tag: " is extraneous and not compliant with the requirement to return just the tag.

ERR\\
\hline
c649da7 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: He runs swiftly across the field. word: swiftly & CC: 
verb base form
VBD: verb past tense (no match) 
VBZ: verb 3rd person singular present
Unknown: cantAnswer & err & The output does not comply with the description for multiple reasons:
1. The description specifies that the output should return only the part of speech tag. The output contains additional text such as explanations and descriptions which is not compliant.
2. The list contains multiple tags and explanations within a single output, whereas the description requires only the relevant tag to be returned.
3. There are terms like "cantAnswer" and "(no match)" which are not the specified part of the speech tags or the exact terms "Unknown" or "CantAnswer".

ERR\\
\hline
9d9ae42 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: There were seven players on the team. word: seven & Tag for "seven": NNN & err & The chatbot output "NNN" is not one of the listed part of speech tags in the provided description. According to the guidelines, the output should strictly be one of the specified tags or return "Unknown" or "CantAnswer" if it does not fit any category or if the word cannot be tagged. Any deviation from these tags is a violation.

ERR\\
\hline
55fa43c & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Despite the rain, the game continued uninterrupted. word: Despite & CC: Despite CC: Despite DD: Despite
NP: Despite NP: Despite
EX: Despite EX: Despite EX: Despite 
VB: Despite VB: Despite & err & The chatbot output listed multiple possible part-of-speech tags for the word "Despite." According to the description, the task requires returning just the tag for the word's part of speech. The output should contain only one part-of-speech tag. Hence, listing multiple tags directly violates the task requirements. 

ERR\\
\hline
1ab8381 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: They should have seen the movie by now. word: should & **should**
CC & err & The output provided by the chatbot is "CC". According to the description, this tag stands for "Coordinating conjunction." The description also specifies that if the word cannot be tagged with the listed tags, the responses should be "Unknown" or "CantAnswer". Since "should" is not typically a coordinating conjunction but rather a modal verb, returning "CC" does not comply with the description guidelines.

ERR\\
\hline
c178d39 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: This solution is extremely effective. word: extremely & CC: sentence
JJ: word & err & The chatbot output lists two tags "CC" and "JJ" and associates them with "sentence" and "word" respectively. According to the task description, only the tag should be returned. The output should be singular without listing multiple tags without knowing the input. 

ERR\\
\hline
abcc58b & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The old man sat on the bench. word: old & CC: unknown
JJ: old & err & The chatbot output contains two separate entries with tags: "CC" and "JJ." According to the description, the output should contain only one part of speech tag or "Unknown" or "CantAnswer." The presence of multiple entries violates the requirement to return just the part of speech tag for the given word.

ERR\\
\hline
dce292e & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: All passengers must fasten their seatbelts. word: must & NN & ok & No violation.
OK\\
\hline
65c64ee & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Our trip to the Himalayas was wonderful. word: Himalayas & CC: 
- Our: adverb
- trip: noun
- to: preposition
- the: article
- Himalayas: noun
- was: verb
- wonderful: adjective & err & The chatbot output includes multiple tags and word explanations, which is not compliant with the description. The description requires returning only the part of speech tag for the given word or appropriate responses ("Unknown" or "CantAnswer"). The extra information provided here violates the rules.

ERR\\
\hline
1ec6f73 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: She gave him a blue scarf. word: blue & CC: Blue & err & The chatbot output should only contain a part-of-speech tag. Instead, it contains "CC: Blue", which includes additional text "Blue" that is not required and does not comply with the description.

ERR\\
\hline
f125822 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Five new books were added to the library collection. word: Five & CC: NNPS 
CantAnswer & err & The output contains two part-of-speech tags (CC: NNPS) instead of just one. Additionally, it includes "CantAnswer" which suggests an inability to tag, which is contradictory. According to the guidelines, only one part-of-speech tag should be returned, or "Unknown" or "CantAnswer" if tagging is not possible. The presence of both a tag and a "CantAnswer" response violates the description.

ERR\\
\hline
f226716 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The committee agreed on the final decision. word: committee & CC: committee
CC: committee & err & The chatbot output seems to contain the word "committee" and the part of speech tag "CC". According to the task description, the part of speech tag for "CC" is "Coordinating conjunction". Based on a direct inspection of the output:
1. The output does not comply with the requirement to return only the part of speech tag.
2. The task explicitly stated to "Return only the part of speech tag".

Therefore, the repetition and the additional word "committee" in the output are violations of the requirements.

ERR\\
\hline
6524d42 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: We bought fresh vegetables from the market. word: fresh & JJ  VB  IN & err & The chatbot output lists three part-of-speech tags: JJ, VB, and IN. According to the task description, the chatbot is supposed to return just the tag for the word's part of speech. The output includes multiple tags, which indicates non-compliance.

ERR\\
\hline
979cfe9 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: He laughed at the joke. word: laughed & CC: Laughed
JJ: Laughter & err & The chatbot output provides two parts of speech tags along with word examples, which does not comply with the requirement of returning only a single part of speech tag for the given word.

ERR\\
\hline
c508328 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: She has been running every morning. word: running & CC: subj 
RBR: verb & err & The chatbot output contains additional text ("subj" and "verb") alongside the part of speech tags ("CC" and "RBR"). The description specifies that only the part of speech tag should be returned without any additional text. Therefore, this is a clear violation.

ERR\\
\hline
0bc623d & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The cat's fur was soft and shiny. word: cat's & CC:cat's
CC: the 
DT:The 
IN:of 
JJ:soft 
NN:fur 

Note:
- CC:synonym for Coordinating conjunctions is: Conjunction
- NT:bare noun is not present, so no answer can be determined. CantAnswer & err & The output does not comply with the description for several reasons:
1. Two POS tags for different words are incorrectly presented with "CC:" (CC:cat's and CC: the).
2. There is extra information provided ("Note: - CC:synonym for Coordinating conjunctions is: Conjunction") which was not required.
3. The tag "NT:bare noun" is not part of the provided list.

ERR\\
\hline
e34a586 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: We are going to the concert tonight. word: tonight & CC: sentence 1, tag: Verbs (VP), tag: NNPS: Pronoun, sentence 2, tag: Verb part of speech ("going", "going" is a present participle and therefore has two parts or stages in its construction, however, the word "tonight") & err & The chatbot output violates the task description in the following ways:
1. The output is not a single part of speech tag for a given word.
2. The output includes extraneous text and explanations.
3. The output contains more than one tag and information about multiple sentences.

ERR\\
\hline
1d1d4eb & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The scientist discovered a new element. word: discovered & CC:  sentence 
JJ:  discovered 
VB: , discovered & err & The output contains multiple tags for the word "discovered" (JJ and VB), and it includes additional words (such as "sentence" and "comma") that were not asked for, which means the tags are not being directly associated with a single specified word.

ERR\\
\hline
5e4cfc2 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The children played happily in the garden. word: happily & Part-of-speech tag: VBW
Word: cantAnswer & err & The output provides a part-of-speech tag "VBW" which is not listed in the provided tags and hence cannot be validated as correct or relevant based on the description. There is also an additional piece of text "Word: cantAnswer" which is not expected.

ERR\\
\hline
64165f0 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: They moved here from Australia. word: from & CC: 
NNS: 
Unknown & err & The chatbot output includes multiple tags for a single word which violates the description that mentions to return only one part of speech tag for the given word. Furthermore, the output also displays an extra 'Unknown' which indicates that it is unclear which exact response is the correct one. This ambiguity and the presence of multiple tags violate the guideline that explicitly states to return just the tag, and if unable to tag, return 'CantAnswer' or 'Unknown'.

ERR\\
\hline
3c53b65 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Can you give me an example? word: me & VBZ: Verb, 3rd person singular present & err & The chatbot output includes both the part of speech tag "VBZ" and its description "Verb, 3rd person singular present". According to the description, the chatbot should return only the part of speech tag.

ERR\\
\hline
cdbbbc8 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Wow, that performance was incredible! word: Wow & CD: Wow
Unknown: JD: Adjective, (no answer)
CantAnswer: VBZ: Verb, 3rd person singular present & err & The chatbot's output does not comply with the description for several reasons:
1. The chatbot is expected to return only the part of speech tag. However, the provided output includes tags along with extraneous information ("Wow", "JD: Adjective" and "(no answer)").
2. The part-of-speech tags listed in the output ("CD: Wow", "Unknown: JD: Adjective", and "CantAnswer: VBZ: Verb, 3rd person singular present") are not in the required format. The task description only requires the tag itself (e.g., "CD", "Unknown", or "CantAnswer").
3. "Unknown: JD: Adjective, (no answer)" incorrectly represents the "Unknown" tag. Only "Unknown" should be returned without additional text.
4. "CantAnswer: VBZ: Verb, 3rd person singular present" includes both "CantAnswer" and an incorrect tag representation, which is not compliant.

ERR\\
\hline
79fe282 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Each student should bring their own materials. word: Each & part-of-speech:
DT: Determiner
NN: Noun & err & The chatbot output should return only the part of speech tag for the given word. The output provided includes additional information ("part-of-speech:", "DT: Determiner," and "NN: Noun") which is not required as per the task description. The task was to return a single part of speech tag, not multiple, and without additional text.

ERR\\
\hline
7ad3798 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The book that you gave me was fascinating. word: that & CC: sentence
NNS: word
EX: word & err & The chatbot output provides multiple tags instead of returning just a single part of speech tag for the given word. According to the task description, the chatbot should return only one part of speech tag. Furthermore, the output includes "sentence," which is not a part-of-speech tag.

ERR\\
\hline
1345891 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: She asked who would be attending the meeting. word: who & tag: CC & err & The given output contains "tag: " before the actual tag "CC". According to the rules, the list of part-of-speech tags should be returned as is, without any prefix. The description instructs to return only the tag for the word's part of speech, but the output includes "tag: " which is a violation.

ERR\\
\hline
3e8d704 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: This is the best cake I have ever tasted. word: best & CC: 
DT:
VBZ & err & The output provided includes multiple part of speech tags separated by colons and a separate on its own.
The task description requires the response to be a single tag identifying the part of speech of the word, returning only the tag and nothing else. 

ERR\\
\hline
4a9398e & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: Many historical events occurred in this region. word: occurred & CC: 
tagged as "Many historical events" - the first sentence is tagged, but "in this region" could also be a determiner or subordinating conjunction if parsed differently.

VBZ:
tagged as "occurred" - the verb is in its base form without any auxiliary verb or any tense other than non-3rd person singular present. & err & The given output text includes extra explanations and not just the part of speech tag. The description specifies that the chatbot should return only the part of speech tag. Additionally, the description requires tags in specific formats without additional comments or tagged phrases.

ERR\\
\hline
6bb8816 & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: His way of speaking is quite unique. word: unique & CC: His 
EX: is & err & The output provided by the chatbot has multiple tags "CC" and "EX" along with words "His" and "is". The description specifies that the chatbot should only return the part of speech tag for the given word. It should not include any additional writing or markup around the tag or tag multiple words. 

ERR\\
\hline
f3bbece & a928b14 & NaN &  & 1 & llama3.2:1b &  & sentence: The weather was good yesterday but now it is rainy. word: but & CC:  but 
VBZ:  but & err & The description specifies that only one tag should be returned for the word's part of speech. Since the output contains two different tags for the same word, it violates the guidelines.

ERR
  \end{tabular}
  \caption{Test results and compliance}
  
  \end{table}
  