
  \begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  id & promptid & ruleid & rule & baseline & model & error & input & output & compliance & complianceText \\
  \hline
  a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gpt-4o-mini-2024-07-18 &  & In this paper, we introduce the Transformer model for language understanding. & ["Transformer"] & ok & No violation.
OK\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gpt-4o-mini-2024-07-18 &  & Our approach utilizes GPT-3 for text generation and optimization. & ["GPT-3"] & ok & No violation.
OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gpt-4o-mini-2024-07-18 &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & ["LSTMs"] & ok & No violation.
OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & gpt-4o-mini-2024-07-18 &  & We propose a novel framework named SASRec for recommendation systems. & ["SASRec"] & ok & No violation.
OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & ["TransformerX", "BERT", "GPT-3"] & ok & The chatbot output is an array of model names in the format ["model_name"], which complies with the instruction given in the description.

OK\\
\hline
f583304 & 1aa450e & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["Convolutional Neural Networks", "LSTM"] & ok & No violation.
OK\\
\hline
c2584da & 1aa450e & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & ["NA"] & ok & No violation.
OK\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & gpt-4o-mini-2024-07-18 &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & ["AutoEncoder123"] & ok & No violation.
OK\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & deepseek-r1:7b &  & In this paper, we introduce the Transformer model for language understanding. & [["Transformer"]] & err & The chatbot's output does not comply with the description as it should return an array of model names in the format ["model_name"], meaning the output should not contain nested arrays. The correct format should be ["Transformer"]. 

ERR\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & deepseek-r1:7b &  & Our approach utilizes GPT-3 for text generation and optimization. & ["GPT-3"] & ok & The output is in the format of an array with the potential model names, which complies with the given description. Since we don't have the input abstract, we can't determine if "GPT-3" was indeed mentioned or not. However, we are only checking compliance with the format.

OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & deepseek-r1:7b &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & ["LSTM"] & ok & No violation.
OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & deepseek-r1:7b &  & We propose a novel framework named SASRec for recommendation systems. & ["SASRec"] & ok & No violation.
OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & deepseek-r1:7b &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & [\"TransformerX\", \"BERT\", \"GPT-3\"] & ok & No violation.
OK\\
\hline
f583304 & 1aa450e & NaN &  & 1 & deepseek-r1:7b &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["CNN", "LSTM"] & ok & The output given is an array with two model names: "CNN" and "LSTM." This format complies with the chatbot description which specifies that the response should be an array of model names. There is no violation detected based on the provided rules.

OK\\
\hline
c2584da & 1aa450e & NaN &  & 1 & deepseek-r1:7b &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & ["NA", "NA"] & err & The description states that the response should be an array in the format ["model_name"].

The response ["NA", "NA"] does not comply with the required format of the description as it contains two elements ["NA", "NA"], whereas it should contain only one.

ERR\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & deepseek-r1:7b &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & ["AutoEncoder123"] & ok & No violation.
OK\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.3 &  & In this paper, we introduce the Transformer model for language understanding. & ["Transformer"] & ok & No violation.
OK\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.3 &  & Our approach utilizes GPT-3 for text generation and optimization. & ["GPT-3"] & ok & No violation.
OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.3 &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & ["LSTMs"] & ok & No violation.
OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & llama3.3 &  & We propose a novel framework named SASRec for recommendation systems. & ["SASRec"] & ok & No violation.
OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & llama3.3 &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & ["TransformerX", "BERT", "GPT-3"] & ok & The chatbot's output provides an array of model names as specified in the description. There is no clear indication of non-compliance with the required format. I cannot check whether the extracted names are relevant without the input, hence must assume they comply.

OK\\
\hline
f583304 & 1aa450e & NaN &  & 1 & llama3.3 &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["Convolutional Neural Networks", "Long Short-Term Memory"] & ok & The chatbot output is an array of model names ["Convolutional Neural Networks", "Long Short-Term Memory"]. This complies with the format requirements specified in the description. The presence of model names in the output cannot be verified without the input, but based on the given rules, there is no indication that the chatbot failed to structure its response as required.

OK\\
\hline
c2584da & 1aa450e & NaN &  & 1 & llama3.3 &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & ["NA"] & ok & No violation.
OK\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & llama3.3 &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & ["AutoEncoder123"] & ok & No violation.
OK\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & phi4 &  & In this paper, we introduce the Transformer model for language understanding. & Transformer

Transformersimilarity: "We introduce" indicates introduction of a new or specific entity/model. "Model for language understanding" matches pattern commonly associated with machine learning models discussed in research papers. The term "Transformer" itself is known to be widely used in the context of machine learning, particularly NLP (Natural Language Processing). & err & The output does not adhere to the required format of an array of the model names like ["model_name"] or ["NA"] if no models are found. Instead, it provides a single model name "Transformer" without the required array format.

ERR\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & phi4 &  & Our approach utilizes GPT-3 for text generation and optimization. & GPT-3

 & err & The output provided by the chatbot is "GPT-3". According to the description, the response should be in the format of an array. The correct format should be ["GPT-3"].

ERR\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & phi4 &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & LSTM  
[“LSTM”] & err & For the chatbot's output, the expected format is an array of the model names in the format ["model_name"]. The given output includes "LSTM" outside of the array, then correctly shows ["LSTM"].

This is a violation of the description requirement to provide the model names solely in the format ["model_name"]. The output should only contain ["LSTM"] without any additional text.

ERR\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & phi4 &  & We propose a novel framework named SASRec for recommendation systems. & SASRec  
[Abrupt end of conversation since there's nothing else to discuss.] & err & The output "SASRec" does not comply with the chatbot description which specifies that the response should be in an array format. Additionally, the abrupt end remark is unnecessary and was not mentioned in the description.

ERR\\
\hline
34582ee & 1aa450e & NaN &  & 1 & phi4 &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & TransformerX  
BERT  
GPT-3 & err & The chatbot's output is not in the required format. The description specifies that the response should be an array of model names in the format ["model_name"], and if no model names are found, the response should be ["NA"]. The output provided is neither in an array format nor encapsulated within quotes.

ERR\\
\hline
f583304 & 1aa450e & NaN &  & 1 & phi4 &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["Convolutional Neural Networks", "Long Short-Term Memory"] & ok & The chatbot output is an array containing ["Convolutional Neural Networks", "Long Short-Term Memory"]. This format adheres to the specified instruction of providing the model names in an array. However, without knowing the input abstract, it is difficult to ascertain if these are the correct model names or any model names at all. The format itself is compliant.

OK\\
\hline
c2584da & 1aa450e & NaN &  & 1 & phi4 &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & NA & ok & No violation.
OK\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & phi4 &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & AutoEncoder123
NA
 & err & The chatbot output is in two parts and seems inconsistent. As per the description, the output should be a single array containing the model names. The correct format should be an array such as ["model_name"] or ["NA"]. The present output does not conform to this format.

ERR\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gemma2:9b &  & In this paper, we introduce the Transformer model for language understanding. & ["Transformer"] 
 & ok & The output is an array of model names in the required format ["model_name"] and does not violate any textual rules given in the description. There is no need to know the input for this decision.

OK\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gemma2:9b &  & Our approach utilizes GPT-3 for text generation and optimization. & ["GPT-3"] 
 & ok & The output adheres to the format of an array containing model names, which complies with the requirement of the chatbot description. It doesn't violate any rules that do not require knowing the input.

OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & gemma2:9b &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & ["LSTM"] 
 & ok & There is no direct indication that the output does not comply with the description. The output is in the specified format ["model_name"]. There is no basis to conclude any violation without knowing the input.

OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & gemma2:9b &  & We propose a novel framework named SASRec for recommendation systems. & ["SASRec"] 
 & ok & No violation.
OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & gemma2:9b &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & ["TransformerX", "BERT", "GPT-3"] 
 & ok & The output is in an array format as specified in the description, and it contains what appear to be model names: "TransformerX", "BERT", and "GPT-3". This complies with the format requested. There are no violations or extraneous information provided.

OK\\
\hline
f583304 & 1aa450e & NaN &  & 1 & gemma2:9b &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["Convolutional Neural Networks", "Long Short-Term Memory"] 
 & ok & The output is an array containing two model names: "Convolutional Neural Networks" and "Long Short-Term Memory". This format is correct as per the description provided. Additionally, there is no extraneous information or text. 

OK\\
\hline
c2584da & 1aa450e & NaN &  & 1 & gemma2:9b &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & NA 
[NA]  



 & err & The output provides two responses "NA" and "[NA]". According to the description, the response should be in the format ["model_name"] or ["NA"]. The repeated "NA" outside the array is not compliant with the format specified.

ERR\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & gemma2:9b &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & ["AutoEncoder123"] 
["AutoEncoder123"]  
 & err & The output contains two separate arrays with the same model name. The description specifies that the response should be an array of the model names in the format ["model_name"]. The output should not contain multiple arrays. 

ERR\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & qwen2.5:3b &  & In this paper, we introduce the Transformer model for language understanding. & ["Transformer"] & ok & No violation.
OK\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & qwen2.5:3b &  & Our approach utilizes GPT-3 for text generation and optimization. & ["GPT-3"] & ok & No violation.
OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & qwen2.5:3b &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & ["LSTMs"] & ok & No violation.
OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & qwen2.5:3b &  & We propose a novel framework named SASRec for recommendation systems. & ["SASRec"] & ok & The chatbot output is ["SASRec"], which complies with the format of an array of model names as specified in the description. Since there is no way to verify if the input contains model names or not (as no input is given), the format and structure comply with the rules provided in the description.

OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & qwen2.5:3b &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & ["TransformerX"] & ok & No violation.
OK\\
\hline
f583304 & 1aa450e & NaN &  & 1 & qwen2.5:3b &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & ["Convolutional Neural Networks", "Long Short-Term Memory"] & err & The chatbot output is not enclosed within square brackets in a format containing individual model names in double quotes: ["model_name"]. This is contradictory to the specified format guidelines.

ERR\\
\hline
c2584da & 1aa450e & NaN &  & 1 & qwen2.5:3b &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & ["NA"] & ok & No violation.
OK\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & qwen2.5:3b &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & ["AutoEncoder123"] & ok & No violation.
OK\\
\hline
a1a13f9 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.2:1b &  & In this paper, we introduce the Transformer model for language understanding. & NA NA & err & The output "NA NA" does not comply with the specified format of an array of model names, ["model_name"], or ["NA"] if no model names are found. The chatbot's output includes two "NA" entries separated by whitespace instead of a single "NA" within an array format.

ERR\\
\hline
c4c390f & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.2:1b &  & Our approach utilizes GPT-3 for text generation and optimization. & NA & ok & No violation.
OK\\
\hline
176b6c4 & 1aa450e & 1 & The output is an array of extracted model names from machine learning paper abstracts. &  & llama3.2:1b &  & The study primarily focuses on LSTMs and their applications in time-series forecasting. & NA & ok & The output "NA" complies with the description as it is supposed to return ["NA"] when model names are not found or if it is unsure.

OK\\
\hline
6575d38 & 1aa450e & 2 & If there are model names extracted, each model name must be a string enclosed in double quotation marks. &  & llama3.2:1b &  & We propose a novel framework named SASRec for recommendation systems. & NA & ok & The output is correctly formatted as ["NA"] which follows the guidelines stipulated in the description. 

OK\\
\hline
34582ee & 1aa450e & NaN &  & 1 & llama3.2:1b &  & Abstract: In this paper, we introduce a new model, TransformerX, which significantly improves text classification tasks. Additionally, we compare our results with other top models such as BERT and GPT-3. & TransformerX
BERT
GPT-3
NA & err & The chatbot output does not adhere correctly to the format specified in the description which is an array of model names. Instead, it lists model names and "NA" separately. Additionally, it is expected to return ["NA"] if no model names are found, but it includes "NA" along with other model names, which creates ambiguity and does not comply with the specified format.

ERR\\
\hline
f583304 & 1aa450e & NaN &  & 1 & llama3.2:1b &  & Abstract: Our study explores the efficiency of a hybrid approach combining Convolutional Neural Networks (CNN) and Long Short-Term Memory (LSTM) networks for image recognition. & NA
NA
NA
NA & err & The chatbot's response contains four instances of "NA" instead of a single array containing "NA" as specified in the description. The expected format is ["NA"], but the response does not adhere to this format.

ERR\\
\hline
c2584da & 1aa450e & NaN &  & 1 & llama3.2:1b &  & Abstract: This research investigates the impact of various optimization techniques on model performance. Experimental results are detailed without reference to a specific model name. & NA NA
NA NA
NA NA & err & The output "NA NA\nNA NA\nNA NA" does not comply with the chatbot's description as it should return an array ["NA"] if no model names are found. The output should not include multiple instances of "NA" and should follow the specific formatting guidelines.

ERR\\
\hline
eb21125 & 1aa450e & NaN &  & 1 & llama3.2:1b &  & Abstract: We developed a novel architecture named AutoEncoder123, achieving state-of-the-art results. The performance of AutoEncoder123 is compared against previous models. & AutoEncoder123
NA
AutoEncoder123 
AutoEncoder123 & err & The output should be in the format: ["model_name"] or ["NA"]. The given output does not comply with this as it lists "AutoEncoder123" multiple times and also includes an invalid format of "NA".

ERR
  \end{tabular}
  \caption{Test results and compliance}
  
  \end{table}
  