
  \begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
  \hline
  id & promptid & ruleid & rule & model & input & output & compliance & complianceText & baseline \\
  \hline
  2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & This is the first sentence. This is the second sentence! Is this the third sentence? & ```html
<p><strong>This is the first sentence.</strong> <em>This</em> <em>is</em> <em>the</em> <em>first</em> <em>sentence.</em></p>
<p><strong>This is the second sentence!</strong> <em>This</em> <em>is</em> <em>the</em> <em>second</em> <em>sentence!</em></p>
<p><strong>Is this the third sentence?</strong> <em>Is</em> <em>this</em> <em>the</em> <em>third</em> <em>sentence?</em></p>
``` & err & The `<em>` tags are applied to every individual word within each sentence instead of selectively emphasizing key words and phrases as specified in the description.
ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> <em>is</em> the <em>first</em> sentence. </p>
<p><strong>This</strong> <em>is</em> the <em>second</em> sentence! </p>
<p><strong>Is</strong> <em>this</em> the <em>third</em> sentence?</p>
 


 & ok & No violation.
OK & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p> & err & The output contains three `<p>` tags, which meets the requirement of having at least three `<p>` tags. However, each `<p>` tag wraps multiple sentences instead of a single sentence as specified in the description. The description instructs to split the paragraph into individual sentences and wrap each sentence with its own `<p>` tag. Additionally, while each `<p>` tag includes one `<strong>` tag and multiple `<em>` tags, the incorrect grouping of sentences within each `<p>` tag violates the specified formatting instructions.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & This is the first sentence. This is the second sentence! Is this the third sentence? & Here's a suggested format for your paragraph:

<p>This is the first sentence.</p>
<p>**This is the second sentence!**</p>
<p>This is the third sentence (shouldn't this be the third sentence?)</p>

However, it seems I was incorrect that there were only three sentences. Here is the corrected response with at least three <p> tags and <strong>, <em>, and </p> tags as requested:

<p>This is the first sentence.</p>
<p><strong>HTML</strong> is a popular markup language used for web development</p>
<p><em>web design</em> and is often used in conjunction with other technologies such</p>
<p>as HTML tags and CSS styling</p> & err & The chatbot output does not consistently include one <strong> tag and multiple <em> tags within each <p> tag as required. Specifically, the first and fourth <p> tags lack both <strong> and <em> tags, the second <p> uses markdown bold (** **) instead of the <strong> tag, and the third <p> contains only a single <em> tag instead of multiple.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & Hello world! Learning to code is fun. Let's write some tests. & ```html
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
``` & ok & No violation.
OK & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong>Hello</strong> <em>world</em>!</p>
<p>Learning to <strong>code</strong> is <em>fun</em>.</p>
<p>Let's <em>write</em> some <strong>tests</strong>.</p> 


Let me know if you'd like me to adjust the emphasis or create any other HTML formatting! & err & Each `<p>` tag contains only one `<em>` tag, but the description requires multiple `<em>` tags within each `<p>` to emphasize key words and phrases.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong><em>Hello</em></strong><em>World!</em> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p> & err & The chatbot output includes multiple `<strong>` tags within each `<p>` tag, whereas the description specifies only one `<strong>` tag per `<p>` and multiple `<em>` tags for emphasis.

ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & Hello world! Learning to code is fun. Let's write some tests. & <p>Hello world! Learning to code is fun.</p><p>Let's write some tests.</p>
<p><strong>While</strong> writing tests, I find it challenging <em>due</em> to limited testing tools and resources.</em></p>
<p><strong>The</strong> current state of development in the project <em>presents</em> a significant hurdle for successful deployment.</em> & err & The first two `<p>` tags do not contain the required `<strong>` and `<em>` tags. Additionally, there are extra closing `</em>` tags outside of their corresponding opening tags in the last two `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & First sentence. Second sentence. Third sentence is here. & ```html
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
``` & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & First sentence. Second sentence. Third sentence is here. & <p><strong>First</strong> <em>sentence</em>.</p>
<p><strong>Second</strong> <em>sentence</em>.</p>
<p><strong>Third</strong> <em>sentence</em> <em>is</em> <em>here</em>.</p>  


Let me know if you'd like to experiment with more complex text formatting! & err & The output includes additional text outside of the required `<p>` tags, which does not comply with the description.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & First sentence. Second sentence. Third sentence is here. & Here's how the paragraph would look with each sentence wrapped in a `<p>` tag and structured as you requested:

```html
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
```

Please note that in the second `<p>` tag, I've repeated "sentence" to adhere strictly to your instructions of adding multiple `<em>` tags inside each paragraph for emphasis. & err & The chatbot's output contains only two `<p>` tags, whereas the description explicitly requires at least three `<p>` tags.

ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & First sentence. Second sentence. Third sentence is here. & Here's the formatted paragraph with three <p> tags, each containing a <strong> tag and one or more <em> tags:

First sentence: This is the first part of the text<strong>This</strong><em>begins</em></p>

Second sentence: The second sentence contains additional information that will be elaborated upon in further paragraphs<strong>Here</strong><em>this</em><span> detail</span></p>

Third sentence:
 
First third sentence. <strong>Text</strong> <em>in</em> <strong>italic</strong> <em>matter</em> 
 
Second third sentence.

First third sentence. This is the same paragraph again<strong>However</strong><em>This</em> was removed to avoid duplicate content

Third third sentence
 This is the final third sentence.<strong>Summary</strong><em> of</em></p> & err & The second `<p>` tag includes a `<span>` tag, which is not specified in the description. Additionally, the third `<p>` tag contains multiple `<strong>` tags instead of just one as required.

ERR & \\
\hline
9ad6081 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gpt-4o-mini & Sentence one. Sentence two. Sentence three. Sentence four. & ```html
<p><strong>Sentence one.</strong> <em>Sentence</em> <em>two.</em></p>
<p><strong>Sentence three.</strong> <em>Sentence</em> <em>four.</em></p>
<p><strong>Sentence one.</strong> <em>Sentence</em> <em>two.</em></p>
<p><strong>Sentence three.</strong> <em>Sentence</em> <em>four.</em></p>
``` & ok & The chatbot's output adheres to the specified description by including four `<p>` tags (meeting the minimum requirement of three), each containing one `<strong>` tag and multiple `<em>` tags, as instructed.

OK & \\
\hline
9ad6081 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gemma2:9b & Sentence one. Sentence two. Sentence three. Sentence four. & <p><strong>Sentence</strong> <em>one</em>. </p>
<p><strong>Sentence</strong> <em>two</em>. </p>
<p><strong>Sentence</strong> <em>three</em>. </p>
<p><strong>Sentence</strong> <em>four</em>. </p> 


Let me know if you'd like me to format a specific paragraph of text with this style!  I can help you customize the emphasis as well. & err & Each `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>`.
ERR & \\
\hline
9ad6081 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & qwen2.5:3b & Sentence one. Sentence two. Sentence three. Sentence four. & <p><strong>There</strong> are <em>multiple sentences</em> in this paragraph, each wrapped with a <p> tag.</p>
<p><strong>Sentence</strong> <em>one</em> should be emphasized as it is the first sentence in the list.</p>
<p><strong>Each sentence</strong> should have its own set of <em>bolded words</em>.</p>
<p><strong>Sentence four</strong> is part of the paragraph and should also be properly formatted with appropriate tags.</p>
This arrangement ensures that each sentence is wrapped in a <p> tag, which allows for better semantic meaning within HTML. Inside each <p> tag, there are additional emphasis applied through <strong> and multiple <em> tags to cover different levels of importance or detail. & err & The chatbot's output includes additional explanatory text outside of the required `<p>` tags, which is not compliant with the description that specifies the output should consist solely of the formatted HTML without extra content.
ERR & \\
\hline
9ad6081 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & llama3.2:1b & Sentence one. Sentence two. Sentence three. Sentence four. & Here is the formatted paragraph:

<p>
  This is the first sentence. The <strong>word</strong> "web" <em>developer</em> is formatting a paragraph of text as HTML. 
</p>

<p>
  Sentence two: The <em>ruler</em>, with its sharp edges, is used to draw straight lines.
  
  Please note that "<em>yesterday</em>" was not emphasized in the original sentence, so I added it here for emphasis.
  
  This paragraph will now be formatted with a stronger word emphasis and double asterism ("**") around each word:
  The <strong>w**word</strong>d<u>eb<em>r</em>u</em>r</strong> is 
  u\&#57;<em>ss</e<em>m</em>e<t)d<i</i><em>t</e</em>-ed a paragraph of text as HTML.
</p>

<p>
  Sentence three: The <em>screen</em> emits light, and the developer will focus on creating a user-friendly interface.

  
  This sentence is quite long and complex. To emphasize it, I added <strong>adjectives</strong>, like "complex", to describe its contents.
  **The**<span class="emphasis">developer</span><b>s**creen</b> emits light, and the <i>up<em>c<i>y</e>er</i>n<ie<f>e*i<n>e<i>r</i></i>iful interfa<c>ce.**

</p>

<p>
  Sentence four: The developer will finally be able to see the results of their hard work.

  This sentence requires careful punctuation and capitalization. I added a strong word, "final", emphasizing its importance.
  <!--This is not an actual <strong>word</strong>, just <span class="emphasis">result</span>.<u>s <i>"finale" </i>s a technical term with multiple meanings and contexts in writing, it has to be spelled out properly.</u> -->
  *The *<b>a<em>p<i</i><b>e<strong>p</strong>m</e></b>a*l<em>t</e>i* <u>j<em>ou*r<k</k>r*n<u*d<em> s</em> a*t*c*h*a<i>n*i*s<b*e*d*t<e*p<i*m</i*b<*>r*i*s*a*s*w*r*k</i*m</j*<em> e</c*i*l*t*i*g*e*n<s*p<c*a<p*u<s*d*k*a<i*s<n*k*t<e>a*s*i*c*h*a<u*v*r<e*j*i*l*s<s*i*f*l*a*b*c*i<m*a<u<t>i*l*s*a*c*i*m*b*i*s*g*x<e*k*e*n<u*o*m</u><em>y*i*m<a*r*d<i<k*u*a<i*n<e*i*n<u*p*d<i>n*k*t<c*i<n*k<u*t*a*<b>a<u*p</a*l*i<t*>i</p> & err & The chatbot output contains multiple sentences within a single `<p>` tag, whereas the description requires each sentence to be wrapped in its own `<p>` tag.

ERR & \\
\hline
9e77696 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gpt-4o-mini & First sentence! Second sentence? Third sentence. Fourth sentence! & ```html
<p><strong>First sentence!</strong> <em>This is the beginning.</em></p>
<p><strong>Second sentence?</strong> <em>Is it in question?</em></p>
<p><strong>Third sentence.</strong> <em>Here we present another thought.</em></p>
<p><strong>Fourth sentence!</strong> <em>Finally, we conclude with this.</em></p>
<p><strong>First sentence!</strong> <em>Repeating the cycle.</em></p>
<p><strong>Second sentence?</strong> <em>Still questioning.</em></p>
<p><strong>Third sentence.</strong> <em>Continuing the dialogue.</em></p>
<p><strong>Fourth sentence!</strong> <em>Ending with a statement.</em></p>
``` & err & Each `<p>` tag contains only one `<em>` tag, whereas the description specifies that multiple `<em>` tags should be used to emphasize key words and phrases.
ERR & \\
\hline
9e77696 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gemma2:9b & First sentence! Second sentence? Third sentence. Fourth sentence! & <p><strong>First</strong> <em>sentence</em>! </p>
<p><strong>Second</strong> <em>sentence</em>? </p>
<p><strong>Third</strong> <em>sentence</em>.</p>
<p><strong>Fourth</strong> <em>sentence</em>!</p>  


Let me know if you have any other text you'd like me to format! & err & Each `<p>` tag in the chatbot output contains only one `<em>` tag, whereas the description specifies that multiple `<em>` tags should be used to emphasize key words and phrases within each paragraph.
ERR & \\
\hline
9e77696 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & qwen2.5:3b & First sentence! Second sentence? Third sentence. Fourth sentence! & <p><strong>First</strong> sentence! <em>Second</em> sentence? <em>Third</em> sentence. <em>Fourth</em> sentence!</p>
<p><strong>First</strong> sentence! <em>Second</em> sentence? <em>Third</em> sentence. <em>Fourth</em> sentence!</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
9e77696 & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & llama3.2:1b & First sentence! Second sentence? Third sentence. Fourth sentence! & Here is the formatted paragraph:


<font face="Arial" size="2">
<b>First</b> sentence!

<p>
<strong>Bullet points</strong> are useful for organizing multiple ideas or lists. 
<span Emphasizing key vocabulary:</span>
<strong>Rapid <em>informational exchange</em></strong>
</p>

<font face="Verdana" size="3">
<em>parsing and analysis have become critical components of modern research.</em>
<p><b>Critical thinking is essential for problem-solving in today's complex world.</b></p>

<b>Novel tools have emerged, making it easier to gather data and analyze results.</b> & err & The output contains only two `<p>` tags instead of the required minimum of three. Additionally, there are HTML tags like `<font>` and `<b>` used outside of `<p>` tags, which does not comply with the instruction to wrap each sentence within `<p>` tags.

ERR & \\
\hline
0155e1c & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gpt-4o-mini & One. Two. Three. & ```html
<p><strong>One.</strong> <em>Two.</em> <em>Three.</em></p>
<p><strong>One.</strong> <em>Two.</em> <em>Three.</em></p>
``` & err & The output contains only two `<p>` tags, but the description requires at least three.
ERR & \\
\hline
0155e1c & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & gemma2:9b & One. Two. Three. & <p><strong>One</strong> <em>two</em> <strong>three</strong>.</p>
<p><strong>One</strong> <em>two</em> <strong>three</strong>.</p>
<p><strong>One</strong> <em>two</em> <strong>three</strong>.</p>   


Let me know if you'd like to see this done with a different paragraph of text! & err & The chatbot output includes multiple `<strong>` tags within each `<p>` tag instead of only one, as specified in the description.
ERR & \\
\hline
0155e1c & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & qwen2.5:3b & One. Two. Three. & <p><strong><em>One.</em></strong><em>Two.</em><strong><em>Three.</em></strong></p>
<p><strong><em>One.</em></strong><em>Two.</em><strong><em>Three.</em></strong></p> & err & The output contains only two `<p>` tags, but the description requires at least three `<p>` tags.
ERR & \\
\hline
0155e1c & b70fdc4 & 2 & The output HTML must contain at least three <p> tags. & llama3.2:1b & One. Two. Three. & Here is the paragraph reformatted with at least three `<p>` tags, one `<strong>` tag, and multiple `<em>` tags:

<p>One moment, please.</p>
<p>The world as we know it <strong>...</</strong></p>
<p>was forever changed by the discovery of a new planet,<em>, which became known as <strong>The New Eden</strong>.</em>.</p>
<p>However,<strong>,</strong> humanity was not ready for such a revolutionary find.</p>
<p>Please stand by while we process your request.</p>
<p>We apologize,</em>, but it seems our system has encountered an error;<em>...</em> & err & The chatbot's output contains `<p>` tags that sometimes lack the required `<strong>` and multiple `<em>` tags inside them. For example, the fifth `<p>` tag does not include any `<strong>` or `<em>` tags. Additionally, there are instances of improperly nested or closed tags, such as a stray `</em>` without a corresponding opening tag. These inconsistencies indicate non-compliance with the described formatting requirements.

ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & This is the first sentence. This is the second sentence! Is this the third sentence? & ```html
<p><strong>This is the first sentence.</strong> <em>This</em> <em>is</em> <em>the</em> <em>first</em> <em>sentence.</em></p>
<p><strong>This is the second sentence!</strong> <em>This</em> <em>is</em> <em>the</em> <em>second</em> <em>sentence!</em></p>
<p><strong>Is this the third sentence?</strong> <em>Is</em> <em>this</em> <em>the</em> <em>third</em> <em>sentence?</em></p>
``` & err & The `<em>` tags are applied to every individual word within each sentence instead of selectively emphasizing key words and phrases as specified in the description.
ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> <em>is</em> the <em>first</em> sentence. </p>
<p><strong>This</strong> <em>is</em> the <em>second</em> sentence! </p>
<p><strong>Is</strong> <em>this</em> the <em>third</em> sentence?</p>
 


 & ok & No violation.
OK & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p> & err & The output contains three `<p>` tags, which meets the requirement of having at least three `<p>` tags. However, each `<p>` tag wraps multiple sentences instead of a single sentence as specified in the description. The description instructs to split the paragraph into individual sentences and wrap each sentence with its own `<p>` tag. Additionally, while each `<p>` tag includes one `<strong>` tag and multiple `<em>` tags, the incorrect grouping of sentences within each `<p>` tag violates the specified formatting instructions.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & This is the first sentence. This is the second sentence! Is this the third sentence? & Here's a suggested format for your paragraph:

<p>This is the first sentence.</p>
<p>**This is the second sentence!**</p>
<p>This is the third sentence (shouldn't this be the third sentence?)</p>

However, it seems I was incorrect that there were only three sentences. Here is the corrected response with at least three <p> tags and <strong>, <em>, and </p> tags as requested:

<p>This is the first sentence.</p>
<p><strong>HTML</strong> is a popular markup language used for web development</p>
<p><em>web design</em> and is often used in conjunction with other technologies such</p>
<p>as HTML tags and CSS styling</p> & err & The chatbot output does not consistently include one <strong> tag and multiple <em> tags within each <p> tag as required. Specifically, the first and fourth <p> tags lack both <strong> and <em> tags, the second <p> uses markdown bold (** **) instead of the <strong> tag, and the third <p> contains only a single <em> tag instead of multiple.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & Hello world! Learning to code is fun. Let's write some tests. & ```html
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
``` & ok & No violation.
OK & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong>Hello</strong> <em>world</em>!</p>
<p>Learning to <strong>code</strong> is <em>fun</em>.</p>
<p>Let's <em>write</em> some <strong>tests</strong>.</p> 


Let me know if you'd like me to adjust the emphasis or create any other HTML formatting! & err & Each `<p>` tag contains only one `<em>` tag, but the description requires multiple `<em>` tags within each `<p>` to emphasize key words and phrases.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong><em>Hello</em></strong><em>World!</em> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p> & err & The chatbot output includes multiple `<strong>` tags within each `<p>` tag, whereas the description specifies only one `<strong>` tag per `<p>` and multiple `<em>` tags for emphasis.

ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & Hello world! Learning to code is fun. Let's write some tests. & <p>Hello world! Learning to code is fun.</p><p>Let's write some tests.</p>
<p><strong>While</strong> writing tests, I find it challenging <em>due</em> to limited testing tools and resources.</em></p>
<p><strong>The</strong> current state of development in the project <em>presents</em> a significant hurdle for successful deployment.</em> & err & The first two `<p>` tags do not contain the required `<strong>` and `<em>` tags. Additionally, there are extra closing `</em>` tags outside of their corresponding opening tags in the last two `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & First sentence. Second sentence. Third sentence is here. & ```html
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
``` & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & First sentence. Second sentence. Third sentence is here. & <p><strong>First</strong> <em>sentence</em>.</p>
<p><strong>Second</strong> <em>sentence</em>.</p>
<p><strong>Third</strong> <em>sentence</em> <em>is</em> <em>here</em>.</p>  


Let me know if you'd like to experiment with more complex text formatting! & err & The output includes additional text outside of the required `<p>` tags, which does not comply with the description.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & First sentence. Second sentence. Third sentence is here. & Here's how the paragraph would look with each sentence wrapped in a `<p>` tag and structured as you requested:

```html
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
```

Please note that in the second `<p>` tag, I've repeated "sentence" to adhere strictly to your instructions of adding multiple `<em>` tags inside each paragraph for emphasis. & err & The chatbot's output contains only two `<p>` tags, whereas the description explicitly requires at least three `<p>` tags.

ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & First sentence. Second sentence. Third sentence is here. & Here's the formatted paragraph with three <p> tags, each containing a <strong> tag and one or more <em> tags:

First sentence: This is the first part of the text<strong>This</strong><em>begins</em></p>

Second sentence: The second sentence contains additional information that will be elaborated upon in further paragraphs<strong>Here</strong><em>this</em><span> detail</span></p>

Third sentence:
 
First third sentence. <strong>Text</strong> <em>in</em> <strong>italic</strong> <em>matter</em> 
 
Second third sentence.

First third sentence. This is the same paragraph again<strong>However</strong><em>This</em> was removed to avoid duplicate content

Third third sentence
 This is the final third sentence.<strong>Summary</strong><em> of</em></p> & err & The second `<p>` tag includes a `<span>` tag, which is not specified in the description. Additionally, the third `<p>` tag contains multiple `<strong>` tags instead of just one as required.

ERR & \\
\hline
91aef55 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & gpt-4o-mini & Sentence one. Sentence two. Sentence three. & ```html
<p><strong>Sentence one.</strong> <em>Sentence two.</em> <em>Sentence three.</em></p>
<p><strong>Sentence one.</strong> <em>Sentence two.</em> <em>Sentence three.</em></p>
<p><strong>Sentence one.</strong> <em>Sentence two.</em> <em>Sentence three.</em></p>
``` & err & The output wraps multiple sentences within each `<p>` tag instead of wrapping each individual sentence in its own `<p>` tag as specified. This violates the requirement to split the paragraph into individual sentences with each sentence enclosed in a separate `<p>` tag.

ERR & \\
\hline
91aef55 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & gemma2:9b & Sentence one. Sentence two. Sentence three. & <p><strong>This </h3> is the first <em>sentence</em>.  </p>

<p><strong>Here's </strong>the *second* <em>sentence</em></p>

 <p><strong>And this </strong>is the *third* <em>sentence.</em> </p>   




Let me know if you want to experiment with different styles or emphasis! & err & The first `<p>` tag incorrectly closes with `</h3>` instead of `</strong>`. Additionally, asterisks (*) are used for emphasis instead of `<em>` tags in the second and third paragraphs. Furthermore, there is extra text outside the HTML structure that wasn't specified in the description.
ERR & \\
\hline
91aef55 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & qwen2.5:3b & Sentence one. Sentence two. Sentence three. & <p><strong>Here is a paragraph</strong> with separate sentences. Each sentence should be wrapped in its own <p> tag.</p>
<p><strong>The first sentence</strong> will contain multiple emphasis words, such as "emphasized" and "keywords". Let's test this now.</p>
<p><strong>This is the third and final sentence</strong>, which might have more than just keywords to emphasize: considerations, insights, or details that enhance the readers understanding of the paragraph.</p> & err & Each `<p>` tag contains one `<strong>` tag but lacks the required multiple `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
91aef55 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & llama3.2:1b & Sentence one. Sentence two. Sentence three. & Here's the formatted paragraph:

<p>"This is a test sentence."</p>
<p>\*\*It\*** is \*\*a\*** test.</p>
<p>This is a test sentence.</p>
<p>\*\*The\*** best\*** way\*** to\*** learn\*** is\*** practice.\*\* <em>This is for</em> testing purposes only.</p>
<p>The ultimate goal is to \*\*learn\*** and \*\*improve\*** your<em> software development skills</em>. & err & The chatbot's output does not use the required `<strong>` tags, instead it includes `**` and `***` which are Markdown syntax and not valid HTML tags. Additionally, not all `<p>` tags contain both one `<strong>` tag and multiple `<em>` tags as specified. For example, the third `<p>` tag lacks any `<strong>` or `<em>` tags.

ERR & \\
\hline
a203120 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & gpt-4o-mini & First sentence. Second sentence. Third sentence. Fourth sentence. & ```html
<p><strong>First sentence.</strong> <em>This</em> <em>is</em> <em>an</em> <em>important</em> <em>statement.</em></p>
<p><strong>Second sentence.</strong> <em>Make</em> <em>sure</em> <em>to</em> <em>pay</em> <em>attention</em> <em>to</em> <em>the</em> <em>details.</em></p>
<p><strong>Third sentence.</strong> <em>Understanding</em> <em>the</em> <em>context</em> <em>is</em> <em>crucial.</em></p>
<p><strong>Fourth sentence.</strong> <em>Always</em> <em>strive</em> <em>for</em> <em>excellence.</em></p>
<p><strong>First sentence.</strong> <em>This</em> <em>is</em> <em>another</em> <em>important</em> <em>statement.</em></p>
<p><strong>Second sentence.</strong> <em>Revisiting</em> <em>your</em> <em>concepts</em> <em>helps</em> <em>reinforce</em> <em>knowledge.</em></p>
<p><strong>Third sentence.</strong> <em>Collaboration</em> <em>is</em> <em>key</em> <em>to</em> <em>growth.</em></p>
<p><strong>Fourth sentence.</strong> <em>Keep</em> <em>pushing</em> <em>forward.</em></p>
``` & ok & No violation.
OK & \\
\hline
a203120 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & gemma2:9b & First sentence. Second sentence. Third sentence. Fourth sentence. & <p><strong>First</strong> <em>sentence</em>. </p>
<p><strong>Second</strong> <em>sentence</em>. </p>
<p><strong>Third</strong> <em>sentence</em>. </p>
<p><strong>Fourth</strong> <em>sentence</em>. </p>


Let me know if you'd like to refine the emphasis with different words or phrases within each sentence! & err & Each `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
a203120 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & qwen2.5:3b & First sentence. Second sentence. Third sentence. Fourth sentence. & <p><strong>First</strong></p>
<span><em>sentence.</em></span>
<p><strong>Second</strong></p>
<span><em>sentence.</em></span>
<p><strong>Third</strong></p>
<span><em>sentence.</em></span>
<p><strong>Fourth</strong></p>
<span><em>sentence.</em></span>
<p><strong>First</strong></p>
<span><em>sentence.</em></span>
<p><strong>Second</strong></p>
<span><em>sentence.</em></span>
<p><strong>Third</strong></p>
<span><em>sentence.</em></span>
<p><strong>Fourth</strong></p> & err & The `<em>` tags are placed outside the `<p>` tags instead of being inside each `<p>` tag as specified.
ERR & \\
\hline
a203120 & b70fdc4 & 8 & The output HTML must contain fewer than three <p> tags. & llama3.2:1b & First sentence. Second sentence. Third sentence. Fourth sentence. & Since the instructions involve formatting a paragraph with individual sentences wrapped in HTML `p` tags, each with one `<strong>` tag on key words/phrases and multiple `<em>` tags on emphasized keywords/phrases, I will provide the formatted text below.


First sentence.

<p>
  <strong>The</strong> 
  first 
  sentence.  
</p>

Second sentence.

<p>
  <strong>The</strong>
  second
  sentence.
  
</p>

Third sentence.

<p>
  <strong>A</strong>
  third
  sentence.
</p>

Fourth sentence.


<p>
  <strong>This</strong> 
  fourth 
  sentence.
</p> & err & The chatbot's output includes `<p>` tags and a single `<strong>` tag within each paragraph as required. However, it fails to include any `<em>` tags for emphasizing key words or phrases inside each `<p>` tag, violating the instruction to add multiple `<em>` tags.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & This is the first sentence. This is the second sentence! Is this the third sentence? & ```html
<p><strong>This is the first sentence.</strong> <em>This</em> <em>is</em> <em>the</em> <em>first</em> <em>sentence.</em></p>
<p><strong>This is the second sentence!</strong> <em>This</em> <em>is</em> <em>the</em> <em>second</em> <em>sentence!</em></p>
<p><strong>Is this the third sentence?</strong> <em>Is</em> <em>this</em> <em>the</em> <em>third</em> <em>sentence?</em></p>
``` & err & The `<em>` tags are applied to every individual word within each sentence instead of selectively emphasizing key words and phrases as specified in the description.
ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> <em>is</em> the <em>first</em> sentence. </p>
<p><strong>This</strong> <em>is</em> the <em>second</em> sentence! </p>
<p><strong>Is</strong> <em>this</em> the <em>third</em> sentence?</p>
 


 & ok & No violation.
OK & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p> & err & The output contains three `<p>` tags, which meets the requirement of having at least three `<p>` tags. However, each `<p>` tag wraps multiple sentences instead of a single sentence as specified in the description. The description instructs to split the paragraph into individual sentences and wrap each sentence with its own `<p>` tag. Additionally, while each `<p>` tag includes one `<strong>` tag and multiple `<em>` tags, the incorrect grouping of sentences within each `<p>` tag violates the specified formatting instructions.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & This is the first sentence. This is the second sentence! Is this the third sentence? & Here's a suggested format for your paragraph:

<p>This is the first sentence.</p>
<p>**This is the second sentence!**</p>
<p>This is the third sentence (shouldn't this be the third sentence?)</p>

However, it seems I was incorrect that there were only three sentences. Here is the corrected response with at least three <p> tags and <strong>, <em>, and </p> tags as requested:

<p>This is the first sentence.</p>
<p><strong>HTML</strong> is a popular markup language used for web development</p>
<p><em>web design</em> and is often used in conjunction with other technologies such</p>
<p>as HTML tags and CSS styling</p> & err & The chatbot output does not consistently include one <strong> tag and multiple <em> tags within each <p> tag as required. Specifically, the first and fourth <p> tags lack both <strong> and <em> tags, the second <p> uses markdown bold (** **) instead of the <strong> tag, and the third <p> contains only a single <em> tag instead of multiple.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & Hello world! Learning to code is fun. Let's write some tests. & ```html
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
``` & ok & No violation.
OK & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong>Hello</strong> <em>world</em>!</p>
<p>Learning to <strong>code</strong> is <em>fun</em>.</p>
<p>Let's <em>write</em> some <strong>tests</strong>.</p> 


Let me know if you'd like me to adjust the emphasis or create any other HTML formatting! & err & Each `<p>` tag contains only one `<em>` tag, but the description requires multiple `<em>` tags within each `<p>` to emphasize key words and phrases.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong><em>Hello</em></strong><em>World!</em> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p> & err & The chatbot output includes multiple `<strong>` tags within each `<p>` tag, whereas the description specifies only one `<strong>` tag per `<p>` and multiple `<em>` tags for emphasis.

ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & Hello world! Learning to code is fun. Let's write some tests. & <p>Hello world! Learning to code is fun.</p><p>Let's write some tests.</p>
<p><strong>While</strong> writing tests, I find it challenging <em>due</em> to limited testing tools and resources.</em></p>
<p><strong>The</strong> current state of development in the project <em>presents</em> a significant hurdle for successful deployment.</em> & err & The first two `<p>` tags do not contain the required `<strong>` and `<em>` tags. Additionally, there are extra closing `</em>` tags outside of their corresponding opening tags in the last two `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & First sentence. Second sentence. Third sentence is here. & ```html
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
<p><strong>First sentence.</strong> <em>Second sentence.</em> <em>Third sentence</em> <em>is here.</em></p>
``` & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & First sentence. Second sentence. Third sentence is here. & <p><strong>First</strong> <em>sentence</em>.</p>
<p><strong>Second</strong> <em>sentence</em>.</p>
<p><strong>Third</strong> <em>sentence</em> <em>is</em> <em>here</em>.</p>  


Let me know if you'd like to experiment with more complex text formatting! & err & The output includes additional text outside of the required `<p>` tags, which does not comply with the description.
ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & First sentence. Second sentence. Third sentence is here. & Here's how the paragraph would look with each sentence wrapped in a `<p>` tag and structured as you requested:

```html
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
<p><strong>First</strong> sentence. <em>Second</em> sentence. <em>Third</em> sentence <em>is</em> <em>here.</em></p>
```

Please note that in the second `<p>` tag, I've repeated "sentence" to adhere strictly to your instructions of adding multiple `<em>` tags inside each paragraph for emphasis. & err & The chatbot's output contains only two `<p>` tags, whereas the description explicitly requires at least three `<p>` tags.

ERR & \\
\hline
e588b24 & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & First sentence. Second sentence. Third sentence is here. & Here's the formatted paragraph with three <p> tags, each containing a <strong> tag and one or more <em> tags:

First sentence: This is the first part of the text<strong>This</strong><em>begins</em></p>

Second sentence: The second sentence contains additional information that will be elaborated upon in further paragraphs<strong>Here</strong><em>this</em><span> detail</span></p>

Third sentence:
 
First third sentence. <strong>Text</strong> <em>in</em> <strong>italic</strong> <em>matter</em> 
 
Second third sentence.

First third sentence. This is the same paragraph again<strong>However</strong><em>This</em> was removed to avoid duplicate content

Third third sentence
 This is the final third sentence.<strong>Summary</strong><em> of</em></p> & err & The second `<p>` tag includes a `<span>` tag, which is not specified in the description. Additionally, the third `<p>` tag contains multiple `<strong>` tags instead of just one as required.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & This is the first sentence. This is the second sentence! Is this the third sentence? & ```html
<p><strong>This is the first sentence.</strong> <em>This</em> <em>is</em> <em>the</em> <em>first</em> <em>sentence.</em></p>
<p><strong>This is the second sentence!</strong> <em>This</em> <em>is</em> <em>the</em> <em>second</em> <em>sentence!</em></p>
<p><strong>Is this the third sentence?</strong> <em>Is</em> <em>this</em> <em>the</em> <em>third</em> <em>sentence?</em></p>
``` & err & The `<em>` tags are applied to every individual word within each sentence instead of selectively emphasizing key words and phrases as specified in the description.
ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> <em>is</em> the <em>first</em> sentence. </p>
<p><strong>This</strong> <em>is</em> the <em>second</em> sentence! </p>
<p><strong>Is</strong> <em>this</em> the <em>third</em> sentence?</p>
 


 & ok & No violation.
OK & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & This is the first sentence. This is the second sentence! Is this the third sentence? & <p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p>
<p><strong>This</strong> is the <em>first</em> <em>sentence</em>. <em>This</em> is the <em>second</em> <em>sentence</em>! Is <strong>this</strong> the <em>third</em> <em>sentence</em>?</p> & err & The output contains three `<p>` tags, which meets the requirement of having at least three `<p>` tags. However, each `<p>` tag wraps multiple sentences instead of a single sentence as specified in the description. The description instructs to split the paragraph into individual sentences and wrap each sentence with its own `<p>` tag. Additionally, while each `<p>` tag includes one `<strong>` tag and multiple `<em>` tags, the incorrect grouping of sentences within each `<p>` tag violates the specified formatting instructions.

ERR & \\
\hline
2608c0e & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & This is the first sentence. This is the second sentence! Is this the third sentence? & Here's a suggested format for your paragraph:

<p>This is the first sentence.</p>
<p>**This is the second sentence!**</p>
<p>This is the third sentence (shouldn't this be the third sentence?)</p>

However, it seems I was incorrect that there were only three sentences. Here is the corrected response with at least three <p> tags and <strong>, <em>, and </p> tags as requested:

<p>This is the first sentence.</p>
<p><strong>HTML</strong> is a popular markup language used for web development</p>
<p><em>web design</em> and is often used in conjunction with other technologies such</p>
<p>as HTML tags and CSS styling</p> & err & The chatbot output does not consistently include one <strong> tag and multiple <em> tags within each <p> tag as required. Specifically, the first and fourth <p> tags lack both <strong> and <em> tags, the second <p> uses markdown bold (** **) instead of the <strong> tag, and the third <p> contains only a single <em> tag instead of multiple.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gpt-4o-mini & Hello world! Learning to code is fun. Let's write some tests. & ```html
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
<p><strong>Hello world!</strong> <em>Learning</em> to <em>code</em> is <em>fun</em>.</p>
<p><strong>Let's</strong> <em>write</em> some <em>tests</em>.</p>
``` & ok & No violation.
OK & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & gemma2:9b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong>Hello</strong> <em>world</em>!</p>
<p>Learning to <strong>code</strong> is <em>fun</em>.</p>
<p>Let's <em>write</em> some <strong>tests</strong>.</p> 


Let me know if you'd like me to adjust the emphasis or create any other HTML formatting! & err & Each `<p>` tag contains only one `<em>` tag, but the description requires multiple `<em>` tags within each `<p>` to emphasize key words and phrases.
ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & qwen2.5:3b & Hello world! Learning to code is fun. Let's write some tests. & <p><strong><em>Hello</em></strong><em>World!</em> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p>
<p><strong><em>Hello</em></strong> <strong><em>World!</em></strong> <strong><em>Learning</em></strong> to <strong><em>code</em></strong> is <strong><em>fun</em></strong>. Let's <strong><em>writes</em></strong> some <strong><em>tests</em></strong>.</p> & err & The chatbot output includes multiple `<strong>` tags within each `<p>` tag, whereas the description specifies only one `<strong>` tag per `<p>` and multiple `<em>` tags for emphasis.

ERR & \\
\hline
b0f81ff & b70fdc4 & 1 & Each sentence from the input paragraph must be enclosed within a <p> tag, where a <p> tag is an HTML element representing a paragraph. & llama3.2:1b & Hello world! Learning to code is fun. Let's write some tests. & <p>Hello world! Learning to code is fun.</p><p>Let's write some tests.</p>
<p><strong>While</strong> writing tests, I find it challenging <em>due</em> to limited testing tools and resources.</em></p>
<p><strong>The</strong> current state of development in the project <em>presents</em> a significant hurdle for successful deployment.</em> & err & The first two `<p>` tags do not contain the required `<strong>` and `<em>` tags. Additionally, there are extra closing `</em>` tags outside of their corresponding opening tags in the last two `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & He loves coding. She enjoys testing! They prefer debugging? & ```html
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
<p><strong>He loves</strong> <em>coding</em>.</p>
<p><strong>She enjoys</strong> <em>testing</em>!</p>
<p><strong>They prefer</strong> <em>debugging</em>?</p>
``` & err & Each `<p>` tag in the output contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>He</strong> <em>loves</em> coding.</p>
<p><strong>She</strong> <em>enjoys testing</em>!</p> 
<p><strong>They</strong> <em>prefer debugging</em>?</p> 


Let me know if you'd like to experiment with other HTML formatting elements! & err & Each `<p>` tag contains only one `<em>` tag, but multiple `<em>` tags are required to emphasize key words and phrases.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & He loves coding. She enjoys testing! They prefer debugging? & <p><strong>Coding</strong></p>
<p><em>She</em></p>
<p><em>enjoys</em></p>
<p><em>testing</em></p>
<p><strong>she</strong></p>
<p><em>prefers</em></p>
<p><strong>debugging?</strong></p> & err & The `<p>` tags do not consistently contain both one `<strong>` tag and multiple `<em>` tags as specified in the description.
ERR & \\
\hline
ba898fc & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & He loves coding. She enjoys testing! They prefer debugging? & Here is the paragraph formatted as HTML:

<p>He lovescoding.</p>
<p>She enjoystesting!</p>
<p>Theypreferdebugging?</p> & err & Each `<p>` tag in the output does not contain the required `<strong>` and `<em>` tags to emphasize key words and phrases.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & First sentence here. Second one goes here. Third sentence follows. & ```html
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
<p><strong>First sentence</strong> <em>here</em>.</p>
<p><strong>Second one</strong> <em>goes</em> <em>here</em>.</p>
<p><strong>Third sentence</strong> <em>follows</em>.</p>
``` & ok & The output contains six `<p>` tags, each wrapping a sentence. Each `<p>` tag includes one `<strong>` tag and one or more `<em>` tags, which aligns with the formatting requirements.

OK & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>The quick</strong> brown fox <em >jumped over</em> the <strong>lazy</strong> dog. </p>
<p>This was a <strong>very common</strong> phrase <em >used in typography</em> for testing typefaces. </p>
<p>It is often used to demonstrate  <strong>font features</strong> and letter <em >spacing</em>. </p>


Let me know if you'd like me to format any more text! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & First sentence here. Second one goes here. Third sentence follows. & <p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p>
<p><strong>First</strong> sentence here. <em>Second</em> one goes here. <em>Third</em> sentence follows.</p> & err & The output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & \\
\hline
5f56d63 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & First sentence here. Second one goes here. Third sentence follows. & **First Sentence**
<p>This is the first sentence of a paragraph, which would typically be formatted as HTML as follows:</p>
<p><strong>HTML</strong></p>

**Second Sentence**
Second sentence description: This is a secondary statement with multiple clauses and phrases that describe the contents of the <em>paragraph</em>.
<p><strong>This</strong><em> is another paragraph, containing words like "description", "clauses", and <em>"paragraphs."</em>.</Strong></p>

**Third Sentence**
Third sentence completion: A final statement with a more detailed description of what constitutes a paragraph in general.
<p><strong>A</Strong><em> third sentence</Em>, offering additional context and clarity on the topic at hand. </p> & err & The first `<p>` tag does not contain the required `<strong>` and `<em>` tags.
ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gpt-4o-mini & A quick brown fox. Jumps over the lazy dog! What a sight? & ```html
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
<p><strong>A quick brown fox</strong> <em>jumps</em> over the <em>lazy dog</em>!</p>
<p><strong>What a sight</strong> <em>to behold</em>?</p>
``` & ok & No violation.
OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & gemma2:9b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong> quick brown <em>fox</em>. </p>
<p><strong>Jumps</strong> over the <em>lazy</em> <em>dog</em>!</p>
<p><strong>What</strong> a <em>sight</em>?</p>



Let me know if you'd like to style these sentences further! I can add things like colors or different font sizes. & ok & The chatbot output includes three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags as specified. Additionally, the chatbot provides an extra sentence about further styling, which does not violate the given instructions since the description does not restrict adding supplementary information.

OK & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & qwen2.5:3b & A quick brown fox. Jumps over the lazy dog! What a sight? & <p><strong>A</strong><em>quick</em> <strong>brown</strong> <em>fox.</em></p>
<p>Jumps<strong> over</strong> the <strong>lazy</strong> <em>dog!</em></p>
<p>What<a><strong>a</strong></a> <em>sight?</em></p> & err & The third `<p>` tag contains an `<a>` tag, which was not specified in the description. Additionally, the second `<p>` tag only includes one `<em>` tag instead of multiple as required.

ERR & \\
\hline
75a0788 & b70fdc4 & 3 & Each <p> tag must contain exactly one <strong> tag, where a <strong> tag is an HTML element used to strongly emphasize text. & llama3.2:1b & A quick brown fox. Jumps over the lazy dog! What a sight? & Here is the modified paragraph with individual sentences wrapped in <p> tags, each sentence formatted with one <strong> tag and multiple <em> tags to emphasize key words and phrases:

<p>
  <strong>A</strong> quick brown fox.
</p>

<p>
  <strong>What</strong>,
  <sup>a</sup> sight?
</p>

<p>
  This is just the initial message with sentences wrapped in paragraph tags, strong tags, and emphasized keywords using em tags.</p> & err & The chatbot output does not include any `<em>` tags within the `<p>` tags as required by the description. Additionally, the third `<p>` tag lacks a `<strong>` tag altogether.

ERR & \\
\hline
3dc10e8 & b70fdc4 &  &  & gpt-4o-mini & text: The quick brown fox jumps over the lazy dog. She sells seashells by the seashore. How much wood would a woodchuck chuck? & ```html
<p><strong>The quick brown fox</strong> <em>jumps</em> <em>over</em> <em>the lazy dog</em>.</p>
<p><strong>She sells seashells</strong> <em>by the seashore</em>.</p>
<p><strong>How much wood</strong> <em>would a woodchuck chuck</em>?</p>
``` & ok & No violation.
OK & 1\\
\hline
3dc10e8 & b70fdc4 &  &  & gemma2:9b & text: The quick brown fox jumps over the lazy dog. She sells seashells by the seashore. How much wood would a woodchuck chuck? & Here's the HTML formatting for your text:

<p><strong>The</strong> <em>quick</em> brown fox <strong>jumps</strong> over the <em>lazy</em> dog.</p>

<p>She <strong>sells</strong> <em>seashells</em> by the <em>seashore</em>.</p>

<p>How much <em>wood</em> would a <em>woodchuck</em> <strong>chuck</strong>?</p> 


Let me know if you'd like to experiment with different emphasis techniques or have any other text you want to format! 
 & err & The first `<p>` tag contains two `<strong>` tags, but each `<p>` should include only one `<strong>` tag as specified.
ERR & 1\\
\hline
3dc10e8 & b70fdc4 &  &  & qwen2.5:3b & text: The quick brown fox jumps over the lazy dog. She sells seashells by the seashore. How much wood would a woodchuck chuck? & Here is the formatted paragraph with each sentence wrapped in its own <p> tag, and properly nested within <strong><em></em></strong> for emphasis:

```html
<p>
  <strong>
    <em>The</em>
    <em>quick</em>
    <em>brown</em>
    fox
    <em>jumps</em>
    <em>over</em>
    <em>the</em>
    <em>lazy</em>
    <em>dog.</em>
  </strong>
</p>

<p>
  <strong>
    <em>She</em>
    <em>sells</em>
    <em>seashells</em>
    <em>by</em>
    <em>the</em>
    <em>seashore.</em>
  </strong>
</p>

<p>
  <strong>
    <em>How</em>
    <em>much</em>
    <em>would</em>
    <em>a</em>
    <em>woodchuck</em>
    <em>chuck?</em>
  </strong>
</p>
``` & ok & No violation.
OK & 1\\
\hline
3dc10e8 & b70fdc4 &  &  & llama3.2:1b & text: The quick brown fox jumps over the lazy dog. She sells seashells by the seashore. How much wood would a woodchuck chuck? & Here is the reformatted paragraph with individual sentences wrapped in <p> tags, and key words and phrases emphasized using <strong> and <em> tags:

<p>This</p> <strong>quick</strong>, <strong>brown</strong> fox jumps</strong> over lazy</strong> dog.</p>

<p"She</p> sells</strong> seashells</strong> by the</em> seashore.</p>

<p>How</em><span> much</em></span> wood would a woodchuck</strong> chuck?</p> & err & The chatbot output contains several HTML syntax errors, such as improperly closed `<strong>` and `<em>` tags, a malformed `<p>` tag (`<p"She</p>`), and incorrectly nested tags (`<em><span> much</em></span>`). These issues violate the described requirement to wrap each sentence in `<p>` tags with properly nested `<strong>` and `<em>` tags inside.
ERR & 1\\
\hline
fb61b87 & b70fdc4 &  &  & gpt-4o-mini & text: Artificial intelligence is transforming industries. Machine learning algorithms are at the core of this revolution. Businesses must adapt to stay competitive. & ```html
<p><strong>Artificial intelligence</strong> is <em>transforming</em> <em>industries</em>.</p>
<p><strong>Machine learning algorithms</strong> are at the <em>core</em> of this <em>revolution</em>.</p>
<p><strong>Businesses</strong> must <em>adapt</em> to stay <em>competitive</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
fb61b87 & b70fdc4 &  &  & gemma2:9b & text: Artificial intelligence is transforming industries. Machine learning algorithms are at the core of this revolution. Businesses must adapt to stay competitive. & <p><strong>Artificial intelligence</strong> is <em>transforming</em> <strong>industries</strong>.</p>

<p><strong>Machine learning</strong> *algorithms* are at the <em>core</em> of this <em>revolution</em>.</p>

<p><strong>Businesses</strong> must *adapt* to *stay* <strong>competitive</strong>.</p>  
 & err & The chatbot's output violates the description in two ways:
1. Each `<p>` tag contains more than one `<strong>` tag, whereas only one `<strong>` tag is required per `<p>`.
2. The output uses asterisks (*) for emphasis instead of the required `<em>` tags.

ERR & 1\\
\hline
fb61b87 & b70fdc4 &  &  & qwen2.5:3b & text: Artificial intelligence is transforming industries. Machine learning algorithms are at the core of this revolution. Businesses must adapt to stay competitive. & ```html
<p><strong>Artificial</strong> <em>intelligence</em> <strong>is</strong> <em>transforming</em> <strong>industries</strong>.</p>
<p><strong>Machine</strong> <em>learning</em> <strong>algorithms</strong> are <em>at</em> <strong>the</strong> <em>core</em> <strong>this</strong> <em>revolution</em>.</p>
<p><strong>Businesses</strong> must <em>adapt</em> to <strong>stay</strong> <em>competitive</em>.</p>
```

Note: Since the paragraph is provided in a single string, I've inserted line breaks and added additional spaces in the HTML for clarity. In actual practice, you might concatenate these segments into one complete string of code if they're coming from server-side or client-side JavaScript, directly integrated within HTML content, etc., rather than being treated as separate lines of input. & err & Each `<p>` tag contains multiple `<strong>` tags, whereas the description specifies adding **one `<strong>` tag** and multiple `<em>` tags inside each `<p>` tag.
ERR & 1\\
\hline
fb61b87 & b70fdc4 &  &  & llama3.2:1b & text: Artificial intelligence is transforming industries. Machine learning algorithms are at the core of this revolution. Businesses must adapt to stay competitive. & Here's the reformatted paragraph with individual sentences wrapped in <p> tags, one <strong> tag inside each sentence for key words and phrases, and multiple <em> tags to emphasize certain parts:

<p>
  Artificial intelligence is transforming industries.
<p>
  Machine learning algorithms are at the core of this revolution.
<p>
  Businesses must adapt to stay competitive. & err & The chatbot's output includes the required number of `<p>` tags but fails to include any `<strong>` or `<em>` tags within each `<p>` tag as specified in the description.
ERR & 1\\
\hline
da118b1 & b70fdc4 &  &  & gpt-4o-mini & text: Climate change poses a significant threat to our planet. Rising sea levels and extreme weather events are becoming more frequent. It is imperative to take immediate action. & ```html
<p><strong>Climate change</strong> poses a <em>significant threat</em> to our <em>planet</em>.</p>
<p><strong>Rising sea levels</strong> and <em>extreme weather events</em> are becoming <em>more frequent</em>.</p>
<p>It is <strong>imperative</strong> to take <em>immediate action</em>.</p>
``` & err & The third `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
da118b1 & b70fdc4 &  &  & gemma2:9b & text: Climate change poses a significant threat to our planet. Rising sea levels and extreme weather events are becoming more frequent. It is imperative to take immediate action. & <p><strong>Climate</strong> change poses a <em>significant</em> <strong>threat</strong> to our <em>planet</em>.</p>
<p>Rising <em>sea levels</em> and <em>extreme weather events</em> are becoming more <em>frequent</em>.</p>
<p>It is <em>imperative</em> to take <em>immediate action</em>.</p>  


 & err & The second and third `<p>` tags do not contain a `<strong>` tag as required.
ERR & 1\\
\hline
da118b1 & b70fdc4 &  &  & qwen2.5:3b & text: Climate change poses a significant threat to our planet. Rising sea levels and extreme weather events are becoming more frequent. It is imperative to take immediate action. & ```html
<p><strong>Climate</strong> change <em>poses</em> a <em>significant</em> <em>threat</em> to <em>our</em> <em>planet</em>. <em>Rising</em> <em>sea</em> <em>levels</em> and <em>extreme</em> <em>weather</em> <em>events</em> are <em>becoming</em> <em>more</em> <em>frequent</em>. It is <strong>imperative</strong> to <em>take</em> <em>immediate</em> <em>action</em>.</p>
``` & err & Only one <p> tag is present, but at least three <p> tags are required.
ERR & 1\\
\hline
da118b1 & b70fdc4 &  &  & llama3.2:1b & text: Climate change poses a significant threat to our planet. Rising sea levels and extreme weather events are becoming more frequent. It is imperative to take immediate action. & <p>"Climate change poses a significant threat to our planet,"</p>
<strong>Despite recent advancements in renewable energy sources, the world still relies on fossil fuels to meet its energy needs.</strong><em>National policies must prioritize energy efficiency and carbon capture technologies for sustainable growth.</em><br/><br/> <strong>Rising sea levels threaten coastal communities worldwide, displacing 143 million people by 2050.</strong><em>The global sea level rise is exacerbated by climate change-induced thawing of polar ice caps.</em><br/><br/>  <strong>Extreme weather events like droughts, heatwaves, and heavy precipitation are becoming more intense.</strong><em>These extreme weather events have devastating impacts on agriculture, economic growth, and human health.</em><br/><br/> <strong>It is imperative to take immediate action to mitigate climate change by reducing greenhouse gas emissions and increasing energy efficiency.</strong><em>The time to act is now  governments, corporations, and individuals must collaborate in the transition to a low-carbon economy.</em><br/> & err & The `<strong>` and `<em>` tags are placed outside the `<p>` tags instead of inside them as specified in the description.
ERR & 1\\
\hline
d95583f & b70fdc4 &  &  & gpt-4o-mini & text: Reading books expands your knowledge. It fosters critical thinking and empathy. Everyone should make time for reading each day. & ```html
<p><strong>Reading books</strong> <em>expands</em> your <em>knowledge</em>.</p>
<p><strong>It</strong> <em>fosters</em> <em>critical thinking</em> and <em>empathy</em>.</p>
<p><strong>Everyone</strong> should make <em>time</em> for <em>reading</em> each <em>day</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
d95583f & b70fdc4 &  &  & gemma2:9b & text: Reading books expands your knowledge. It fosters critical thinking and empathy. Everyone should make time for reading each day. & <p><strong>Reading</strong> books expands your <em>knowledge</em>.</p>
<p>It fosters <em>critical thinking</em> and <em>empathy</em>.</p>
<p><strong>Everyone</strong> should make time for <em>reading</em> <u>each</u> day.</p> 


Let me know if you'd like to experiment with different emphasis tags or styles! & err & The second `<p>` tag lacks a `<strong>` tag, and the third `<p>` tag includes an `<u>` tag, which is not specified in the description.
ERR & 1\\
\hline
d95583f & b70fdc4 &  &  & qwen2.5:3b & text: Reading books expands your knowledge. It fosters critical thinking and empathy. Everyone should make time for reading each day. & Here is the paragraph formatted with <p>, <strong>, and multiple <em> tags:

```html
<p><strong><em>Reading</em></strong> books expands your knowledge.<em><strong><em>It</em></strong> fosters critical thinking,</em> and<em> empathy.</em> Everyone should make time for reading each day.</p>
```

Each sentence is wrapped in a <p> tag, with the first word of each sentence emphasized by placing it inside a nested <em> tag, as well as any important phrases within <strong> tags. & err & The chatbot output uses only one `<p>` tag instead of at least three as specified.
ERR & 1\\
\hline
d95583f & b70fdc4 &  &  & llama3.2:1b & text: Reading books expands your knowledge. It fosters critical thinking and empathy. Everyone should make time for reading each day. & <p>Reading books increases your knowledge rapidly.</p>
<i>It</i>=<strong> fostered</strong><em>r critical thought processes</em>, cultivating a deeper understanding of complex ideas and concepts.</p>

<p>Moreover, <strong><em>reading</em></strong> book titles convey rich sensory information, enhancing one's ability to visualize scenes and characters.</p>
<i>By</i>=<strong><em>engaging</em></strong><em>with</em>A<em>s</em>+t<em>t</em>+<em>O</em>+<em>H</em>-e</i>, readers are able to <em>nurture</em>T</em>i>a wider spectrum of emotions and attitudes.</p>

<p>Furthermore, the process of reading has been shown to have numerous <strong><em>sociological</em></strong><em>patriotritic</em>-<em>al</em>-factors to consider, allowing readers to contextualize their own experiences within a broader cultural narrative.</p>
<i>From</i>+<strong><em>a</em></strong><em>more</em>+<em>deterministic</em><em>viewpoint</em>, book <em>reading</em>naturally leads to introspection, self-awareness, and personal growth.</i> & err & The chatbot's output contains improperly closed `<p>` tags and includes content outside of `<p>` tags. Additionally, not all `<p>` tags consistently contain the required `<strong>` and multiple `<em>` tags as specified.

ERR & 1\\
\hline
cce0006 & b70fdc4 &  &  & gpt-4o-mini & text: Cooking at home can be healthier and more economical. Experimenting with new recipes is a great way to enhance your culinary skills. Sharing meals with family strengthens bonds. & ```html
<p><strong>Cooking at home</strong> can be <em>healthier</em> and more <em>economical</em>.</p>
<p><strong>Experimenting with new recipes</strong> is a great way to <em>enhance</em> your <em>culinary skills</em>.</p>
<p><strong>Sharing meals with family</strong> strengthens <em>bonds</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
cce0006 & b70fdc4 &  &  & gemma2:9b & text: Cooking at home can be healthier and more economical. Experimenting with new recipes is a great way to enhance your culinary skills. Sharing meals with family strengthens bonds. & <p><strong>Cooking</strong> at home can be <em>healthier</em> and <em>more economical</em>.</p>
<p><strong>Experimenting</strong> with <em>new recipes</em> is a <em>great</em> way to <strong>enhance</strong> your <em>culinary skills</em>.</p>
<p><strong>Sharing meals</strong> with <em>family</em> **strengthens** <em>bonds</em>.</p> 


Let me know if you'd like me to experiment with other HTML formatting options! & err & The chatbot used multiple `<strong>` tags within a single `<p>` tag instead of limiting it to one per paragraph as specified. Additionally, it incorrectly used `**` for bolding instead of the `<strong>` tag in the third paragraph.

ERR & 1\\
\hline
cce0006 & b70fdc4 &  &  & qwen2.5:3b & text: Cooking at home can be healthier and more economical. Experimenting with new recipes is a great way to enhance your culinary skills. Sharing meals with family strengthens bonds. & Here is the paragraph split into sentences, each wrapped in <p> tags with emphasis on key words using <strong> and multiple <em> tags:

```html
<p><strong>Cooking</strong> at home can be healthier and more economical.</p>
<p><strong>Experimenting</strong> with new recipes is a <em>great way</em> to <em>enhance</em> your <strong>culinary</strong> skills.</p>
<p><strong>Sharing</strong> meals with family strengthens <strong>relationships</strong>.</p>
```

Note that the text provided had only two sentences. I've divided it into three sentences as per your instruction. & err & The third `<p>` tag contains two `<strong>` tags instead of the required one.
ERR & 1\\
\hline
cce0006 & b70fdc4 &  &  & llama3.2:1b & text: Cooking at home can be healthier and more economical. Experimenting with new recipes is a great way to enhance your culinary skills. Sharing meals with family strengthens bonds. & Here is the formatted paragraph:

<p>Cooking at home can be healthier and more economical.</p>
<p><strong>Cooking at home</strong> can <em>be healthier</em> and <em>more economical</em>.</p>
<p><strong>Experimenting</strong> with new recipes is a great way to enhance your culinary skills.</p>
<p><strong>Sharing meals</strong> with family strengthens bonds.</p> & err & Several `<p>` tags lack the required `<strong>` and `<em>` tags. Specifically, the first `<p>` does not contain any `<strong>` or `<em>` tags, and both the third and fourth `<p>` tags include `<strong>` tags but are missing `<em>` tags.

ERR & 1\\
\hline
8f6904f & b70fdc4 &  &  & gpt-4o-mini & text: Traveling opens your mind to different cultures. It provides opportunities to learn new languages and traditions. Exploring new places can be both exciting and enlightening. & ```html
<p><strong>Traveling</strong> <em>opens</em> your mind to <em>different cultures</em>.</p>
<p><strong>It</strong> <em>provides opportunities</em> to learn <em>new languages</em> and <em>traditions</em>.</p>
<p><strong>Exploring</strong> new places can be both <em>exciting</em> and <em>enlightening</em>.</p>
``` & ok & The chatbot output correctly includes at least three `<p>` tags, each wrapping a sentence. Additionally, each `<p>` tag contains one `<strong>` tag and multiple `<em>` tags, fulfilling the requirement to emphasize key words and phrases.

OK & 1\\
\hline
8f6904f & b70fdc4 &  &  & gemma2:9b & text: Traveling opens your mind to different cultures. It provides opportunities to learn new languages and traditions. Exploring new places can be both exciting and enlightening. & Here is the provided text formatted as HTML with  <p>, <strong >, and <em> tags:

<p><strong>Traveling</strong> opens your mind to <em >different cultures</em>. </p>
<p>It provides <strong >opportunities</strong> to learn <em >new languages</em> and <em >traditions</em>.</p>
<p>Exploring <strong >new places</strong> can be both <em >exciting</em>  and <em >enlightening</em>.</p> 


Let me know if you'd like to experiment with formatting other sections of text! & err & The first `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
8f6904f & b70fdc4 &  &  & qwen2.5:3b & text: Traveling opens your mind to different cultures. It provides opportunities to learn new languages and traditions. Exploring new places can be both exciting and enlightening. & ```html
<p><strong>Traveling</strong> opens <em>your</em> <em>mind</em> to <em>different</em> <em>cultures</em>. It provides opportunities to learn <em>new</em> <em>languages</em> and <em>traditions</em>. Exploring new places can be both <em>exciting</em> and <em>enlightening</em>.</p>
```

Note: The response is duplicated because of the repetition in your request. However, since you provided the correct HTML structure with emphasis on key words already, I will only present one instance here. & err & The chatbot output uses a single `<p>` tag to enclose all sentences, whereas the description requires each sentence to be wrapped in its own `<p>` tag, totaling at least three `<p>` tags.

ERR & 1\\
\hline
8f6904f & b70fdc4 &  &  & llama3.2:1b & text: Traveling opens your mind to different cultures. It provides opportunities to learn new languages and traditions. Exploring new places can be both exciting and enlightening. & Here is the formatted paragraph:

<p>This travel experience expands <strong>one's</strong> understanding of the world, fostering a deeper appreciation for diverse <em>cultures</em>.</p>

<p>The prospect of traveling allows individuals to immerse themselves in unfamiliar environments and adopt new perspectives.</p>

<p>This process can be both mentally stimulating and intellectually challenging;</p> & err & In the chatbot's output, only the first `<p>` tag contains both a `<strong>` tag and an `<em>` tag as required. The second and third `<p>` tags lack these tags, failing to emphasize key words and phrases within each paragraph.

ERR & 1\\
\hline
1c07f38 & b70fdc4 &  &  & gpt-4o-mini & text: Regular exercise improves physical health. It also enhances mental well-being by reducing stress. Incorporating fitness into your routine is essential for a balanced life. & ```html
<p><strong>Regular exercise</strong> <em>improves</em> <em>physical health</em>.</p>
<p><strong>It also</strong> <em>enhances</em> <em>mental well-being</em> by <em>reducing</em> <em>stress</em>.</p>
<p><strong>Incorporating fitness</strong> into your <em>routine</em> is <em>essential</em> for a <em>balanced life</em>.</p>
``` & ok & The chatbot output adheres to the specified requirements by wrapping each sentence in a `<p>` tag, ensuring there are at least three `<p>` tags. Within each `<p>` tag, it correctly includes one `<strong>` tag and multiple `<em>` tags to emphasize key words and phrases as instructed.

OK & 1\\
\hline
1c07f38 & b70fdc4 &  &  & gemma2:9b & text: Regular exercise improves physical health. It also enhances mental well-being by reducing stress. Incorporating fitness into your routine is essential for a balanced life. & <p><strong>Regular exercise</strong> improves <em>physical health</em>.</p>
<p>It also enhances <em>mental well-being</em> by <em>reducing stress</em>.</p>
<p>Incorporating <em>fitness</em> into your routine is <strong>essential</strong> for a <em>balanced life</em>.</p> 


Let me know if you'd like to experiment with different ways to emphasize the text! & err & The second `<p>` tag is missing a `<strong>` tag, which violates the requirement to include one `<strong>` tag within each `<p>` tag.
ERR & 1\\
\hline
1c07f38 & b70fdc4 &  &  & qwen2.5:3b & text: Regular exercise improves physical health. It also enhances mental well-being by reducing stress. Incorporating fitness into your routine is essential for a balanced life. & ```html
<p><strong>Regular</strong> exercise improves <em>physical</em> health. It also enhances <em>mental</em> well-being by <em>reducing</em> stress. Incorporating <em>fitness</em> into your routine is essential for a balanced life.</p>
``` & err & The output uses only one `<p>` tag to contain all three sentences, whereas the description requires each sentence to be wrapped in its own `<p>` tag, resulting in at least three `<p>` tags.

ERR & 1\\
\hline
1c07f38 & b70fdc4 &  &  & llama3.2:1b & text: Regular exercise improves physical health. It also enhances mental well-being by reducing stress. Incorporating fitness into your routine is essential for a balanced life. & Here's the paragraph with individual sentences wrapped in <p> tags and each sentence with an extra <strong> tag to emphasize key words/phrases and an equivalent number of <em> tags to italicize them:

<p><strong>Regular exercise</strong> improves physical health. <em>Maintains overall well-being including</em> mental health.</p>

<p><strong>Incorporating fitness</strong> into your routine is essential for a balanced life.</p>

<p><strong>The benefits of regular exercise</strong></p> & err & The chatbot output contains three `<p>` tags, which meets the minimum requirement. However, the first `<p>` tag includes two sentences instead of wrapping each sentence in its own `<p>` tag as specified. Additionally, not all `<p>` tags contain the required multiple `<em>` tags for emphasizing key words and phrases.

ERR & 1\\
\hline
1f3c654 & b70fdc4 &  &  & gpt-4o-mini & text: Gardening requires patience and dedication. Watching plants grow can be incredibly rewarding. It also contributes to a sustainable environment. & ```html
<p><strong>Gardening</strong> requires <em>patience</em> and <em>dedication</em>.</p>
<p>Watching <strong>plants</strong> grow can be <em>incredibly</em> <em>rewarding</em>.</p>
<p>It also contributes to a <strong>sustainable environment</strong>.</p>
``` & err & The third `<p>` tag contains a `<strong>` tag but lacks any `<em>` tags, which is required to emphasize key words and phrases.
ERR & 1\\
\hline
1f3c654 & b70fdc4 &  &  & gemma2:9b & text: Gardening requires patience and dedication. Watching plants grow can be incredibly rewarding. It also contributes to a sustainable environment. & <p><strong>Gardening</strong> <em>requires</em> <strong>patience</strong> and <em>dedication</em>.</p>
<p><em>Watching</em> <strong>plants</strong> <em>grow</em> can be incredibly <em>rewarding</em>.</p>
<p>It also <em>contributes</em> to a <strong>sustainable</strong> <em>environment</em>.</p> 


 & err & The first `<p>` tag contains two `<strong>` tags, whereas the description requires only one `<strong>` tag per `<p>` tag.
ERR & 1\\
\hline
1f3c654 & b70fdc4 &  &  & qwen2.5:3b & text: Gardening requires patience and dedication. Watching plants grow can be incredibly rewarding. It also contributes to a sustainable environment. & ```html
<p><strong>Gardening</strong> requires <em>patience</em> and <em>dedication</em>. Watching <em>plants</em> <em>grow</em> can be incredibly rewarding. It also <em>contributes</em> to a <em>sustainable</em> environment.</p>
``` & err & The chatbot output wraps all sentences within a single `<p>` tag instead of splitting them into individual `<p>` tags as specified. Additionally, there should be at least three `<p>` tags, each containing one `<strong>` tag and multiple `<em>` tags. Since these requirements are not met, the output does not comply with the description.

ERR & 1\\
\hline
1f3c654 & b70fdc4 &  &  & llama3.2:1b & text: Gardening requires patience and dedication. Watching plants grow can be incredibly rewarding. It also contributes to a sustainable environment. & Here is the formatted paragraph:

<p><strong>Gardening</strong> <em>requires</em> <strong>patience</strong> <em>and</em> <strong>dedication</strong>. Watching plants grow can be incredibly rewarding.</p>

<p><strong>It</strong></p>
<p><strong>also</strong> <em>contributes</em> <strong>sustainably</strong> <em>to</em> <strong>a</strong> <em>sustainable</em> <strong>environment</strong>.</p> & err & The output contains multiple <strong> tags within each <p> tag, whereas the description specifies adding only one <strong> tag per <p> tag.
ERR & 1\\
\hline
1785532 & b70fdc4 &  &  & gpt-4o-mini & text: Learning a new language can be challenging. However, it offers numerous cognitive benefits. Bilingual individuals often have better problem-solving skills. & ```html
<p><strong>Learning a new language</strong> can be <em>challenging</em>.</p>
<p>However, it offers <strong>numerous cognitive benefits</strong> <em>that enhance</em> mental agility.</p>
<p><strong>Bilingual individuals</strong> often have <em>better problem-solving skills</em>.</p>
``` & err & Each `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
1785532 & b70fdc4 &  &  & gemma2:9b & text: Learning a new language can be challenging. However, it offers numerous cognitive benefits. Bilingual individuals often have better problem-solving skills. & Here is the HTML formatting of the paragraph with <p>, <strong>, and <em> tags:

<p><strong>Learning</strong> a new language can be <em>challenging</em>. </p>
<p>However, it offers <em>numerous</em> <strong>cognitive</strong> benefits.</p>
<p><strong>Bilingual</strong> individuals often have better <em>problem-solving</em> skills.</p> 


 Let me know if you'd like to see the paragraph formatted in a different way! & err & Each `<p>` tag contains only one `<em>` tag, but the description requires multiple `<em>` tags within each `<p>`.
ERR & 1\\
\hline
1785532 & b70fdc4 &  &  & qwen2.5:3b & text: Learning a new language can be challenging. However, it offers numerous cognitive benefits. Bilingual individuals often have better problem-solving skills. & ```html
<p><strong>Learning</strong> a <em>new</em> <em>language</em> can be <em>challenging</em>. However, it offers numerous <em>cognitive</em> benefits. Bilingual individuals often have better <em>problem-solving</em> skills.</p>
```

```html
<p><strong>Bilingual</strong> individuals often have <em>better</em> <em>problem-solving</em> skills.</p>
``` & err & The output contains only two `<p>` tags, but the description requires at least three `<p>` tags.
ERR & 1\\
\hline
1785532 & b70fdc4 &  &  & llama3.2:1b & text: Learning a new language can be challenging. However, it offers numerous cognitive benefits. Bilingual individuals often have better problem-solving skills. & Here is the formatted paragraph:

\&lt;p\&gt;Learning a new language can be challenging. \&lt;/p\&gt;

**<strong>However</strong>, it offers numerous cognitive benefits. </strong>**

\&lt;p\&gt;<em><strong>Bilingual</strong> individuals often have better problem-solving skills.</em></p>

This code splits the paragraph into 3 sentences, each wrapped in <p> and an <strong> >em tags to emphasize key words and phrases added inside, respectively. & err & The chatbot output only includes two `<p>` tags instead of the required minimum of three. Additionally, the second sentence lacks proper `<p>` tags and contains mismatched `</strong>` tags, failing to include both `<strong>` and `<em>` tags within each `<p>` tag as specified.
ERR & 1\\
\hline
dfc7fe1 & b70fdc4 &  &  & gpt-4o-mini & text: Technology has revolutionized communication. Social media platforms allow instant connection across the globe. However, it's important to use them responsibly. & ```html
<p><strong>Technology</strong> has <em>revolutionized</em> <em>communication</em>.</p>
<p><strong>Social media platforms</strong> allow <em>instant</em> <em>connection</em> across the globe.</p>
<p>However, it's <strong>important</strong> to use them <em>responsibly</em>.</p>
``` & err & The third `<p>` tag contains only one `<em>` tag instead of multiple as required.
ERR & 1\\
\hline
dfc7fe1 & b70fdc4 &  &  & gemma2:9b & text: Technology has revolutionized communication. Social media platforms allow instant connection across the globe. However, it's important to use them responsibly. & <p><strong>Technology</strong> has <em>revolutionized</em> <strong>communication</strong>.</p>
<p><strong>Social media</strong> platforms allow <em>instant connection</em> across the <em>globe</em>.</p>
<p>However, it's <em>important</em> to use them <strong>responsibly</strong>.</p>  


Let me know if you'd like to experiment with different emphasis styles or have another paragraph you want to format! 
 & err & The first `<p>` tag contains two `<strong>` tags instead of the required one.

ERR & 1\\
\hline
dfc7fe1 & b70fdc4 &  &  & qwen2.5:3b & text: Technology has revolutionized communication. Social media platforms allow instant connection across the globe. However, it's important to use them responsibly. & ```html
<p><strong>Technology</strong> has revolutionized <em>communication</em>.<br>Social media platforms allow <strong>instant</strong> <em>connection</em> across the globe.<br>However, it's <strong>important</strong> to use them <em>responsibly</em>.</p>
``` & err & The chatbot output uses a single `<p>` tag to contain all sentences, whereas the description requires each sentence to be wrapped in its own `<p>` tag with at least three `<p>` tags in total. Additionally, the use of `<br>` tags to separate sentences within one `<p>` tag does not comply with the instruction to split the paragraph into individual sentences.

ERR & 1\\
\hline
dfc7fe1 & b70fdc4 &  &  & llama3.2:1b & text: Technology has revolutionized communication. Social media platforms allow instant connection across the globe. However, it's important to use them responsibly. & Here is the formatted paragraph with three <p> tags, each wrapped with a <strong> tag and multiple <em> tags:

<p><strong>Technology</strong> has revolutionized communication.</p>
<p><strong>Social</strong> media platforms allow instant connection across the globe.</p>
<p><strong>However</strong>, it's important to use them responsibly.</p>

The keywords "technology" and "social media" are emphasized for a stronger impact. The use of <em>instant</em> and "<i>globally</i>" adds emphasis on their relevance to the paragraph. & err & The chatbot's output does not include multiple <em> tags within each <p> tag as specified. Additionally, it incorrectly uses an <i> tag instead of an <em> tag for emphasis.

ERR & 1\\
\hline
68ced21 & b70fdc4 &  &  & gpt-4o-mini & text: Music has the power to evoke strong emotions. Whether it's classical or modern, it can uplift your spirits. Attending live concerts is a fantastic experience. & ```html
<p><strong>Music</strong> has the power to <em>evoke</em> strong <em>emotions</em>.</p>
<p>Whether it's <strong>classical</strong> or <strong>modern</strong>, it can <em>uplift</em> your <em>spirits</em>.</p>
<p>Attending <strong>live concerts</strong> is a <em>fantastic</em> experience.</p>
``` & err & The second `<p>` tag contains two `<strong>` tags instead of the required one. Additionally, the third `<p>` tag has only one `<em>` tag, whereas multiple `<em>` tags are needed.

ERR & 1\\
\hline
68ced21 & b70fdc4 &  &  & gemma2:9b & text: Music has the power to evoke strong emotions. Whether it's classical or modern, it can uplift your spirits. Attending live concerts is a fantastic experience. & Here's the HTML formatted text:

<p><strong>Music</strong> has the power to evoke <em>strong</em> emotions. </p>
<p>Whether it's <em>classical</em> or <em>modern</em>, it can uplift your <em>spirits</em>.</p>
<p>Attending <em>live concerts</em> is a <em>fantastic</em> experience.</p> 


Let me know if you need any other text formatted!   & err & The second and third `<p>` tags lack the required `<strong>` tag, only containing `<em>` tags instead.

ERR & 1\\
\hline
68ced21 & b70fdc4 &  &  & qwen2.5:3b & text: Music has the power to evoke strong emotions. Whether it's classical or modern, it can uplift your spirits. Attending live concerts is a fantastic experience. & ```html
<p><strong>Music</strong> has the power to <em>evolve</em> and<i> evoke</i> strong <em>emotions</em>. Whether it's classical or modern, it can<i> uplift</i> your <em>spirits</em>. Attending live concerts is a fantastic<i> experience</i>.</p>
<p><strong>Music</strong> has the power to <em>evolve</em> and<i> evoke</i> strong <em>emotions</em>. Whether it's classical or modern, it can<i> uplift</i> your <em>spirits</em>. Attending live concerts is a fantastic<i> experience</i>.</p>
<p><strong>Music</strong> has the power to <em>evolve</em> and<i> evoke</i> strong <em>emotions</em>. Whether it's classical or modern, it can<i> uplift</i> your <em>spirits</em>. Attending live concerts is a fantastic<i> experience</i>.</p>
```
Note: Since the original paragraph only has one sentence, I've duplicated the sentence three times as per your instructions. However, if there were multiple paragraphs with individual sentences, each would be treated individually, resulting in multiple <p> tags for each distinct sentence. & err & The chatbot's output uses `<i>` tags for emphasis instead of exclusively using `<em>` tags as specified in the description.
ERR & 1\\
\hline
68ced21 & b70fdc4 &  &  & llama3.2:1b & text: Music has the power to evoke strong emotions. Whether it's classical or modern, it can uplift your spirits. Attending live concerts is a fantastic experience. & <p>
  <p><strong>Music</strong> has the power to evoke <em>strong</em> emotions.</p>
  <p><strong>Music</strong> has the power to evoke <em>strong</em> emotions.</p>
  <p><strong>Musical</strong> experiences can be transformative and memorable.</p>
  <p><strong>Hearing</strong> music live in a large venue is an exhilarating experience.</p>
</p>

<p>
  <p><strong>Whether</strong> it's classical or modern, music can be <em>enjoyable</em>.</p>
  The emotional impact of music can vary <em>significantly</em> from person to person.</p>
  <p><strong>"Music</strong>, man... It just takes you there." (said by many an aspiring musician)</p> & err & The chatbot's output contains outer `<p>` tags that improperly encapsulate inner `<p>` tags, which violates proper HTML structure. Additionally, one of the sentences within the second outer `<p>` tag is not wrapped with a `<p>` tag as required.

ERR & 1\\
\hline
f4f8f47 & b70fdc4 &  &  & gpt-4o-mini & text: Volunteering in your community can make a difference. It helps those in need and fosters a sense of belonging. Everyone should consider giving their time to a cause. & ```html
<p><strong>Volunteering</strong> in your <em>community</em> can make a <em>difference</em>.</p>
<p>It helps those in <em>need</em> and fosters a sense of <strong>belonging</strong>.</p>
<p>Everyone should consider <strong>giving</strong> their time to a <em>cause</em>.</p>
``` & err & Some `<p>` tags contain only one `<em>` tag instead of multiple as required by the description.
ERR & 1\\
\hline
f4f8f47 & b70fdc4 &  &  & gemma2:9b & text: Volunteering in your community can make a difference. It helps those in need and fosters a sense of belonging. Everyone should consider giving their time to a cause. & <p><strong>Volunteering</strong> in your <em>community</em> can make a <strong>difference</strong>.</p>
<p>It <em>helps</em> those in <em>need</em> and <em>fosters</em> a <em>sense</em> of <strong>belonging</strong>.</p>
<p><strong>Everyone</strong> should consider <em>giving</em> their <em>time</em> to a <strong>cause</strong>.</p>


 & err & The first and third `<p>` tags contain two `<strong>` tags each, whereas only one `<strong>` tag per `<p>` tag is required.
ERR & 1\\
\hline
f4f8f47 & b70fdc4 &  &  & qwen2.5:3b & text: Volunteering in your community can make a difference. It helps those in need and fosters a sense of belonging. Everyone should consider giving their time to a cause. & Here is the formatted HTML for the provided text:

```html
<p><strong>Volunteering</strong> in <em>your community</em> can make a difference. It helps those in need and fosters a sense of belonging. Everyone should consider giving their time to a cause.</p>
```

Note that the `<p>` tags are already provided as per your instruction, but each paragraph is marked with emphasis on key terms using appropriate HTML tags such as `<strong>`, `<em>`. & err & Only one <p> tag is present, but the description requires at least three <p> tags.
ERR & 1\\
\hline
f4f8f47 & b70fdc4 &  &  & llama3.2:1b & text: Volunteering in your community can make a difference. It helps those in need and fosters a sense of belonging. Everyone should consider giving their time to a cause. & Here is the reformatted paragraph with <p> tags added for each sentence, followed by <strong> and <em> tags:

<p>{{text}}</p><p>This can be found on websites about volunteering. It helps those in need and fosters a sense of belonging.</p>
<p>You can make a difference starting from your local community.</p><p class="strong" style="font-weight:900;">Everyone should consider giving their time to a cause.</p>
<p class="em">Volunteering is not just about giving, but also about receiving the benefits it brings.</p><p class="strong" style="font-weight:900;">Making a difference starts with one small step, every single day.</p> & err & The chatbot's output does not include any `<strong>` or `<em>` tags within the `<p>` tags, as required by the description.
ERR & 1\\
\hline
9aefa0d & b70fdc4 &  &  & gpt-4o-mini & text: Education is the foundation of personal and societal growth. It empowers individuals to achieve their goals. Investing in education benefits everyone. & ```html
<p><strong>Education</strong> is the foundation of <em>personal</em> and <em>societal</em> growth.</p>
<p>It <strong>empowers</strong> individuals to achieve their <em>goals</em>.</p>
<p><strong>Investing</strong> in education benefits <em>everyone</em>.</p>
``` & err & In the second and third `<p>` tags, there is only one `<em>` tag instead of multiple as required by the description.
ERR & 1\\
\hline
9aefa0d & b70fdc4 &  &  & gemma2:9b & text: Education is the foundation of personal and societal growth. It empowers individuals to achieve their goals. Investing in education benefits everyone. & <p><strong>Education</strong> is the <em>foundation</em> of <em>personal</em> and <em>societal growth</em>.</p>

<p>It <strong>empowers</strong> individuals to <em>achieve</em> their <em>goals</em>.</p> 

<p><strong>Investing</strong> in education <em>benefits everyone</em>.</p> 


Let me know if you want to experiment with other formatting options! & err & The chatbot's output includes an additional sentence outside of the `<p>` tags ("Let me know if you want to experiment with other formatting options!"), which is not specified in the description. The description only instructs on how to format the paragraph, without adding any extra content.

ERR & 1\\
\hline
9aefa0d & b70fdc4 &  &  & qwen2.5:3b & text: Education is the foundation of personal and societal growth. It empowers individuals to achieve their goals. Investing in education benefits everyone. & Here is the formatted paragraph based on your instructions:

```html
<p><strong>Education</strong> is the foundation of <em>personal</em> and <em>societal</em> growth. It <em>empowers</em> individuals to achieve their goals. Investing in education benefits everyone.</p>
```

Note: Since the original text was a single string, it appeared combined above for simplicity. When applied as HTML, each paragraph would start with a `<p>` tag and contain one or more `<strong>` tags followed by multiple `<em>` tags to highlight keywords and phrases within the paragraph structure. & err & The output contains only one `<p>` tag instead of the required at least three `<p>` tags.
ERR & 1\\
\hline
9aefa0d & b70fdc4 &  &  & llama3.2:1b & text: Education is the foundation of personal and societal growth. It empowers individuals to achieve their goals. Investing in education benefits everyone. & Here is the formatted text:

<p>Education is the foundation of personal and societal growth.</p>
<input type="strong" name "-" value "=" class="capitalize">
<p>It <i>empowers</i> individuals to achieve their goals.</p>
<p><input type="strong" name="-" value=">" class="capitalize"></p>
<p>Investing in education benefits everyone.</p> & err & The chatbot's output does not include the required `<strong>` and `<em>` tags within each `<p>` tag. Instead, it incorrectly uses `<input>` tags and `<i>` tags, which do not align with the provided description.

ERR & 1\\
\hline
5d523c3 & b70fdc4 &  &  & gpt-4o-mini & text: Art allows for creative expression and innovation. It can challenge perceptions and inspire change. Supporting artists enriches cultural diversity. & ```html
<p><strong>Art</strong> allows for <em>creative</em> <em>expression</em> and <em>innovation</em>.</p>
<p>It can <strong>challenge</strong> <em>perceptions</em> and <em>inspire</em> <em>change</em>.</p>
<p>Supporting <strong>artists</strong> enriches <em>cultural</em> <em>diversity</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
5d523c3 & b70fdc4 &  &  & gemma2:9b & text: Art allows for creative expression and innovation. It can challenge perceptions and inspire change. Supporting artists enriches cultural diversity. & <p><strong>Art</strong> allows for <em>creative expression</em> and <em>innovation</em>.</p> 
<p>It can challenge <em>perceptions</em> and <em>inspire change</em>.</p>
<p>Supporting <em>artists</em> enriches <em>cultural diversity</em>.</p>  
 & err & The second and third `<p>` tags do not contain a `<strong>` tag as required by the description.
ERR & 1\\
\hline
5d523c3 & b70fdc4 &  &  & qwen2.5:3b & text: Art allows for creative expression and innovation. It can challenge perceptions and inspire change. Supporting artists enriches cultural diversity. & ```html
<p><strong>Art</strong> allows for <em>creative</em> <em>expression</em> and <em>innovation</em>. It can challenge <em>perceptions</em> and <em>inspire</em> change. Supporting artists enriches cultural diversity.</p>
```

For the second part of your text:
```html
<p><strong>Art</strong> allows for <em>creative</em> <em>expression</em> and <em>innovation</em>. It can challenge <em>perceptions</em> and <em>inspire</em> change. Supporting artists enriches cultural diversity.</p>
```

Both HTML snippets have been formatted with the specified structure and emphasized keywords/phrases as per your instructions. & err & The chatbot output contains only one `<p>` tag wrapping all three sentences, whereas the description explicitly requires splitting the paragraph into individual sentences with each sentence enclosed in its own `<p>` tag. Additionally, it specifies that there should be at least three `<p>` tags. Since the output does not meet this requirement, it does not comply with the description.

ERR & 1\\
\hline
5d523c3 & b70fdc4 &  &  & llama3.2:1b & text: Art allows for creative expression and innovation. It can challenge perceptions and inspire change. Supporting artists enriches cultural diversity. & Here is the formatted paragraph as HTML with <p> tags, <strong> tags, and <em> tags:

<p>Art allows for creative expression and innovation.</p>
<strong>It</strong> can challenge perceptions and inspire change.</p>
<p>Supporting</p>
<strong>artists</-strong> enriches cultural diversity. & err & The output does not contain at least three properly formatted <p> tags, and within each <p> tag, the required <strong> and <em> tags are either missing or incorrectly nested. Specifically, the second sentence lacks an opening <p> tag, the third <p> tag does not include any <strong> or <em> tags, and the fourth line has a malformed </-strong> tag instead of </strong>.
ERR & 1\\
\hline
2e09176 & b70fdc4 &  &  & gpt-4o-mini & text: Financial literacy is crucial for managing personal finances. Understanding budgeting, saving, and investing leads to financial security. Everyone should strive to improve their financial knowledge. & ```html
<p><strong>Financial literacy</strong> is crucial for <em>managing</em> personal <em>finances</em>.</p>
<p>Understanding <strong>budgeting</strong>, <em>saving</em>, and <em>investing</em> leads to <strong>financial security</strong>.</p>
<p>Everyone should strive to <strong>improve</strong> their <em>financial knowledge</em>.</p>
``` & err & The second `<p>` tag contains multiple `<strong>` tags, whereas the description specifies that each `<p>` tag should include only one `<strong>` tag.

ERR & 1\\
\hline
2e09176 & b70fdc4 &  &  & gemma2:9b & text: Financial literacy is crucial for managing personal finances. Understanding budgeting, saving, and investing leads to financial security. Everyone should strive to improve their financial knowledge. & <p><strong>Financial</strong> <em>literacy</em> is crucial for managing <em>personal finances</em>.</p>
<p>Understanding <em>budgeting</em>, <em>saving</em>, and <em>investing</em> leads to <em>financial security</em>.</p>
<p><strong>Everyone</strong> should strive to improve their <em>financial knowledge</em>.</p>  


**Explanation:**

* Each sentence is now enclosed within `<p>` tags, creating separate paragraphs.
*  `<strong>` tags are used to bold important words like "Financial" and "Everyone."
* `<em>` tags are used to emphasize key phrases, like "personal finances," "budgeting," "saving," "investing," "financial security," and "financial knowledge." 



Let me know if you'd like to explore other ways to format this text or emphasize different words! & err & The second `<p>` tag does not include a `<strong>` tag as required.
ERR & 1\\
\hline
2e09176 & b70fdc4 &  &  & qwen2.5:3b & text: Financial literacy is crucial for managing personal finances. Understanding budgeting, saving, and investing leads to financial security. Everyone should strive to improve their financial knowledge. & <p><strong>Financial</strong> literacy <em>is</em> crucial <em>for</em> <em>managing</em> <em>personal</em> <em>finances</em>. Understanding <em>budgeting</em>, <em>saving</em>, and <em>investing</em> leads to <em>financial</em> <em>security</em>. Everyone should <em>strive</em> <em>to</em> <em>improve</em> <em>their</em> <em>financial</em> <em>knowledge</em>.</p>

<p><strong>Financial</strong> literacy <em>is</em> crucial <em>for</em> <em>managing</em> <em>personal</em> <em>finances</em>. Understanding <em>budgeting</em>, <em>saving</em>, and <em>investing</em> leads to <em>financial</em> <em>security</em>. Everyone should <em>strive</em> <em>to</em> <em>improve</em> <em>their</em> <em>financial</em> <em>knowledge</em>.</p>

<p><strong>Financial</strong> literacy <em>is</em> crucial <em>for</em> <em>managing</em> <em>personal</em> <em>finances</em>. Understanding <em>budgeting</em>, <em>saving</em>, and <em>investing</em> leads to <em>financial</em> <em>security</em>. Everyone should <em>strive</em> <em>to</em> <em>improve</em> <em>their</em> <em>financial</em> <em>knowledge</em>.</p> & err & The chatbot output wraps multiple sentences within each `<p>` tag instead of wrapping each individual sentence in its own `<p>` tag as specified in the description.

ERR & 1\\
\hline
2e09176 & b70fdc4 &  &  & llama3.2:1b & text: Financial literacy is crucial for managing personal finances. Understanding budgeting, saving, and investing leads to financial security. Everyone should strive to improve their financial knowledge. & Here's the reformatted paragraph with individual sentences wrapped in <p> tags, followed by emphasis with <strong>`, <em>`, or both:

<p>Financial literacy is crucial for managing personal finances.</p>
<p>\&strong;Understanding budgeting,\&#160;<em>saving</em> and investing leads to financial security.</p>
<p>(\&#160;Everyday people can improve their financial knowledge by learning about personal finance.)</p> & err & The first and third `<p>` tags do not contain any `<strong>` or `<em>` tags as required. Additionally, the second `<p>` tag incorrectly uses `\&strong;` instead of `<strong>`, and the use of parentheses and `\&#160;` is inappropriate for adding emphasis.

ERR & 1\\
\hline
d9aa526 & b70fdc4 &  &  & gpt-4o-mini & text: Meditation can enhance mental clarity and reduce anxiety. Practicing mindfulness promotes overall well-being. Incorporating meditation into daily life can be highly beneficial. & ```html
<p><strong>Meditation</strong> can <em>enhance</em> mental <em>clarity</em> and <em>reduce</em> <strong>anxiety</strong>.</p>
<p><strong>Practicing mindfulness</strong> promotes <em>overall</em> well-being.</p>
<p><strong>Incorporating</strong> meditation into <em>daily life</em> can be <em>highly</em> beneficial.</p>
``` & err & Each `<p>` tag should contain exactly one `<strong>` tag, but the first `<p>` contains two `<strong>` tags.
ERR & 1\\
\hline
d9aa526 & b70fdc4 &  &  & gemma2:9b & text: Meditation can enhance mental clarity and reduce anxiety. Practicing mindfulness promotes overall well-being. Incorporating meditation into daily life can be highly beneficial. & Here's the HTML formatting:

<p><strong>Meditation</strong> can enhance <em>mental clarity</em> and <em>reduce anxiety</em>.</p>
<p>Practicing <em>mindfulness</em> promotes <em>overall well-being</em>. </p>
<p>Incorporating <strong>meditation</strong> into <em>daily life</em> can be <em>highly beneficial</em>.</p> 


Let me know if you'd like to explore other ways to emphasize text within HTML! & err & The second `<p>` tag does not contain a `<strong>` tag as required.
ERR & 1\\
\hline
d9aa526 & b70fdc4 &  &  & qwen2.5:3b & text: Meditation can enhance mental clarity and reduce anxiety. Practicing mindfulness promotes overall well-being. Incorporating meditation into daily life can be highly beneficial. & ```html
<p><strong>Meditation</strong> can <em>enhance</em> mental clarity and <em>reduce</em> anxiety.</p>
<p><strong>Practicing</strong> mindfulness promotes overall well-being.</p>
<p><strong>Incorporating</strong> meditation into daily life can be highly beneficial.</p>
``` & err & The second and third `<p>` tags lack any `<em>` tags, violating the requirement to include multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
d9aa526 & b70fdc4 &  &  & llama3.2:1b & text: Meditation can enhance mental clarity and reduce anxiety. Practicing mindfulness promotes overall well-being. Incorporating meditation into daily life can be highly beneficial. & Here is the formatted paragraph with individual sentences, added <strong> tags to emphasize key words and phrases, and <em> tags to highlight special terms:

**<p><strong>Meditation</strong> can enhance mental clarity and reduce anxiety.</p> **

**<p>Practicing mindfulness promotes overall well-being.</p> **

**<p>Incorporating meditation into daily life can be highly beneficial.</p>** & err & The chatbot's output includes `<p>` tags and `<strong>` tags as specified, but it does not include any `<em>` tags within the `<p>` tags as required by the description.

ERR & 1\\
\hline
64872ff & b70fdc4 &  &  & gpt-4o-mini & text: The internet has made information more accessible than ever. It facilitates learning and connects people worldwide. However, it's essential to verify sources for accuracy. & ```html
<p><strong>The internet</strong> has made <em>information</em> more <em>accessible</em> than ever.</p>
<p>It <strong>facilitates</strong> <em>learning</em> and <em>connects</em> people <em>worldwide</em>.</p>
<p>However, it's <strong>essential</strong> to <em>verify</em> <em>sources</em> for <em>accuracy</em>.</p>
``` & ok & The output contains three `<p>` tags, each enclosing one `<strong>` tag and multiple `<em>` tags as required.
OK & 1\\
\hline
64872ff & b70fdc4 &  &  & gemma2:9b & text: The internet has made information more accessible than ever. It facilitates learning and connects people worldwide. However, it's essential to verify sources for accuracy. & <p><strong>The</strong> <em>internet</em> has made <em>information</em> more <em>accessible</em> than <em>ever</em>.</p>
<p><strong>It</strong> facilitates <em >learning</em> and connects <em>people</em> <em >worldwide</em>.</p>
<p><strong>However</strong>, it's <em>essential</em> to verify <em>sources</em> for <em>accuracy</em>.</p> & ok & No violation.
OK & 1\\
\hline
64872ff & b70fdc4 &  &  & qwen2.5:3b & text: The internet has made information more accessible than ever. It facilitates learning and connects people worldwide. However, it's essential to verify sources for accuracy. & ```html
<p><strong>Internet</strong> has made information <em>more accessible</em> than ever. It <em>facilitates</em> learning and connects people <em>worldwide</em>. However, it's <em>essential</em> to verify sources for accuracy.</p>
```

Note: Although the text is presented as two blocks of code, they are meant to be treated as one input string. The formatting provided is consistent with both instances. & err & The chatbot output only uses a single `<p>` tag for all sentences instead of wrapping each individual sentence with its own `<p>` tag as specified. Additionally, since all sentences are within one `<p>` tag, each sentence does not have its own `<strong>` tag, which violates the requirement for each `<p>` tag to contain one `<strong>` tag and multiple `<em>` tags.

ERR & 1\\
\hline
64872ff & b70fdc4 &  &  & llama3.2:1b & text: The internet has made information more accessible than ever. It facilitates learning and connects people worldwide. However, it's essential to verify sources for accuracy. & Here is the reformatted paragraph with each sentence wrapped in a <p> tag, with an extra <strong> tag for emphasis and multiple <em> tags for key words and phrases:

<p>Text: The internet has made information more accessible than ever.</p>
<span class="strong"><p>The internet has made information more accessible than ever.</p></span>
<p>It facilitates learning and connects people worldwide.</p>
<p>However, it's essential to verify sources for accuracy.</p>

Note: I've added <span class="strong"></span> around the "strong" tag, which is a semantic highlighting approach that highlights the text as strong emphasized. This helps to emphasize the word "essential". & err & The chatbot's output does not include any <strong> or <em> tags within the <p> tags as specified in the description. Additionally, the use of a <span class="strong"> wrapper around a <p> tag is not aligned with the instructions.
ERR & 1\\
\hline
739aa25 & b70fdc4 &  &  & gpt-4o-mini & text: Sports teach valuable life lessons such as teamwork and perseverance. They also promote physical health. Participating in sports can be both fun and rewarding. & ```html
<p><strong>Sports teach</strong> <em>valuable</em> <em>life lessons</em> such as <em>teamwork</em> and <em>perseverance</em>.</p>
<p><strong>They also promote</strong> <em>physical health</em>.</p>
<p><strong>Participating in sports</strong> can be both <em>fun</em> and <em>rewarding</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
739aa25 & b70fdc4 &  &  & gemma2:9b & text: Sports teach valuable life lessons such as teamwork and perseverance. They also promote physical health. Participating in sports can be both fun and rewarding. & <p><strong>Sports</strong> teach valuable <em>life lessons</em> such as <em>teamwork</em> and <em>perseverance</em>.</p>

<p>They also <strong>promote</strong> <em>physical health</em>.</p>

<p>Participating in <strong>sports</strong> can be both <em>fun</em> and <em>rewarding</em>.</p>  
 & ok & No violation.
OK & 1\\
\hline
739aa25 & b70fdc4 &  &  & qwen2.5:3b & text: Sports teach valuable life lessons such as teamwork and perseverance. They also promote physical health. Participating in sports can be both fun and rewarding. & ```html
<p><strong>Text:</strong></p>
<p><em>Sports</em> teach valuable life <strong>lessons</strong> such as <em>teamwork</em> and <em>perseverance</em>. They also promote physical health.</p>
<p><em>Participating</em> in sports can be both fun and rewarding.</p>
```

```html
<p><strong>Text:</strong></p>
<p><em>Sports</em> teach valuable life <strong>lessons</strong> such as <em>teamwork</em> and <em>perseverance</em>. They also promote physical health.</p>
<p><em>Participating</em> in sports can be both fun and rewarding.</p>
```

Both versions are equivalent, but here is a unified version for clarity:

```html
<p><strong>Text:</strong></p>
<p><em>Sports</em> teach valuable life <strong>lessons</strong> such as <em>teamwork</em> and <em>perseverance</em>. They also promote physical health.</p>
<p><em>Participating</em> in sports can be both fun and rewarding.</p>
``` & err & The first `<p>` tag contains only a `<strong>` tag and lacks any `<em>` tags as required.
ERR & 1\\
\hline
739aa25 & b70fdc4 &  &  & llama3.2:1b & text: Sports teach valuable life lessons such as teamwork and perseverance. They also promote physical health. Participating in sports can be both fun and rewarding. & Here is the formatted paragraph with individual sentences wrapped in <p> tags, a <strong> tag for emphasis, and multiple <em> tags to emphasize key words and phrases:

<p>
Sports teach valuable life lessons **such as teamwork** and perseverance.
</p>

<p>
They also promote physical health. 
</p>

<p>
Participating in sports can be both fun <em>and rewarding.</em> & err & The chatbot output does not include the required `<strong>` tags within each `<p>` tag, uses `**` instead of `<strong>` for bold text, and does not provide multiple `<em>` tags within each paragraph as specified.
ERR & 1\\
\hline
8bedc02 & b70fdc4 &  &  & gpt-4o-mini & text: Renewable energy sources are essential for a sustainable future. Solar and wind power reduce our reliance on fossil fuels. Investing in green technology is imperative. & ```html
<p><strong>Renewable energy sources</strong> are <em>essential</em> for a <em>sustainable</em> future.</p>
<p><strong>Solar and wind power</strong> reduce our <em>reliance</em> on <em>fossil fuels</em>.</p>
<p><strong>Investing in green technology</strong> is <em>imperative</em>.</p>
``` & ok & The output contains three `<p>` tags, each with one `<strong>` tag and multiple `<em>` tags, adhering to the specified formatting requirements.

OK & 1\\
\hline
8bedc02 & b70fdc4 &  &  & gemma2:9b & text: Renewable energy sources are essential for a sustainable future. Solar and wind power reduce our reliance on fossil fuels. Investing in green technology is imperative. & <p><strong>Renewable</strong> <em>energy</em> <strong>sources</strong> are essential for a **sustainable** _future_.</p>
<p><strong>Solar</strong> and **wind** _power_ reduce our *reliance* on **fossil fuels**.</p>
<p>Investing in *_green technology_* is **imperative**.</p>   


 & err & The third `<p>` tag does not contain a `<strong>` tag, and not all `<p>` tags include multiple `<em>` tags as required.
ERR & 1\\
\hline
8bedc02 & b70fdc4 &  &  & qwen2.5:3b & text: Renewable energy sources are essential for a sustainable future. Solar and wind power reduce our reliance on fossil fuels. Investing in green technology is imperative. & ```html
<p><strong>Renewable</strong> energy sources are <em>essential</em> for a <strong>sustainable</strong> future.</p>
<p>Solar and wind power reduce our reliance on <em>fossil</em> fuels.</p>
<p>Investing in green technology is <strong>imperative</strong>.</p>
``` & err & The first `<p>` tag contains two `<strong>` tags instead of the required one. The second `<p>` tag lacks a `<strong>` tag, and the third `<p>` tag does not include any `<em>` tags. These deviations from the description indicate non-compliance.
ERR & 1\\
\hline
8bedc02 & b70fdc4 &  &  & llama3.2:1b & text: Renewable energy sources are essential for a sustainable future. Solar and wind power reduce our reliance on fossil fuels. Investing in green technology is imperative. & <p>Renewable energy sources are essential <strong>for</strong> a sustainable future.</p>
<p><strong>Solar</strong></p> and <em>wind</em> power reduce our reliance on <strong>fossil</strong> fuels.</p>
<p><strong>Investing</strong> in green technology is imperative.</p> & err & The second `<p>` tag is improperly closed, and the first and third `<p>` tags lack the required `<em>` tags inside them.
ERR & 1\\
\hline
dd2e391 & b70fdc4 &  &  & gpt-4o-mini & text: Pets provide companionship and emotional support. Caring for animals can improve mental health. Adopting a pet is a lifelong commitment. & ```html
<p><strong>Pets</strong> provide <em>companionship</em> and <em>emotional support</em>.</p>
<p><strong>Caring for animals</strong> can <em>improve</em> <em>mental health</em>.</p>
<p><strong>Adopting a pet</strong> is a <em>lifelong commitment</em>.</p>
``` & ok & All three `<p>` tags are present, each containing one `<strong>` tag and multiple `<em>` tags as specified.
OK & 1\\
\hline
dd2e391 & b70fdc4 &  &  & gemma2:9b & text: Pets provide companionship and emotional support. Caring for animals can improve mental health. Adopting a pet is a lifelong commitment. & Here's the paragraph formatted as HTML with emphasized text:

<p><strong>Pets</strong> provide <em>companionship</em> and <em>emotional support</em>.</p>
<p><strong>Caring</strong> for <em>animals</em> can improve <em>mental health</em>.</p>
<p><strong>Adopting</strong> a <em>pet</em> is a <em>lifelong commitment</em>.</p> 


Let me know if you'd like to experiment with different ways to emphasize the text! & ok & No violation.
OK & 1\\
\hline
dd2e391 & b70fdc4 &  &  & qwen2.5:3b & text: Pets provide companionship and emotional support. Caring for animals can improve mental health. Adopting a pet is a lifelong commitment. & ```html
<p><strong>Pets</strong> provide companionship and <em>emotional support</em>. Caring for <strong>animals</strong> can <em>improve</em> mental health. Adopting a <strong>pet</strong> is a lifelong commitment.</p>
```

When split into individual sentences, the HTML structure would be:

```html
<p><strong>Pets</strong> provide companionship and <em>emotional support</em>.</p>
<p>Caring for <strong>animals</strong> can <em>improve</em> mental health.</p>
<p>Aptering a <strong>pet</strong> is a lifelong commitment.</p>
``` & err & The chatbot wrapped all sentences within a single `<p>` tag instead of splitting them into individual `<p>` tags as specified.

ERR & 1\\
\hline
dd2e391 & b70fdc4 &  &  & llama3.2:1b & text: Pets provide companionship and emotional support. Caring for animals can improve mental health. Adopting a pet is a lifelong commitment. & Here's the formatted paragraph with individual sentences, <p> tags, <strong>tags**, and <em>natural**</em> emphasis added:

<p>
  Pets provide companionship and emotional support.
  <strong>Caring for animals can improve mental health.</strong>
  Adopting a pet is a lifelong commitment. (Note: I left the space after "mental health" as it doesn't have an equivalent in <strong><em> natural </em></strong> context)

However, if you would like to rewrite the paragraph with stronger emphasis on the relationship between animals and mental health, you could rephrase it to:

<p>
  Pets provide companionship and emotional support. (<strong>Caring for animals can improve your mental wellbeing.</strong>)
  The strong bond between humans and pets has been shown (<em>natural</em>) to have a positive impact on our mental health.
 
In this revised paragraph, I used <strong>><em>natural</em></strong> emphasis to highlight the inherent connection between animals and human mental health. & err & The chatbot's output contains only two `<p>` tags, whereas the description requires at least three `<p>` tags.
ERR & 1\\
\hline
e6aa574 & b70fdc4 &  &  & gpt-4o-mini & text: Effective time management boosts productivity. Prioritizing tasks helps achieve goals efficiently. It's important to balance work and personal life. & ```html
<p><strong>Effective time management</strong> <em>boosts</em> <em>productivity</em>.</p>
<p><strong>Prioritizing tasks</strong> <em>helps</em> <em>achieve</em> <em>goals</em> <em>efficiently</em>.</p>
<p><strong>It's important</strong> <em>to balance</em> <em>work</em> and <em>personal life</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
e6aa574 & b70fdc4 &  &  & gemma2:9b & text: Effective time management boosts productivity. Prioritizing tasks helps achieve goals efficiently. It's important to balance work and personal life. & <p><strong>Effective</strong> time <em>management</em> boosts <em>productivity</em>.</p>

<p><strong>Prioritizing </strong>tasks helps achieve <em>goals</em> <em>efficiently</em>.</p> 

<p>It's <strong>important</strong> to balance <em>work</em> and <em>personal life</em>.</p>  
 & ok & No violation.
OK & 1\\
\hline
e6aa574 & b70fdc4 &  &  & qwen2.5:3b & text: Effective time management boosts productivity. Prioritizing tasks helps achieve goals efficiently. It's important to balance work and personal life. & ```html
<p><strong>Effective</strong> time <em>management</em> boosts <em>productivity</em>. Prioritizing <em>tasks</em> helps <em>achieve</em> <em>goals</em> efficiently. It's important to balance <em>work</em> and <em>personal life</em>.</p>
``` & err & The chatbot output contains only one `<p>` tag encompassing all three sentences, whereas the description requires each sentence to be wrapped in its own `<p>` tag, resulting in at least three `<p>` tags.
ERR & 1\\
\hline
e6aa574 & b70fdc4 &  &  & llama3.2:1b & text: Effective time management boosts productivity. Prioritizing tasks helps achieve goals efficiently. It's important to balance work and personal life. & Here is the reformatted paragraph with three <p> tags, and each sentence wrapped with a <strong> tag and multiple <em> tags:

<p strong>Effective time management boosts productivity.</strong>

<p strong>Prioritizing tasks helps achieve goals efficiently.</strong>

<p strong>It's important to balance work and personal life.</strong>

<p em>Time-saving techniques**, such as the Pomodoro Technique**, can help you stay focused and accomplish more in less time.**

<p em>scheduling breaks** is crucial for maintaining productivity and avoiding burnout. You deserve to have a work-life balance that allows you to recharge and refocus regularly. It's worth making time for activities that bring you joy and serve as a reminder of your well-being. & err & The `<p>` tags are incorrectly formatted with attributes like `<p strong>` instead of properly nesting `<strong>` tags within `<p>` tags. Additionally, some `<p>` tags do not include the required `<strong>` and `<em>` tags.

ERR & 1\\
\hline
b98166c & b70fdc4 &  &  & gpt-4o-mini & text: Culinary arts blend creativity with technical skills. Chefs experiment with flavors and presentation. Dining experiences can be memorable and delightful. & ```html
<p><strong>Culinary arts</strong> <em>blend</em> <em>creativity</em> with <em>technical skills</em>.</p>
<p><strong>Chefs</strong> <em>experiment</em> with <em>flavors</em> and <em>presentation</em>.</p>
<p><strong>Dining experiences</strong> can be <em>memorable</em> and <em>delightful</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
b98166c & b70fdc4 &  &  & gemma2:9b & text: Culinary arts blend creativity with technical skills. Chefs experiment with flavors and presentation. Dining experiences can be memorable and delightful. & <p><strong>Culinary</strong> <em>arts</em> blend <em>creativity</em> with <em>technical skills</em>.</p>
<p><strong>Chefs</strong> experiment with <em>flavors</em> and <em>presentation</em>.</p>
<p><strong>Dining</strong> experiences can be <em>memorable</em> and <em>delightful</em>.</p>  


Let me know if you'd like to see more examples or have other text you want me to format! & ok & No violation.
OK & 1\\
\hline
b98166c & b70fdc4 &  &  & qwen2.5:3b & text: Culinary arts blend creativity with technical skills. Chefs experiment with flavors and presentation. Dining experiences can be memorable and delightful. & ```html
<p><strong>Text:</strong>Culinary arts blend creativity with technical skills.</p>
<p><strong>Text:</strong>Chefs experiment with flavors and presentation.</p>
<p><strong>Text:</strong>Dining experiences can be memorable and delightful.</p>
```

Note: I've provided two sets of HTML code. The first one is based on the original text you've given, and the second set for your reference using the updated paragraph. & err & The chatbot output does not include the required `<em>` tags inside each `<p>` tag to emphasize key words and phrases.

ERR & 1\\
\hline
b98166c & b70fdc4 &  &  & llama3.2:1b & text: Culinary arts blend creativity with technical skills. Chefs experiment with flavors and presentation. Dining experiences can be memorable and delightful. & **This is the text that needs to be formatted**

<p>This is a paragraph of text that needs formatting.</p>
<p>Culinary <strong>arts</strong> blend <strong>creativity</strong> with technical <strong>skills</strong>.</p>
<p>Chefs experiment with <em>flavors</em> and presentation.</p>
<p>Dining experiences can be memorable and <em>delightful</em></p>
<p>Culinary arts combine creative cooking techniques, precise measuring skills, and attention to detail. & err & The first `<p>` tag does not contain any `<strong>` or `<em>` tags as required. Additionally, the last `<p>` tag is missing a closing `</p>` tag.
ERR & 1\\
\hline
264fc11 & b70fdc4 &  &  & gpt-4o-mini & text: Public speaking can be daunting but is a valuable skill. It enhances communication abilities and confidence. Practicing regularly can overcome fear. & ```html
<p><strong>Public speaking</strong> can be <em>daunting</em> but is a <em>valuable skill</em>.</p>
<p>It enhances <strong>communication abilities</strong> and <em>confidence</em>.</p>
<p><strong>Practicing regularly</strong> can <em>overcome fear</em>.</p>
``` & err & Two of the `<p>` tags contain only one `<em>` tag, whereas each `<p>` tag is required to have multiple `<em>` tags.
ERR & 1\\
\hline
264fc11 & b70fdc4 &  &  & gemma2:9b & text: Public speaking can be daunting but is a valuable skill. It enhances communication abilities and confidence. Practicing regularly can overcome fear. & <p><strong>Public</strong> speaking can be <em>daunting</em> but is a <em>valuable skill</em>. </p>
<p>It enhances <em>communication abilities</em> and <em>confidence</em>. </p>
<p>Practicing <em>regularly</em> can overcome <em>fear</em>. </p> 


 & err & The second and third `<p>` tags are missing the required `<strong>` tag.
ERR & 1\\
\hline
264fc11 & b70fdc4 &  &  & qwen2.5:3b & text: Public speaking can be daunting but is a valuable skill. It enhances communication abilities and confidence. Practicing regularly can overcome fear. & ```html
<p><strong>Public</strong> speaking can be <strong>demanding</strong> but is a valuable skill. It enhances communication <strong>abilities</strong> and <em>confidence</em>. Practicing regularly can <em>overcome</em> fear.</p>
```

Note: The original text was presented verbatim, so it does not contain any variation to accommodate the additional emphasis tags as requested in the instruction. As such, only one set of emphasis tags were applied per sentence due to the provided paragraph structure and content. & err & Only one `<p>` tag was used, but the description requires at least three `<p>` tags.
ERR & 1\\
\hline
264fc11 & b70fdc4 &  &  & llama3.2:1b & text: Public speaking can be daunting but is a valuable skill. It enhances communication abilities and confidence. Practicing regularly can overcome fear. & Here's the formatted paragraph:

<p>Public speaking can be daunting with little practice, but it serves as a valuable asset to enhance our professional communication abilities and boost self-confidence.</strong>p>
<p>This highlights how mastering public speaking skills is essential for overcoming social anxiety and fostering an individual's confidence in expressing their thoughts effectively.</strong><em>and</em>

<p>Public speaking can be daunting with little practice, but it serves as a valuable asset to enhance our professional communication abilities and boost self-confidence..</strong>p>
<p>The ability to communicate persuasively and convincingly is a critical aspect of many careers that may require public speaking roles.</strong><em>and</em>

<p>This highlights how mastering public speaking skills is essential for overcoming social anxiety and fostering an individual's confidence in expressing their thoughts effectively..<em>especially</em>, when dealing with large audiences or challenging topics.</strong>p>
<p>and</p> & err & The chatbot incorrectly closes the `<p>` tags with `</strong>p>`, which is invalid HTML syntax. Additionally, some `<p>` tags lack proper closing tags, and the structure of `<strong>` and `<em>` tags within the `<p>` tags does not consistently follow the required format.

ERR & 1\\
\hline
1e6e2c6 & b70fdc4 &  &  & gpt-4o-mini & text: Hiking offers a chance to connect with nature. It promotes physical fitness and mental relaxation. Exploring trails can be an invigorating adventure. & ```html
<p><strong>Hiking</strong> offers a chance to <em>connect</em> with <em>nature</em>.</p>
<p><strong>It</strong> promotes <em>physical fitness</em> and <em>mental relaxation</em>.</p>
<p><strong>Exploring trails</strong> can be an <em>invigorating</em> <em>adventure</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
1e6e2c6 & b70fdc4 &  &  & gemma2:9b & text: Hiking offers a chance to connect with nature. It promotes physical fitness and mental relaxation. Exploring trails can be an invigorating adventure. & <p><strong>Hiking</strong> offers a chance to <em>connect</em> with <em>nature</em>.</p>
<p>It promotes <em>physical fitness</em> and <em>mental relaxation</em>.</p>
<p>Exploring <em>trails</em> can be an <em>invigorating adventure</em>.</p> 


Let me know if you'd like to modify the emphasis or add more HTML elements! & err & The second and third `<p>` tags are missing the required `<strong>` tag inside them.
ERR & 1\\
\hline
1e6e2c6 & b70fdc4 &  &  & qwen2.5:3b & text: Hiking offers a chance to connect with nature. It promotes physical fitness and mental relaxation. Exploring trails can be an invigorating adventure. & ```html
<p><strong>Hiking</strong> offers a <em>chance</em> to <em>connect</em> with nature. It <em>promotes</em> physical fitness and <em>mental relaxation</em>. Exploring trails can be an <em>invigorating</em> adventure.</p>
``` & err & The output uses only one `<p>` tag for all sentences instead of wrapping each sentence in its own `<p>` tag, and it does not meet the requirement of having at least three `<p>` tags.

ERR & 1\\
\hline
1e6e2c6 & b70fdc4 &  &  & llama3.2:1b & text: Hiking offers a chance to connect with nature. It promotes physical fitness and mental relaxation. Exploring trails can be an invigorating adventure. & Here is the formatted paragraph:

<p><strong>Exploring</strong> </p>
<p><em>promoting</em><em>nature</em><em>,</em></p>
<p><strong>Mental</strong><em> </em><strong>Relaxation</strong></p>

**Explanation**: The first <p> tag wraps the text starting from "Exploring", emphasizing the physical aspect with multiple em tags. & err & The chatbot's output does not comply with the description. Specifically:

1. **First `<p>` Tag**: Contains only a `<strong>` tag without any `<em>` tags, whereas the description requires one `<strong>` tag *and* multiple `<em>` tags within each `<p>` tag.
2. **Third `<p>` Tag**: Contains two `<strong>` tags instead of just one, violating the requirement of having only one `<strong>` tag per `<p>` tag.

ERR & 1\\
\hline
e74ae53 & b70fdc4 &  &  & gpt-4o-mini & text: Entrepreneurship drives innovation and economic growth. Starting a business requires determination and resilience. Successful entrepreneurs inspire others. & ```html
<p><strong>Entrepreneurship</strong> drives <em>innovation</em> and <em>economic growth</em>.</p>
<p>Starting a <strong>business</strong> requires <em>determination</em> and <em>resilience</em>.</p>
<p>Successful <strong>entrepreneurs</strong> <em>inspire</em> others.</p>
``` & err & In the third `<p>` tag, there is only one `<em>` tag used to emphasize a word, whereas the description requires multiple `<em>` tags within each `<p>` tag to emphasize key words and phrases.
ERR & 1\\
\hline
e74ae53 & b70fdc4 &  &  & gemma2:9b & text: Entrepreneurship drives innovation and economic growth. Starting a business requires determination and resilience. Successful entrepreneurs inspire others. & Here's the HTML code with the paragraph formatted as you requested:

<p><strong>Entrepreneurship</strong> drives <em>innovation</em> and <em>economic growth</em>.</p>
<p><strong>Starting</strong> a <em>business</em> requires <em>determination</em> and <em>resilience</em>.</p>
<p><strong>Successful entrepreneurs</strong> <em>inspire</em> <em>others</em>.</p> 


Let me know if you have any other text you'd like to format! & ok & The output contains three `<p>` tags, each with one `<strong>` tag and multiple `<em>` tags, adhering to the specified formatting requirements.
OK & 1\\
\hline
e74ae53 & b70fdc4 &  &  & qwen2.5:3b & text: Entrepreneurship drives innovation and economic growth. Starting a business requires determination and resilience. Successful entrepreneurs inspire others. & Here is the formatted paragraph with <p>, <strong>, and multiple <em> tags applied as per your instructions:

```html
<p><strong>Entrepreneurship</strong> drives <em>innovation</em> and <em>economic growth</em>. Starting a business requires <em>determination</em> and <em>resilience</em>. Successful entrepreneurs inspire others.</p>
```

Each sentence has been split into an individual paragraph, and appropriate emphasis has been added using the tags as specified. & err & The output uses only one `<p>` tag instead of the required minimum of three `<p>` tags.
ERR & 1\\
\hline
e74ae53 & b70fdc4 &  &  & llama3.2:1b & text: Entrepreneurship drives innovation and economic growth. Starting a business requires determination and resilience. Successful entrepreneurs inspire others. & <p>\n<strong>Entrepreneurship drives innovation and economic growth.</strong><br>\n<p>This is the main point of your original paragraph.</p>

<p>\nThe process of starting a business involves making early decisions, such as idea validation and market research.<br>\n<p>We will highlight key points below:</p>\

<p>\n<strong>Entrepreneurship drives innovation</strong><br>\n<p>Driving innovation is at the core of entrepreneurship. It enables businesses to stay ahead of the competition.</p>

<p>\nThe ability to make tough decisions and take calculated risks is also a key trait of successful entrepreneurs.<br>\n<p>We will elaborate on this point later in our analysis.</p>

<p>\n<strong>Economic growth</strong><br>\n<p>Entrepreneurship is closely tied to economic growth. By creating new jobs and stimulating economic activity, businesses can contribute to overall economic well-being.</p> & err & The chatbot output incorrectly uses `<p>` tags instead of the correct `<p>` tags and does not include the required `<em>` tags within each `<p>` tag to emphasize key words and phrases.
ERR & 1\\
\hline
97a03db & b70fdc4 &  &  & gpt-4o-mini & text: Photography captures moments and tells stories. It can be both a hobby and a profession. Mastering different techniques enhances the quality of photos. & ```html
<p><strong>Photography</strong> <em>captures</em> moments and <em>tells</em> stories.</p>
<p>It can be both a <strong>hobby</strong> and a <em>profession</em>.</p>
<p><strong>Mastering</strong> different <em>techniques</em> enhances the <em>quality</em> of photos.</p>
``` & ok & OK & 1\\
\hline
97a03db & b70fdc4 &  &  & gemma2:9b & text: Photography captures moments and tells stories. It can be both a hobby and a profession. Mastering different techniques enhances the quality of photos. & Here is the HTML formatted paragraph with emphasized keywords:

<p><strong>Photography</strong> captures <em>moments</em> and <em>tells stories</em>. </p>
<p>It can be <strong>both</strong> a <em>hobby</em> and a <em>profession</em>.</p>
<p><strong>Mastering</strong> <em>different techniques</em> enhances the <em>quality of photos</em>.</p> 


 Let me know if you'd like to experiment with different emphasis styles! & ok & No violation.
OK & 1\\
\hline
97a03db & b70fdc4 &  &  & qwen2.5:3b & text: Photography captures moments and tells stories. It can be both a hobby and a profession. Mastering different techniques enhances the quality of photos. & Here is your formatted paragraph with multiple <p> tags containing emphasized keywords wrapped within them:

```html
<p><strong>Photography</strong> captures moments and tells stories. <em>It</em> can be both a hobby and a profession. Mastering different techniques enhances the <em>quality of photos</em>.</p>
```

Each sentence is now formatted with appropriate emphasis using HTML tags. & err & The chatbot's output uses a single `<p>` tag to contain all sentences instead of wrapping each individual sentence within its own `<p>` tag as specified. Additionally, the requirement to have at least three `<p>` tags is not met.

ERR & 1\\
\hline
97a03db & b70fdc4 &  &  & llama3.2:1b & text: Photography captures moments and tells stories. It can be both a hobby and a profession. Mastering different techniques enhances the quality of photos. & <p>Photography captures moments and tells stories.</p>
<strong>It</strong> <em>can</em> <em>be</em> <strong>a</strong> <em>buddy</em> <em>and</em> <em>a</em> <em>work</em> <span>\&#x20;together.</span>

<p>Photography captures moments and tells stories.</p>
<strong>It</strong> <em>can</em> <em>be</em> <strong>beyond</strong> <em>a</em> <strong>manual</strong> <em>expiration</em> <a href="#beyond_manual_expiration">(to)</a>,
<strong>(where</strong>) it is created,

<p>Photography captures moments and tells stories.</p>
<strong>It</strong> <em>can</em> <em>be</em> <strong>a</strong> <em>buddy</em> <em>and</em> <em>a</em> <strong>work</strong> <span>,<br/>and</span>
<sup>A</sup>

<p>Photography captures moments and tells stories.</p>
<strong>It</strong> <em>can</em> <em>be</em> <strong>beyond</strong> <em>a</em> <strong/manual</strong> <em>follower</em>,<br/>the<a href="#beyond_manual_follower">latest</a><span (>2016 is also often highlighted as being a notable moment in the field of artificial intelligence and machine learning, thanks to the development of Google Photos by Sundar Pichai</span>: & err & The `<strong>` and `<em>` tags are placed outside the `<p>` tags instead of being inside each `<p>` tag as specified in the description.
ERR & 1\\
\hline
12ad33e & b70fdc4 &  &  & gpt-4o-mini & text: Literature reflects society's values and issues. It can challenge norms and provoke thought. Analyzing texts deepens understanding of human experiences. & ```html
<p><strong>Literature</strong> <em>reflects</em> society's <em>values</em> and <em>issues</em>.</p>
<p><strong>It</strong> can <em>challenge</em> norms and <em>provoke</em> thought.</p>
<p><strong>Analyzing</strong> texts <em>deepens</em> understanding of <em>human experiences</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
12ad33e & b70fdc4 &  &  & gemma2:9b & text: Literature reflects society's values and issues. It can challenge norms and provoke thought. Analyzing texts deepens understanding of human experiences. & <p><strong>Literature</strong> reflects society's <em>values</em> and <em>issues</em>.</p>
<p>It can <strong>challenge</strong> <em>norms</em> and <em>provoke thought</em>.</p>
<p><strong>Analyzing</strong> texts <em>deepens</em> understanding of <em>human experiences</em>.</p> 


 & ok & No violation.
OK & 1\\
\hline
12ad33e & b70fdc4 &  &  & qwen2.5:3b & text: Literature reflects society's values and issues. It can challenge norms and provoke thought. Analyzing texts deepens understanding of human experiences. & ```html
<p><strong>Literature</strong> reflects <em>society's</em> values and <em>issues</em>. It can challenge <em>norms</em> and <em>provoke</em> thought. Analyzing texts deepens understanding of human <em>experiences</em>.</p>
<p><strong>Literature</strong> reflects <em>society's</em> values and <em>issues</em>. It can challenge <em>norms</em> and <em>provoke</em> thought. Analyzing texts deepens understanding of human <em>experiences</em>.</p>
```

Note: Given the repetition in your provided text, I have only formatted one paragraph with emphasis applied to specific keywords and phrases within each sentence. If you need this information repeated or structured differently, please let me know! & err & The chatbot output contains only two `<p>` tags, whereas the description explicitly requires **at least three `<p>` tags**. This violates the specified requirement for the number of paragraph tags.

ERR & 1\\
\hline
12ad33e & b70fdc4 &  &  & llama3.2:1b & text: Literature reflects society's values and issues. It can challenge norms and provoke thought. Analyzing texts deepens understanding of human experiences. & <p> Literature reflects society's values and issues.</p> <strong>Literature</strong> <em>reflects</em> <em>society's</em> <em>values</em> <em>and</em> <em>issues</em>.</p> 

<p> It can challenge norms and provoke thought.</p> 
<strong>It</strong> <em>can</em> <em>challenge</em> <em>norms</em> <em>and</em> <em>provoke</em> <em>thought</em>.</p> 

<p>Analyzing texts deepens understanding of human experiences.</p>
<strong>Analyzing</strong> <em>texts</em> <em>deepens</em> <em>understanding</em> <em>of</em><em>human</em> <em>speriences</em>. & err & The <strong> and <em> tags are placed outside the <p> tags instead of being inside each <p> tag as specified.
ERR & 1\\
\hline
a6a0192 & b70fdc4 &  &  & gpt-4o-mini & text: Fashion evolves with cultural and societal changes. It allows individuals to express their identity. Sustainable fashion is gaining importance. & ```html
<p><strong>Fashion</strong> <em>evolves</em> with <em>cultural</em> and <em>societal</em> <em>changes</em>.</p>
<p><strong>It</strong> <em>allows</em> individuals to <em>express</em> their <em>identity</em>.</p>
<p><strong>Sustainable fashion</strong> is <em>gaining</em> <em>importance</em>.</p>
``` & ok & All three `<p>` tags contain one `<strong>` tag and multiple `<em>` tags as specified.
OK & 1\\
\hline
a6a0192 & b70fdc4 &  &  & gemma2:9b & text: Fashion evolves with cultural and societal changes. It allows individuals to express their identity. Sustainable fashion is gaining importance. & <p><strong>Fashion</strong> evolves with <em>cultural</em> and <em>societal</em> <strong>changes</strong>.</p>
<p>It allows <strong>individuals</strong> to express their <em>identity</em>.</p>
<p><strong>Sustainable fashion</strong> is gaining <em>importance</em>.</p> 


Let me know if you'd like me to format any other text! & err & The first `<p>` tag contains two `<strong>` tags, which violates the requirement of having only one `<strong>` tag per `<p>` tag.
ERR & 1\\
\hline
a6a0192 & b70fdc4 &  &  & qwen2.5:3b & text: Fashion evolves with cultural and societal changes. It allows individuals to express their identity. Sustainable fashion is gaining importance. & ```html
<p><strong>Formatting</strong> text into <em>HTML</em> can be challenging, but splitting the paragraph into individual sentences <strong>and wrapping each sentence with a</strong> <em>\&lt;p\&gt;</em>tag makes it much more readable and organized. Inside each <em>\&lt;p\&gt;</em> tag, adding one <strong><em><em>\&lt;strong\&gt;</em></strong></em> tag and multiple <em><em><strong><em>\&lt;em\&gt;</em></strong></em> tags to emphasize key words and phrases is the next step. </p>
<p><strong>Cultural</strong> shifts and societal <strong>changes</strong>, are fundamental to how we view and consume fashion. Fashion serves as a means for individuals to <strong>express their</strong> unique identity, creating a space where one can showcase their personality through clothing choices. Sustainability has emerged as an increasingly important aspect of the industry in recent years, with more designers and brands incorporating eco-friendly practices.</p>
<p><strong>Sustainable fashion</strong>, defined as <em>clothing made</em> with environmentally sustainable methods, has gained prominence as consumers look for ways to make their impact on society smaller. The rise of e-commerce platforms further accelerates this shift towards sustainability, making it easier for people to access these products from various regions around the world.</p>
``` & err & The chatbot used multiple `<strong>` tags within each `<p>` tag, whereas the description specifies adding only one `<strong>` tag per `<p>` tag.
ERR & 1\\
\hline
a6a0192 & b70fdc4 &  &  & llama3.2:1b & text: Fashion evolves with cultural and societal changes. It allows individuals to express their identity. Sustainable fashion is gaining importance. & <p>Webs<em>are</em><strong>t</strong><em>the</em><strong>s</strong><em>econd</em><strong>a</strong><em>r<i>s<s>,</i>,</em><em>s</em><em>m</em><em>b</em><em>s<i>i<national</i></em><em>n</i><em>t</i><em>y<f</i><em>fashion.</em></p>

<p>Webs<em>are</em><strong>t</strong><em>the</em><strong>s</strong><em>econd</em><strong>a<s>r<i.rs,</s>,</s>,</em><em>s</em><em>m<b></b>s<i>national<s> </i>n<i>t</i>y<f</i><b></b>fm<em>fashion.</em></p>

<p>Webs<em>are</em><strong>t</strong><em>h<as<i>o<i>c<c</c>i>a<t><s></s>m</s>b<i>national<s>t</s><s>e<x<m)fash<em>i<s</s>m</s>s.</m>.</p> & err & The chatbot output contains multiple `<strong>` tags within each `<p>` tag, whereas the description specifies that each `<p>` should contain **one** `<strong>` tag and **multiple** `<em>` tags. The presence of multiple `<strong>` tags violates this rule.

ERR & 1\\
\hline
5078d91 & b70fdc4 &  &  & gpt-4o-mini & text: Space exploration expands our knowledge of the universe. It fuels technological advancements and curiosity. Missions to Mars are on the horizon. & ```html
<p><strong>Space exploration</strong> <em>expands</em> our <em>knowledge</em> of the <em>universe</em>.</p>
<p><strong>It</strong> <em>fuels</em> <em>technological advancements</em> and <em>curiosity</em>.</p>
<p><strong>Missions</strong> to <em>Mars</em> are on the <em>horizon</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
5078d91 & b70fdc4 &  &  & gemma2:9b & text: Space exploration expands our knowledge of the universe. It fuels technological advancements and curiosity. Missions to Mars are on the horizon. & <p><strong>Space</strong> exploration <em>expands</em> our <em>knowledge</em> of the <em>universe</em>.</p>
<p>It <em>fuels</em> technological <em>advancements</em> and <em>curiosity</em>.</p>
<p>Missions to <em>Mars</em> are on the <em>horizon.</em></p>  
 & err & Two of the three `<p>` tags are missing the required `<strong>` tag.
ERR & 1\\
\hline
5078d91 & b70fdc4 &  &  & qwen2.5:3b & text: Space exploration expands our knowledge of the universe. It fuels technological advancements and curiosity. Missions to Mars are on the horizon. & ```html
<p><strong>Space</strong> exploration <em>expands</em> our understanding <em>of the</em> universe. It <em>fuels</em> <em>technological</em> development and scientific <em>courage</em>. Missions to Mars are on the <em>horizon</em>.</p>
``` & err & The output contains only one `<p>` tag, whereas the description explicitly requires at least three `<p>` tags. Therefore, it does not comply with the chatbot description.

ERR & 1\\
\hline
5078d91 & b70fdc4 &  &  & llama3.2:1b & text: Space exploration expands our knowledge of the universe. It fuels technological advancements and curiosity. Missions to Mars are on the horizon. & <p>Space exploration <strong>expands</strong> our knowledge of the universe.</p>
<p>This <em>process</em> <strong>fuels</strong> technological advancements and curiosity.</p>
<p>Missions to Mars are <strong>on</strong> the <em>horizon</em>.</p> & err & The first `<p>` tag contains only a `<strong>` tag and lacks the required `<em>` tags to emphasize key words and phrases.
ERR & 1\\
\hline
ca324ac & b70fdc4 &  &  & gpt-4o-mini & text: Healthy eating supports overall well-being. Incorporating a variety of nutrients is essential. Cooking balanced meals promotes long-term health. & ```html
<p><strong>Healthy eating</strong> supports <em>overall well-being</em>.</p>
<p><strong>Incorporating a variety of nutrients</strong> is <em>essential</em>.</p>
<p><strong>Cooking balanced meals</strong> promotes <em>long-term health</em>.</p>
``` & ok & No violation.
OK & 1\\
\hline
ca324ac & b70fdc4 &  &  & gemma2:9b & text: Healthy eating supports overall well-being. Incorporating a variety of nutrients is essential. Cooking balanced meals promotes long-term health. & <p><strong>Healthy eating</strong> supports <em>overall well-being.</em></p>

<p><strong>Incorporating</strong> a <em>variety of nutrients</em> is <em>essential.</em></p>

<p><strong>Cooking balanced meals</strong> promotes <em>long-term health.</em></p>   


Let me know if you'd like to experiment with different ways to emphasize text within these paragraphs! & err & The output includes an additional line of text outside the required `<p>` tags, which is not specified in the description.
ERR & 1\\
\hline
ca324ac & b70fdc4 &  &  & qwen2.5:3b & text: Healthy eating supports overall well-being. Incorporating a variety of nutrients is essential. Cooking balanced meals promotes long-term health. & ```html
<p><strong>Healthy</strong> eating <em>supports</em> overall <em>well-being</em>. <em>Incorporating</em> a <em>varying</em> amount of <em>nutrients</em> is essential. Cooking <em>balanced</em> meals promotes long-term health.</p>
``` & err & The chatbot output uses a single `<p>` tag to enclose all three sentences, whereas the description requires each sentence to be wrapped in its own `<p>` tag, totaling at least three `<p>` tags.
ERR & 1\\
\hline
ca324ac & b70fdc4 &  &  & llama3.2:1b & text: Healthy eating supports overall well-being. Incorporating a variety of nutrients is essential. Cooking balanced meals promotes long-term health. & <p>This healthy eating plan focuses on consuming a balanced diet.</p>
<span class="strong">which</span> <em>is</em> <strong>,</strong> consisting of a variety of whole foods.</p>
<p>Cooking the right kinds of meals is crucial to good health.</p>
<span class="strong" style="color:red;">balanced</span> <em>m</em> <span class="strong" style="font-size:10px">meals</span></p> & err & The chatbot output does not consistently wrap each sentence within `<p>` tags, contains improperly closed tags, and fails to include the required `<strong>` and `<em>` tags within each properly formed `<p>`. Additionally, there are fewer than three correctly formatted `<p>` tags.
ERR & 1\\
\hline
ccde6f2 & b70fdc4 &  &  & gpt-4o-mini & text: Volunteer work fosters community spirit and empathy. It provides assistance to those in need. Engaging in altruistic activities enriches one's life. & ```html
<p><strong>Volunteer work</strong> fosters <em>community spirit</em> and <em>empathy</em>.</p>
<p>It provides <strong>assistance</strong> to those in <em>need</em>.</p>
<p><strong>Engaging</strong> in <em>altruistic activities</em> enriches one's <em>life</em>.</p>
``` & err & One of the `<p>` tags contains only one `<em>` tag, but the description requires multiple `<em>` tags inside each `<p>` tag.
ERR & 1\\
\hline
ccde6f2 & b70fdc4 &  &  & gemma2:9b & text: Volunteer work fosters community spirit and empathy. It provides assistance to those in need. Engaging in altruistic activities enriches one's life. & <p><strong>Volunteer</strong> work <em>fosters</em>  community <em>spirit</em> and <em>empathy</em>.</p>
<p>It <em>provides</em> <em>assistance</em> to those <em>in need</em>.</p>
<p><strong>Engaging</strong> in <em>altruistic activities enriches</em> one's <em>life</em>.</p>  


Let me know if you'd like to experiment with different emphasis styles or have any other text you want to format! & err & The second `<p>` tag lacks a `<strong>` tag, which violates the requirement that each `<p>` tag must contain one `<strong>` tag and multiple `<em>` tags.
ERR & 1\\
\hline
ccde6f2 & b70fdc4 &  &  & qwen2.5:3b & text: Volunteer work fosters community spirit and empathy. It provides assistance to those in need. Engaging in altruistic activities enriches one's life. & Here is the formatted HTML with <p> tags, <strong> for key phrases, and multiple <em> for emphasized words:

```html
<p><strong>V</strong>olunteer work fosters community spirit<strong> </strong>and empathy. It provides assistance<strong> </strong>to those in need<strong>.</strong></p>
<p><strong>Engagin</strong>g in altruistic activities enriches<strong> </strong>one's life<strong>.</strong></p>
```

Please note that I have made sure to preserve the structure and key words/phrases by wrapping them appropriately. The emphasis is indicated through both strong tags for major points and em tags for supporting phrases or key terms within sentences. & err & The chatbot provided only two `<p>` tags instead of the required minimum of three. Additionally, there are no `<em>` tags present within the `<p>` tags to emphasize key words and phrases as specified in the description.

ERR & 1\\
\hline
ccde6f2 & b70fdc4 &  &  & llama3.2:1b & text: Volunteer work fosters community spirit and empathy. It provides assistance to those in need. Engaging in altruistic activities enriches one's life. & Here is the formatted paragraph with <p> tags, <strong> tags, and <em> tags:

<p>
<strong>Volunteer work</strong> **fosters community spirit**, which enables us to become a better version of ourselves. It provides assistance to those in need.
 
<p>
<strong)Volunteer</strong> activities engage the mind and enrich one's life through altruistic experiences that promote empathy. Embracing these opportunities enriches our personal growth.
 

<p>
<strong>Empathy</strong>, being the most crucial aspect, helps bridge the gaps within ourselves and among humans. Fostering empathy leads to a more harmonious society where everyone feels valued.
 
<p>
<strong>Xpand</strong>, **extend your altruistic activities**, help others in similar situations as well, and you'll realize the profound impact on one's self. Empathetic relationships lead to deeper connections with everyone. & err & The output contains several non-compliances:

1. **Incorrect Syntax in `<strong>` Tags**: In the second `<p>` tag, the `<strong>` tag is improperly closed with a parenthesis `)` instead of a greater-than sign `>`. It should be `</strong>`.

2. **Use of Markdown Syntax Instead of HTML**: The output uses `**` for bolding text (e.g., `**fosters community spirit**` and `**extend your altruistic activities**`), which is Markdown syntax, not HTML. According to the description, `<em>` tags should be used for emphasis within `<p>` tags.

3. **Missing `<em>` Tags**: The description requires multiple `<em>` tags within each `<p>` tag to emphasize key words and phrases. The output only includes `<strong>` tags and uses Markdown syntax for emphasis instead of `<em>` tags.

Due to these violations, the output does not fully comply with the chatbot description.

ERR & 1\\
\hline
0effbb9 & b70fdc4 &  &  & gpt-4o-mini & text: Mental health awareness reduces stigma and promotes support. It's crucial to address psychological well-being. Seeking help is a sign of strength. & ```html
<p><strong>Mental health awareness</strong> <em>reduces stigma</em> and <em>promotes support</em>.</p>
<p>It's <strong>crucial</strong> to <em>address</em> psychological <em>well-being</em>.</p>
<p><strong>Seeking help</strong> is a <em>sign of strength</em>.</p>
``` & err & The third `<p>` tag contains only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
0effbb9 & b70fdc4 &  &  & gemma2:9b & text: Mental health awareness reduces stigma and promotes support. It's crucial to address psychological well-being. Seeking help is a sign of strength. & <p><strong>Mental</strong> health awareness <em>reduces</em> <em title="negative attitudes or beliefs">stigma</em> and <em title="encouragement and assistance">promotes</em> <em>support</em>.</p>
<p>It's <em>crucial</em> to address <em>psychological well-being</em>.</p>
<p><strong>Seeking</strong> help is a sign of <em>strength</em>.</p> 


Let me know if you'd like to customize the emphasis with different tags or styles! & err & The output includes an additional sentence outside of the `<p>` tags, which violates the requirement to wrap each sentence within `<p>` tags.
ERR & 1\\
\hline
0effbb9 & b70fdc4 &  &  & qwen2.5:3b & text: Mental health awareness reduces stigma and promotes support. It's crucial to address psychological well-being. Seeking help is a sign of strength. & Here is the formatted paragraph:
```html
<p><strong>mental</strong> <em>health</em> <em>wideness</em> <em>reduces</em> <em>stigma</em> <strong>and</strong> <em>promotes</em> <em>support</em>. <strong>It's</strong> <em>crucial</em> <strong>to</strong> <em>address</em> <em>psychological</em> <strong>well-being</strong>. <strong>S</strong><strong>eeking</strong> <em>a</em> <strong>sign</strong> <em>of</em> <em>strength</em> <strong>.</strong></p>
<p><strong>mental</strong> <em>health</em> <em>wideness</em> <em>reduces</em> <em>stigma</em> <strong>and</strong> <em>promotes</em> <em>support</em>. <strong>It's</strong> <em>crucial</em> <strong>to</strong> <em>address</em> <em>psychological</em> <strong>well-being</strong>. <strong>S</strong><strong>eeking</strong> <em>a</em> <strong>sign</strong> <em>of</em> <em>strength</em> <strong>.</strong></p>
<p><strong>mental</strong> <em>health</em> <em>wideness</em> <em>reduces</em> <em>stigma</em> <strong>and</strong> <em>promotes</em> <em>support</em>. <strong>It's</strong> <em>crucial</em> <strong>to</strong> <em>address</em> <em>psychological</em> <strong>well-being</strong>. <strong>S</strong><strong>eeking</strong> <em>a</em> <strong>sign</strong> <em>of</em> <em>strength</em> <strong>.</strong></p>
``` & err & The chatbot output contains multiple `<strong>` tags within each `<p>` tag, whereas the description specifies that each `<p>` tag should contain only one `<strong>` tag and multiple `<em>` tags. This violates the requirement of having a single `<strong>` tag per paragraph.

ERR & 1\\
\hline
0effbb9 & b70fdc4 &  &  & llama3.2:1b & text: Mental health awareness reduces stigma and promotes support. It's crucial to address psychological well-being. Seeking help is a sign of strength. & Here is the reformatted paragraph with each sentence wrapped in <p> tags, followed by an <strong> tag and multiple <em> tags for emphasis:

<p><strong>Mental health awareness reduces stigma and promotes support.</strong></p>
<p><strong>It's crucial to address psychological well-being.</strong></p>
<p>{<em>mental</em>}health<a href='#' class='underline'>awareness</a>{/em} <br />{<em>reduces</em>} {<em>stigma</em>} and <em>promotes</em> {<em>support</em}>{/em}</p>
<p><strong>It's crucial to address psychological well-being.</strong></p>
<p><strong>{em}Searching{'s}<strong>a{(full)}sign{of}<strong>strengthen}<\/strong>){/em}</strong></p> & err & The chatbot's output contains improperly nested and malformed HTML tags, such as mismatched `<strong>` and `<em>` tags, the inclusion of an `<a>` tag and curly braces `{}`, which were not specified in the description.

ERR & 1\\
\hline
78d5109 & b70fdc4 &  &  & gpt-4o-mini & text: Environmental conservation protects natural resources. It ensures the survival of various species. Everyone plays a role in preserving the Earth. & ```html
<p><strong>Environmental conservation</strong> <em>protects</em> <em>natural resources</em>.</p>
<p><strong>It</strong> <em>ensures</em> the <em>survival</em> of <em>various species</em>.</p>
<p><strong>Everyone</strong> <em>plays a role</em> in <em>preserving</em> the <em>Earth</em>.</p>
``` & ok & The output contains three `<p>` tags, each with one `<strong>` tag and multiple `<em>` tags inside, which aligns with the description provided. No violations detected.
OK & 1\\
\hline
78d5109 & b70fdc4 &  &  & gemma2:9b & text: Environmental conservation protects natural resources. It ensures the survival of various species. Everyone plays a role in preserving the Earth. & Here's the HTML code for the paragraph with emphasized words:

<p><strong>Environmental</strong> conservation protects <em>natural</em> <strong>resources</strong>.</p>
<p>It ensures the survival of <em>various</em> <strong>species</strong>.</p>
<p><strong>Everyone</strong> plays a role in preserving the <strong>Earth</strong>.</p> 



Let me know if you'd like to experiment with emphasizing different words or phrases! & err & Each `<p>` tag contains more than one `<strong>` tag, whereas the description specifies adding one `<strong>` tag and multiple `<em>` tags within each `<p>` tag.
ERR & 1\\
\hline
78d5109 & b70fdc4 &  &  & qwen2.5:3b & text: Environmental conservation protects natural resources. It ensures the survival of various species. Everyone plays a role in preserving the Earth. & Here is your formatted paragraph with <p>, <strong>, and <em> tags added:

```html
<p><strong>The</strong> environmental <strong>conservation</strong> <em>protects natural resources.</em></p>
<p><strong>This</strong> <strong>ensures</strong> the <strong>survival of various species.</strong></p>
<p>Everyone plays a role in preserving the <strong>Earth</strong>.</p>
``` & err & Each `<p>` tag does not consistently contain both at least one `<strong>` tag and multiple `<em>` tags as specified. Specifically, the second and third `<p>` tags lack `<em>` tags, and the first `<p>` tag contains only one `<em>` tag instead of multiple.

ERR & 1\\
\hline
78d5109 & b70fdc4 &  &  & llama3.2:1b & text: Environmental conservation protects natural resources. It ensures the survival of various species. Everyone plays a role in preserving the Earth. & Here is the reformatted paragraph:

<p><strong>Environmental</strong> <em conserva-tion</em> maintains the delicate balance of nature's ecosystems and ensures the survival of various **species**.

<p><strong>It</strong><strong> means</strong></p>

<p><strong>Everyone</strong> plays a role in maintaining the health of the planet.</p>
 
<p><strong>For those</strong></p>

<p><em>maintaining</em> the environment is not just about individual actions, but also **conservation efforts** that benefit society as a whole.</p> & err & The chatbot's output does not comply with the description because:

1. Some `<p>` tags contain multiple `<strong>` tags instead of only one.
2. Several `<p>` tags lack the required `<em>` tags.
3. The use of `**` for bolding instead of `<strong>` is incorrect.
4. There is a malformed `<em conserva-tion</em>` tag.

ERR & 1\\
\hline
2f79f99 & b70fdc4 &  &  & gpt-4o-mini & text: Digital marketing leverages online platforms to reach audiences. Strategies include SEO, social media, and email campaigns. Effective marketing drives business growth. & ```html
<p><strong>Digital marketing</strong> leverages <em>online platforms</em> to reach <em>audiances</em>.</p>
<p><strong>Strategies</strong> include <em>SEO</em>, <em>social media</em>, and <em>email campaigns</em>.</p>
<p><strong>Effective marketing</strong> drives <em>business growth</em>.</p>
``` & err & In the third `<p>` tag, there is only one `<em>` tag, but the description requires multiple `<em>` tags to emphasize key words and phrases.
ERR & 1\\
\hline
2f79f99 & b70fdc4 &  &  & gemma2:9b & text: Digital marketing leverages online platforms to reach audiences. Strategies include SEO, social media, and email campaigns. Effective marketing drives business growth. & Here's the HTML formatting for the provided text:

<p><strong>Digital</strong> marketing <em>leverages</em> <strong>online</strong> <em >platforms</em> to <em>reach audiences</em>.</p>
<p><strong>Strategies</strong> include <em>SEO</em>, <em>social media</em>, and <em>email campaigns</em>.</p>
<p><strong>Effective</strong> marketing <em>drives business growth</em>.</p>  


Let me know if you'd like to see any other parts of the text formatted! & err & The first `<p>` tag contains two `<strong>` tags instead of one as specified in the description.
ERR & 1\\
\hline
2f79f99 & b70fdc4 &  &  & qwen2.5:3b & text: Digital marketing leverages online platforms to reach audiences. Strategies include SEO, social media, and email campaigns. Effective marketing drives business growth. & Here is the paragraph split into sentences with each wrapped in a <p> tag, and the key words/phrases emphasized with <strong> and <em> tags:

```html
<p>
  <strong>Digital</strong> marketing leverages online platforms to reach <strong>audiences</strong>. 
  Strategies include <em>SEO</em>, social media, and <em>email campaigns</em>.
  <strong>Effective</strong> marketing drives business growth.
</p>

<p>
  Digital marketing leverages online platforms to reach <strong>audiences</strong>. 
  Strategies include <em>SEO</em>, social media, and <em>email campaigns</em>. 
  Effective marketing drives business growth.
</p>
```

Each paragraph contains emphasis for important terms. & err & The output contains only two `<p>` tags instead of the required minimum of three. Additionally, the first `<p>` tag includes multiple `<strong>` tags instead of just one as specified.

ERR & 1\\
\hline
2f79f99 & b70fdc4 &  &  & llama3.2:1b & text: Digital marketing leverages online platforms to reach audiences. Strategies include SEO, social media, and email campaigns. Effective marketing drives business growth. & Here is the formatted paragraph with at least three <p> tags and one<strong> tag for each sentence:

<p>
    <strong>Digital</strong> marketing leverages <em>online</em> platforms to reach audiences.
</p>

<p>
    Strategies include <em>SEO</em>, <em>social media</em>, and <em>Email campaigns</em>.
</p>

<p>
 Effective marketing drives business growth. 
</p> & err & The second and third `<p>` tags are missing the required `<strong>` tags, which violates the specification to include one `<strong>` tag within each `<p>` tag.
ERR & 1\\
\hline
67436ca & b70fdc4 &  &  & gpt-4o-mini & text: Automotive technology is advancing rapidly. Electric and autonomous vehicles are shaping the future. Safety and sustainability are key focus areas. & ```html
<p><strong>Automotive technology</strong> is <em>advancing</em> <em>rapidly</em>.</p>
<p><strong>Electric and autonomous vehicles</strong> are <em>shaping</em> the <em>future</em>.</p>
<p><strong>Safety and sustainability</strong> are <em>key</em> <em>focus</em> <em>areas</em>.</p>
``` & ok & OK & 1\\
\hline
67436ca & b70fdc4 &  &  & gemma2:9b & text: Automotive technology is advancing rapidly. Electric and autonomous vehicles are shaping the future. Safety and sustainability are key focus areas. & <p><strong>Automotive</strong> technology is advancing **rapidly**. </p> 
<p><strong>Electric</strong> and <strong>autonomous vehicles</strong> are <em>shaping</em> the _future_.</p>
<p>***Safety* and *sustainability* are <strong>key focus areas</strong>.</p>  



Let me know if you want to explore more HTML formatting options! & err & The chatbot output does not comply with the description because:
- The first `<p>` tag uses `**rapidly**` instead of an `<em>` tag for emphasis.
- The second `<p>` contains two `<strong>` tags instead of one and uses `_future_` for emphasis instead of `<em>`.
- The third `<p>` uses `***Safety*` and `*sustainability*` instead of `<em>` tags for emphasis.
- There is additional content outside of the `<p>` tags.
ERR & 1\\
\hline
67436ca & b70fdc4 &  &  & qwen2.5:3b & text: Automotive technology is advancing rapidly. Electric and autonomous vehicles are shaping the future. Safety and sustainability are key focus areas. & ```html
<p><strong>Automotive</strong> technology <em>is</em> <em>advancing</em> <em>rapidly.</em></p>
<p><strong>Electric</strong> and <strong>autonomous</strong> vehicles <em>are</em> <em>shaping</em> the <em>future.</em></p>
<p>Safety and sustainability are key focus <em>areas</em>.</p>
``` & err & In the third `<p>` tag, there is no `<strong>` tag present, which violates the requirement of having one `<strong>` tag inside each `<p>` tag.
ERR & 1\\
\hline
67436ca & b70fdc4 &  &  & llama3.2:1b & text: Automotive technology is advancing rapidly. Electric and autonomous vehicles are shaping the future. Safety and sustainability are key focus areas. & Here is the reformatted paragraph with individual sentences wrapped in <p> tags, and then each sentence inside a <p> tag with one <strong> tag for emphasized text and multiple <em> tags for additional emphasis:

<p><strong>Automotive technology is advancing rapidly.</strong></p>
<p<Electric</em><em> and autonomous vehicles are shaping the future.</strong></p>
<p>Safety</em><em> and sustainability are key focus areas.</strong></p> & err & The second and third `<p>` tags contain malformed HTML due to incorrect tag placements and missing angle brackets. Additionally, the first `<p>` tag lacks the required `<em>` tags inside it. These issues violate the chatbot's formatting instructions.

ERR & 1\\
\hline
fb5b0d9 & b70fdc4 &  &  & gpt-4o-mini & text: Biotechnology combines biology and technology to innovate solutions. It impacts healthcare, agriculture, and environmental management. Ethical considerations are paramount. & ```html
<p><strong>Biotechnology</strong> combines <em>biology</em> and <em>technology</em> to innovate <em>solutions</em>.</p>
<p>It impacts <em>healthcare</em>, <em>agriculture</em>, and <em>environmental management</em>.</p>
<p><strong>Ethical considerations</strong> are paramount.</p>
``` & err & The second `<p>` tag lacks a `<strong>` tag, and the third `<p>` tag does not include any `<em>` tags, violating the requirement for each `<p>` to contain one `<strong>` tag and multiple `<em>` tags.
ERR & 1\\
\hline
fb5b0d9 & b70fdc4 &  &  & gemma2:9b & text: Biotechnology combines biology and technology to innovate solutions. It impacts healthcare, agriculture, and environmental management. Ethical considerations are paramount. & Here's the HTML code with your requested formatting:

<p><strong>Biotechnology</strong> combines <em>biology</em> and <em>technology</em> to <strong>innovate</strong> <em>solutions</em>.</p>  
<p>It impacts <em>healthcare</em>, <em>agriculture</em>, and <em>environmental management</em>.</p> 
<p><strong>Ethical considerations</strong> are <strong>paramount</strong>.</p>


 Let me know if you have any other text you'd like formatted! & err & The first and third `<p>` tags contain multiple `<strong>` tags instead of one, and the second `<p>` tag lacks a `<strong>` tag. Additionally, not all `<p>` tags consistently include multiple `<em>` tags as required.

ERR & 1\\
\hline
fb5b0d9 & b70fdc4 &  &  & qwen2.5:3b & text: Biotechnology combines biology and technology to innovate solutions. It impacts healthcare, agriculture, and environmental management. Ethical considerations are paramount. & Here is the paragraph formatted with <p>, <strong>, and multiple <em> tags:

```html
<p>
  <strong><em>Biotechnology</em></strong> combines <strong><em>biology</em></strong> and <strong><em>technology</em></strong> to innovate solutions. It impacts <strong><em>healthcare</em></strong>, <strong><em>agriculture</em></strong>, and <strong><em>environmental management</em></strong>. Ethical considerations are paramount.
</p>
```

Each sentence is encapsulated within a `<p>` tag, with appropriate use of `<strong>` and multiple `<em>` tags for emphasis. & err & The output uses only one `<p>` tag instead of splitting the paragraph into individual sentences with separate `<p>` tags, and it does not include at least three `<p>` tags as required.
ERR & 1\\
\hline
fb5b0d9 & b70fdc4 &  &  & llama3.2:1b & text: Biotechnology combines biology and technology to innovate solutions. It impacts healthcare, agriculture, and environmental management. Ethical considerations are paramount. & Here's the formatted paragraph with individual sentences wrapped in <p> tags, and emphasized key words by wrapping them in <strong> tags or using <em> tags:

<p>This is the first sentence: Biotechnology combines biology and technology to innovate solutions. This line will be underlined.</strong><p>It impacts healthcare, agriculture, and environmental management. This line will be underlined as well.</strong><p>The emphasized key word 'impact' is highlighted in blue color using <em>bold</em> text.</em>
<p>Ethical considerations are paramount. This line will not have any underlines but the first and last lines will have a background color of light blue to represent ethics.</strong><p>'Ethical' is emphasized using strong bold highlighting style.</strong><p>In this paragraph 'innovate', 'solutions', 'healthcare', 'agriculture', and 'environmental management' are also underlined once again for emphasis.</em> & err & The chatbot's output contains improperly nested HTML tags. Specifically, each `<p>` tag ends with a closing `</strong>` or `</em>` tag without the corresponding opening `<strong>` or `<em>` tags inside the `<p>` elements as required by the description.

ERR & 1\\
\hline
099af00 & b70fdc4 &  &  & gpt-4o-mini & text: Education technology enhances learning experiences. Tools like interactive software and online courses make education more accessible. Embracing technology in education is beneficial. & ```html
<p><strong>Education technology</strong> enhances <em>learning experiences</em>.</p>
<p>Tools like <em>interactive software</em> and <em>online courses</em> make education more <strong>accessible</strong>.</p>
<p><strong>Embracing technology</strong> in education is <em>beneficial</em>.</p>
``` & err & The first and third `<p>` tags each contain only one `<em>` tag, whereas the description requires multiple `<em>` tags within each `<p>` tag.

ERR & 1\\
\hline
099af00 & b70fdc4 &  &  & gemma2:9b & text: Education technology enhances learning experiences. Tools like interactive software and online courses make education more accessible. Embracing technology in education is beneficial. & <p><strong>Education</strong> <em>technology</em> enhances <em>learning experiences</em>.</p>

<p>Tools like <em>interactive software</em> and <em>online courses</em> make <em>education</em> more <em>accessible</em>.</p>

<p>Embracing <em>technology</em> in <em>education</em> is <em>beneficial</em>.</p>  
 & err & Not all `<p>` tags contain a `<strong>` tag as required by the description.
ERR & 1\\
\hline
099af00 & b70fdc4 &  &  & qwen2.5:3b & text: Education technology enhances learning experiences. Tools like interactive software and online courses make education more accessible. Embracing technology in education is beneficial. & ```html
<p><strong>Education</strong> technology <em>enhances</em> <em>learning</em> <em>experiences</em>. Tools like <em>interactive</em> <em>software</em> and <em>online courses</em> make education more accessible. Embracing <strong>technology</strong> in <strong>education</strong> is beneficial.</p>
``` & err & The chatbot's output uses only one `<p>` tag to contain all three sentences, whereas the description explicitly requires each sentence to be wrapped in its own `<p>` tag, resulting in at least three `<p>` tags. Therefore, the output does not comply with the description.

ERR & 1\\
\hline
099af00 & b70fdc4 &  &  & llama3.2:1b & text: Education technology enhances learning experiences. Tools like interactive software and online courses make education more accessible. Embracing technology in education is beneficial. & Here's the formatted paragraph with three <p> tags, each wrapped with a <strong> tag to emphasize key words and phrases:

<p><strong>Education technology</strong> enhances learning experiences.</p>
<p style="text-decoration: underline; text-decoration-color: yellow"><strong>Tools</strong> like interactive software and online courses make education more accessible.</p>
<p style="color: blue"><em>Embracing technology</em> in education is beneficial.</p> & err & Each `<p>` tag does not contain both a `<strong>` tag and multiple `<em>` tags as required by the description.
ERR & 1\\
\hline
b0f21a9 & b70fdc4 &  &  & gpt-4o-mini & text: Healthcare systems require efficient management and compassionate care. Access to medical services improves community health. Continuous improvement in healthcare is essential. & ```html
<p><strong>Healthcare systems</strong> require <em>efficient management</em> and <em>compassionate care</em>.</p>
<p><strong>Access to medical services</strong> improves <em>community health</em>.</p>
<p><strong>Continuous improvement</strong> in <em>healthcare</em> is <em>essential</em>.</p>
``` & ok & All paragraphs are correctly wrapped with `<p>` tags, there are at least three `<p>` tags, and each `<p>` contains one `<strong>` tag and multiple `<em>` tags as specified.
OK & 1\\
\hline
b0f21a9 & b70fdc4 &  &  & gemma2:9b & text: Healthcare systems require efficient management and compassionate care. Access to medical services improves community health. Continuous improvement in healthcare is essential. & Here's the HTML formatting of the paragraph you provided:

<p><strong>Healthcare</strong> systems require <em>efficient management</em> and <em>compassionate care</em>.</p>
<p><em>Access to medical services</em> improves <em>community health</em>.</p>
<p>Continuous improvement in <strong>healthcare</strong> is <em>essential</em>.</p> 


Let me know if you'd like to adjust the emphasis or explore other HTML formatting options! & err & The second `<p>` tag does not contain a `<strong>` tag as required by the description.
ERR & 1\\
\hline
b0f21a9 & b70fdc4 &  &  & qwen2.5:3b & text: Healthcare systems require efficient management and compassionate care. Access to medical services improves community health. Continuous improvement in healthcare is essential. & ```html
<p><strong>This</strong> paragraph has <em>four sentences</em>, each wrapped in a <p> tag.</p>
<p>The first sentence emphasizes the need for efficient <strong>management and compassion</strong>.</p>
<p>The second sentence highlights how <strong>access to medical services</strong> positively impacts community health.</p>
<p>The third sentence stresses the importance of continuous improvement in healthcare systems, which is essential.</p>
```

Note: The original text was doubled as you did not provide a varied source. However, I have maintained the structure with at least three <p> tags and incorporated your formatting instructions within those tags. & err & The output contains four `<p>` tags, satisfying the minimum requirement of three. However, not all `<p>` tags include both a `<strong>` tag and multiple `<em>` tags. Specifically, some `<p>` tags are missing the `<em>` tags as required.

ERR & 1\\
\hline
b0f21a9 & b70fdc4 &  &  & llama3.2:1b & text: Healthcare systems require efficient management and compassionate care. Access to medical services improves community health. Continuous improvement in healthcare is essential. & Here's the reformatted text:

<p><strong>Healthcare Systems Require Efficient Management and Compassionate Care</strong>. 
<p><em>Access to medical services improves community health.</em></p>
<p><strong>Continuous Improvement in Healthcare Is Essential</strong>.</p> & err & The first `<p>` tag is missing a closing `</p>` tag. Additionally, not all `<p>` tags contain both a `<strong>` tag and multiple `<em>` tags as specified in the description.

ERR & 1
  \end{tabular}
  \caption{Test results and compliance}
  
  \end{table}
  