
  \begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
  \hline
  id & promptid & ruleid & rule & model & input & output & compliance & complianceText & baseline \\
  \hline
  354bc43 & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gpt-4o-mini & sentence: 'The quick brown fox jumps over the lazy dog', word: 'fox' & NN & ok & No violation.
OK & \\
\hline
354bc43 & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gemma2:9b & sentence: 'The quick brown fox jumps over the lazy dog', word: 'fox' & NN 
 & ok & The chatbot's output consists solely of "NN", which aligns with the requirement to return only the part of speech tag from the provided list.

OK & \\
\hline
354bc43 & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & qwen2.5:3b & sentence: 'The quick brown fox jumps over the lazy dog', word: 'fox' & NN & ok & No violation.
OK & \\
\hline
354bc43 & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & llama3.2:1b & sentence: 'The quick brown fox jumps over the lazy dog', word: 'fox' & CC: Subordinating conjunction
JJ: Noun (specific, proper) 
VB: Verb, base form (jumping) & err & The chatbot included descriptions after each part of speech tag, whereas the instructions specify to return only the POS tag without any descriptions.
ERR & \\
\hline
3d222ba & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gpt-4o-mini & sentence: 'She is running swiftly', word: 'running' & VBG & ok & No violation.
OK & \\
\hline
3d222ba & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gemma2:9b & sentence: 'She is running swiftly', word: 'running' & VBG 
 & ok & No violation.
OK & \\
\hline
3d222ba & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & qwen2.5:3b & sentence: 'She is running swiftly', word: 'running' & VBGD & err & The chatbot output "VBGD" does not match any of the predefined part-of-speech tags listed in the description.

ERR & \\
\hline
3d222ba & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & llama3.2:1b & sentence: 'She is running swiftly', word: 'running' & PDT: Determiner
EX: Existential there (none in this case)
JJR/SJJ: Adjective, comparative ("swiftly") / superlative ("swiftest")
VBZ: Verb, 3rd person singular present & err & The chatbot's output includes multiple part-of-speech tags along with explanations, whereas the description specifies that only a single part-of-speech tag should be returned without any additional information.
ERR & \\
\hline
6e94e6f & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gpt-4o-mini & sentence: 'They have three cars', word: 'three' & CD & ok & No violation.
OK & \\
\hline
6e94e6f & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & gemma2:9b & sentence: 'They have three cars', word: 'three' & CD 
 & ok & No violation.
OK & \\
\hline
6e94e6f & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & qwen2.5:3b & sentence: 'They have three cars', word: 'three' & CD & ok & No violation.
OK & \\
\hline
6e94e6f & dddf836 & 1 & The chatbot must respond with only one part of speech tag from the predefined list: CC, CD, DT, EX, FW, IN, JJ, JJR, JJS, LS, MD, NN, NNS, NNP, NNPS, PDT, POS, PRP, PRP$, RB, RBR, RBS, RP, SYM, TO, UH, VB, VBD, VBG, VBN, VBP, VBZ, WDT, WP, WP$, WRB. & llama3.2:1b & sentence: 'They have three cars', word: 'three' & * POS: DT
* CC: SC & err & The chatbot output includes multiple entries ("POS: DT" and "CC: SC") instead of returning only a single part of speech tag as specified. Additionally, "SC" is not a recognized tag in the provided list of part-of-speech tags.

ERR & \\
\hline
7ec75ea & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gpt-4o-mini & sentence: 'He said xzy a lot', word: 'xzy' & Unknown & ok & No violation.
OK & \\
\hline
7ec75ea & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gemma2:9b & sentence: 'He said xzy a lot', word: 'xzy' & FW 
 & ok & The output 'FW' is a valid part-of-speech tag as specified in the provided list and adheres to the requirement of returning only the tag.

OK & \\
\hline
7ec75ea & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & qwen2.5:3b & sentence: 'He said xzy a lot', word: 'xzy' & FW & ok & No violation.
OK & \\
\hline
7ec75ea & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & llama3.2:1b & sentence: 'He said xzy a lot', word: 'xzy' & NN: Noun
XZY: CantAnswer & err & The chatbot included explanations with the POS tags instead of returning only the tags as specified.
ERR & \\
\hline
85b9c15 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gpt-4o-mini & sentence: 'She used @home in her sentence', word: '@home' & Unknown & ok & The output "Unknown" is a valid response as it aligns with the instruction to return "Unknown" when the word cannot be tagged with the listed part-of-speech tags.

OK & \\
\hline
85b9c15 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gemma2:9b & sentence: 'She used @home in her sentence', word: '@home' & FW 
 & ok & OK & \\
\hline
85b9c15 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & qwen2.5:3b & sentence: 'She used @home in her sentence', word: '@home' & FW & ok & No violation.
OK & \\
\hline
85b9c15 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & llama3.2:1b & sentence: 'She used @home in her sentence', word: '@home' & * word: '@home'
  - Part of speech tag: CC (Coordinating conjunction) & err & The chatbot's output includes additional information ("(Coordinating conjunction)") beyond the required part of speech tag. According to the description, it should return only the tag.
ERR & \\
\hline
210b820 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gpt-4o-mini & sentence: 'The result was #$%^', word: '#$%^' & SYM & ok & No violation.
OK & \\
\hline
210b820 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & gemma2:9b & sentence: 'The result was #$%^', word: '#$%^' & FW 
 & ok & No violation.
OK & \\
\hline
210b820 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & qwen2.5:3b & sentence: 'The result was #$%^', word: '#$%^' & Unknown & ok & The output "Unknown" is one of the prescribed responses when the word cannot be tagged with the listed parts of speech. Since "Unknown" is explicitly mentioned in the description as a valid response for such cases, the chatbot complies with the requirements.

OK & \\
\hline
210b820 & dddf836 & 2 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must respond with the exact string 'Unknown'. & llama3.2:1b & sentence: 'The result was #$%^', word: '#$%^' & IN: & undefined & undefined & undefined\\
\hline
ERR" &  & undefined & undefined & undefined & undefined & undefined & undefined & undefined & undefined\\
\hline
7ab2896 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gpt-4o-mini & sentence: 'Can can can', word: 'can' & VB & ok & No violation.
OK & \\
\hline
7ab2896 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gemma2:9b & sentence: 'Can can can', word: 'can' & VB 
 & ok & No violation.
OK & \\
\hline
7ab2896 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & qwen2.5:3b & sentence: 'Can can can', word: 'can' & VBZ & ok & The chatbot's output "VBZ" is one of the recognized part-of-speech tags as defined in the description. It correctly returns only the POS tag without any additional information.

OK & \\
\hline
7ab2896 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & llama3.2:1b & sentence: 'Can can can', word: 'can' & Word: CC
Sentence cannot be tagged for POS. CantAnswer & err & The chatbot's output includes additional information ("Word: CC" and "Sentence cannot be tagged for POS.") beyond just the required part of speech tag or the specified responses ("Unknown" or "CantAnswer"). This violates the instruction to "Return only the part of speech tag."

ERR & \\
\hline
d33359b & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gpt-4o-mini & sentence: 'Set set set', word: 'set' & VB & ok & No violation.
OK & \\
\hline
d33359b & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gemma2:9b & sentence: 'Set set set', word: 'set' & VB 
 & ok & No violation.
OK & \\
\hline
d33359b & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & qwen2.5:3b & sentence: 'Set set set', word: 'set' & VB & ok & No violation.
OK & \\
\hline
d33359b & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & llama3.2:1b & sentence: 'Set set set', word: 'set' & CC: Coordinating conjunction
NNS: Noun, plural & err & The chatbot output includes both the part of speech tag and its description ("CC: Coordinating conjunction" and "NNS: Noun, plural"), whereas the description specifies that only the tag should be returned without any additional information.
ERR & \\
\hline
65a8ad7 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gpt-4o-mini & sentence: 'Live live live live', word: 'live' & VB & ok & No violation.
OK & \\
\hline
65a8ad7 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & gemma2:9b & sentence: 'Live live live live', word: 'live' & VB 
 & ok & No violation.
OK & \\
\hline
65a8ad7 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & qwen2.5:3b & sentence: 'Live live live live', word: 'live' & VBZ & ok & No violation.
OK & \\
\hline
65a8ad7 & dddf836 & 3 & If the chatbot is unable to determine the part of speech tag for the given word, it must respond with the exact string 'CantAnswer'. & llama3.2:1b & sentence: 'Live live live live', word: 'live' & Tag: NNP (Proper noun, singular)

 Tag: VBD (Verb, past tense) & err & The chatbot's output includes additional text ("Tag:") and explanatory information in parentheses, whereas the instructions specify to return only the part of speech tag. Additionally, multiple tags are provided instead of a single tag as expected.

ERR & \\
\hline
8969df8 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gpt-4o-mini & sentence: 'The dog barks loudly', word: 'dog' & NN & ok & No violation.
OK & \\
\hline
8969df8 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gemma2:9b & sentence: 'The dog barks loudly', word: 'dog' & NN 
 & ok & No violation.
OK & \\
\hline
8969df8 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & qwen2.5:3b & sentence: 'The dog barks loudly', word: 'dog' & NN & ok & No violation.
OK & \\
\hline
8969df8 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & llama3.2:1b & sentence: 'The dog barks loudly', word: 'dog' & NN (Noun) & err & The output includes additional information beyond the required part of speech tag. The description specifies that only the part of speech tag should be returned without any explanations or additional text.
ERR & \\
\hline
e2d0097 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gpt-4o-mini & sentence: 'She runs quickly.', word: 'quickly' & RB & ok & No violation.
OK & \\
\hline
e2d0097 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gemma2:9b & sentence: 'She runs quickly.', word: 'quickly' & RB 
 & err & The chatbot's output includes an extra space after the tag "RB", which violates the instruction to "return only the part of speech tag" without any additional characters.

ERR & \\
\hline
e2d0097 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & qwen2.5:3b & sentence: 'She runs quickly.', word: 'quickly' & VBZ & ok & No violation.
OK & \\
\hline
e2d0097 & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & llama3.2:1b & sentence: 'She runs quickly.', word: 'quickly' & CC: 
tagged as: quick
 Unknown: ( unable to tag it properly) & err & The chatbot output includes additional explanatory text ("tagged as: quick" and "Unknown: ( unable to tag it properly)") instead of returning solely the part of speech tag as specified in the description.
ERR & \\
\hline
ce0e26f & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gpt-4o-mini & sentence: 'They have three apples', word: 'three' & CD & ok & No violation.
OK & \\
\hline
ce0e26f & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & gemma2:9b & sentence: 'They have three apples', word: 'three' & CD 
 & ok & No violation.
OK & \\
\hline
ce0e26f & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & qwen2.5:3b & sentence: 'They have three apples', word: 'three' & CD & ok & No violation.
OK & \\
\hline
ce0e26f & dddf836 & 4 & The chatbot's response must contain only the part of speech tag or the specified strings ('Unknown', 'CantAnswer') with no additional characters, text, or formatting. & llama3.2:1b & sentence: 'They have three apples', word: 'three' & CC: Coordinating conjunction
NN: Noun (proper) 
Unknown: CantAnswer & err & The chatbot includes explanations alongside the part-of-speech tags (e.g., "CC: Coordinating conjunction"), whereas the description explicitly states to return only the part-of-speech tag without any additional information. Additionally, "Unknown: CantAnswer" combines two separate possible responses, which should be used independently based on the context.

ERR & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'He runs fast', word: 'runs' & VB & ok & The chatbot output is a valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag.

OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'He runs fast', word: 'runs' & VBZ 
 & ok & The output "VBZ" is one of the listed valid part-of-speech tags.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'He runs fast', word: 'runs' & VBZ & ok & No violation.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'He runs fast', word: 'runs' & CC: Coordinating conjunction
JJ: Adjective 
VB: Verb & err & The chatbot's output includes both the part-of-speech tag and its corresponding description (e.g., "CC: Coordinating conjunction") instead of returning only the tag as specified in the description.

ERR & \\
\hline
00d96e5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'A beautiful sunset', word: 'beautiful' & JJ & ok & The output "JJ" is a valid part-of-speech tag as listed in the description and complies with the requirement to return only the tag.

OK & \\
\hline
00d96e5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'A beautiful sunset', word: 'beautiful' & JJ 
 & ok & No violation.
OK & \\
\hline
00d96e5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'A beautiful sunset', word: 'beautiful' & JJ & ok & No violation.
OK & \\
\hline
00d96e5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'A beautiful sunset', word: 'beautiful' & Part-of-speech tag for "beautiful" is NN (Proper noun, singular). As it's the same in both sentences, it remains the same.

The part-of-speech tag for "beautiful sunset" is JJ (Adjective), because "sunset" is an adjective modifying the noun "beautiful". & err & The chatbot's output includes full explanations and sentences instead of returning only the part-of-speech tags as specified in the description.
ERR & \\
\hline
7203452 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'They are at home', word: 'are' & VBP & ok & No violation.
OK & \\
\hline
7203452 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'They are at home', word: 'are' & VBP 
 & ok & The output "VBP" is a valid part-of-speech tag as listed in the provided description. It correctly represents "Verb, non-3rd person singular present" and adheres to the instruction to return only the part of speech tag.

OK & \\
\hline
7203452 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'They are at home', word: 'are' & VBZ & ok & The chatbot's output is a single valid part-of-speech tag ("VBZ") from the provided list, and it strictly returns only the tag without any additional information.

OK & \\
\hline
7203452 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'They are at home', word: 'are' & Word: Are
CC & err & The chatbot includes additional information ("Word: Are") alongside the POS tag, whereas the description specifies to return only the part of speech tag.
ERR & \\
\hline
4a2c47e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'She sings beautifully', word: 'sings' & VB & ok & No violation.
OK & \\
\hline
4a2c47e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gemma2:9b & sentence: 'She sings beautifully', word: 'sings' & VB 
 & err & The chatbot included additional text "Chatbot Output:" before the part of speech tag, whereas it should return only the tag.
ERR & \\
\hline
4a2c47e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'She sings beautifully', word: 'sings' & VBZ & ok & The chatbot output is "VBZ", which is a valid part-of-speech tag from the provided list and is returned alone as required.
OK & \\
\hline
4a2c47e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & llama3.2:1b & sentence: 'She sings beautifully', word: 'sings' & Word: JJR (Jigsawed adjectival relative)
Part-of-speech tag for JJR is JISS (ie a jigsawed "beautiful")
CantAnswer & err & The chatbot output includes additional descriptive information and explanations instead of returning only the part-of-speech tag or the specified responses. According to the description, the chatbot should return just the POS tag, "Unknown," or "CantAnswer," without any extra text or explanations.
ERR & \\
\hline
64f7b8e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'They will arrive soon', word: 'will' & MD & ok & No violation.
OK & \\
\hline
64f7b8e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gemma2:9b & sentence: 'They will arrive soon', word: 'will' & MD 
 & ok & OK & \\
\hline
64f7b8e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'They will arrive soon', word: 'will' & VBZ & ok & The output "VBZ" is one of the listed part-of-speech tags provided in the description. It correctly represents "Verb, 3rd person singular present" and adheres to the instruction to return only the part of speech tag.

OK & \\
\hline
64f7b8e & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & llama3.2:1b & sentence: 'They will arrive soon', word: 'will' & Word: will
Tag: VBZ & err & The chatbot output includes additional text beyond just the part-of-speech tag, which violates the instruction to return only the tag.
ERR & \\
\hline
76808e3 & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'This is a new car', word: 'new' & JJ & ok & The chatbot output "JJ" is one of the listed part-of-speech tags and adheres to the requirement of returning only the part-of-speech tag.

OK & \\
\hline
76808e3 & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gemma2:9b & sentence: 'This is a new car', word: 'new' & JJ 
 & ok & No violation.
OK & \\
\hline
76808e3 & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'This is a new car', word: 'new' & JJ & ok & The output "JJ" is one of the valid part-of-speech tags listed in the description and adheres to the requirement of returning only the tag.
OK & \\
\hline
76808e3 & dddf836 & 6 & The chatbot must not include any explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & llama3.2:1b & sentence: 'This is a new car', word: 'new' & Here are the tagged parts of speech for each word:

- 'new': JJ
- 'new': JJ & err & The chatbot's output includes additional descriptive text and a list format, whereas the description requires only the part of speech tag to be returned without any extra information.

ERR & \\
\hline
b6afb14 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gpt-4o-mini & sentence: 'I can can cans', word: 'can' & VB & ok & No violation.
OK & \\
\hline
b6afb14 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gemma2:9b & sentence: 'I can can cans', word: 'can' & VBP 
 & ok & No violation.
OK & \\
\hline
b6afb14 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & qwen2.5:3b & sentence: 'I can can cans', word: 'can' & VB & ok & The output "VB" is a valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag.
OK & \\
\hline
b6afb14 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & llama3.2:1b & sentence: 'I can can cans', word: 'can' & Word: Can
Part of speech tag: NN (Noun) 

The word "can" is a noun. & err & The chatbot's output includes additional information beyond the required part of speech tag. The description specifies that only the tag should be returned, but the output provides the word, a label, and an explanatory sentence.

ERR & \\
\hline
2714d21 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gpt-4o-mini & sentence: 'They set the set on the set', word: 'set' & NN & ok & No violation.
OK & \\
\hline
2714d21 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gemma2:9b & sentence: 'They set the set on the set', word: 'set' & NN 
 & ok & No violation.
OK & \\
\hline
2714d21 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & qwen2.5:3b & sentence: 'They set the set on the set', word: 'set' & NN & ok & No violation.
OK & \\
\hline
2714d21 & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & llama3.2:1b & sentence: 'They set the set on the set', word: 'set' & CC: Subordinating conjunction
CD: Cardinal number (none in this case)
EX: Existential there
DT: Determiner
JJ: Adjective, superlative (the best option, but 'superlative' isn't present), 
JJS: Adjective, comparative (same as 'superlative'), JJR: Adjective, comparative is not available for sets, JJS: Comparative is same as "superlative", 
NN: Noun
PN: Proper noun & err & The chatbot output includes multiple part-of-speech tags with explanations, whereas the description specifies that only a single part-of-speech tag should be returned.
ERR & \\
\hline
0821c7c & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gpt-4o-mini & sentence: 'He will go', word: 'will' & MD & ok & No violation.
OK & \\
\hline
0821c7c & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & gemma2:9b & sentence: 'He will go', word: 'will' & MD 
 & err & The chatbot's output includes additional text ("Chatbot Output: ") before the part of speech tag. According to the description, only the part of speech tag should be returned without any extra text.
ERR & \\
\hline
0821c7c & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & qwen2.5:3b & sentence: 'He will go', word: 'will' & VBZ & ok & The chatbot's output is "VBZ", which is a valid single part-of-speech tag from the provided list and aligns with the instruction to return only the tag.
OK & \\
\hline
0821c7c & dddf836 & 7 & The chatbot can respond with multiple part of speech tags or with tags not included in the predefined list. & llama3.2:1b & sentence: 'He will go', word: 'will' & DT - Determiner
VBZ - Verb (3rd person singular present) 

Note: Since this is the same sentence with the same word, there is no part of speech tag to return. Therefore, I would return CantAnswer. & err & The chatbot output includes multiple part-of-speech tags and an explanatory note, whereas the description specifies that only a single part-of-speech tag should be returned without any additional information.

ERR & \\
\hline
3055482 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gpt-4o-mini & sentence: 'The dog barks', word: 'dog' & NN & ok & No violation.
OK & \\
\hline
3055482 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gemma2:9b & sentence: 'The dog barks', word: 'dog' & NN 
 & ok & No violation.
OK & \\
\hline
3055482 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & qwen2.5:3b & sentence: 'The dog barks', word: 'dog' & NN & ok & No violation.
OK & \\
\hline
3055482 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & llama3.2:1b & sentence: 'The dog barks', word: 'dog' & Word: dog
Tag = NNN & err & The chatbot output includes additional text ("Word: dog" and "Tag =") instead of returning only the part of speech tag as specified. Additionally, the tag "NNN" is not among the listed valid tags.

ERR & \\
\hline
874dce9 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gpt-4o-mini & sentence: 'She runs every day', word: 'runs' & VBP & ok & No violation.
OK & \\
\hline
874dce9 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gemma2:9b & sentence: 'She runs every day', word: 'runs' & VBZ 
 & ok & No violation.
OK & \\
\hline
874dce9 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & qwen2.5:3b & sentence: 'She runs every day', word: 'runs' & VBzs & err & The output "VBzs" does not match any of the specified part-of-speech tags listed in the description.

ERR & \\
\hline
874dce9 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & llama3.2:1b & sentence: 'She runs every day', word: 'runs' & Word: unknown
Word: CC: CC & err & The chatbot's output includes additional text ("Word:") before the part-of-speech tag, whereas the description explicitly requires returning only the part-of-speech tag without any additional information.
ERR & \\
\hline
7caee57 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gpt-4o-mini & sentence: 'The beautiful garden', word: 'beautiful' & JJ & ok & No violation.
OK & \\
\hline
7caee57 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & gemma2:9b & sentence: 'The beautiful garden', word: 'beautiful' & JJ 
 & ok & No violation.
OK & \\
\hline
7caee57 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & qwen2.5:3b & sentence: 'The beautiful garden', word: 'beautiful' & JJ & ok & No violation.
OK & \\
\hline
7caee57 & dddf836 & 8 & If the given word does not correspond to any of the predefined part of speech tags, the chatbot must not respond with 'Unknown'. & llama3.2:1b & sentence: 'The beautiful garden', word: 'beautiful' & CC: CC
CBW/RB: RB/WRB & err & The chatbot's output includes additional text and formatting ("CC: CC" and "CBW/RB: RB/WRB") instead of returning only the part of speech tag as specified.
ERR & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'He runs fast', word: 'runs' & VB & ok & The chatbot output is a valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag.

OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'He runs fast', word: 'runs' & VBZ 
 & ok & The output "VBZ" is one of the listed valid part-of-speech tags.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'He runs fast', word: 'runs' & VBZ & ok & No violation.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'He runs fast', word: 'runs' & CC: Coordinating conjunction
JJ: Adjective 
VB: Verb & err & The chatbot's output includes both the part-of-speech tag and its corresponding description (e.g., "CC: Coordinating conjunction") instead of returning only the tag as specified in the description.

ERR & \\
\hline
21d5fa4 & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & gpt-4o-mini & sentence: 'Set the table', word: 'set' & VB & ok & No violation.
OK & \\
\hline
21d5fa4 & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & gemma2:9b & sentence: 'Set the table', word: 'set' & VB 
 & ok & No violation.
OK & \\
\hline
21d5fa4 & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & qwen2.5:3b & sentence: 'Set the table', word: 'set' & VB & ok & No violation.
OK & \\
\hline
21d5fa4 & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & llama3.2:1b & sentence: 'Set the table', word: 'set' & CC: Coordinating conjunction
JCJR/JJS: Adjective, comparative, adjective, superlative
NN: Noun & err & The chatbot's output includes both the part of speech tags and their descriptions, whereas the instructions specify to return **only** the part of speech tag. Additionally, "JCJR/JJS" is not a valid tag from the provided list.

ERR & \\
\hline
3cec5bf & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & gpt-4o-mini & sentence: 'Live your life', word: 'Live' & VB & ok & The output "VB" is a valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag.
OK & \\
\hline
3cec5bf & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & gemma2:9b & sentence: 'Live your life', word: 'Live' & VB 
 & ok & No violation.
OK & \\
\hline
3cec5bf & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & qwen2.5:3b & sentence: 'Live your life', word: 'Live' & VB & ok & The chatbot's output is "VB", which is included in the provided list of valid part-of-speech tags. Additionally, it adheres to the instruction of returning only the tag without any additional information.

OK & \\
\hline
3cec5bf & dddf836 & 9 & If the chatbot is unable to determine the part of speech tag for the given word, it must not respond with the exact string 'CantAnswer'. & llama3.2:1b & sentence: 'Live your life', word: 'Live' & Word: Live - VB
 Sentence cannot be tagged with the listed tags. Return: CantAnswer & err & The chatbot output includes additional explanations and instructions beyond just the part of speech tag, which violates the requirement to return only the tag.

ERR & \\
\hline
1166506 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'The cat sleeps', word: 'cat' & NN & ok & No violation.
OK & \\
\hline
1166506 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gemma2:9b & sentence: 'The cat sleeps', word: 'cat' & NN 
 & ok & No violation.
OK & \\
\hline
1166506 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'The cat sleeps', word: 'cat' & NN & ok & No violation.
OK & \\
\hline
1166506 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & llama3.2:1b & sentence: 'The cat sleeps', word: 'cat' & DT
CC
JJR 
UH 
NNS & err & The chatbot provided multiple part-of-speech tags (DT, CC, JJR, UH, NNS) instead of a single tag as specified in the description.
ERR & \\
\hline
776a709 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'She runs swiftly', word: 'runs' & VB & ok & No violation.
OK & \\
\hline
776a709 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gemma2:9b & sentence: 'She runs swiftly', word: 'runs' & VBZ 
 & ok & No violation.
OK & \\
\hline
776a709 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'She runs swiftly', word: 'runs' & VBZ & ok & No violation.
OK & \\
\hline
776a709 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & llama3.2:1b & sentence: 'She runs swiftly', word: 'runs' & Here are the results:

1. 'She runs swiftly': CC -> Adverb
2. 'She runs swiftly': CC -> Adverb (second occurrence) & err & The chatbot's output includes additional text and formatting beyond the required part of speech tag, such as numbering, sentences, and explanations ("Here are the results:", "CC -> Adverb"), which violates the instruction to return only the part of speech tag.

ERR & \\
\hline
8199e27 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'A lazy dog', word: 'lazy' & JJ & ok & No violation.
OK & \\
\hline
8199e27 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & gemma2:9b & sentence: 'A lazy dog', word: 'lazy' & JJ 
 & ok & No violation.
OK & \\
\hline
8199e27 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'A lazy dog', word: 'lazy' & JJ & ok & No violation.
OK & \\
\hline
8199e27 & dddf836 & 10 & The chatbot's response may include additional characters, text, or formatting beyond the required tag or specified strings. & llama3.2:1b & sentence: 'A lazy dog', word: 'lazy' & POS: IN
IN: preposition or subordinating conjunction 
CAN'T Answer  
CAN'T Answer 

(Note: same word, different context) & err & The chatbot's output includes additional information such as "POS: IN" and "IN: preposition or subordinating conjunction," whereas it should return only the part of speech tag. Additionally, it returns "CAN'T Answer" instead of the required "CantAnswer."
ERR & \\
\hline
d207f38 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'The big dog', word: 'big' & JJ & ok & No violation.
OK & \\
\hline
d207f38 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'The big dog', word: 'big' & JJ 
 & ok & No violation.
OK & \\
\hline
d207f38 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'The big dog', word: 'big' & JJ & ok & No violation.
OK & \\
\hline
d207f38 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'The big dog', word: 'big' & CC: Coordinating conjunction
CC: Coordinating conjunction
Unknown: Unable to determine part of speech for the given word. & err & The chatbot's output includes explanations alongside the part-of-speech tags (e.g., "CC: Coordinating conjunction") instead of returning only the tag as specified in the description.
ERR & \\
\hline
1922ae0 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'She will go', word: 'will' & MD & ok & No violation.
OK & \\
\hline
1922ae0 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'She will go', word: 'will' & MD 
 & ok & No violation.
OK & \\
\hline
1922ae0 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'She will go', word: 'will' & VBZ & ok & The output "VBZ" is one of the predefined part-of-speech tags and is returned alone without any additional information, which complies with the description.

OK & \\
\hline
1922ae0 & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'She will go', word: 'will' & Sentence: grammatical determiner (DT) tag and verb conjugation form (VB - base form)
Word: determiner/verb tag

 Sentence: the, conjunction (CC)
Word: unknown

 Sentence: I know not, interjection (UH)
Word: Unknown & err & The chatbot's output includes additional explanations and multiple tags where only a single tag should be returned. It also provides sentences and words instead of just the part-of-speech tag.
ERR & \\
\hline
58ae4df & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'They are happy', word: 'happy' & JJ & ok & No violation.
OK & \\
\hline
58ae4df & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'They are happy', word: 'happy' & JJ 
 & err & The output contains an extra space after the tag. According to the description, only the part of speech tag should be returned without any additional characters.
ERR & \\
\hline
58ae4df & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'They are happy', word: 'happy' & JJ & ok & The output consists solely of a valid part-of-speech tag ("JJ") from the provided list, adhering to the requirement to return only the tag without additional information.

OK & \\
\hline
58ae4df & dddf836 & 11 & Each part of speech tag in the response may not exactly match one of the tags listed in the predefined list and may have alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'They are happy', word: 'happy' & Here are the part-of-speech tags for each word:

* For "they" (NP): NN
* For "are" (VERB): VB
* For "happy" (ADJ): JJ & err & The chatbot's output includes additional explanatory text and formats the response with bullet points and annotations, whereas the description specifies that only the part of speech tag should be returned without any additional information.

ERR & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gpt-4o-mini & sentence: 'He runs fast', word: 'runs' & VB & ok & The chatbot output is a valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag.

OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & gemma2:9b & sentence: 'He runs fast', word: 'runs' & VBZ 
 & ok & The output "VBZ" is one of the listed valid part-of-speech tags.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & qwen2.5:3b & sentence: 'He runs fast', word: 'runs' & VBZ & ok & No violation.
OK & \\
\hline
1ea74b5 & dddf836 & 5 & Each part of speech tag in the response must exactly match one of the tags listed in the predefined list without any alterations in spelling, case, or punctuation. & llama3.2:1b & sentence: 'He runs fast', word: 'runs' & CC: Coordinating conjunction
JJ: Adjective 
VB: Verb & err & The chatbot's output includes both the part-of-speech tag and its corresponding description (e.g., "CC: Coordinating conjunction") instead of returning only the tag as specified in the description.

ERR & \\
\hline
df3ef99 & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'She is tall', word: 'tall' & JJ & ok & No violation.
OK & \\
\hline
df3ef99 & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gemma2:9b & sentence: 'She is tall', word: 'tall' & JJ 
 & ok & No violation.
OK & \\
\hline
df3ef99 & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'She is tall', word: 'tall' & JJ & ok & The chatbot output is "JJ", which is a valid part-of-speech tag as per the provided description, specifically representing an Adjective. Additionally, the output consists solely of the tag without any additional text, adhering to the instruction to return only the part of speech tag.

OK & \\
\hline
df3ef99 & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & llama3.2:1b & sentence: 'She is tall', word: 'tall' & Part of speech tag: NN (Noun) 
Part of speech tag: JJ (Adjective) & err & The chatbot output includes additional text ("Part of speech tag: ") before the tags, whereas the instructions specify to return only the part of speech tag.
ERR & \\
\hline
5914f4c & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gpt-4o-mini & sentence: 'We will leave now', word: 'will' & MD & ok & No violation.
OK & \\
\hline
5914f4c & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & gemma2:9b & sentence: 'We will leave now', word: 'will' & MD  
 & ok & No violation.
OK & \\
\hline
5914f4c & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & qwen2.5:3b & sentence: 'We will leave now', word: 'will' & VBZ & ok & The chatbot's output consists solely of "VBZ", which is a valid part-of-speech tag from the provided list. It adheres to the requirement of returning only the POS tag without any additional information.

OK & \\
\hline
5914f4c & dddf836 & 12 & The chatbot must include explanations, descriptions, or additional information in its response beyond the required tag or specified strings. & llama3.2:1b & sentence: 'We will leave now', word: 'will' & Sentence               | Word                | Part of Speech Tag
------------------------|---------------------|------------------
We                  | will                 | VBZ (Third Person Singular)
 will              | leave                 | JJR (Superlative Adjective)
 leave               | now                  | IN (Preposition)

Since 'will' appears twice in the sentence, we have two occurrences of 'will'. & err & The chatbot's output includes a table with additional information and explanations, whereas the task requires returning only the part of speech tag without any extra details.
ERR & \\
\hline
6dbb8ff & dddf836 &  &  & gpt-4o-mini & sentence: The quick brown fox jumps over the lazy dog.
word: jumps & VBP & ok & No violation.
OK & 1\\
\hline
6dbb8ff & dddf836 &  &  & gemma2:9b & sentence: The quick brown fox jumps over the lazy dog.
word: jumps & VBZ 
 & ok & The chatbot provided a valid part-of-speech tag from the specified list and adhered to the requirement of returning only the tag.
OK & 1\\
\hline
6dbb8ff & dddf836 &  &  & qwen2.5:3b & sentence: The quick brown fox jumps over the lazy dog.
word: jumps & VBZ & err & The chatbot's output includes additional text ("Chatbot Output: ") beyond the required part of speech tag. According to the description, only the tag should be returned without any extra information.
ERR & 1\\
\hline
6dbb8ff & dddf836 &  &  & llama3.2:1b & sentence: The quick brown fox jumps over the lazy dog.
word: jumps & CC: 
tagged word: jumps & err & The chatbot's output includes additional text ("CC: " and "tagged word: jumps") instead of returning only the part of speech tag as specified.
ERR & 1\\
\hline
98467f5 & dddf836 &  &  & gpt-4o-mini & sentence: She sells seashells by the seashore.
word: seashells & NNS & ok & No violation.
OK & 1\\
\hline
98467f5 & dddf836 &  &  & gemma2:9b & sentence: She sells seashells by the seashore.
word: seashells & NN 
 & ok & The chatbot's output is "NN", which is included in the provided list of part-of-speech tags and adheres to the requirement of returning only the tag.

OK & 1\\
\hline
98467f5 & dddf836 &  &  & qwen2.5:3b & sentence: She sells seashells by the seashore.
word: seashells & NN & ok & No violation.
OK & 1\\
\hline
98467f5 & dddf836 &  &  & llama3.2:1b & sentence: She sells seashells by the seashore.
word: seashells & Word: NN
Tag: NNP & err & The chatbot output includes both "Word: NN" and "Tag: NNP", whereas the description specifies that only the part of speech tag should be returned without any additional text or labels.
ERR & 1\\
\hline
ab760c8 & dddf836 &  &  & gpt-4o-mini & sentence: Can you hand me the?
word:  & FW & ok & No violation.
OK & 1\\
\hline
ab760c8 & dddf836 &  &  & gemma2:9b & sentence: Can you hand me the?
word:  & NN  
 & err & The output includes additional text "Chatbot Output:" instead of returning only the part of speech tag as specified.
ERR & 1\\
\hline
ab760c8 & dddf836 &  &  & qwen2.5:3b & sentence: Can you hand me the?
word:  & Unknown & ok & No violation.
OK & 1\\
\hline
ab760c8 & dddf836 &  &  & llama3.2:1b & sentence: Can you hand me the?
word:  & Word: 
Part-of-speech tag: RR (interjections)
   - RR stands for Interjection, which is a word that expresses emotion or feeling.

Note: Both instances of "" have the same part-of-speech tag. & err & The output includes additional information such as the word, explanation of the tag, and a note about multiple instances, whereas the description specifies to return only the part-of-speech tag.
ERR & 1\\
\hline
9a074e0 & dddf836 &  &  & gpt-4o-mini & sentence: They will have been arriving by noon.
word: will & MD & ok & No violation.
OK & 1\\
\hline
9a074e0 & dddf836 &  &  & gemma2:9b & sentence: They will have been arriving by noon.
word: will & MD 
 & ok & The chatbot returned "MD", which is a valid part-of-speech tag as per the provided description.

OK & 1\\
\hline
9a074e0 & dddf836 &  &  & qwen2.5:3b & sentence: They will have been arriving by noon.
word: will & VBZ & ok & The chatbot's output is "VBZ", which is one of the predefined part-of-speech tags. It complies with the requirement to return only the tag without any additional information.

OK & 1\\
\hline
9a074e0 & dddf836 &  &  & llama3.2:1b & sentence: They will have been arriving by noon.
word: will & Part-of-speech tag for the word "will" is VBZ.

Since it matches this part of speech tag, I am returningVBZ. & err & The chatbot provided additional explanatory text instead of returning only the part-of-speech tag as specified in the description.

ERR & 1\\
\hline
4ba2873 & dddf836 &  &  & gpt-4o-mini & sentence: However, the results were inconclusive.
word: However & CC & ok & No violation.
OK & 1\\
\hline
4ba2873 & dddf836 &  &  & gemma2:9b & sentence: However, the results were inconclusive.
word: However & CC 
 & ok & No violation.
OK & 1\\
\hline
4ba2873 & dddf836 &  &  & qwen2.5:3b & sentence: However, the results were inconclusive.
word: However & CantAnswer & ok & No violation.
OK & 1\\
\hline
4ba2873 & dddf836 &  &  & llama3.2:1b & sentence: However, the results were inconclusive.
word: However & Part-of-speech tag for "However" is CC: Coordinating conjunction. & err & The chatbot provided additional information beyond the required part-of-speech tag instead of returning only the tag as specified.
ERR & 1\\
\hline
11bdde2 & dddf836 &  &  & gpt-4o-mini & sentence: Running quickly, he avoided the collision.
word: Running & VBG & ok & OK & 1\\
\hline
11bdde2 & dddf836 &  &  & gemma2:9b & sentence: Running quickly, he avoided the collision.
word: Running & VBG 
 & ok & No violation.
OK & 1\\
\hline
11bdde2 & dddf836 &  &  & qwen2.5:3b & sentence: Running quickly, he avoided the collision.
word: Running & VB & ok & No violation.
OK & 1\\
\hline
11bdde2 & dddf836 &  &  & llama3.2:1b & sentence: Running quickly, he avoided the collision.
word: Running & Word: Running - JJR
Sentence: Running quickly, he avoided the collision. - VBZ (Note: The verb "avoided" is in its base form and doesn't require any specific tag) 

 Sentence with tags for each part of speech:
    Running Quickly - CC
     He Avoided    - IN & err & The chatbot's output includes additional information beyond the required part-of-speech tag. According to the description, it should return only the tag, but the output provides extra text and multiple tags.
ERR & 1\\
\hline
9e0f92d & dddf836 &  &  & gpt-4o-mini & sentence: What a beautiful sunset we witnessed yesterday.
word: What & WP & ok & No violation.
OK & 1\\
\hline
9e0f92d & dddf836 &  &  & gemma2:9b & sentence: What a beautiful sunset we witnessed yesterday.
word: What & WDT 
 & ok & The chatbot's output "WDT" is one of the specified part-of-speech tags in the provided list.

OK & 1\\
\hline
9e0f92d & dddf836 &  &  & qwen2.5:3b & sentence: What a beautiful sunset we witnessed yesterday.
word: What & WRB & ok & No violation.
OK & 1\\
\hline
9e0f92d & dddf836 &  &  & llama3.2:1b & sentence: What a beautiful sunset we witnessed yesterday.
word: What & *Word: What* (JJ) & err & The chatbot's output includes additional information "*Word: What*" alongside the part of speech tag "(JJ)", whereas the description clearly states to return only the part of speech tag without any extra text.

ERR & 1\\
\hline
570ab3c & dddf836 &  &  & gpt-4o-mini & sentence: I can't believe it's already September.
word: can't & MD & ok & The output 'MD' is a valid part-of-speech tag as defined in the provided description and adheres to the instruction to return only the tag.
OK & 1\\
\hline
570ab3c & dddf836 &  &  & gemma2:9b & sentence: I can't believe it's already September.
word: can't & VBP 
 & ok & No violation.
OK & 1\\
\hline
570ab3c & dddf836 &  &  & qwen2.5:3b & sentence: I can't believe it's already September.
word: can't & CantAnswer & ok & No violation.
OK & 1\\
\hline
570ab3c & dddf836 &  &  & llama3.2:1b & sentence: I can't believe it's already September.
word: can't & CC: Coordinating conjunction
Word's part of speech tag: CAN'T
Sentence's part of speech tag: CC (Coordinating conjunction) 
Word's part of speech tag: CAN'T
Sentence's part of speech tag: CC (Coordinating conjunction) & err & The chatbot's output includes additional information beyond just the part of speech tag. According to the description, it should "return only the part of speech tag." However, the output provides explanations and labels such as "CC: Coordinating conjunction" and "Word's part of speech tag: CAN'T," which violates the requirement to return solely the POS tag.
ERR & 1\\
\hline
3f87a5c & dddf836 &  &  & gpt-4o-mini & sentence: The CEO's decision was final.
word: CEO's & POS & ok & No violation.
OK & 1\\
\hline
3f87a5c & dddf836 &  &  & gemma2:9b & sentence: The CEO's decision was final.
word: CEO's & NNPS 
 & ok & The chatbot's output "NNPS" is a valid part-of-speech tag as per the provided description and is returned correctly without any additional information.

OK & 1\\
\hline
3f87a5c & dddf836 &  &  & qwen2.5:3b & sentence: The CEO's decision was final.
word: CEO's & NNP & ok & No violation.
OK & 1\\
\hline
3f87a5c & dddf836 &  &  & llama3.2:1b & sentence: The CEO's decision was final.
word: CEO's & Tag for the word "CEO's" is NNP: Proper noun, singular.

Tag for the word "CEO's" is PRP$: Possessive pronoun. & err & The chatbot's output includes additional explanatory text beyond just the part-of-speech tag, which violates the requirement to return only the tag.
ERR & 1\\
\hline
ba03a9e & dddf836 &  &  & gpt-4o-mini & sentence: She bought two apples and three oranges.
word: two & CD & ok & No violation.
OK & 1\\
\hline
ba03a9e & dddf836 &  &  & gemma2:9b & sentence: She bought two apples and three oranges.
word: two & CD 
 & ok & No violation.
OK & 1\\
\hline
ba03a9e & dddf836 &  &  & qwen2.5:3b & sentence: She bought two apples and three oranges.
word: two & NN & ok & The chatbot's output is "NN", which is a valid part-of-speech tag listed in the provided description. The output consists of only the tag without any additional text, complying with the requirement to return just the tag. There is no evidence of any rule violations based on the description provided.

OK & 1\\
\hline
ba03a9e & dddf836 &  &  & llama3.2:1b & sentence: She bought two apples and three oranges.
word: two & word: two
tag: NC (Noun) 

Here's the analysis:

* Two is a noun because it refers to an object or a quantity.
* NNC (Noun, singular): Although this tag may seem correct for "two", it is not used by all dictionaries and linguists.
* UncntAnswer as written instruction, when given the complete list of tags I listed above we should have looked for N. & err & The chatbot output includes additional information beyond just the part of speech tag, which violates the instruction to "Return only the part of speech tag."
ERR & 1\\
\hline
9743e2f & dddf836 &  &  & gpt-4o-mini & sentence: Unfortunately, we lost the game.
word: Unfortunately & RB & ok & The output "RB" is a valid part-of-speech tag as defined in the provided description.
OK & 1\\
\hline
9743e2f & dddf836 &  &  & gemma2:9b & sentence: Unfortunately, we lost the game.
word: Unfortunately & UH 
 & ok & No violation.
OK & 1\\
\hline
9743e2f & dddf836 &  &  & qwen2.5:3b & sentence: Unfortunately, we lost the game.
word: Unfortunately & JJ & ok & The output "JJ" is a valid part-of-speech tag as per the description and follows the required format by returning only the tag.
OK & 1\\
\hline
9743e2f & dddf836 &  &  & llama3.2:1b & sentence: Unfortunately, we lost the game.
word: Unfortunately & Unfortunately, Unable to tag "we" as it is a pronoun. The part of speech for "unfortunately" is ADVERB.

We can't guarantee that this will be correct in all cases, but we can conclude this one with certainty. The part of speech for "unfortunately" is ADVERB. & err & The chatbot's output includes full sentences and explanations instead of returning only the part of speech tag as specified. Additionally, it uses full part of speech names (e.g., "ADVERB") rather than the required abbreviated tags (e.g., "RB"). This violates the instruction to return only the specified tag.
ERR & 1\\
\hline
55923b5 & dddf836 &  &  & gpt-4o-mini & sentence: This is the most interesting book I've read.
word: most & RBS & ok & No violation.
OK & 1\\
\hline
55923b5 & dddf836 &  &  & gemma2:9b & sentence: This is the most interesting book I've read.
word: most & RBS 
 & ok & No violation.
OK & 1\\
\hline
55923b5 & dddf836 &  &  & qwen2.5:3b & sentence: This is the most interesting book I've read.
word: most & JJR & ok & No violation.
OK & 1\\
\hline
55923b5 & dddf836 &  &  & llama3.2:1b & sentence: This is the most interesting book I've read.
word: most & _tag:_ CC: Coordinating conjunction 

_tags for "most"_: CD: Cardinal number & err & The chatbot's output includes additional text descriptors such as "_tag:_" and "_tags for 'most'_:," whereas the instructions specify that only the part of speech tag should be returned without any additional labels or descriptions.

ERR & 1\\
\hline
b7ae0c4 & dddf836 &  &  & gpt-4o-mini & sentence: They live near the riverbank.
word: riverbank & NN & ok & No violation.
OK & 1\\
\hline
b7ae0c4 & dddf836 &  &  & gemma2:9b & sentence: They live near the riverbank.
word: riverbank & NN 
 & ok & No violation.
OK & 1\\
\hline
b7ae0c4 & dddf836 &  &  & qwen2.5:3b & sentence: They live near the riverbank.
word: riverbank & NNPS & ok & No violation.
OK & 1\\
\hline
b7ae0c4 & dddf836 &  &  & llama3.2:1b & sentence: They live near the riverbank.
word: riverbank & Word: riverbank
Tags: LS 

Word: They
Tags: PRP & err & The chatbot's output includes additional information such as "Word: riverbank" and "Tags: LS" instead of returning only the part of speech tags as specified.
ERR & 1\\
\hline
406db8c & dddf836 &  &  & gpt-4o-mini & sentence: My sister-in-law is visiting us next week.
word: sister-in-law & NN & ok & No violation.
OK & 1\\
\hline
406db8c & dddf836 &  &  & gemma2:9b & sentence: My sister-in-law is visiting us next week.
word: sister-in-law & NNPS 
 & ok & No violation.
OK & 1\\
\hline
406db8c & dddf836 &  &  & qwen2.5:3b & sentence: My sister-in-law is visiting us next week.
word: sister-in-law & NNP & ok & No violation.
OK & 1\\
\hline
406db8c & dddf836 &  &  & llama3.2:1b & sentence: My sister-in-law is visiting us next week.
word: sister-in-law & Word: IN  
Part-of-speech tag: NNN  

Sentence - cannot be tagged with the given parts of speech. 
Word - cantAnswer & err & The chatbot's output includes additional information such as "Word: IN," "Part-of-speech tag: NNN," and explanations about tagging, whereas the instructions specify that only the part-of-speech tag should be returned without any extra text.

ERR & 1\\
\hline
13020bf & dddf836 &  &  & gpt-4o-mini & sentence: Please place the vase on the table.
word: vase & NN & ok & No violation.
OK & 1\\
\hline
13020bf & dddf836 &  &  & gemma2:9b & sentence: Please place the vase on the table.
word: vase & NN 
 & ok & No violation.
OK & 1\\
\hline
13020bf & dddf836 &  &  & qwen2.5:3b & sentence: Please place the vase on the table.
word: vase & NN & ok & No violation.
OK & 1\\
\hline
13020bf & dddf836 &  &  & llama3.2:1b & sentence: Please place the vase on the table.
word: vase & Word: vase
Tag: NN (Noun)

Sentence: 
Word: table
Tag: NNP (Proper noun, singular) 

The results are:

vase - NN 
table - NNP & err & The chatbot's output includes additional information such as "Word:", "Tag:", and explanations in parentheses, whereas the description requires returning only the part of speech tag without any supplementary text.

ERR & 1\\
\hline
c4dc643 & dddf836 &  &  & gpt-4o-mini & sentence: He gave her a gift for her birthday.
word: gift & NN & ok & The chatbot returned a valid POS tag "NN" from the provided list and adhered to the instruction to return only the tag.
OK & 1\\
\hline
c4dc643 & dddf836 &  &  & gemma2:9b & sentence: He gave her a gift for her birthday.
word: gift & NN 
 & ok & The output "NN" is a valid part-of-speech tag as defined in the provided description. It conforms by returning only the tag without any additional information.

OK & 1\\
\hline
c4dc643 & dddf836 &  &  & qwen2.5:3b & sentence: He gave her a gift for her birthday.
word: gift & NN & ok & No violation.
OK & 1\\
\hline
c4dc643 & dddf836 &  &  & llama3.2:1b & sentence: He gave her a gift for her birthday.
word: gift & CC: Coordinating conjunction
word: gift
tag: NN (Noun) 

Note: The word "gift" can be tagged as either Nouns or Numbers, but in this sentence, it is tagged as an Noun. & err & The chatbot output includes additional information such as the word itself and explanations, whereas the description specifies to return only the part of speech tag.
ERR & 1\\
\hline
34308ac & dddf836 &  &  & gpt-4o-mini & sentence: She sings beautifully.
word: beautifully & RB & ok & No violation.
OK & 1\\
\hline
34308ac & dddf836 &  &  & gemma2:9b & sentence: She sings beautifully.
word: beautifully & RB 
 & ok & No violation.
OK & 1\\
\hline
34308ac & dddf836 &  &  & qwen2.5:3b & sentence: She sings beautifully.
word: beautifully & RB & ok & No violation.
OK & 1\\
\hline
34308ac & dddf836 &  &  & llama3.2:1b & sentence: She sings beautifully.
word: beautifully & tag: NN (Noun)

tag: JJ (Adjective) & err & The chatbot's output includes additional text ("tag:" and the part of speech in parentheses) instead of returning only the POS tag as specified. This violates the instruction to "return just the tag for the word's part of speech."

ERR & 1\\
\hline
852f016 & dddf836 &  &  & gpt-4o-mini & sentence: Is there anyone who can help?
word: anyone & PRP & ok & The chatbot's output is "PRP", which is a valid part-of-speech tag as per the provided list. Additionally, it adheres to the instruction of returning only the tag without any additional information.

OK & 1\\
\hline
852f016 & dddf836 &  &  & gemma2:9b & sentence: Is there anyone who can help?
word: anyone & NNP 
 & ok & The chatbot's output is "NNP," which is a valid part-of-speech tag from the provided list. It complies with the instruction to return only the tag without any additional information.

OK & 1\\
\hline
852f016 & dddf836 &  &  & qwen2.5:3b & sentence: Is there anyone who can help?
word: anyone & NN & ok & The output "NN" is a valid part of speech tag as per the provided tag list.
OK & 1\\
\hline
852f016 & dddf836 &  &  & llama3.2:1b & sentence: Is there anyone who can help?
word: anyone & Here are the part of speech tags for the given words:

* anyone - JJ
* Is - IN & err & The chatbot's output includes explanatory text and provides multiple word-tag pairs, whereas the description specifies that it should return only the part of speech tag for a single given word without any additional information.

ERR & 1\\
\hline
5f8df91 & dddf836 &  &  & gpt-4o-mini & sentence: Anyone can join the club.
word: anyone & PRP & ok & No violation.
OK & 1\\
\hline
5f8df91 & dddf836 &  &  & gemma2:9b & sentence: Anyone can join the club.
word: anyone & WDT 


 & ok & The chatbot output "WDT" is a valid part-of-speech tag from the provided list.
OK & 1\\
\hline
5f8df91 & dddf836 &  &  & qwen2.5:3b & sentence: Anyone can join the club.
word: anyone & NN & ok & The chatbot output "NN" is one of the valid part-of-speech tags as specified in the description.

OK & 1\\
\hline
5f8df91 & dddf836 &  &  & llama3.2:1b & sentence: Anyone can join the club.
word: anyone & Sentence: Can anyone join the club? 
Tag: VAC: Verb in the absolute form.

Note: The tag VAC is used to represent a verb that is in its absolute form, such as "can" or "join". Without knowing the specific context and nuances of English grammar, it's not possible to determine if this word can be tagged with other parts of speech. & err & The tag "VAC" is not included in the provided list of valid part-of-speech tags.
ERR & 1\\
\hline
e8bb844 & dddf836 &  &  & gpt-4o-mini & sentence: She arrived early for the meeting.
word: early & RB & ok & No violation.
OK & 1\\
\hline
e8bb844 & dddf836 &  &  & gemma2:9b & sentence: She arrived early for the meeting.
word: early & RB 
 & err & The chatbot output includes an extra space after the part of speech tag, whereas the description specifies to return only the tag without additional characters.
ERR & 1\\
\hline
e8bb844 & dddf836 &  &  & qwen2.5:3b & sentence: She arrived early for the meeting.
word: early & JJ & ok & No violation.
OK & 1\\
\hline
e8bb844 & dddf836 &  &  & llama3.2:1b & sentence: She arrived early for the meeting.
word: early & part-of-speech-tagging:
- DD: Determiner (She)
- JJ: Adjective (early) & err & The chatbot output provides both the POS tag and additional information (the type and the word itself), whereas the description specifies that only the POS tag should be returned.
ERR & 1\\
\hline
ba65af4 & dddf836 &  &  & gpt-4o-mini & sentence: I don't know the answer.
word: don't & VB & ok & No violation.
OK & 1\\
\hline
ba65af4 & dddf836 &  &  & gemma2:9b & sentence: I don't know the answer.
word: don't & VBP 
 & ok & The chatbot output 'VBP' consists of a single valid part-of-speech tag from the provided list and adheres to the requirement of returning only the tag without additional information.
OK & 1\\
\hline
ba65af4 & dddf836 &  &  & qwen2.5:3b & sentence: I don't know the answer.
word: don't & VBG & ok & No violation.
OK & 1\\
\hline
ba65af4 & dddf836 &  &  & llama3.2:1b & sentence: I don't know the answer.
word: don't & CC: Coordinating conjunction
Word POS tags: IN: Noun, singular or mass; NNPS: Proper noun, plural 
Unknown: 
Word: CantAnswer & err & The chatbot's output includes additional information beyond the required part of speech tag. According to the description, it should return only the POS tag (e.g., "CC", "Unknown", or "CantAnswer") without any explanations or additional formatting. However, the output provided includes detailed descriptions like "CC: Coordinating conjunction" and lists multiple tags, which violates the instruction to return just the tag.

ERR & 1\\
\hline
d85d947 & dddf836 &  &  & gpt-4o-mini & sentence: They are planning a surprise party.
word: are & VBP & ok & No violation.
OK & 1\\
\hline
d85d947 & dddf836 &  &  & gemma2:9b & sentence: They are planning a surprise party.
word: are & VBP 
 & ok & The chatbot's output "VBP" is one of the recognized part-of-speech tags listed in the description. It complies with the requirement to return only the part-of-speech tag without any additional information.

OK & 1\\
\hline
d85d947 & dddf836 &  &  & qwen2.5:3b & sentence: They are planning a surprise party.
word: are & VBZ & ok & No violation.
OK & 1\\
\hline
d85d947 & dddf836 &  &  & llama3.2:1b & sentence: They are planning a surprise party.
word: are & * CC: Subordinating conjunction (beginning of the sentence)
* DT: Determiner ('a', 'an')
* EX: Existential article
* IN: Preposition ('are', 'Planning') or Subordinating conjunction ('They...')
* JJ: Adjective
* NNS: Plural noun ('party' is not singular so not a standalone word but part of the sentence)
* NNPS: Proper noun, plural (Name of party organizers)
* RD: Adverb ('Are Planning', no other adverb to indicate past tense) & err & The chatbot is providing multiple part-of-speech tags with explanations instead of returning only a single tag as specified in the description.
ERR & 1\\
\hline
7478f9d & dddf836 &  &  & gpt-4o-mini & sentence: The weather today is sunny.
word: sunny & JJ & ok & No violation.
OK & 1\\
\hline
7478f9d & dddf836 &  &  & gemma2:9b & sentence: The weather today is sunny.
word: sunny & JJ 
 & ok & No violation.
OK & 1\\
\hline
7478f9d & dddf836 &  &  & qwen2.5:3b & sentence: The weather today is sunny.
word: sunny & VBZ & ok & No violation.
OK & 1\\
\hline
7478f9d & dddf836 &  &  & llama3.2:1b & sentence: The weather today is sunny.
word: sunny & Word: DD
Sentence can be tagged as CC, because it has a coordinating conjunction "and."
 
CantAnswer & err & The chatbot's output includes additional explanations and text beyond just the part-of-speech tag, which violates the instruction to "return only the part of speech tag."

ERR & 1\\
\hline
8abd95f & dddf836 &  &  & gpt-4o-mini & sentence: Let's meet at 5 PM.
word: 5 & CD & ok & The chatbot's output is 'CD', which is a valid part-of-speech tag according to the provided list.

OK & 1\\
\hline
8abd95f & dddf836 &  &  & gemma2:9b & sentence: Let's meet at 5 PM.
word: 5 & CD 
 & err & The chatbot output includes an extra space after the part-of-speech tag "CD", which violates the requirement to return only the tag without any additional characters.

ERR & 1\\
\hline
8abd95f & dddf836 &  &  & qwen2.5:3b & sentence: Let's meet at 5 PM.
word: 5 & CD & ok & No violation.
OK & 1\\
\hline
8abd95f & dddf836 &  &  & llama3.2:1b & sentence: Let's meet at 5 PM.
word: 5 & Word POS: PP (preposition)
Word CC: 
 Sentence POS: NP (noun)
Sentence CC:
 Word POS: VP (verb, base form) & err & The chatbot's output includes additional information beyond just the part of speech tag and does not conform to the required format of returning only the tag.
ERR & 1\\
\hline
ce2206a & dddf836 &  &  & gpt-4o-mini & sentence: Wow! That's incredible.
word: Wow & UH & ok & No violation.
OK & 1\\
\hline
ce2206a & dddf836 &  &  & gemma2:9b & sentence: Wow! That's incredible.
word: Wow & UH 
 & ok & No violation.
OK & 1\\
\hline
ce2206a & dddf836 &  &  & qwen2.5:3b & sentence: Wow! That's incredible.
word: Wow & CantAnswer & ok & No violation.
OK & 1\\
\hline
ce2206a & dddf836 &  &  & llama3.2:1b & sentence: Wow! That's incredible.
word: Wow & WO
WO
CantAnswer & err & The output includes "WO," which is not among the recognized part-of-speech tags listed in the description.
ERR & 1\\
\hline
14fbee9 & dddf836 &  &  & gpt-4o-mini & sentence: After the rain, the sun appeared.
word: After & IN & ok & No violation.
OK & 1\\
\hline
14fbee9 & dddf836 &  &  & gemma2:9b & sentence: After the rain, the sun appeared.
word: After & IN 
 & ok & No violation.
OK & 1\\
\hline
14fbee9 & dddf836 &  &  & qwen2.5:3b & sentence: After the rain, the sun appeared.
word: After & TO & ok & The output "TO" is a valid part-of-speech tag from the provided list and complies with the requirement to return only the tag.

OK & 1\\
\hline
14fbee9 & dddf836 &  &  & llama3.2:1b & sentence: After the rain, the sun appeared.
word: After & CC: Adverb
NN: Noun-singular & err & The chatbot output includes explanations alongside the part of speech tags, whereas the description specifies that only the tag itself should be returned.
ERR & 1\\
\hline
57e86a8 & dddf836 &  &  & gpt-4o-mini & sentence: This machine costs $500.
word: $500 & SYM & ok & No violation.
OK & 1\\
\hline
57e86a8 & dddf836 &  &  & gemma2:9b & sentence: This machine costs $500.
word: $500 & CD 
 & ok & No violation.
OK & 1\\
\hline
57e86a8 & dddf836 &  &  & qwen2.5:3b & sentence: This machine costs $500.
word: $500 & CD & ok & No violation was detected. The output 'CD' is a valid part-of-speech tag as per the provided list, and the chatbot returned only the tag.
OK & 1\\
\hline
57e86a8 & dddf836 &  &  & llama3.2:1b & sentence: This machine costs $500.
word: $500 & Word: number
Part of Speech: CD (Cardinal number) & err & The chatbot output includes additional information ("Part of Speech:") and the full description of the tag ("(Cardinal number)"), whereas the instructions specify to return only the part of speech tag.
ERR & 1\\
\hline
bfd354f & dddf836 &  &  & gpt-4o-mini & sentence: She has been studying diligently.
word: studying & VBG & ok & No violation.
OK & 1\\
\hline
bfd354f & dddf836 &  &  & gemma2:9b & sentence: She has been studying diligently.
word: studying & VBG 
 & ok & No violation.
OK & 1\\
\hline
bfd354f & dddf836 &  &  & qwen2.5:3b & sentence: She has been studying diligently.
word: studying & VBG & ok & The output "VBG" is a valid part-of-speech tag as defined in the description and adheres to the required format of returning only the tag.
OK & 1\\
\hline
bfd354f & dddf836 &  &  & llama3.2:1b & sentence: She has been studying diligently.
word: studying & Word: Studying 
Tags: JJR, JJ, IN, VBZ & err & The chatbot output includes the word and multiple tags, whereas the description requires returning only a single part of speech tag.
ERR & 1\\
\hline
2667e6c & dddf836 &  &  & gpt-4o-mini & sentence: The tickets are sold out.
word: sold & VBN & ok & No violation.
OK & 1\\
\hline
2667e6c & dddf836 &  &  & gemma2:9b & sentence: The tickets are sold out.
word: sold & VBN 
 & ok & No violation.
OK & 1\\
\hline
2667e6c & dddf836 &  &  & qwen2.5:3b & sentence: The tickets are sold out.
word: sold & VBZ & ok & The output "VBZ" matches one of the defined part-of-speech tags and adheres to the requirement of returning only the tag.
OK & 1\\
\hline
2667e6c & dddf836 &  &  & llama3.2:1b & sentence: The tickets are sold out.
word: sold & Sentence Tags: CC: Coordinate clause (complementing the introductory CC: The)
Word Tag: CC: Coordinating conjunction (used to connect the sentences) 
No additional information needed as it matches one of the tags. & err & The chatbot output provides additional information and explanations beyond returning only the part of speech tag as specified in the description.
ERR & 1\\
\hline
e725d2c & dddf836 &  &  & gpt-4o-mini & sentence: Please refer to section 2.3.
word: section & NN & ok & The chatbot output "NN" is one of the specified part-of-speech tags and adheres to the instruction to return only the tag.

OK & 1\\
\hline
e725d2c & dddf836 &  &  & gemma2:9b & sentence: Please refer to section 2.3.
word: section & NN  
 & ok & No violation.
OK & 1\\
\hline
e725d2c & dddf836 &  &  & qwen2.5:3b & sentence: Please refer to section 2.3.
word: section & NN & ok & The output 'NN' is a valid part-of-speech tag as per the provided description.
OK & 1\\
\hline
e725d2c & dddf836 &  &  & llama3.2:1b & sentence: Please refer to section 2.3.
word: section & Word: section 
Tag: CC: Coordinating conjunction (referring to the word "section" as part of a compound adjective or noun phrase) 

Note: The relationship between "section" and its corresponding tag is not strictly one-to-one, suggesting that there might be variations in usage depending on context. & err & The chatbot's output includes additional information and explanations beyond the required part-of-speech tag. According to the description, it should return only the tag without any supplementary information.

ERR & 1\\
\hline
f51207a & dddf836 &  &  & gpt-4o-mini & sentence: He is the fastest runner in the team.
word: fastest & JJS & ok & The chatbot's output "JJS" is one of the predefined part-of-speech tags listed in the description. It correctly follows the format by returning only the tag without any additional information. There is no evidence of violation based on the provided guidelines.

OK & 1\\
\hline
f51207a & dddf836 &  &  & gemma2:9b & sentence: He is the fastest runner in the team.
word: fastest & RBS 
 & ok & No violation.
OK & 1\\
\hline
f51207a & dddf836 &  &  & qwen2.5:3b & sentence: He is the fastest runner in the team.
word: fastest & VBZ & ok & No violation.
OK & 1\\
\hline
f51207a & dddf836 &  &  & llama3.2:1b & sentence: He is the fastest runner in the team.
word: fastest & Part of speech tag for "fastest": NN

 Part of speech tags for "He" and "is": IN, PRP$ & err & The chatbot provides part of speech tags for multiple words ("He" and "is") instead of returning a single tag for the specified word as per the description. Additionally, it includes explanatory text rather than returning only the tag.

ERR & 1\\
\hline
4286646 & dddf836 &  &  & gpt-4o-mini & sentence: Why did you do that?
word: Why & WRB & ok & No violation.
OK & 1\\
\hline
4286646 & dddf836 &  &  & gemma2:9b & sentence: Why did you do that?
word: Why & WDT 
 & ok & No violation.
OK & 1\\
\hline
4286646 & dddf836 &  &  & qwen2.5:3b & sentence: Why did you do that?
word: Why & WDT & ok & No violation.
OK & 1\\
\hline
4286646 & dddf836 &  &  & llama3.2:1b & sentence: Why did you do that?
word: Why & * Sentence: why (Why is the first word.  CantAnswer because there can't be tagged with WDT)
* Word: Why 
   * Tag: Why (WDT) & err & The chatbot's output includes extra information such as the sentence and explanations, whereas the instructions specify to return only the part of speech tag.
ERR & 1\\
\hline
9577fa9 & dddf836 &  &  & gpt-4o-mini & sentence: They moved to a new city last year.
word: moved & VBD & ok & No violation.
OK & 1\\
\hline
9577fa9 & dddf836 &  &  & gemma2:9b & sentence: They moved to a new city last year.
word: moved & VBD 
 & ok & No violation.
OK & 1\\
\hline
9577fa9 & dddf836 &  &  & qwen2.5:3b & sentence: They moved to a new city last year.
word: moved & VB & ok & No violation.
OK & 1\\
\hline
9577fa9 & dddf836 &  &  & llama3.2:1b & sentence: They moved to a new city last year.
word: moved & Tag: VB
Reason: The word "moved" is a base form verb. & err & The chatbot output includes additional information ("Reason: The word 'moved' is a base form verb.") beyond the required part of speech tag. According to the description, the chatbot should return only the part of speech tag without any explanations or reasons.

ERR & 1\\
\hline
585e126 & dddf836 &  &  & gpt-4o-mini & sentence: On the table lies a mysterious box.
word: lies & VBZ & ok & The output 'VBZ' is included in the list of valid part-of-speech tags provided in the description.
OK & 1\\
\hline
585e126 & dddf836 &  &  & gemma2:9b & sentence: On the table lies a mysterious box.
word: lies & VBD 
 & ok & The chatbot's output is "VBD," which is one of the valid part-of-speech tags listed in the description. The output consists solely of the tag without any additional text or formatting, adhering to the instruction to return only the part of speech tag.

OK & 1\\
\hline
585e126 & dddf836 &  &  & qwen2.5:3b & sentence: On the table lies a mysterious box.
word: lies & VBZ & ok & OK & 1\\
\hline
585e126 & dddf836 &  &  & llama3.2:1b & sentence: On the table lies a mysterious box.
word: lies & Tagged word: CC (Coordinating conjunction)
 
Tagged word: ADJ (Adjective) & err & The chatbot's output includes additional descriptive text ("Tagged word:" and the explanation in parentheses) instead of returning only the part of speech tag as specified. Additionally, the tag "ADJ" is not among the listed tags in the description, which requires returning "Unknown" for unlisted tags.

ERR & 1\\
\hline
feb31ac & dddf836 &  &  & gpt-4o-mini & sentence: The movie was exceptionally good.
word: exceptionally & RB & ok & The chatbot's output is "RB", which is a valid part-of-speech tag from the provided list. The output is solely the tag without any additional information, adhering to the instruction to return only the part-of-speech tag.

OK & 1\\
\hline
feb31ac & dddf836 &  &  & gemma2:9b & sentence: The movie was exceptionally good.
word: exceptionally & RB 
 & err & The chatbot's response includes additional text ("Chatbot Output: ") before the part-of-speech tag, whereas the description specifies that only the part-of-speech tag should be returned without any extra information.

ERR & 1\\
\hline
feb31ac & dddf836 &  &  & qwen2.5:3b & sentence: The movie was exceptionally good.
word: exceptionally & JJR & ok & No violation.
OK & 1\\
\hline
feb31ac & dddf836 &  &  & llama3.2:1b & sentence: The movie was exceptionally good.
word: exceptionally & Word: exceptionally
Tag: JJR

Word: exceptionally
Tag: comparative & err & The chatbot's output includes additional labels ("Word:" and "Tag:") and provides more information than just the part of speech tag as specified in the description.

ERR & 1\\
\hline
d97d20a & dddf836 &  &  & gpt-4o-mini & sentence: Break a leg in your performance tonight!
word: Break & VB & ok & The chatbot's output "VB" is a valid part-of-speech tag from the provided list and adheres to the instruction to return only the tag.
OK & 1\\
\hline
d97d20a & dddf836 &  &  & gemma2:9b & sentence: Break a leg in your performance tonight!
word: Break & VB 
 & ok & The chatbot's output "VB" is one of the valid part-of-speech tags listed in the description and adheres to the requirement of returning only the tag.
OK & 1\\
\hline
d97d20a & dddf836 &  &  & qwen2.5:3b & sentence: Break a leg in your performance tonight!
word: Break & VB & ok & No violation.
OK & 1\\
\hline
d97d20a & dddf836 &  &  & llama3.2:1b & sentence: Break a leg in your performance tonight!
word: Break & * Break: NNS (Noun, plural)
* Break: VBD (Verb, past tense) & err & The chatbot's output includes the word and its explanation alongside the part of speech tags, whereas the description specifies that only the part of speech tag should be returned.

ERR & 1
  \end{tabular}
  \caption{Test results and compliance}
  
  \end{table}
  